### 2017-10-28 paper.tex
First commit

%% Version 4.3.2, 25 August 2014
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Template.tex --  LaTeX-based template for submissions to the 
% American Meteorological Society
%
% Template developed by Amy Hendrickson, 2013, TeXnology Inc., 
% amyh@texnology.com, http://www.texnology.com
% following earlier work by Brian Papa, American Meteorological Society
%
% Email questions to latex@ametsoc.org.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PREAMBLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% Start with one of the following:
% DOUBLE-SPACED VERSION FOR SUBMISSION TO THE AMS
\documentclass{ametsoc}

% TWO-COLUMN JOURNAL PAGE LAYOUT---FOR AUTHOR USE ONLY
% \documentclass[twocol]{ametsoc}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% To be entered only if twocol option is used

\journal{jamc}

%  Please choose a journal abbreviation to use above from the following list:
% 
%   jamc     (Journal of Applied Meteorology and Climatology)
%   jtech     (Journal of Atmospheric and Oceanic Technology)
%   jhm      (Journal of Hydrometeorology)
%   jpo     (Journal of Physical Oceanography)
%   jas      (Journal of Atmospheric Sciences)	
%   jcli      (Journal of Climate)
%   mwr      (Monthly Weather Review)
%   wcas      (Weather, Climate, and Society)
%   waf       (Weather and Forecasting)
%   bams (Bulletin of the American Meteorological Society)
%   ei    (Earth Interactions)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Citations should be of the form ``author year''  not ``author, year''
\bibpunct{(}{)}{;}{a}{}{,}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% To be entered by author:

%% May use \\ to break lines in title:

\title{Tropopause Evolution in a Rapidly Intensifying Tropical Cyclone: A Static Stability Budget Analysis}

%%% Enter authors' names, as you see in this example:
%%% Use \correspondingauthor{} and \thanks{Current Affiliation:...}
%%% immediately following the appropriate author.
%%%
%%% Note that the \correspondingauthor{} command is NECESSARY.
%%% The \thanks{} commands are OPTIONAL.

    %\authors{Author One\correspondingauthor{Author One, 
    % American Meteorological Society, 
    % 45 Beacon St., Boston, MA 02108.}
% and Author Two\thanks{Current affiliation: American Meteorological Society, 
    % 45 Beacon St., Boston, MA 02108.}}

\authors{Patrick Duran\correspondingauthor{Department of Atmospheric and Environmental Sciences, University at Albany, State University of New York, 1400 Washington Avenue, Albany, NY.}}

%% Follow this form:
    % \affiliation{American Meteorological Society, 
    % Boston, Massachusetts.}

\affiliation{University at Albany, State University of New York,
Albany, NY}

%% Follow this form:
    %\email{latex@ametsoc.org}

\email{pduran2008@gmail.com}

%% If appropriate, add additional authors, different affiliations:
    %\extraauthor{Extra Author}
    %\extraaffil{Affiliation, City, State/Province, Country}

\extraauthor{John Molinari}
%\extraaffil{}

%% May repeat for a additional authors/affiliations:

%\extraauthor{}
%\extraaffil{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ABSTRACT
%
% Enter your abstract here
% Abstracts should not exceed 250 words in length!
%
% For BAMS authors only: If your article requires a Capsule Summary, please place the capsule text at the end of your abstract
% and identify it as the capsule. Example: This is the end of the abstract. (Capsule Summary) This is the capsule summary.

\abstract{Enter the text of your abstract here.}

\begin{document}

%% Necessary!
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% MAIN BODY OF PAPER
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%

%% In all cases, if there is only one entry of this type within
%% the higher level heading, use the star form: 
%%
% \section{Section title}
% \subsection*{subsection}
% text...
% \section{Section title}

%vs

% \section{Section title}
% \subsection{subsection one}
% text...
% \subsection{subsection two}
% \section{Section title}

%%%
% \section{First primary heading}

% \subsection{First secondary heading}

% \subsubsection{First tertiary heading}

% \paragraph{First quaternary heading}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ACKNOWLEDGMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\acknowledgments
Start acknowledgments here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% APPENDIXES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Use \appendix if there is only one appendix.
%\appendix

% Use \appendix[A], \appendix}[B], if you have multiple appendixes.
%\appendix[A]

%% Appendix title is necessary! For appendix title:
%\appendixtitle{}

%%% Appendix section numbering (note, skip \section and begin with \subsection)
% \subsection{First primary heading}

% \subsubsection{First secondary heading}

% \paragraph{First tertiary heading}

%% Important!
%\appendcaption{<appendix letter and number>}{<caption>} 
%must be used for figures and tables in appendixes, e.g.,
%
%\begin{figure}
%\noindent\includegraphics[width=19pc,angle=0]{figure01.pdf}\\
%\appendcaption{A1}{Caption here.}
%\end{figure}
%
% All appendix figures/tables should be placed in order AFTER the main figures/tables, i.e., tables, appendix tables, figures, appendix figures.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% REFERENCES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Make your BibTeX bibliography by using these commands:
% \bibliographystyle{ametsoc2014}
% \bibliography{references}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TABLES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Enter tables at the end of the document, before figures.
%%
%
%\begin{table}[t]
%\caption{This is a sample table caption and table layout.  Enter as many tables as
%  necessary at the end of your manuscript. Table from Lorenz (1963).}\label{t1}
%\begin{center}
%\begin{tabular}{ccccrrcrc}
%\hline\hline
%$N$ & $X$ & $Y$ & $Z$\\
%\hline
% 0000 & 0000 & 0010 & 0000 \\
% 0005 & 0004 & 0012 & 0000 \\
% 0010 & 0009 & 0020 & 0000 \\
% 0015 & 0016 & 0036 & 0002 \\
% 0020 & 0030 & 0066 & 0007 \\
% 0025 & 0054 & 0115 & 0024 \\
%\hline
%\end{tabular}
%\end{center}
%\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% FIGURES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Enter figures at the end of the document, after tables.
%%
%
%\begin{figure}[t]
%  \noindent\includegraphics[width=19pc,angle=0]{figure01.pdf}\\
%  \caption{Enter the caption for your figure here.  Repeat as
%  necessary for each of your figures. Figure from \protect\cite{Knutti2008}.}\label{f1}
%\end{figure}

\end{document}

### 2017-11-15 paper.tex
A few minor modifications

@@
 
-\journal{jamc}
+\journal{jas}
 
@@
 
-\authors{Patrick Duran\correspondingauthor{Department of Atmospheric and Environmental Sciences, University at Albany, State University of New York, 1400 Washington Avenue, Albany, NY.}}
+\authors{Patrick Duran\correspondingauthor{Department of Atmospheric and Environmental Sciences, University at Albany, State University of New York, 1400 Washington Avenue, Albany, NY.} and John Molinari}
 
@@
 
-\extraauthor{John Molinari}
+%\extraauthor{}
 %\extraaffil{}
@@
 %
+
+To assess how well the budget captures the observed static stability variability, 24-hour changes in static stability are computed at every grid point in the domain shown in Fig.
+2 and compared to the changes indicated by the budget equation.
+Probability density functions (PDFs) of the absolute value of these static stability changes are plotted in Fig. 3 for each of the first four days of the simulation.
+The PDFs of the budget changes over these 24-hour periods (Fig. 3, orange lines) closely follow those of the model changes (Fig. 3a, red lines). 
+Meanwhile, the vast majority of grid points in the region exhibit residuals near zero (Fig. 3a, blue lines).
+The similarity between the PDFs of the model and budget changes, together with the near-zero residual values, indicates that the budget performs well in the tropopause layer, and can be used to assess the changes in static stability during these time periods.
 

### 2017-11-15 paper.tex
Removed text describing PDFs of budget terms. Will use averages of absolute values instead.

--- 2017-10-28 paper.tex
@@
 %%
-% \section{Section title}
+ \section{Introduction}
+
+ \section{Model Setup}
+
+ \section{Results}
+
 % \subsection*{subsection}

### 2017-11-15 paper.tex
Added Figs. 1-4 and Results text for Figs. 1-3 and part of Fig. 4.

@@
 
+Put description of Fig.~\ref{fig:vmax+pmin} in this section.
+Don't forget to mention 1-2-1 smoother.
+
+ \section{Budget Computation}
+
  \section{Results}
 
-% \subsection*{subsection}
+ \subsection{Static stability evolution}
+
+The simulated static stability evolution closely follows that observed in Hurricane Patricia (2015; \citeauthor{Duran+Molinari2018} \citeyear{Duran+Molinari2018}).
+The average N\textsuperscript{2} over the first day of the simulation (Fig.~\ref{fig:n2-24hr-avgs}a) indicates the presence of a static stability maximum about 400 m above the cold-point tropopause.
+This lower-stratospheric stable layer had begun to erode during the initial spin-up period, with the maximum destabilitzation occurring at the innermost radii.
+This decrease in static stability continued into the second day of the simulation (Fig.~\ref{fig:n2-24hr-avgs}b) as the storm intensified to hurricane strength (Fig.~\ref{fig:vmax+pmin}).
+Destabilization was particularly pronounced over the developing eye, where the time-mean cold-point tropopause height increased by up to 400 m compared to the previous day.
+Over the developing eyewall and outer rainband regions, meanwhile, the time-mean tropopause height remained nearly constant.
+During the third day of the simulation (Fig.~\ref{fig:n2-24hr-avgs}c), static stability over the eye region continued to decrease, and the cold-point tropopause height rose to 18.3 km at the storm center.
+The tropopause sloped sharply downward over the innermost radii, reaching the 16.4-km level near the 50-km radius.
+This local minimum in tropopause height corresponded to the eyewall region, where upper-tropospheric static stability increased during this time period.
+Outside of the eyewall region, static stability began to increase in the layer immediately overlying the cold-point tropopause.
+This stable layer sloped upward with radius, which corresponded to an upward-sloping tropopause radially outside of the eywall region.
+Over the next 24 hours (Fig.~\ref{fig:n2-24hr-avgs}d), as the storm's maximum 10-m wind speed leveled off near 80 m s\textsuperscript{-1} (Fig.~\ref{fig:vmax+pmin}), the upper-tropospheric static stability within the eyewall region continued to strengthen, along with the static stability within the lower stratosphere radially outside of the eyewall.
+As the stable layer strengthened, its altitude rose slightly, which corresponded to a slight increase in tropopause height outside of the eyewall during this period.
+Within the upper troposphere radially outside of the eyewall, meanwhile, static stability decreased such that it was nearly neutral in a thin layer between the 120- and 150-km radii.
+The eye region likewise continued to destabilize, and the cold-point tropopause height increased to a level above 18.5 km.
+
+ \subsection{Potential temperature budget analysis}
+
+% \subsubsection{Budget performance}
+
+The left column of Fig.~\ref{fig:modbudres} depicts 24-hour changes in N\textsuperscript{2} over each of the four days of the simulation. 
+These represent bulk changes computed by subtracting the instantaneous N\textsuperscript{2} at the initial time from the instantaneous N\textsuperscript{2} at the final time. 
+The middle column of Fig.~\ref{fig:modbudres} represents the change in N\textsuperscript{2} computed using Eq. XXX and the process described in Section 3. 
+The residual between these two computations (Fig.~\ref{fig:modbudres}, right column) is much smaller than the change in N\textsuperscript{2}, meaning that the budget peforms well within the analysis domain.
+
 % text...
@@
 %
-%\begin{figure}
-%\noindent\includegraphics[width=19pc,angle=0]{figure01.pdf}\\
-%\appendcaption{A1}{Caption here.}
-%\end{figure}
+
 %
@@
 % Make your BibTeX bibliography by using these commands:
-% \bibliographystyle{ametsoc2014}
-% \bibliography{references}
+ \bibliographystyle{ametsoc2014}
+ \bibliography{references}
 
@@
 %
+
+%FIGURE 1%
+\begin{figure}[ht]
+\centerline{\includegraphics[width=19pc]{figures/fig01_vmax+pmin.png}}
+\caption{The maximum 10-m wind speed (top panel; m s\textsuperscript{-2}) and minimum sea-level pressure (bottom panel; hPa) in the simulated storm (blue lines) and from Hurricane Patricia's best track (red stars).}
+\label{fig:vmax+pmin}
+\end{figure}
+
+%FIGURE 2%
+\begin{figure*}[ht]
+\centerline{\includegraphics[width=39pc]{figures/fig02_n2-24hr-avgs.png}}
+\caption{Twenty-four-hour averages of squared Brunt-V{\"a}is{\"a}l{\"a} frequency (10\textsuperscript{-4} s\textsuperscript{-2}) over the first four days of the simulation.
+Orange lines represent the cold-point tropopause computed from the mean temperature field over the same time periods.}
+\label{fig:n2-24hr-avgs}
+\end{figure*}
+
+%FIGURE 3%
+\begin{figure*}[ht]
+\centerline{\includegraphics[width=39pc]{figures/fig03_R-Z_mod+bud+res.png}}
+\caption{Left panels: Twenty-four-hour changes in squared Brunt-V{\"a}is{\"a}l{\"a} frequency (10\textsuperscript{-4} s\textsuperscript{-2}) over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, (d) 72-96 hours.
+Middle Panels: The N\textsuperscript{2} change over the same time periods computed using Eq.
+XXX.
+Right Panels: The budget residual over the same time periods, computed by subtracting the budget change (middle column) from the model change (left column).}
+\label{fig:modbudres}
+\end{figure*}
+
+%FIGURE 4%
+\begin{figure}[ht]
+\centerline{\includegraphics[width=19pc]{figures/fig04_AVG_budterms.png}}
+\caption{Time series of the contribution of each of the budget terms to the squared Brunt-V{\"a}is{\"a}l{\"a} frequency (10\textsuperscript{-4} s\textsuperscript{-2}) tendency.
+For each budget term, the absolute value of the N\textsuperscript{2} tendency is averaged both temporally and spatially over 1-hour periods, using output every minute, and within the radius-height domain depicted in Fig.~\ref{fig:modbudres}.}
+\label{fig:modbudres}
+\end{figure*}
+
 %\begin{figure}[t]

### 2017-11-16 paper.tex
Added some results text for Fig. 4.

@@
 
+There will be a whole bunch of papers cited here...
+
  \section{Model Setup}
@@
 Put description of Fig.~\ref{fig:vmax+pmin} in this section.
+
 Don't forget to mention 1-2-1 smoother.
@@
  \section{Budget Computation}
+
+Add details of budget computation here...
 
@@
 
-The simulated static stability evolution closely follows that observed in Hurricane Patricia (2015; \citeauthor{Duran+Molinari2018} \citeyear{Duran+Molinari2018}).
 The average N\textsuperscript{2} over the first day of the simulation (Fig.~\ref{fig:n2-24hr-avgs}a) indicates the presence of a static stability maximum about 400 m above the cold-point tropopause.
@@
 Destabilization was particularly pronounced over the developing eye, where the time-mean cold-point tropopause height increased by up to 400 m compared to the previous day.
-Over the developing eyewall and outer rainband regions, meanwhile, the time-mean tropopause height remained nearly constant.
-During the third day of the simulation (Fig.~\ref{fig:n2-24hr-avgs}c), static stability over the eye region continued to decrease, and the cold-point tropopause height rose to 18.3 km at the storm center.
+Over the developing eyewall and outer rainband regions, meanwhile, the tropopause height remained nearly constant.
+During the third day of the simulation (Fig.~\ref{fig:n2-24hr-avgs}c), static stability over the eye continued to decrease, and the cold-point tropopause height rose to 18.3 km at the storm center.
 The tropopause sloped sharply downward over the innermost radii, reaching the 16.4-km level near the 50-km radius.
@@
 The eye region likewise continued to destabilize, and the cold-point tropopause height increased to a level above 18.5 km.
+This static stability evolution closely follows that observed in Hurricane Patricia (2015; \citeauthor{Duran+Molinari2018} \citeyear{Duran+Molinari2018}).
 
- \subsection{Potential temperature budget analysis}
-
-% \subsubsection{Budget performance}
+ \subsection{Static stability budget analysis}
 
@@
 These represent bulk changes computed by subtracting the instantaneous N\textsuperscript{2} at the initial time from the instantaneous N\textsuperscript{2} at the final time. 
-The middle column of Fig.~\ref{fig:modbudres} represents the change in N\textsuperscript{2} computed using Eq. XXX and the process described in Section 3. 
+The middle column of Fig.~\ref{fig:modbudres} represents the change in N\textsuperscript{2} computed using Eq. XXX and the method described in Section 3. 
 The residual between these two computations (Fig.~\ref{fig:modbudres}, right column) is much smaller than the change in N\textsuperscript{2}, meaning that the budget peforms well within the analysis domain.
+
+A time series of the contribution of each of the budget terms in Eq. XXX to the tropopause-layer static stability tendency (Fig.\ref{fig:avgbudterms}) reveals that three terms dominate the budget.
+For this figure, each of the budget terms are computed using the method described in Section 3, except using 1-hour averaging intervals instead of 24-hour intervals.
+The absolute values of these tendencies are then averaged over the radius-height domain depicted in Fig.~\ref{fig:modbudres} and plotted as a time series\footnote{It will be seeen in subsequent figures that each of the terms contributes both positively and negatively to the N\textsuperscript{2} tendency within the analysis domain.
+Thus, taking an average over the domain tends to wash out the positive and negative contributions.
+To circumvent this problem, the absolute value of each of the terms is averaged, yielding a time series of the mean magnitude of each budget term.}.
 
@@
 \centerline{\includegraphics[width=19pc]{figures/fig04_AVG_budterms.png}}
-\caption{Time series of the contribution of each of the budget terms to the squared Brunt-V{\"a}is{\"a}l{\"a} frequency (10\textsuperscript{-4} s\textsuperscript{-2}) tendency.
-For each budget term, the absolute value of the N\textsuperscript{2} tendency is averaged both temporally and spatially over 1-hour periods, using output every minute, and within the radius-height domain depicted in Fig.~\ref{fig:modbudres}.}
-\label{fig:modbudres}
+\caption{Time series of the contribution of each of the budget terms to the time tendency of the squared Brunt-V{\"a}is{\"a}l{\"a} frequency (N\textsuperscript{2}; 10\textsuperscript{-4} s\textsuperscript{-2}).
+For each budget term, the absolute value of the N\textsuperscript{2} tendency is averaged both temporally over 1-hour periods (using output every minute), and spatially within the radius-height domain depicted in Fig.~\ref{fig:modbudres}.}
+\label{fig:avgbudterms}
 \end{figure*}

### 2017-11-16 paper.tex
Added to and revised Results for Fig. 4. Added Figs. 5-8 with no captions.

@@
 
-A time series of the contribution of each of the budget terms in Eq. XXX to the tropopause-layer static stability tendency (Fig.\ref{fig:avgbudterms}) reveals that three terms dominate the budget.
-For this figure, each of the budget terms are computed using the method described in Section 3, except using 1-hour averaging intervals instead of 24-hour intervals.
+To determine which of the budget terms are most important, a time series of the contribution of each of the budget terms in Eq.
+XXX to the tropopause-layer static stability tendency is plotted in Fig.
+\ref{fig:avgbudterms}.
+For this figure, each of the budget terms is computed using the method described in Section 3, except with 1-hour averaging intervals instead of 24-hour intervals.
 The absolute values of these tendencies are then averaged over the radius-height domain depicted in Fig.~\ref{fig:modbudres} and plotted as a time series\footnote{It will be seeen in subsequent figures that each of the terms contributes both positively and negatively to the N\textsuperscript{2} tendency within the analysis domain.
@@
 To circumvent this problem, the absolute value of each of the terms is averaged, yielding a time series of the mean magnitude of each budget term.}. 
+Advection (Fig.~\ref{fig:avgbudterms}, red line) plays an important role in the mean tropopause-layer static stability tendency at all times, and vertical turbulence (Fig.~\ref{fig:avgbudterms}, blue line) and radiation (Fig.~\ref{fig:avgbudterms}, dark green line) both become important after 48 hours.
+Although the contribution from horizontal turbulence (Fig.~\ref{fig:avgbudterms}, purple line) becomes more important after 72 hours, it is confined to a very small region immediately surrounding the eyewall tangential velocity maximum (not shown), and is negligible throughout the rest of the tropopause layer.
+The remaining two processes - microphysics and dissipative heating (Fig.~\ref{fig:avgbudterms}, orange and light green lines, respectively) - lie atop one another near zero.
+These time series indicate that, at all times, three budget terms dominate the tropopause-layer static stability tendency: advection, vertical turbulence, and radiation.
+Variations in the magnitude and spatial structure of these terms drive the static stability changes depicted in Fig.~\ref{fig:n2-24hr-avgs}; subsequent sections will focus on these variations and what causes them.
+
+\paragraph{0-24 hours}
+\paragraph{24-48 hours}
+\paragraph{48-72 hours}
+\paragraph{72-96 hours}
 
@@
 \label{fig:avgbudterms}
+\end{figure}
+
+%FIGURE 5%
+\begin{figure*}[ht]
+\centerline{\includegraphics[width=39pc]{figures/fig05_h000-h024-budgetterms.png}}
+\caption{}
+\label{fig:00-24}
+\end{figure*}
+
+%FIGURE 6%
+\begin{figure*}[ht]
+\centerline{\includegraphics[width=39pc]{figures/fig06_h024-h048-budgetterms.png}}
+\caption{}
+\label{fig:24-48}
+\end{figure*}
+
+%FIGURE 7%
+\begin{figure*}[ht]
+\centerline{\includegraphics[width=39pc]{figures/fig07_h048-h072-budgetterms.png}}
+\caption{}
+\label{fig:48-72}
+\end{figure*}
+
+%FIGURE 8%
+\begin{figure*}[ht]
+\centerline{\includegraphics[width=39pc]{figures/fig08_h072-h096-budgetterms.png}}
+\caption{}
+\label{fig:72-96}
 \end{figure*}

### 2017-11-19 paper.tex
Added captions for Figs. 5-8.

@@
 
-\abstract{Enter the text of your abstract here.}
+\abstract{We have some cool results!}
 
@@
 \centerline{\includegraphics[width=39pc]{figures/fig05_h000-h024-budgetterms.png}}
-\caption{}
-\label{fig:00-24}
+\caption{(a) Total change in N\textsuperscript{2} over the 0-24-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 hr)\textsuperscript{-1}) and the contributions to that change from (b) the sum of horizontal and vertical advection, (c) vertical turbulence, and (d) the sum of longwave and shortwave radiation.}
+\label{fig:stab-00-24}
 \end{figure*}
@@
 \centerline{\includegraphics[width=39pc]{figures/fig06_h024-h048-budgetterms.png}}
-\caption{}
-\label{fig:24-48}
+\caption{As in Fig.~\ref{fig:stab-00-24}, but for the 24-48-hour period.}
+\label{fig:stab-24-48}
 \end{figure*}
@@
 \begin{figure*}[ht]
-\centerline{\includegraphics[width=39pc]{figures/fig07_h048-h072-budgetterms.png}}
-\caption{}
-\label{fig:48-72}
+\centerline{\includegraphics[width=33pc]{figures/fig07_h048-h072-budgetterms.png}}
+\caption{(a) Total change in N\textsuperscript{2} over the 48-72-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 hr)\textsuperscript{-1}) and the contributions to that change from (b) the sum of horizontal and vertical advection, (c) vertical turbulence, (d) the sum of longwave and shortwave radiation, (e) the sum of horizontal advection, vertical advection, and vertical turublence, and (f) the sum of horizontal advection, vertical advection, vertical turbulence, and longwave and shortwave radiation.}
+\label{fig:stab-48-72}
 \end{figure*}
@@
 \begin{figure*}[ht]
-\centerline{\includegraphics[width=39pc]{figures/fig08_h072-h096-budgetterms.png}}
-\caption{}
-\label{fig:72-96}
+\centerline{\includegraphics[width=33pc]{figures/fig08_h072-h096-budgetterms.png}}
+\caption{As in Fig.~\ref{fig:stab-48-72}, but for the 72-96-hour period.}
+\label{fig:stab-72-96}
 \end{figure*}

### 2017-11-21 paper.tex
Added Figs. 9-11 and captions. Added Results texts for Figs. 5-7.

@@
 This stable layer sloped upward with radius, which corresponded to an upward-sloping tropopause radially outside of the eywall region.
-Over the next 24 hours (Fig.~\ref{fig:n2-24hr-avgs}d), as the storm's maximum 10-m wind speed leveled off near 80 m s\textsuperscript{-1} (Fig.~\ref{fig:vmax+pmin}), the upper-tropospheric static stability within the eyewall region continued to strengthen, along with the static stability within the lower stratosphere radially outside of the eyewall.
+Over the next 24 hours (Fig.~\ref{fig:n2-24hr-avgs}d), as the storm's maximum 10-m wind speed leveled off near 80 m s\textsuperscript{-1} (Fig.~\ref{fig:vmax+pmin}), the upper-tropospheric static stability within the eyewall region continued to strengthen, as did the static stability just above the cold-point tropopause radially outside of the eyewall.
 As the stable layer strengthened, its altitude rose slightly, which corresponded to a slight increase in tropopause height outside of the eyewall during this period.
@@
 \paragraph{0-24 hours}
+The first 24 hours of the simulation was characterized by a weakening of the lower-stratospheric static stability maximum above 17 km (Fig.~\ref{fig:stab-0-24}a, purple shading) and an increase in static stability below (green shading).
+Although these tendencies extended out to the 200-km radius, they were particularly pronounced at innermost radii.
+A comparison of the contributions of advection (Fig.~\ref{fig:stab-0-24}b), vertical turbulence (Fig.~\ref{fig:stab-0-24}c), and radiation (Fig.~\ref{fig:stab-0-24}d) reveals that advection is primarily responsible for the change in static stability during this period.
+...Explain this in the context of radial and vertical velocities...
+
 \paragraph{24-48 hours}
+During the second day of the simulation, the lower-stratospheric stable layer continued to weaken (Fig.~\ref{fig:stab-24-48}a).
+This weakening trend in the 16.75-17.75-km layer extended from the 50 km radius outward to past 200 km, and was primarily driven by advection (Fig.~\ref{fig:stab-24-48}b).
+Below this layer, static stability began to increse slightly.
+This stabilization had contributions from both vertical turbulence (Fig.~\ref{fig:stab-24-48}c) and radiation (Fig.~\ref{fig:stab-24-48}d) in the 16-16.5-km layer.
+...Explain this in context of mean vertical mixing coefficient and mean radiative heating tendency...
+Meanwhile, radially inward of 60 km, static stability below 17.5 km continued to weaken, primarily due to advective processes.
+
 \paragraph{48-72 hours}
+The third day of the simulation marked a dramatic change in the structure of the tropopause-layer static stability tendencies.
+During this time, static stability increased markedly in an upward-sloping region within the 30-60-km radial band (Fig.~\ref{fig:stab-48-72}a), and also increased within the 16.75-17.5-km layer out to at least the 200-km radius.
+As this layer stabilized, the layer immediately below it destabilized in a broad region extending from 60-200 km.
+Examination of the contribution from total advection (Fig.~\ref{fig:stab-48-72}b) reveals that advection no longer dominates the static stability tendencies.
+Instead, a combination of vertical turbulence (Fig.~\ref{fig:stab-48-72}c) and radiation (Fig.~\ref{fig:stab-48-72}d) overcomes the destabilizing influence of advection to create the layer of increasing static stability.
+Meanwhile, the destabilizing influence of vertical turbulence in a broad region below 17 km combines with a small region of destabilization due to radiation in the 50-120-km radial band combine to destabilize the layer below 16.5 km in the 50-200-km radial band.
+Comparing the sum of advection and vertical turbulence (Fig.~\ref{fig:stab-48-72}e) to the sum of advection, vertical turbulence, and radiation (Fig.~\ref{fig:stab-48-72}f) reveals that radiation plays a fundamental role in the re-strengthening of the lower-stratospheric stable layer during this time.
+
 \paragraph{72-96 hours}
@@
 \begin{figure*}[ht]
-\centerline{\includegraphics[width=39pc]{figures/fig03_R-Z_mod+bud+res.png}}
+\centerline{\includegraphics[width=33pc]{figures/fig03_R-Z_mod+bud+res.png}}
 \caption{Left panels: Twenty-four-hour changes in squared Brunt-V{\"a}is{\"a}l{\"a} frequency (10\textsuperscript{-4} s\textsuperscript{-2}) over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, (d) 72-96 hours.
@@
 
+%FIGURE 9%
+\begin{figure*}[ht]
+\centerline{\includegraphics[width=39pc]{figures/fig09_u.png}}
+\caption{Radial velocity (m s\textsuperscript{-1}; filled contours), potential temperature (K; thick black contours), and cold point tropopause height (orange line) averaged over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, and (d) 72-96 hours.}
+\label{fig:u}
+\end{figure*}
+
+%FIGURE 10%
+\begin{figure*}[ht]
+\centerline{\includegraphics[width=39pc]{figures/fig10_w.png}}
+\caption{Vertical velocity (cm s\textsuperscript{-1}; filled contours), potential temperature (K; thick black contours), and cold point tropopause height (orange line) averaged over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, and (d) 72-96 hours.}
+\label{fig:w}
+\end{figure*}
+
+%FIGURE 11%
+\begin{figure*}[ht]
+\centerline{\includegraphics[width=39pc]{figures/fig11_qtot.png}}
+\caption{Total condensate mixing ratio (g kg\textsuperscript{-1}) and cold point tropopause height (orange line) averaged over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, and (d) 72-96 hours.}
+\label{fig:qtot}
+\end{figure*}
+
 %\begin{figure}[t]

### 2017-11-27 paper.tex
Added Model Setup section, along with a number of citations

@@
 
-Put description of Fig.~\ref{fig:vmax+pmin} in this section.
-
-Don't forget to mention 1-2-1 smoother.
+The numerical simulations were performed using version 19.4 of Cloud Model 1 (CM1) described in \cite{BryanRotunno2009} and available online at http://www2.mmm.ucar.edu/people/bryan/cm1/.
+The fully-compressible equations of motion were integrated on a 3000-km-wide, 35-km-deep, axisymmetric grid with 1-km horizontal and 250-m vertical grid spacing.
+Horizontal turbulence was parameterized using a Smagorinsky scheme described in \citeauthor{BryanRotunno2009} (\citeyear{BryanRotunno2009}, their Eq.
+17), with a prescribed mixing length that varied linearly from 100 m at a surface pressure of 1015 hPa to 1000 m at a surface pressure of 900 hPa.
+This formulation allows for realistically-large horizontal mixing lengths near the hurricane's inner core, consistent with the results of \cite{Bryan2012}, while not over-representing horizontal turbulence in convection at outer radii.
+Vertical turbulence was parameterized using the formulation of \citeauthor{MarkowskiBryan2016} (\citeyear{MarkowskiBryan2016}, their Eq. 6), using an asymptotic vertical mixing length of 100 m.
+A Rayleigh damping layer was applied outside of the 2900-km radius and above the 25-km level to prevent spurious gravity wave reflection at the model boundaries.
+Microphysical processes were parameterized using the \cite{Thompson} microphysics scheme and radiative heating tendencies were computed every two minutes using the RRTMG longwave and shortwave schemes \citep{Iacono}.
+A horizontally-homogeneous temperature and humidity field was initialized with a mean sounding computed using all dropsondes deployed during the TCI flight conducted within and around Tropical Storm Patricia on 21 October, 2015 (see \citeauthor{DoyleTCI} \citeyear{DoyleTCI} for details.)
+Above 19 km, where few TCI observations were available, the temperature profile was assumed to be isothermal.
+Since relative humidity measurements were unreliable at temperatures below -40\textdegree C \citep{BellTCI}, the water vapor mixing ratio was set to zero above 16 km.
 
@@
  \section{Results}
+
+Put description of Fig.~\ref{fig:vmax+pmin} in this section.
+
+Don't forget to mention 1-2-1 smoother.
 

### 2017-11-28 paper.tex
Began the Budget Computation section, including the addition of the unsaturated N^2 equation.

@@
 Since relative humidity measurements were unreliable at temperatures below -40\textdegree C \citep{BellTCI}, the water vapor mixing ratio was set to zero above 16 km.
+The vortex described in \citeauthor{RotunnoEmanuel} (\citeyear{RotunnoEmanuel}, their Eq. 37) was used to initialize the wind field, setting all parameters equal to the values used therein.
 
@@
 
-Add details of budget computation here...
+The static stability can be expressed as the squared Brunt V{\"a}is{\"a}l{\"a} frequency:
+   \begin{equation} \label{eq:n2moist}
+   EQ. 18 OF BRYAN AND ROTUNNO. ALSO USE EQ. 19
+   \end{equation}
+In the tropopause layer, $q_s$, $\frac{\partial q_s}{\partial T}$, and $\frac{\partial q_t}{\partial z}$ approach zero; thus, Eq. \ref{eq:n2moist} reduces to:
+   \begin{equation} \label{eq:n2dry}
+   N^2 = \frac{g}{\theta_v}\frac{\partial \theta_v}{\partial z},
+   \end{equation}
+where \textit{g} is gravitational acceleration and $\theta_v$ is the virtual potential temperature.
+To compute $N^2$, CM1 uses Eq. \ref{eq:n2moist} in saturated environments and Eq. \ref{eq:n2dry} in unsaturated environments.
+For mathematical simplicity, only Eq. \ref{eq:n2dry} will be used for the budget computations herein\footnote{The validity of this approximation will be substantiated later in tihs section.}.
+Taking the time derivative of Eq.\ref{eq:n2dry} yields the static stability tendency:
 

### 2017-11-29 paper.tex
A few minor changes throughout.

@@
 The fully-compressible equations of motion were integrated on a 3000-km-wide, 35-km-deep, axisymmetric grid with 1-km horizontal and 250-m vertical grid spacing.
-Horizontal turbulence was parameterized using a Smagorinsky scheme described in \citeauthor{BryanRotunno2009} (\citeyear{BryanRotunno2009}, their Eq.
-17), with a prescribed mixing length that varied linearly from 100 m at a surface pressure of 1015 hPa to 1000 m at a surface pressure of 900 hPa.
+Horizontal turbulence was parameterized using the Smagorinsky scheme described in \citeauthor{BryanRotunno2009} (\citeyear{BryanRotunno2009}, pg.
+1773), with a prescribed mixing length that varied linearly from 100 m at a surface pressure of 1015 hPa to 1000 m at a surface pressure of 900 hPa.
 This formulation allows for realistically-large horizontal mixing lengths near the hurricane's inner core, consistent with the results of \cite{Bryan2012}, while not over-representing horizontal turbulence in convection at outer radii.
@@
 Above 19 km, where few TCI observations were available, the temperature profile was assumed to be isothermal.
-Since relative humidity measurements were unreliable at temperatures below -40\textdegree C \citep{BellTCI}, the water vapor mixing ratio was set to zero above 16 km.
+Since relative humidity measurements were unreliable at temperatures below -40\textdegree C \citep{BellTCI}, relative humidity was set equal to 50\% above 11.5 km (the level above which temperature dropped below -40\textdegree C).
 The vortex described in \citeauthor{RotunnoEmanuel} (\citeyear{RotunnoEmanuel}, their Eq. 37) was used to initialize the wind field, setting all parameters equal to the values used therein.
@@
 To compute $N^2$, CM1 uses Eq. \ref{eq:n2moist} in saturated environments and Eq. \ref{eq:n2dry} in unsaturated environments.
-For mathematical simplicity, only Eq. \ref{eq:n2dry} will be used for the budget computations herein\footnote{The validity of this approximation will be substantiated later in tihs section.}.
+For mathematical simplicity, only Eq. \ref{eq:n2dry} will be used for the budget computations herein\footnote{The validity of this approximation will be substantiated later in this section.}.
 Taking the time derivative of Eq.\ref{eq:n2dry} yields the static stability tendency:
@@
 \acknowledgments
-Start acknowledgments here.
+George Bryan, Jeff Kepert, and Rob Fovell.
 

### 2017-12-06 paper.tex
Added a page of Introduction, some references, and some Acknowledgements

@@
 
+Perhaps introduce upper-tropospheric static stability and its relationship to the diurnal cycle before going into Patricia? Include references to Dunion, Navarro, and O'Neill here.
+
+After undergoing a remarkably rapid intensification (RI), Hurricane Patricia (2015) set a new record as the strongest tropical cyclone (TC) ever observed in the Western Hemisphere (\citeauthor{Kimberlainetal2016} \citeyear{Kimberlainetal2016}; \citeauthor{Rogersetal2017} \citeyear{Rogersetal2017}).
+High-altitude dropsonde observations taken by the Tropical Cyclone Intensity (TCI) Experiment captured this RI in unprecedented detail \citep{DoyleTCI}.
+These observations revealed remarkable changes in the structure of the cold-point tropopause and upper-level static stability as the storm intensified \citep{Duran+Molinari2018}.
+At tropical storm intensity, shortly before RI commenced, a strong inversion layer existed just above Patricia's cold-point tropopause, which was located near 17.2 km.
+During the first half of the RI period, this inversion layer weakened throughout Patricia's inner core, with the weakening most pronounced over the developing eye.
+By the time the storm reached its maximum intensity, the inversion layer over the eye had disappeared almost completely, which was accompanied by an increase in the tropopause height to a level at or above the highest-available dropsonde data point (18.3 km) at two locations.
+Meanwhile over the eyewall region, the static stability re-strengthened and the tropopause was limited to a level at or below 17.5 km.
+The mechanisms that led to these changes in upper-level static stability and tropopause height are the subject of the current paper.
+
+More recently, \cite{Dunionetal2014} documented a periodic oscillation of infrared brightness temperature in hurricanes, which they call the "TC diurnal pulse."
 There will be a whole bunch of papers cited here...
+
+At some point (probably in the Discussion) mention the possible importance of static stability asymmetries, in the context of the Dunion diurnal pulse
 
@@
 \acknowledgments
-George Bryan, Jeff Kepert, and Rob Fovell.
+We are indebted to Dr. George Bryan for his continued development and support of Cloud Model 1.
+We also thank Drs. Jeffrey Kepert, Robert Fovell, and Erika Navarro for fruitful conversations related to this work.
+ADD GRANT NUMBER
 

### 2017-12-07 paper.tex
Added to the Introduction and changed the wording in a few places. Revised Model Setup section and created Discussion section.

@@
 The numerical simulations were performed using version 19.4 of Cloud Model 1 (CM1) described in \cite{BryanRotunno2009} and available online at http://www2.mmm.ucar.edu/people/bryan/cm1/.
-The fully-compressible equations of motion were integrated on a 3000-km-wide, 35-km-deep, axisymmetric grid with 1-km horizontal and 250-m vertical grid spacing.
+The equations of motion were integrated on a 3000-km-wide, 30-km-deep grid axisymmetric grid with 1-km horizontal and 250-m vertical grid spacing.
+The computations were performed on an \textit{f}-plane at 15\textdegree{N} latitude, over a sea surface with constant temperature of 30.5\textdegree C, which matches that observed near Hurricane Patricia (2015; \citeauthor{Kimberlainetal2016} \citeyear{Kimberlainetal2016}.
 Horizontal turbulence was parameterized using the Smagorinsky scheme described in \citeauthor{BryanRotunno2009} (\citeyear{BryanRotunno2009}, pg.
@@
 A Rayleigh damping layer was applied outside of the 2900-km radius and above the 25-km level to prevent spurious gravity wave reflection at the model boundaries.
-Microphysical processes were parameterized using the \cite{Thompson} microphysics scheme and radiative heating tendencies were computed every two minutes using the RRTMG longwave and shortwave schemes \citep{Iacono}.
+Microphysical processes were parameterized using the \cite{Thompson} microphysics scheme and radiative heating tendencies were computed every two minutes using the Rapid Radiative Transfer Model WHAT DOES THE G STAND FOR?
+(RRTMG) longwave and shortwave schemes \citep{Iacono}.
 A horizontally-homogeneous temperature and humidity field was initialized with a mean sounding computed using all dropsondes deployed during the TCI flight conducted within and around Tropical Storm Patricia on 21 October, 2015 (see \citeauthor{DoyleTCI} \citeyear{DoyleTCI} for details.)
-Above 19 km, where few TCI observations were available, the temperature profile was assumed to be isothermal.
+Above 19 km, where few TCI observations were available, the temperature profile was taken from the Climate Forecast System Reanalysis (CFSR) grid point nearest Patricia's storm center, valid at 18 UTC 21 October, 2015.
 Since relative humidity measurements were unreliable at temperatures below -40\textdegree C \citep{BellTCI}, relative humidity was set equal to 50\% above 11.5 km (the level above which temperature dropped below -40\textdegree C).
@@
    \end{equation}
-In the tropopause layer, $q_s$, $\frac{\partial q_s}{\partial T}$, and $\frac{\partial q_t}{\partial z}$ approach zero; thus, Eq. \ref{eq:n2moist} reduces to:
+In the tropopause layer, $q_s$, $\frac{\partial q_s}{\partial T}$, and $\frac{\partial q_t}{\partial z}$ are small. Assuming that these quantities are zero, Eq. \ref{eq:n2moist} reduces to:
    \begin{equation} \label{eq:n2dry}
@@
 where \textit{g} is gravitational acceleration and $\theta_v$ is the virtual potential temperature.
-To compute $N^2$, CM1 uses Eq. \ref{eq:n2moist} in saturated environments and Eq. \ref{eq:n2dry} in unsaturated environments.
-For mathematical simplicity, only Eq. \ref{eq:n2dry} will be used for the budget computations herein\footnote{The validity of this approximation will be substantiated later in this section.}.
-Taking the time derivative of Eq.\ref{eq:n2dry} yields the static stability tendency:
+To compute $N^2$, CM1 uses Eq.
+\ref{eq:n2moist} in saturated environments and Eq.
+\ref{eq:n2dry} in unsaturated environments; for mathematical simplicity, however, only Eq.
+\ref{eq:n2dry} will be used for the budget computations herein\footnote{The validity of this approximation will be substantiated later in this section.}.
+
+Taking the time derivative of Eq. \ref{eq:n2dry} yields the static stability tendency:
+
+The potential temperature tendency can be partitioned into ### "budget variables," which are output directly by the model every two minutes:
+
+POTENTIAL TEMPERATURE TENDENCY EQUATION
 
@@
 
+  \section{Discussion}
+
+Dunion et al. speculate that the diurna pulse only occurs in mature storms. Maybe the development of the near-tropopause stable layer could partially explain the reason for this.
 % text...

### 2017-12-07 paper.tex
Added a couple of equations to Introduction. A few minor revisions to Introduction text.

@@
    \begin{equation} \label{eq:n2moist}
-   EQ. 18 OF BRYAN AND ROTUNNO. ALSO USE EQ. 19
+   N_m^2 = \frac{g}{T}(\frac{\partial T}{\partial z}+\Gamma_m)(1+\frac{T}{R_d/R_v+q_s}\frac{\partial q_s}{\partial T})-\frac{g}{1+q_t}\frac{\partial q_t}{\partial z},
    \end{equation}
-In the tropopause layer, $q_s$, $\frac{\partial q_s}{\partial T}$, and $\frac{\partial q_t}{\partial z}$ are small. Assuming that these quantities are zero, Eq. \ref{eq:n2moist} reduces to:
+where g is gravitational acceleration, T is temperature, $R_d$ and $R_v$ are the gas constants of dry air and water vapor, respectively, $q_s$ is the saturation mixing ratio, and $q_t$ is the total condensate mixing ratio.
+$Gamma_m$ is the moist-adiabatic lapse rate:
+   \begin{equation} \label{eq:gamma_m}
+   \Gamma_m = DETERMINE WHAT THIS IS FOR THE NON-CONSERVATIVE EQUATION SET
+   \end {equation}
+In the tropopause layer, $q_s$, $\frac{\partial q_s}{\partial T}$, and $\frac{\partial q_t}{\partial z}$ approach zero. In this limiting case, Eq. \ref{eq:n2moist} reduces to:
    \begin{equation} \label{eq:n2dry}
@@
 Taking the time derivative of Eq. \ref{eq:n2dry} yields the static stability tendency:
+   \begin{equation} \label{eq:dn2dt}
+   \
 

### 2017-12-07 paper.tex
Added static stability tendency equation and some description to Budget Computation section.

@@
 where g is gravitational acceleration, T is temperature, $R_d$ and $R_v$ are the gas constants of dry air and water vapor, respectively, $q_s$ is the saturation mixing ratio, and $q_t$ is the total condensate mixing ratio.
-$Gamma_m$ is the moist-adiabatic lapse rate:
+$\Gamma_m$ is the moist-adiabatic lapse rate:
    \begin{equation} \label{eq:gamma_m}
@@
    \begin{equation} \label{eq:dn2dt}
-   \
-
-The potential temperature tendency can be partitioned into ### "budget variables," which are output directly by the model every two minutes:
-
-POTENTIAL TEMPERATURE TENDENCY EQUATION
-
+   \frac{\partial N^2}{\partial t} = \frac{g}{\theta}\frac{\partial}{\partial z}\frac{\partial \theta}{\partial t}+\frac{g}{\theta^2}\frac{\partial \theta}{\partial z}\frac{\partial \theta}{\partial t},
+   \end{equation}
+where the potential temperature tendency, $\frac{\partial \theta}{\partial z}$, is:
+   \begin{equation} \label{eq:dthetadt}
+   \frac{\partial \theta}{\partial t} = 
+   \end{equation}
+Each term on the right-hand side of Eq. \ref{eq:dthetadt} represents a potential temperature budget variable, each of which is output directly by the model every minute.
+These tendencies are substituted for $\frac{\partial \theta}{\partial t}$ in Eq. \ref{eq:dn2dt}, yielding the static stability tendency attributable to each budget term every minute.
  \section{Results}

### 2017-12-07 paper.tex
Added a few equations and some text to Budget Computation section.

@@
    \end{equation}
-where g is gravitational acceleration, T is temperature, $R_d$ and $R_v$ are the gas constants of dry air and water vapor, respectively, $q_s$ is the saturation mixing ratio, and $q_t$ is the total condensate mixing ratio.
-$\Gamma_m$ is the moist-adiabatic lapse rate:
+where $g$ is gravitational acceleration, $T$ is temperature, $R_d$ and $R_v$ are the gas constants of dry air and water vapor, respectively, $q_s$ is the saturation mixing ratio, $q_t$ is the total condensate mixing ratio, and $\Gamma_m$ is the moist-adiabatic lapse rate:
    \begin{equation} \label{eq:gamma_m}
@@
    \end{equation}
-where \textit{g} is gravitational acceleration and $\theta_v$ is the virtual potential temperature.
+where $\theta_v$ is the virtual potential temperature.
 To compute $N^2$, CM1 uses Eq.
 \ref{eq:n2moist} in saturated environments and Eq.
-\ref{eq:n2dry} in unsaturated environments; for mathematical simplicity, however, only Eq.
+\ref{eq:n2dry} in sub-saturated environments; for mathematical simplicity, however, only Eq.
 \ref{eq:n2dry} will be used for the budget computations herein\footnote{The validity of this approximation will be substantiated later in this section.}.
@@
    \begin{equation} \label{eq:dthetadt}
-   \frac{\partial \theta}{\partial t} = 
+   \frac{\partial \theta}{\partial t} = HADV+VADV+HTURB+VTURB+MP+RAD+DISS 
    \end{equation}
 Each term on the right-hand side of Eq. \ref{eq:dthetadt} represents a potential temperature budget variable, each of which is output directly by the model every minute.
-These tendencies are substituted for $\frac{\partial \theta}{\partial t}$ in Eq. \ref{eq:dn2dt}, yielding the static stability tendency attributable to each budget term every minute.
+HADV and VADV are the radial and vertical advective tendencies, HTURB and VTURB are the radial and vertical tendencies from the turbulence parameterization, MP is the tendency from the microphysics scheme, RAD is the tendency from the radiation scheme, and DISS is the tendency due to turbulent dissipation.
+This equation neglects Rayleigh damping, since this term is zero everywhere below 25 km, and the analysis domain does not extend to that height.
+Each term in Eq. \ref{eq:dthetadt} is substituted for $\frac{\partial \theta}{\partial t}$ in Eq. \ref{eq:dn2dt}, yielding the contribution of each budget term to the static stability tendency.
+These terms are then summed, yielding an instantaneous "budget change" in $N^2$ every minute.
+These instantaneous budget changes are then averaged over 24-hour periods and compared to the total model change in $N^2$ over that same time period, i.e.:
+   \begin{equation} \label{eq:budgetchange}
+   \Delta N^2_{budget} = \sum_{t=t_0}^{t_0+\delta t} \frac{\partial N^2}{\partial t}\mid_t, NEED BAR OVER SUMMATION
+   \end{equation}
+   \begin{equation} \label{eq:modelchange}
+   \Delta N^2_{model} = N^2_{t_0+\delta t}-N^2_{t_0},
+   \end{equation}
+where $t_0$ is an initial time and $\delta_t$ is 24 hours.
+In Eq. \ref{eq:budgetchange}, Eq. \ref{eq:n2moist} in saturated environments and Eq. \ref{eq:n2dry} in sub-saturated environments; $t_0$ is an initial time and $\delta_t$ is 24 hours.
+
  \section{Results}

### 2017-12-18 paper.tex
A few changes here and there...

@@
 After undergoing a remarkably rapid intensification (RI), Hurricane Patricia (2015) set a new record as the strongest tropical cyclone (TC) ever observed in the Western Hemisphere (\citeauthor{Kimberlainetal2016} \citeyear{Kimberlainetal2016}; \citeauthor{Rogersetal2017} \citeyear{Rogersetal2017}).
-High-altitude dropsonde observations taken by the Tropical Cyclone Intensity (TCI) Experiment captured this RI in unprecedented detail \citep{DoyleTCI}.
+High-altitude dropsonde observations taken during the Tropical Cyclone Intensity (TCI) Experiment captured this RI in unprecedented detail \citep{DoyleTCI}.
 These observations revealed remarkable changes in the structure of the cold-point tropopause and upper-level static stability as the storm intensified \citep{Duran+Molinari2018}.
@@
 
-The numerical simulations were performed using version 19.4 of Cloud Model 1 (CM1) described in \cite{BryanRotunno2009} and available online at http://www2.mmm.ucar.edu/people/bryan/cm1/.
-The equations of motion were integrated on a 3000-km-wide, 30-km-deep grid axisymmetric grid with 1-km horizontal and 250-m vertical grid spacing.
-The computations were performed on an \textit{f}-plane at 15\textdegree{N} latitude, over a sea surface with constant temperature of 30.5\textdegree C, which matches that observed near Hurricane Patricia (2015; \citeauthor{Kimberlainetal2016} \citeyear{Kimberlainetal2016}.
+The numerical simulations were performed using version 19.4 of Cloud Model 1 (CM1) described in \cite{BryanRotunno2009}.
+The equations of motion were integrated on a 3000-km-wide, 30-km-deep axisymmetric grid with 1-km horizontal and 250-m vertical grid spacing.
+The computations were performed on an \textit{f}-plane at 15\textdegree{N} latitude, over a sea surface with constant temperature of 30.5\textdegree C, which matches that observed near Hurricane Patricia (2015; \citeauthor{Kimberlainetal2016} \citeyear{Kimberlainetal2016}).
 Horizontal turbulence was parameterized using the Smagorinsky scheme described in \citeauthor{BryanRotunno2009} (\citeyear{BryanRotunno2009}, pg.
@@
 A Rayleigh damping layer was applied outside of the 2900-km radius and above the 25-km level to prevent spurious gravity wave reflection at the model boundaries.
-Microphysical processes were parameterized using the \cite{Thompson} microphysics scheme and radiative heating tendencies were computed every two minutes using the Rapid Radiative Transfer Model WHAT DOES THE G STAND FOR?
+Microphysical processes were parameterized using the \cite{Thompson} microphysics scheme and radiative heating tendencies were computed every two minutes using the Rapid Radiative Transfer Model for GCMs?
 (RRTMG) longwave and shortwave schemes \citep{Iacono}.
@@
    \begin{equation} \label{eq:n2moist}
-   N_m^2 = \frac{g}{T}(\frac{\partial T}{\partial z}+\Gamma_m)(1+\frac{T}{R_d/R_v+q_s}\frac{\partial q_s}{\partial T})-\frac{g}{1+q_t}\frac{\partial q_t}{\partial z},
+   N_m^2 = \frac{g}{T}\left(\frac{\partial T}{\partial z}+\Gamma_m\right)\left(1+\frac{T}{R_d/R_v+q_s}\frac{\partial q_s}{\partial T}\right)-\frac{g}{1+q_t}\frac{\partial q_t}{\partial z},
    \end{equation}
@@
    \end{equation}
-where the potential temperature tendency, $\frac{\partial \theta}{\partial z}$, is:
+where the potential temperature tendency, $\frac{\partial \theta}{\partial z}$, can be written:
    \begin{equation} \label{eq:dthetadt}

### 2017-12-18 paper.tex
A few corrections and word changes.

--- 2017-12-07 paper.tex
@@
    \end {equation}
-In the tropopause layer, $q_s$, $\frac{\partial q_s}{\partial T}$, and $\frac{\partial q_t}{\partial z}$ approach zero. In this limiting case, Eq. \ref{eq:n2moist} reduces to:
+In the tropopause layer, $q_s$, ${\partial q_s}/{\partial T}$, and ${\partial q_t}/{\partial z}$ approach zero. In this limiting case, Eq. \ref{eq:n2moist} reduces to:
    \begin{equation} \label{eq:n2dry}
@@
    \begin{equation} \label{eq:dn2dt}
-   \frac{\partial N^2}{\partial t} = \frac{g}{\theta}\frac{\partial}{\partial z}\frac{\partial \theta}{\partial t}+\frac{g}{\theta^2}\frac{\partial \theta}{\partial z}\frac{\partial \theta}{\partial t},
+   \frac{\partial N^2}{\partial t} = \frac{g}{\theta}\frac{\partial}{\partial z}\frac{\partial \theta}{\partial t}-\frac{g}{\theta^2}\frac{\partial \theta}{\partial z}\frac{\partial \theta}{\partial t},
    \end{equation}
-where the potential temperature tendency, $\frac{\partial \theta}{\partial z}$, is:
+where the potential temperature tendency, ${\partial \theta}/{\partial t}$, can be expressed as the sum of seven physical processes:
    \begin{equation} \label{eq:dthetadt}
@@
 HADV and VADV are the radial and vertical advective tendencies, HTURB and VTURB are the radial and vertical tendencies from the turbulence parameterization, MP is the tendency from the microphysics scheme, RAD is the tendency from the radiation scheme, and DISS is the tendency due to turbulent dissipation.
-This equation neglects Rayleigh damping, since this term is zero everywhere below 25 km, and the analysis domain does not extend to that height.
-Each term in Eq. \ref{eq:dthetadt} is substituted for $\frac{\partial \theta}{\partial t}$ in Eq. \ref{eq:dn2dt}, yielding the contribution of each budget term to the static stability tendency.
-These terms are then summed, yielding an instantaneous "budget change" in $N^2$ every minute.
-These instantaneous budget changes are then averaged over 24-hour periods and compared to the total model change in $N^2$ over that same time period, i.e.:
+This equation neglects Rayleigh damping, since this term is zero everywhere below 25 km, and the analysis domain does not extend to that level.
+Each term in Eq. \ref{eq:dthetadt} is substituted for ${\partial \theta}/{\partial t}$ in Eq. \ref{eq:dn2dt}, yielding the contribution of each budget term to the static stability tendency.
+These terms are summed, yielding an instantaneous "budget change" in $N^2$ every minute.
+The budget changes are then averaged over 24-hour periods and compared to the total model change in $N^2$ over that same time period using a residual, i.e.:
    \begin{equation} \label{eq:budgetchange}
@@
    \end{equation}
-where $t_0$ is an initial time and $\delta_t$ is 24 hours.
+   \begin{equation} \label{eq:residual}
+   Residual = \Delta N^2_{model}-\Delta N^2_{budget}
+   \end{equation}
+where $t_0$ is an initial time and $\delta t$ is 24 hours.
 In Eq. \ref{eq:budgetchange}, Eq. \ref{eq:n2moist} in saturated environments and Eq. \ref{eq:n2dry} in sub-saturated environments; $t_0$ is an initial time and $\delta_t$ is 24 hours.
+
+CONTINUATION OF THIS SECTION IS IN MY RESEARCH NOTEBOOK
 

### 2017-12-18 paper.tex

@@
    \end{equation}
-where the potential temperature tendency, ${\partial \theta}/{\partial t}$, can be expressed as the sum of seven physical processes:
+where the potential temperature tendency, $\frac{\partial \theta}{\partial z}$, can be written:
    \begin{equation} \label{eq:dthetadt}

### 2017-12-18 paper.tex
Added moist-adiabatic lapse rate equation

@@
    \begin{equation} \label{eq:gamma_m}
-   \Gamma_m = DETERMINE WHAT THIS IS FOR THE NON-CONSERVATIVE EQUATION SET
+   \Gamma_m = g(1+q_t)\left(\frac{1+L_vq_s/R_dT}{c_p_m +L_v\partial q_s/\partial T}\right)
    \end {equation}
@@
 \ref{eq:n2moist} in saturated environments and Eq.
-\ref{eq:n2dry} in sub-saturated environments; for mathematical simplicity, however, only Eq.
+\ref{eq:n2dry} in sub-saturated environments, but for simplicity only Eq.
 \ref{eq:n2dry} will be used for the budget computations herein\footnote{The validity of this approximation will be substantiated later in this section.}.
@@
    \end{equation}
-where the potential temperature tendency, $\frac{\partial \theta}{\partial z}$, can be written:
+where the potential temperature tendency, $\partial \theta/\partial z$, can be written:
    \begin{equation} \label{eq:dthetadt}

### 2017-12-18 paper.tex
Finished the Budget Computation section.

@@
    \begin{equation} \label{eq:gamma_m}
-   \Gamma_m = g(1+q_t)\left(\frac{1+L_vq_s/R_dT}{c_p_m +L_v\partial q_s/\partial T}\right)
+   \Gamma_m = g(1+q_t)\left(\frac{1+L_vq_s/R_dT}{c_p_m +L_v\partial q_s/\partial T}\right),
    \end {equation}
+where $L_v$ is the latent heat of vaporization and $c_{pm}$ is the specific heat of moist air at constant pressure.
 In the tropopause layer, $q_s$, ${\partial q_s}/{\partial T}$, and ${\partial q_t}/{\partial z}$ approach zero. In this limiting case, Eq. \ref{eq:n2moist} reduces to:
@@
 
-CONTINUATION OF THIS SECTION IS IN MY RESEARCH NOTEBOOK
+Eqs. \ref{eq:budgetchange}-\ref{eq:residual} are plotted for four consecutive 24-hour periods in Fig. \ref{fig:mod+bud+res}.
+For this and all subsequent radial-vertical cross sections, a 1-2-1 smoother is applied once in the radial direction to eliminate $2\Delta r$ noise that appears in some of the raw model output and calculated fields.
+The left column of Fig.~\ref{fig:mod+bud+res} depicts the model changes (Eq.
+\ref{eq:modelchange}), the center column depicts the budget changes (Eq.
+\ref{eq:budgetchange}), and the right column depicts the residuals (Eq.
+\ref{eq:residual}).
+In every 24-hour period, the budget changes are nearly identical to the model changes, which is reflected in the near-zero residuals in the right column.
+This indicates that the budget accurately represents the model variability, which implies that the neglect of moisture in the budget computation introduces negligible error within the anaysis domain\footnote{This is not the case in the lower- and mid-troposphere, where the residual actually exceeds the budget variability in many places, likely due to the neglect of moisture; thus we limit this analysis to the upper troposphere and lower stratosphere.}.
+
+In the tropopause layer, some of the budget terms are small enough to be ignored.
+To determine which of the budget terms are most important, a time series of the contribution of each of the budget terms in Eq.
+\ref{eq:dthetadt} to the tropopause-layer static stability tendency is plotted in Fig.
+\ref{fig:avgbudterms}.
+For this figure, each of the budget terms is computed using the method described in Section 3, except with 1-hour averaging intervals instead of 24-hour intervals.
+The absolute values of these tendencies are then averaged over the radius-height domain depicted in Fig.~\ref{fig:mod+bud+res} and plotted as a time series\footnote{It will be seeen in subsequent figures that each of the terms contributes both positively and negatively to the N\textsuperscript{2} tendency within the analysis domain.
+Thus, taking an average over the domain tends to wash out the positive and negative contributions.
+To circumvent this problem, the absolute value of each of the terms is averaged, yielding a time series of the mean magnitude of each budget term.}. 
+Advection (Fig.~\ref{fig:avgbudterms}, red line) plays an important role in the mean tropopause-layer static stability tendency at all times, and vertical turbulence (Fig.~\ref{fig:avgbudterms}, blue line) and radiation (Fig.~\ref{fig:avgbudterms}, dark green line) both become important after 48 hours.
+Although the contribution from horizontal turbulence (Fig.~\ref{fig:avgbudterms}, purple line) becomes more important after 72 hours, it is confined to a very small region immediately surrounding the eyewall tangential velocity maximum (not shown), and is negligible throughout the rest of the tropopause layer.
+The remaining two processes - microphysics and dissipative heating (Fig.~\ref{fig:avgbudterms}, orange and light green lines, respectively) - lie atop one another near zero.
+These time series indicate that, at all times, three budget terms dominate the tropopause-layer static stability tendency: advection, vertical turbulence, and radiation.
+Variations in the magnitude and spatial structure of these terms drive the static stability changes depicted in Fig.~\ref{fig:mod+bud+res}; subsequent sections will focus on these variations and what causes them.
 
  \section{Results}
-
-Put description of Fig.~\ref{fig:vmax+pmin} in this section.
-
-Don't forget to mention 1-2-1 smoother.
 
@@
  \subsection{Static stability budget analysis}
-
-The left column of Fig.~\ref{fig:modbudres} depicts 24-hour changes in N\textsuperscript{2} over each of the four days of the simulation. 
-These represent bulk changes computed by subtracting the instantaneous N\textsuperscript{2} at the initial time from the instantaneous N\textsuperscript{2} at the final time. 
-The middle column of Fig.~\ref{fig:modbudres} represents the change in N\textsuperscript{2} computed using Eq. XXX and the method described in Section 3. 
-The residual between these two computations (Fig.~\ref{fig:modbudres}, right column) is much smaller than the change in N\textsuperscript{2}, meaning that the budget peforms well within the analysis domain.
-
-To determine which of the budget terms are most important, a time series of the contribution of each of the budget terms in Eq.
-XXX to the tropopause-layer static stability tendency is plotted in Fig.
-\ref{fig:avgbudterms}.
-For this figure, each of the budget terms is computed using the method described in Section 3, except with 1-hour averaging intervals instead of 24-hour intervals.
-The absolute values of these tendencies are then averaged over the radius-height domain depicted in Fig.~\ref{fig:modbudres} and plotted as a time series\footnote{It will be seeen in subsequent figures that each of the terms contributes both positively and negatively to the N\textsuperscript{2} tendency within the analysis domain.
-Thus, taking an average over the domain tends to wash out the positive and negative contributions.
-To circumvent this problem, the absolute value of each of the terms is averaged, yielding a time series of the mean magnitude of each budget term.}. 
-Advection (Fig.~\ref{fig:avgbudterms}, red line) plays an important role in the mean tropopause-layer static stability tendency at all times, and vertical turbulence (Fig.~\ref{fig:avgbudterms}, blue line) and radiation (Fig.~\ref{fig:avgbudterms}, dark green line) both become important after 48 hours.
-Although the contribution from horizontal turbulence (Fig.~\ref{fig:avgbudterms}, purple line) becomes more important after 72 hours, it is confined to a very small region immediately surrounding the eyewall tangential velocity maximum (not shown), and is negligible throughout the rest of the tropopause layer.
-The remaining two processes - microphysics and dissipative heating (Fig.~\ref{fig:avgbudterms}, orange and light green lines, respectively) - lie atop one another near zero.
-These time series indicate that, at all times, three budget terms dominate the tropopause-layer static stability tendency: advection, vertical turbulence, and radiation.
-Variations in the magnitude and spatial structure of these terms drive the static stability changes depicted in Fig.~\ref{fig:n2-24hr-avgs}; subsequent sections will focus on these variations and what causes them.
 
@@
 \begin{figure}[ht]
+\centerline{\includegraphics[width=39pc]{figures/fig01_R-Z_mod+bud+res.png}}
+\caption{Left panels: Twenty-four-hour changes in squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$ 10\textsuperscript{-4} s\textsuperscript{-2}) over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, (d) 72-96 hours.
+Middle Panels: The $N^2$ change over the same time periods computed using Eq.
+\ref.
+Right Panels: The budget residual over the same time periods, computed by subtracting the budget change (middle column) from the model change (left column).}
+\label{fig:mod+bud+res}
+\end{figure}
+
+%FIGURE 2%
+\begin{figure}[ht]
 \centerline{\includegraphics[width=19pc]{figures/fig01_vmax+pmin.png}}
@@
 
-%FIGURE 2%
+%FIGURE 3%
 \begin{figure*}[ht]
@@
 \label{fig:n2-24hr-avgs}
-\end{figure*}
-
-%FIGURE 3%
-\begin{figure*}[ht]
-\centerline{\includegraphics[width=33pc]{figures/fig03_R-Z_mod+bud+res.png}}
-\caption{Left panels: Twenty-four-hour changes in squared Brunt-V{\"a}is{\"a}l{\"a} frequency (10\textsuperscript{-4} s\textsuperscript{-2}) over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, (d) 72-96 hours.
-Middle Panels: The N\textsuperscript{2} change over the same time periods computed using Eq.
-XXX.
-Right Panels: The budget residual over the same time periods, computed by subtracting the budget change (middle column) from the model change (left column).}
-\label{fig:modbudres}
 \end{figure*}

### 2018-01-10 paper.tex
A whole bunch of changes over Christmas break.

@@
 
+More recently, \cite{Dunionetal2014} documented a periodic oscillation of infrared brightness temperature in hurricanes, which they call the "TC diurnal pulse."
+There will be a whole bunch of papers cited here...
+
 After undergoing a remarkably rapid intensification (RI), Hurricane Patricia (2015) set a new record as the strongest tropical cyclone (TC) ever observed in the Western Hemisphere (\citeauthor{Kimberlainetal2016} \citeyear{Kimberlainetal2016}; \citeauthor{Rogersetal2017} \citeyear{Rogersetal2017}).
@@
 
-More recently, \cite{Dunionetal2014} documented a periodic oscillation of infrared brightness temperature in hurricanes, which they call the "TC diurnal pulse."
-There will be a whole bunch of papers cited here...
+INCLUDE IN THIS INTRODUCTION DAN STERN'S POTENTIAL TEMPERATURE BUDGET PAPERS
 
@@
 A Rayleigh damping layer was applied outside of the 2900-km radius and above the 25-km level to prevent spurious gravity wave reflection at the model boundaries.
-Microphysical processes were parameterized using the \cite{Thompson} microphysics scheme and radiative heating tendencies were computed every two minutes using the Rapid Radiative Transfer Model for GCMs?
-(RRTMG) longwave and shortwave schemes \citep{Iacono}.
-A horizontally-homogeneous temperature and humidity field was initialized with a mean sounding computed using all dropsondes deployed during the TCI flight conducted within and around Tropical Storm Patricia on 21 October, 2015 (see \citeauthor{DoyleTCI} \citeyear{DoyleTCI} for details.)
-Above 19 km, where few TCI observations were available, the temperature profile was taken from the Climate Forecast System Reanalysis (CFSR) grid point nearest Patricia's storm center, valid at 18 UTC 21 October, 2015.
-Since relative humidity measurements were unreliable at temperatures below -40\textdegree C \citep{BellTCI}, relative humidity was set equal to 50\% above 11.5 km (the level above which temperature dropped below -40\textdegree C).
+Microphysical processes were parameterized using the \cite{Thompson} microphysics scheme and radiative heating tendencies were computed every two minutes using the Rapid Radiative Transfer Model for GCMs (RRTMG) longwave and shortwave schemes \citep{Iacono}.
+The initial temperature and humidity field was horizontally-homogeneous and determined by averaging all Climate Forecast System Reanalysis (CFSR) grid points within 1000 km of Patricia's center of circulation at 18 UTC 21 October 2015.
+%A horizontally-homogeneous temperature and humidity field was initialized with a mean sounding computed using all dropsondes deployed during the TCI flight conducted within and around Tropical Storm Patricia on 21 October, 2015 (see \citeauthor{DoyleTCI} \citeyear{DoyleTCI} for details.)
+%Above 19 km, where few TCI observations were available, the temperature profile was taken from the Climate Forecast System Reanalysis (CFSR) grid point nearest Patricia's storm center, valid at 18 UTC 21 October, 2015.
+%Since relative humidity measurements were unreliable at temperatures below -40\textdegree C \citep{BellTCI}, relative humidity was set equal to 50\% above 11.5 km (the level above which temperature dropped below -40\textdegree C).
 The vortex described in \citeauthor{RotunnoEmanuel} (\citeyear{RotunnoEmanuel}, their Eq. 37) was used to initialize the wind field, setting all parameters equal to the values used therein.
+
+Although hurricanes simulated in an axisymmetric framework tend to be more intense than those observed in nature, the intensity evolution of this simulation matches reasonably well with that observed in Hurricane Patricia.
+After an initial spin-up period of about 20 hours, the modeled storm (Fig.\ref{fig:vmax+pmin}, blue lines) began an RI period that lasted approximately 30 hours.
+After this RI, the storm continued to intensify more slowly until the maximum 10-m wind speed reached 89 m s\textsuperscript{-1} and the minimum sea-level pressure reached its minimum of 846 mb, 81 hours into the simulation.
+Hurricane Patricia (red stars) exhibited a similar intensity evolution, with an RI period leading to a maximum 10-m wind speed of 95 m s\textsuperscript{-1} and a minimum sea-level pressure of 872 hPa.
+Despite the limitations of the axisymmetric framework, the extraordinary intensity of Hurricane Patricia and the rapidity of its intensification makes Patricia a particularly good candidate for axisymmetric analysis.
 
@@
 where $\theta_v$ is the virtual potential temperature.
-To compute $N^2$, CM1 uses Eq.
-\ref{eq:n2moist} in saturated environments and Eq.
-\ref{eq:n2dry} in sub-saturated environments, but for simplicity only Eq.
+To compute $N^2$, CM1 uses Eq.\ref{eq:n2moist} in saturated environments and Eq.
+\ref{eq:n2dry} in sub-saturated environments.
+For simplicity, however, only Eq.
 \ref{eq:n2dry} will be used for the budget computations herein\footnote{The validity of this approximation will be substantiated later in this section.}.
@@
    \end{equation}
-where the potential temperature tendency, $\partial \theta/\partial z$, can be written:
+where the potential temperature tendency, $\partial \theta/\partial t$, can be written:
    \begin{equation} \label{eq:dthetadt}
@@
    \end{equation}
-Each term on the right-hand side of Eq. \ref{eq:dthetadt} represents a potential temperature budget variable, each of which is output directly by the model every minute.
+Each term on the right-hand side of Eq.\ref{eq:dthetadt} represents a potential temperature budget variable, each of which is output directly by the model every minute.
 HADV and VADV are the radial and vertical advective tendencies, HTURB and VTURB are the radial and vertical tendencies from the turbulence parameterization, MP is the tendency from the microphysics scheme, RAD is the tendency from the radiation scheme, and DISS is the tendency due to turbulent dissipation.
@@
    \begin{equation} \label{eq:budgetchange}
-   \Delta N^2_{budget} = \sum_{t=t_0}^{t_0+\delta t} \frac{\partial N^2}{\partial t}\mid_t, NEED BAR OVER SUMMATION
+   \Delta N^2_{budget} = \frac{1}{\delta t}\sum_{t=t_0}^{t_0+\delta t} \left.\frac{\partial N^2}{\partial t}\right\vert_t
    \end{equation}
    \begin{equation} \label{eq:modelchange}
-   \Delta N^2_{model} = N^2_{t_0+\delta t}-N^2_{t_0},
+   \Delta N^2_{model} = N^2_{t_0+\delta t}-N^2_{t_0}
    \end{equation}
@@
 where $t_0$ is an initial time and $\delta t$ is 24 hours.
-In Eq. \ref{eq:budgetchange}, Eq. \ref{eq:n2moist} in saturated environments and Eq. \ref{eq:n2dry} in sub-saturated environments; $t_0$ is an initial time and $\delta_t$ is 24 hours.
 
@@
 For this figure, each of the budget terms is computed using the method described in Section 3, except with 1-hour averaging intervals instead of 24-hour intervals.
-The absolute values of these tendencies are then averaged over the radius-height domain depicted in Fig.~\ref{fig:mod+bud+res} and plotted as a time series\footnote{It will be seeen in subsequent figures that each of the terms contributes both positively and negatively to the N\textsuperscript{2} tendency within the analysis domain.
+The absolute values of these tendencies are then averaged over over a radius-height domain surrounding the tropopause and plotted as a time series\footnote{It will be seeen in subsequent figures that each of the terms contributes both positively and negatively to the N\textsuperscript{2} tendency within the analysis domain.
 Thus, taking an average over the domain tends to wash out the positive and negative contributions.
 To circumvent this problem, the absolute value of each of the terms is averaged, yielding a time series of the mean magnitude of each budget term.}. 
-Advection (Fig.~\ref{fig:avgbudterms}, red line) plays an important role in the mean tropopause-layer static stability tendency at all times, and vertical turbulence (Fig.~\ref{fig:avgbudterms}, blue line) and radiation (Fig.~\ref{fig:avgbudterms}, dark green line) both become important after 48 hours.
-Although the contribution from horizontal turbulence (Fig.~\ref{fig:avgbudterms}, purple line) becomes more important after 72 hours, it is confined to a very small region immediately surrounding the eyewall tangential velocity maximum (not shown), and is negligible throughout the rest of the tropopause layer.
+Advection (Fig.~\ref{fig:avgbudterms}, red line) plays an important role in the mean tropopause-layer static stability tendency at all times, and vertical turbulence (Fig.~\ref{fig:avgbudterms}, blue line) and radiation (Fig.~\ref{fig:avgbudterms}, dark green line) also contribute significantly.%both become important after 48 hours.
+Although the contribution from horizontal turbulence (Fig.~\ref{fig:avgbudterms}, purple line) becomes more important after 48 hours, it is confined to a very small region immediately surrounding the eyewall tangential velocity maximum (not shown), and is negligible throughout the rest of the tropopause layer.
 The remaining two processes - microphysics and dissipative heating (Fig.~\ref{fig:avgbudterms}, orange and light green lines, respectively) - lie atop one another near zero.
@@
 
-The average N\textsuperscript{2} over the first day of the simulation (Fig.~\ref{fig:n2-24hr-avgs}a) indicates the presence of a static stability maximum about 400 m above the cold-point tropopause.
+The average $N^2$ over the first day of the simulation (Fig.~\ref{fig:n2-24hr-avgs}a) indicates the presence of a weak static stability maximum just above the cold-point tropopause.
 This lower-stratospheric stable layer had begun to erode during the initial spin-up period, with the maximum destabilitzation occurring at the innermost radii.
 This decrease in static stability continued into the second day of the simulation (Fig.~\ref{fig:n2-24hr-avgs}b) as the storm intensified to hurricane strength (Fig.~\ref{fig:vmax+pmin}).
-Destabilization was particularly pronounced over the developing eye, where the time-mean cold-point tropopause height increased by up to 400 m compared to the previous day.
-Over the developing eyewall and outer rainband regions, meanwhile, the tropopause height remained nearly constant.
-During the third day of the simulation (Fig.~\ref{fig:n2-24hr-avgs}c), static stability over the eye continued to decrease, and the cold-point tropopause height rose to 18.3 km at the storm center.
-The tropopause sloped sharply downward over the innermost radii, reaching the 16.4-km level near the 50-km radius.
+Destabilization was particularly pronounced over the developing eye, where the time-mean cold-point tropopause height increased by up to one km compared to the previous day.
+Over the developing eyewall and rainband regions, meanwhile, the tropopause height remained nearly constant.
+During the third day of the simulation (Fig.~\ref{fig:n2-24hr-avgs}c), static stability over the eye continued to decrease, and the cold-point tropopause height rose to nearly 20 km over the eye.
+The tropopause sloped sharply downward outside of the 20-km radius, reaching a minimum altitude of 16.4 km only 45 km from the storm center.
 This local minimum in tropopause height corresponded to the eyewall region, where upper-tropospheric static stability increased during this time period.
-Outside of the eyewall region, static stability began to increase in the layer immediately overlying the cold-point tropopause.
+At larger radii, static stability began to increase in the layer immediately overlying the cold-point tropopause.
 This stable layer sloped upward with radius, which corresponded to an upward-sloping tropopause radially outside of the eywall region.
-Over the next 24 hours (Fig.~\ref{fig:n2-24hr-avgs}d), as the storm's maximum 10-m wind speed leveled off near 80 m s\textsuperscript{-1} (Fig.~\ref{fig:vmax+pmin}), the upper-tropospheric static stability within the eyewall region continued to strengthen, as did the static stability just above the cold-point tropopause radially outside of the eyewall.
-As the stable layer strengthened, its altitude rose slightly, which corresponded to a slight increase in tropopause height outside of the eyewall during this period.
-Within the upper troposphere radially outside of the eyewall, meanwhile, static stability decreased such that it was nearly neutral in a thin layer between the 120- and 150-km radii.
-The eye region likewise continued to destabilize, and the cold-point tropopause height increased to a level above 18.5 km.
+Over the next 24 hours (Fig.~\ref{fig:n2-24hr-avgs}d), as the storm's maximum 10-m wind speed remained quasi-steady near 80 m s\textsuperscript{-1} (Fig.~\ref{fig:vmax+pmin}), the tropopause-layer static stability continued to increase.
+%As this stable layer strengthened, its altitude rose slightly, which corresponded to a slight increase in tropopause height outside of the eyewall during this period.
+%Within the upper troposphere radially outside of the eyewall, meanwhile, static stability decreased such that it was nearly neutral in a thin layer between the 120- and 150-km radii.
+Within the eye, the layer between 16 and 19 km continued to destabilize, and the cold-point tropopause height increased to a level above 21.5 km.
 This static stability evolution closely follows that observed in Hurricane Patricia (2015; \citeauthor{Duran+Molinari2018} \citeyear{Duran+Molinari2018}).
+Since most of the static stability variability
 
@@
 
-Dunion et al. speculate that the diurna pulse only occurs in mature storms. Maybe the development of the near-tropopause stable layer could partially explain the reason for this.
+Radiative heating and turbulence viscosity figures?
+
+Discuss how turbulence increases the static stability in some regions --> vertical gradients of turblence intensity.
+
+Dunion et al. speculate that the diurnal pulse only occurs in mature storms. Maybe the development of the near-tropopause stable layer could partially explain the reason for this.
 % text...
@@
 \acknowledgments
-We are indebted to Dr. George Bryan for his continued development and support of Cloud Model 1.
-We also thank Drs. Jeffrey Kepert, Robert Fovell, and Erika Navarro for fruitful conversations related to this work.
+We are indebted to George Bryan for his continued development and support of Cloud Model 1.
+We also thank Jeffrey Kepert, Robert Fovell, and Erika Navarro for helpful conversations related to this work.
 ADD GRANT NUMBER
@@
 \begin{figure}[ht]
-\centerline{\includegraphics[width=39pc]{figures/fig01_R-Z_mod+bud+res.png}}
+\centerline{\includegraphics[width=19pc]{figures/vmax+pmin.png}}
+\caption{The maximum 10-m wind speed (top panel; m s\textsuperscript{-1}) and minimum sea-level pressure (bottom panel; hPa) in the simulated storm (blue lines) and from Hurricane Patricia's best track (red stars).}
+\label{fig:vmax+pmin}
+\end{figure}
+
+%FIGURE 2%
+\begin{figure}[ht]
+\centerline{\includegraphics[width=33pc]{figures/mod+bud+res.png}}
 \caption{Left panels: Twenty-four-hour changes in squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$ 10\textsuperscript{-4} s\textsuperscript{-2}) over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, (d) 72-96 hours.
 Middle Panels: The $N^2$ change over the same time periods computed using Eq.
-\ref.
+\ref{eq:budgetchange}.
 Right Panels: The budget residual over the same time periods, computed by subtracting the budget change (middle column) from the model change (left column).}
@@
 
-%FIGURE 2%
-\begin{figure}[ht]
-\centerline{\includegraphics[width=19pc]{figures/fig01_vmax+pmin.png}}
-\caption{The maximum 10-m wind speed (top panel; m s\textsuperscript{-2}) and minimum sea-level pressure (bottom panel; hPa) in the simulated storm (blue lines) and from Hurricane Patricia's best track (red stars).}
-\label{fig:vmax+pmin}
-\end{figure}
-
 %FIGURE 3%
 \begin{figure*}[ht]
-\centerline{\includegraphics[width=39pc]{figures/fig02_n2-24hr-avgs.png}}
+\centerline{\includegraphics[width=39pc]{figures/n2-24hr-avgs.png}}
 \caption{Twenty-four-hour averages of squared Brunt-V{\"a}is{\"a}l{\"a} frequency (10\textsuperscript{-4} s\textsuperscript{-2}) over the first four days of the simulation.
-Orange lines represent the cold-point tropopause computed from the mean temperature field over the same time periods.}
+Orange lines represent the cold-point tropopause determined by the mean temperature field over the same time periods.}
 \label{fig:n2-24hr-avgs}
@@
 \begin{figure}[ht]
-\centerline{\includegraphics[width=19pc]{figures/fig04_AVG_budterms.png}}
+\centerline{\includegraphics[width=19pc]{figures/AVG_budterms.png}}
 \caption{Time series of the contribution of each of the budget terms to the time tendency of the squared Brunt-V{\"a}is{\"a}l{\"a} frequency (N\textsuperscript{2}; 10\textsuperscript{-4} s\textsuperscript{-2}).
-For each budget term, the absolute value of the N\textsuperscript{2} tendency is averaged both temporally over 1-hour periods (using output every minute), and spatially within the radius-height domain depicted in Fig.~\ref{fig:modbudres}.}
+For each budget term, the absolute value of the N\textsuperscript{2} tendency is averaged temporally over 1-hour periods (using output every minute), and spatially in a region extending from 0 to 200 km radius and 14 to 19 km altitude.}
 \label{fig:avgbudterms}
@@
 \begin{figure*}[ht]
-\centerline{\includegraphics[width=39pc]{figures/fig05_h000-h024-budgetterms.png}}
+\centerline{\includegraphics[width=39pc]{figures/h000-h024-budgetterms.png}}
 \caption{(a) Total change in N\textsuperscript{2} over the 0-24-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 hr)\textsuperscript{-1}) and the contributions to that change from (b) the sum of horizontal and vertical advection, (c) vertical turbulence, and (d) the sum of longwave and shortwave radiation.}
@@
 \begin{figure*}[ht]
-\centerline{\includegraphics[width=39pc]{figures/fig06_h024-h048-budgetterms.png}}
+\centerline{\includegraphics[width=39pc]{figures/h024-h048-budgetterms.png}}
 \caption{As in Fig.~\ref{fig:stab-00-24}, but for the 24-48-hour period.}
@@
 \begin{figure*}[ht]
-\centerline{\includegraphics[width=33pc]{figures/fig07_h048-h072-budgetterms.png}}
+\centerline{\includegraphics[width=27pc]{figures/h048-h072-budgetterms.png}}
 \caption{(a) Total change in N\textsuperscript{2} over the 48-72-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 hr)\textsuperscript{-1}) and the contributions to that change from (b) the sum of horizontal and vertical advection, (c) vertical turbulence, (d) the sum of longwave and shortwave radiation, (e) the sum of horizontal advection, vertical advection, and vertical turublence, and (f) the sum of horizontal advection, vertical advection, vertical turbulence, and longwave and shortwave radiation.}
@@
 \begin{figure*}[ht]
-\centerline{\includegraphics[width=33pc]{figures/fig08_h072-h096-budgetterms.png}}
+\centerline{\includegraphics[width=33pc]{figures/h072-h096-budgetterms.png}}
 \caption{As in Fig.~\ref{fig:stab-48-72}, but for the 72-96-hour period.}
@@
 \begin{figure*}[ht]
-\centerline{\includegraphics[width=39pc]{figures/fig09_u.png}}
+\centerline{\includegraphics[width=39pc]{figures/u.png}}
 \caption{Radial velocity (m s\textsuperscript{-1}; filled contours), potential temperature (K; thick black contours), and cold point tropopause height (orange line) averaged over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, and (d) 72-96 hours.}
@@
 \begin{figure*}[ht]
-\centerline{\includegraphics[width=39pc]{figures/fig10_w.png}}
+\centerline{\includegraphics[width=39pc]{figures/w.png}}
 \caption{Vertical velocity (cm s\textsuperscript{-1}; filled contours), potential temperature (K; thick black contours), and cold point tropopause height (orange line) averaged over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, and (d) 72-96 hours.}
@@
 \begin{figure*}[ht]
-\centerline{\includegraphics[width=39pc]{figures/fig11_qtot.png}}
+\centerline{\includegraphics[width=39pc]{figures/qtot.png}}
 \caption{Total condensate mixing ratio (g kg\textsuperscript{-1}) and cold point tropopause height (orange line) averaged over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, and (d) 72-96 hours.}

### 2018-01-10 paper.tex
Added radiation and eddy diffusivity figures and changed figures to run12.

@@
 \begin{figure}[ht]
-\centerline{\includegraphics[width=33pc]{figures/mod+bud+res.png}}
+\centerline{\includegraphics[width=39pc]{figures/mod+bud+res.png}}
 \caption{Left panels: Twenty-four-hour changes in squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$ 10\textsuperscript{-4} s\textsuperscript{-2}) over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, (d) 72-96 hours.
@@
 \caption{Time series of the contribution of each of the budget terms to the time tendency of the squared Brunt-V{\"a}is{\"a}l{\"a} frequency (N\textsuperscript{2}; 10\textsuperscript{-4} s\textsuperscript{-2}).
-For each budget term, the absolute value of the N\textsuperscript{2} tendency is averaged temporally over 1-hour periods (using output every minute), and spatially in a region extending from 0 to 200 km radius and 14 to 19 km altitude.}
+For each budget term, the absolute value of the N\textsuperscript{2} tendency is averaged temporally over 1-hour periods (using output every minute), and spatially in a region extending from 0 to 200 km radius and 14 to 21 km altitude.}
 \label{fig:avgbudterms}
@@
 \begin{figure*}[ht]
-\centerline{\includegraphics[width=39pc]{figures/h000-h024-budgetterms.png}}
-\caption{(a) Total change in N\textsuperscript{2} over the 0-24-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 hr)\textsuperscript{-1}) and the contributions to that change from (b) the sum of horizontal and vertical advection, (c) vertical turbulence, and (d) the sum of longwave and shortwave radiation.}
+\centerline{\includegraphics[width=27pc]{figures/h000-h024-budgetterms.png}}
+\caption{(a) Total change in N\textsuperscript{2} over the 0-24-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 hr)\textsuperscript{-1}) and the contributions to that change from (b) the sum of horizontal and vertical advection, (c) vertical turbulence, (d) longwave and shortwave radiation, (e) the sum of horizontal advection, vertical advection, and vertical turublence, and (f) the sum of horizontal advection, vertical advection, vertical turbulence, and longwave and shortwave radiation.}
 \label{fig:stab-00-24}
@@
 \begin{figure*}[ht]
-\centerline{\includegraphics[width=39pc]{figures/h024-h048-budgetterms.png}}
+\centerline{\includegraphics[width=27pc]{figures/h024-h048-budgetterms.png}}
 \caption{As in Fig.~\ref{fig:stab-00-24}, but for the 24-48-hour period.}
@@
 \centerline{\includegraphics[width=27pc]{figures/h048-h072-budgetterms.png}}
-\caption{(a) Total change in N\textsuperscript{2} over the 48-72-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 hr)\textsuperscript{-1}) and the contributions to that change from (b) the sum of horizontal and vertical advection, (c) vertical turbulence, (d) the sum of longwave and shortwave radiation, (e) the sum of horizontal advection, vertical advection, and vertical turublence, and (f) the sum of horizontal advection, vertical advection, vertical turbulence, and longwave and shortwave radiation.}
+\caption{As in Fig.~\ref{fig:stab-00-24}, but for the 48-72-hour period.}
 \label{fig:stab-48-72}
@@
 %FIGURE 8%
+%\begin{figure*}[ht]
+%\centerline{\includegraphics[width=33pc]{figures/h072-h096-budgetterms.png}}
+%\caption{As in Fig.~\ref{fig:stab-48-72}, but for the 72-96-hour period.}
+%\label{fig:stab-72-96}
+%\end{figure*}
+
+%FIGURE 8%
 \begin{figure*}[ht]
-\centerline{\includegraphics[width=33pc]{figures/h072-h096-budgetterms.png}}
-\caption{As in Fig.~\ref{fig:stab-48-72}, but for the 72-96-hour period.}
-\label{fig:stab-72-96}
+\centerline{\includegraphics[width=39pc]{figures/u.png}}
+\caption{Radial velocity (m s\textsuperscript{-1}; filled contours), potential temperature (K; thick black contours), and cold point tropopause height (orange lines) averaged over (a) 0-24 hours, (b) 24-48 hours, and (c) 48-72 hours.}
+\label{fig:u}
 \end{figure*}
@@
 \begin{figure*}[ht]
-\centerline{\includegraphics[width=39pc]{figures/u.png}}
-\caption{Radial velocity (m s\textsuperscript{-1}; filled contours), potential temperature (K; thick black contours), and cold point tropopause height (orange line) averaged over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, and (d) 72-96 hours.}
-\label{fig:u}
+\centerline{\includegraphics[width=39pc]{figures/w.png}}
+\caption{Vertical velocity (cm s\textsuperscript{-1}; filled contours), potential temperature (K; thick black contours), and cold point tropopause height (orange lines) averaged over (a) 0-24 hours, (b) 24-48 hours, and (c) 48-72 hours.}
+\label{fig:w}
 \end{figure*}
@@
 \begin{figure*}[ht]
-\centerline{\includegraphics[width=39pc]{figures/w.png}}
-\caption{Vertical velocity (cm s\textsuperscript{-1}; filled contours), potential temperature (K; thick black contours), and cold point tropopause height (orange line) averaged over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, and (d) 72-96 hours.}
-\label{fig:w}
+\centerline{\includegraphics[width=39pc]{figures/qtot.png}}
+\caption{Total condensate mixing ratio (g kg\textsuperscript{-1}) and cold point tropopause height (orange lines) averaged over (a) 0-24 hours, (b) 24-48 hours, and (c) 48-72 hours.}
+\label{fig:qtot}
 \end{figure*}
@@
 \begin{figure*}[ht]
-\centerline{\includegraphics[width=39pc]{figures/qtot.png}}
-\caption{Total condensate mixing ratio (g kg\textsuperscript{-1}) and cold point tropopause height (orange line) averaged over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, and (d) 72-96 hours.}
-\label{fig:qtot}
+\centerline{\includegraphics[width=39pc]{figures/radten.png}}
+\caption{Radiative heating rate (K hr\textsuperscript{-1}) and cold point tropopause height (orange lines) averaged over (a) 0-24 hours, (b) 24-48 hours, and (c) 48-72 hours.}
+\label{fig:radten}
 \end{figure*}
 
+%FIGURE 12%
+\begin{figure*}[ht]
+\centerline{\includegraphics[width=39pc]{figures/khvten.png}}
+\caption{Vertical eddy diffusivity (m\textsuperscript{2} s\textsuperscript{-2}; filled contours), cold point tropopause height (cyan lines), and radial velocity (m s\textsuperscript{-1}; thick black lines) averaged over (a) 0-24 hours, (b) 24-48 hours, and (c) 48-72 hours.}
+\label{fig:radten}
+\end{figure*}
+
+%\begin{figure}[t]
+%\begin{figure}[t]
 %\begin{figure}[t]

### 2018-01-27 paper.tex
A few changes here and there.

@@
 
-Perhaps introduce upper-tropospheric static stability and its relationship to the diurnal cycle before going into Patricia? Include references to Dunion, Navarro, and O'Neill here.
-
-More recently, \cite{Dunionetal2014} documented a periodic oscillation of infrared brightness temperature in hurricanes, which they call the "TC diurnal pulse."
-There will be a whole bunch of papers cited here...
+%Perhaps introduce upper-tropospheric static stability and its relationship to the diurnal cycle before going into Patricia? Include references to Dunion, Navarro, and O'Neill here.
+%More recently, \cite{Dunionetal2014} documented a periodic oscillation of infrared brightness temperature in hurricanes, which they call the "TC diurnal pulse."
+%There will be a whole bunch of papers cited here...
+%At some point (probably in the Discussion) mention the possible importance of static stability asymmetries, in the context of the Dunion diurnal pulse
 
@@
 INCLUDE IN THIS INTRODUCTION DAN STERN'S POTENTIAL TEMPERATURE BUDGET PAPERS
-
-At some point (probably in the Discussion) mention the possible importance of static stability asymmetries, in the context of the Dunion diurnal pulse
+ALSO INCLUDE KEPERT'S STATIC STABILITY BUDGET PAPER
 
@@
 Microphysical processes were parameterized using the \cite{Thompson} microphysics scheme and radiative heating tendencies were computed every two minutes using the Rapid Radiative Transfer Model for GCMs (RRTMG) longwave and shortwave schemes \citep{Iacono}.
-The initial temperature and humidity field was horizontally-homogeneous and determined by averaging all Climate Forecast System Reanalysis (CFSR) grid points within 1000 km of Patricia's center of circulation at 18 UTC 21 October 2015.
+The initial temperature and humidity field was horizontally homogeneous and determined by averaging all Climate Forecast System Reanalysis (CFSR) grid points within 100 km of Patricia's center of circulation at 18 UTC 21 October 2015.
 %A horizontally-homogeneous temperature and humidity field was initialized with a mean sounding computed using all dropsondes deployed during the TCI flight conducted within and around Tropical Storm Patricia on 21 October, 2015 (see \citeauthor{DoyleTCI} \citeyear{DoyleTCI} for details.)
@@
 For simplicity, however, only Eq.
-\ref{eq:n2dry} will be used for the budget computations herein\footnote{The validity of this approximation will be substantiated later in this section.}.
+\ref{eq:n2dry} will be employed for the budget computations herein\footnote{The validity of this approximation will be substantiated later in this section.}.
 
@@
    \end{equation}
-Each term on the right-hand side of Eq.\ref{eq:dthetadt} represents a potential temperature budget variable, each of which is output directly by the model every minute.
+Each term on the right-hand side of Eq. \ref{eq:dthetadt} represents a $\theta$ budget variable, each of which is output directly by the model every minute.
 HADV and VADV are the radial and vertical advective tendencies, HTURB and VTURB are the radial and vertical tendencies from the turbulence parameterization, MP is the tendency from the microphysics scheme, RAD is the tendency from the radiation scheme, and DISS is the tendency due to turbulent dissipation.
@@
 These terms are summed, yielding an instantaneous "budget change" in $N^2$ every minute.
-The budget changes are then averaged over 24-hour periods and compared to the total model change in $N^2$ over that same time period using a residual, i.e.:
+The budget changes are then averaged over 24-hour periods and compared to the total model change in $N^2$ over that same time period, i.e.:
    \begin{equation} \label{eq:budgetchange}
@@
 For this figure, each of the budget terms is computed using the method described in Section 3, except with 1-hour averaging intervals instead of 24-hour intervals.
-The absolute values of these tendencies are then averaged over over a radius-height domain surrounding the tropopause and plotted as a time series\footnote{It will be seeen in subsequent figures that each of the terms contributes both positively and negatively to the N\textsuperscript{2} tendency within the analysis domain.
+The absolute values of these tendencies are then averaged over a radius-height domain surrounding the tropopause and plotted as a time series\footnote{It will be seeen in subsequent figures that each of the terms contributes both positively and negatively to the N\textsuperscript{2} tendency within the analysis domain.
 Thus, taking an average over the domain tends to wash out the positive and negative contributions.
-To circumvent this problem, the absolute value of each of the terms is averaged, yielding a time series of the mean magnitude of each budget term.}. 
-Advection (Fig.~\ref{fig:avgbudterms}, red line) plays an important role in the mean tropopause-layer static stability tendency at all times, and vertical turbulence (Fig.~\ref{fig:avgbudterms}, blue line) and radiation (Fig.~\ref{fig:avgbudterms}, dark green line) also contribute significantly.%both become important after 48 hours.
+To circumvent this problem, the absolute value of each of the terms is averaged.}. 
+Advection (Fig.~\ref{fig:avgbudterms}, red line) plays an important role in the mean tropopause-layer static stability tendency at all times, and vertical turbulence (Fig.~\ref{fig:avgbudterms}, blue line) and radiation (Fig.~\ref{fig:avgbudterms}, dark green line) also contribute significantly.
+%both become important after 48 hours.
 Although the contribution from horizontal turbulence (Fig.~\ref{fig:avgbudterms}, purple line) becomes more important after 48 hours, it is confined to a very small region immediately surrounding the eyewall tangential velocity maximum (not shown), and is negligible throughout the rest of the tropopause layer.
@@
 \centerline{\includegraphics[width=39pc]{figures/mod+bud+res.png}}
-\caption{Left panels: Twenty-four-hour changes in squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$ 10\textsuperscript{-4} s\textsuperscript{-2}) over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, (d) 72-96 hours.
+\caption{Left panels: Twenty-four-hour changes in squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$; 10\textsuperscript{-4} s\textsuperscript{-2}) over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, (d) 72-96 hours.
 Middle Panels: The $N^2$ change over the same time periods computed using Eq.

### 2018-01-30 paper.tex
Expanded introduction and added references.

@@
 After undergoing a remarkably rapid intensification (RI), Hurricane Patricia (2015) set a new record as the strongest tropical cyclone (TC) ever observed in the Western Hemisphere (\citeauthor{Kimberlainetal2016} \citeyear{Kimberlainetal2016}; \citeauthor{Rogersetal2017} \citeyear{Rogersetal2017}).
-High-altitude dropsonde observations taken during the Tropical Cyclone Intensity (TCI) Experiment captured this RI in unprecedented detail \citep{DoyleTCI}.
-These observations revealed remarkable changes in the structure of the cold-point tropopause and upper-level static stability as the storm intensified \citep{Duran+Molinari2018}.
+High-altitude dropsonde observations taken during the Tropical Cyclone Intensity (TCI) experiment captured this RI in unprecedented detail \citep{DoyleTCI}.
+These observations revealed remarkable changes in the structure of the cold-point tropopause and upper-level static stability as the storm intensified \citep{DuranMolinari2018}.
+
 At tropical storm intensity, shortly before RI commenced, a strong inversion layer existed just above Patricia's cold-point tropopause, which was located near 17.2 km.
@@
 
-INCLUDE IN THIS INTRODUCTION DAN STERN'S POTENTIAL TEMPERATURE BUDGET PAPERS
-ALSO INCLUDE KEPERT'S STATIC STABILITY BUDGET PAPER
+Despite the importance of tropopause-layer thermodynamics in theoretical models of hurricanes (\citeauthor{EmanuelRotunno2011} \citeyear{EmanuelRotunno2011}; \citeauthor{Emanuel2012} \citeyear{Emanuel2012}), few papers have examined the upper-tropospheric evolution of TCs.
+\cite{KomaromiDoyle2017} found that stronger TCs tended to have a higher and warmer tropopause over their inner core than weaker TCs.
+Their results are consistent with the evolution observed over the inner core of Hurricane Patricia, in which the tropopause height increased and the tropopause temperature warmed throughout RI \citep{DuranMolinari2018}.
+The simulations of \cite{OhnoSatoh2015} suggested that the development of an upper-level warm core within the eye acted to decrease the static stability near the tropopause.
+Although the mechanisms that drive this static stability evolution have not been examined explicitly, the potential temperature ($\theta$) budget analysis of \cite{SternZhang2013} examined the development of the TC warm core.
+They found that radial and vertical advection both play important roles in warm core development throughout RI, with subgrid-scale diffusion becoming particularly important during the later stage of RI.
+
+The analysis herein is based upon that of \cite{SternZhang2013}, except using a static stability budget similar to that of \cite{Kepertetal2016} rather than a $\theta$ budget.
 
@@
 Within the eye, the layer between 16 and 19 km continued to destabilize, and the cold-point tropopause height increased to a level above 21.5 km.
-This static stability evolution closely follows that observed in Hurricane Patricia (2015; \citeauthor{Duran+Molinari2018} \citeyear{Duran+Molinari2018}).
+This static stability evolution closely follows that observed in Hurricane Patricia (2015; \citeauthor{DuranMolinari2018} \citeyear{DuranMolinari2018}).
 Since most of the static stability variability

### 2018-01-31 paper.tex
Updated first part of Results section.

@@
 The average $N^2$ over the first day of the simulation (Fig.~\ref{fig:n2-24hr-avgs}a) indicates the presence of a weak static stability maximum just above the cold-point tropopause.
-This lower-stratospheric stable layer had begun to erode during the initial spin-up period, with the maximum destabilitzation occurring at the innermost radii.
-This decrease in static stability continued into the second day of the simulation (Fig.~\ref{fig:n2-24hr-avgs}b) as the storm intensified to hurricane strength (Fig.~\ref{fig:vmax+pmin}).
-Destabilization was particularly pronounced over the developing eye, where the time-mean cold-point tropopause height increased by up to one km compared to the previous day.
-Over the developing eyewall and rainband regions, meanwhile, the tropopause height remained nearly constant.
-During the third day of the simulation (Fig.~\ref{fig:n2-24hr-avgs}c), static stability over the eye continued to decrease, and the cold-point tropopause height rose to nearly 20 km over the eye.
-The tropopause sloped sharply downward outside of the 20-km radius, reaching a minimum altitude of 16.4 km only 45 km from the storm center.
-This local minimum in tropopause height corresponded to the eyewall region, where upper-tropospheric static stability increased during this time period.
-At larger radii, static stability began to increase in the layer immediately overlying the cold-point tropopause.
-This stable layer sloped upward with radius, which corresponded to an upward-sloping tropopause radially outside of the eywall region.
-Over the next 24 hours (Fig.~\ref{fig:n2-24hr-avgs}d), as the storm's maximum 10-m wind speed remained quasi-steady near 80 m s\textsuperscript{-1} (Fig.~\ref{fig:vmax+pmin}), the tropopause-layer static stability continued to increase.
-%As this stable layer strengthened, its altitude rose slightly, which corresponded to a slight increase in tropopause height outside of the eyewall during this period.
-%Within the upper troposphere radially outside of the eyewall, meanwhile, static stability decreased such that it was nearly neutral in a thin layer between the 120- and 150-km radii.
-Within the eye, the layer between 16 and 19 km continued to destabilize, and the cold-point tropopause height increased to a level above 21.5 km.
+Over the subsequent 24 hours, during which RI occurred, this static stability maximum weakened within the 20 km radius (Fig.~\ref{fig:n2-24-hr-avgs}b).
+This decreasing $N^2$ corresponded to an increase in the tropopause height within the developing eye, maximizing at the storm center.
+Outside of the eye, meanwhile, the tropopause height decresed over the eyewall region (25-60-km radius) and increased only slightly outside of the 60 km radius.
+In this outer region, the lower-stratospheric $N^2$ maximum strengthened during RI.
+These trends continued as the storm's intensity leveled off in the 48-72-hour period (Fig.~\ref{fig:n2-24hr-avgs}c).
+The tropopause height increased to nearly 21 km at the storm center and sloped sharply downward to 16.3 km on the inner edge of the eyewall, near the 30 km radius.
 This static stability evolution closely follows that observed in Hurricane Patricia (2015; \citeauthor{DuranMolinari2018} \citeyear{DuranMolinari2018}).

### 2018-02-06 paper.tex
Added new results to Results section.

@@
    \begin{equation} \label{eq:n2dry}
-   N^2 = \frac{g}{\theta_v}\frac{\partial \theta_v}{\partial z},
+   N^2 = \frac{g}{\theta}\frac{\partial \theta}{\partial z},
    \end{equation}
-where $\theta_v$ is the virtual potential temperature.
+where $\theta$ is the potential temperature.
+
 To compute $N^2$, CM1 uses Eq.\ref{eq:n2moist} in saturated environments and Eq.
@@
 The average $N^2$ over the first day of the simulation (Fig.~\ref{fig:n2-24hr-avgs}a) indicates the presence of a weak static stability maximum just above the cold-point tropopause.
-Over the subsequent 24 hours, during which RI occurred, this static stability maximum weakened within the 20 km radius (Fig.~\ref{fig:n2-24-hr-avgs}b).
-This decreasing $N^2$ corresponded to an increase in the tropopause height within the developing eye, maximizing at the storm center.
-Outside of the eye, meanwhile, the tropopause height decresed over the eyewall region (25-60-km radius) and increased only slightly outside of the 60 km radius.
-In this outer region, the lower-stratospheric $N^2$ maximum strengthened during RI.
+Over the subsequent 24 hours, during the RI period, the static stability within and above this layer decreased near the storm center (Fig.~\ref{fig:n2-24hr-avgs}b).
+This decreasing $N^2$ corresponded to an increase in the tropopause height within the developing eye, maximized at the storm center.
+Outside of the eye, meanwhile, the tropopause height decresed over the eyewall region (25-60-km radius) and increased only slightly outside of the 60-km radius.
+In this outer region, the $N^2$ maximum just above the tropopause strengthened during RI.
 These trends continued as the storm's intensity leveled off in the 48-72-hour period (Fig.~\ref{fig:n2-24hr-avgs}c).
 The tropopause height increased to nearly 21 km at the storm center and sloped sharply downward to 16.3 km on the inner edge of the eyewall, near the 30 km radius.
-This static stability evolution closely follows that observed in Hurricane Patricia (2015; \citeauthor{DuranMolinari2018} \citeyear{DuranMolinari2018}).
-Since most of the static stability variability
+Static stability outside of the eye, meanwhile, continued to increase just above the cold-point tropopause.
+This $N^2$ evolution closely follows that observed in Hurricane Patricia (2015; \citeauthor{DuranMolinari2018} \citeyear{DuranMolinari2018}).
+The mechanisms that led to these static stability changes will be investigated in the subsequent sections.
 
@@
 \paragraph{0-24 hours}
-The first 24 hours of the simulation was characterized by a weakening of the lower-stratospheric static stability maximum above 17 km (Fig.~\ref{fig:stab-0-24}a, purple shading) and an increase in static stability below (green shading).
+The weakening of the lower-stratospheric static stability maximum during the initial spin-up period is reflected in the total $N^2$ budget change over this time (Fig.~\ref{fig:stab-00-24}a).
+The 17-18-km layer was characterized by decreasing $N^2$ (purple shading), maximizing at the storm center.
+The layer immediately below the tropopause, meanwhile, saw strengthening $N^2$ during this time period.
 Although these tendencies extended out to the 200-km radius, they were particularly pronounced at innermost radii.
-A comparison of the contributions of advection (Fig.~\ref{fig:stab-0-24}b), vertical turbulence (Fig.~\ref{fig:stab-0-24}c), and radiation (Fig.~\ref{fig:stab-0-24}d) reveals that advection is primarily responsible for the change in static stability during this period.
+A comparison of the contributions of advection (Fig.~\ref{fig:stab-00-24}b), vertical turbulence (Fig.~\ref{fig:stab-00-24}c), and radiation (Fig.~\ref{fig:stab-00-24}d) reveals that advection is primarily responsible for the change in static stability during this period.
+Although vertical turbulence acts in opposition to advection (i.e.
+it acts to stabilize regions that advection acts to destabilize), the magnitude of the advective tendencies is larger, particularly at the innermost radii.
+The sum of advection and vertical turbulence (Fig.~\ref{fig:stab-00-24}e) almost exactly replicates the static stability tendencies above 17 km.
+Radiative tendencies (Fig.~\ref{fig:stab-00-24}d) act to destabilize the layer below about 16 km and stabilize the layer between 16 and 17 km.
+The sum of advection, vertical turbulence, and radiation (Fig.~\ref{fig:stab-00-24}f) reproduces the total change in $N^2$ almost exactly.
+
 ...Explain this in the context of radial and vertical velocities...
+...See Stern and Zhang, Page 84, Section 3d...
+...Add mention of total condensate and radiative heating tendencies as it relates to statbility tendency due to rad...
 
 \paragraph{24-48 hours}
-During the second day of the simulation, the lower-stratospheric stable layer continued to weaken (Fig.~\ref{fig:stab-24-48}a).
-This weakening trend in the 16.75-17.75-km layer extended from the 50 km radius outward to past 200 km, and was primarily driven by advection (Fig.~\ref{fig:stab-24-48}b).
-Below this layer, static stability began to increse slightly.
-This stabilization had contributions from both vertical turbulence (Fig.~\ref{fig:stab-24-48}c) and radiation (Fig.~\ref{fig:stab-24-48}d) in the 16-16.5-km layer.
-...Explain this in context of mean vertical mixing coefficient and mean radiative heating tendency...
-Meanwhile, radially inward of 60 km, static stability below 17.5 km continued to weaken, primarily due to advective processes.
+During the RI period within the eye, $N^2$ generally decreased above 16 km and increased below (Fig.~\ref{fig:stab-24-48}a).
+These tendencies at the innermost radii were driven almost entirely by advection (Fig.~\ref{fig:stab-24-48}b); vertical turbulence (Fig.~\ref{fig:stab-24-48}c) and radiation (Fig.~\ref{fig:stab-24-48}d) contributed negligibly to the static stability tendencies in this region.
+Outside of the eye, meanwhile, the $N^2$ evolution exhibited alternating layers of positive and negative tendencies.
+Near and above 18 km existed an upward-sloping region of decreasing $N^2$ that extended out to the 180-km radius.
+In this region, neither vertical turbulence nor radiation exhibited negative $N^2$ tendencies; advection was the only forcing for destabilization.
+Immediately below this layer was a region of increasing $N^2$, which sloped upward from 17 km near the 30-km radius to just below 18 km outside of the 100 km radius.
+Advection and vertical turbulence both contributed to this positive $N^2$ tendency, with advection playing an important role below about 17.5 km and and turbulence playing an important role above.
+The sum of advection and turbulence (Fig.~\ref{fig:stab-24-48}e) reveals two discontiguous regions of increasing $N^2$ rather than one contiguous region.
+The addition of radiation to these two terms, however, (Fig.~\ref{fig:stab-24-48}f) provides the link between these two regions, indicating that radiation also plays a role in strengthening the stable layer just above the tropopause.
+Below 17 km, a horizontally-extensive layer of decreasing $N^2$ also was forced by a combination of advection, vertical turbulence, and radiation.
+The sum of advection and vertical turbulence accounts only for two isolated regions of decreasing $N^2$ in this layer, and actually forces stabilization in part of the region.
+For example, just above 16 km in the 150-200-km radial band, the sum of advection and vertical turbulence forces an increase in $N^2$.
+Likewise, throughout most of the 30-60-km radial band in this layer, advection and vertical turbulence combine to force near-zero or positive $N^2$ tendencies.
+Radiative tendencies overcome this forcing for stabilization in both of these regions to produce the radially-extensive region of destabilization just below the tropopause.
+
+TWO REGIONS WHERE Panel (f) differs from panel (a): 30-60 km radial band below 16 km, which is actually canceled out by a vertical gradient of latent heating, and the thin region of strong stabilization between 15-17.5 km near r=30 km, which is canceled out by horizontal turbulence.
 

### 2018-02-06 paper.tex
A few small changes.
Started 48-72 hours section of Results

@@
 \paragraph{24-48 hours}
-During the RI period within the eye, $N^2$ generally decreased above 16 km and increased below (Fig.~\ref{fig:stab-24-48}a).
+During the RI period, $N^2$ within the eye generally decreased above 16 km and increased below (Fig.~\ref{fig:stab-24-48}a).
 These tendencies at the innermost radii were driven almost entirely by advection (Fig.~\ref{fig:stab-24-48}b); vertical turbulence (Fig.~\ref{fig:stab-24-48}c) and radiation (Fig.~\ref{fig:stab-24-48}d) contributed negligibly to the static stability tendencies in this region.
-Outside of the eye, meanwhile, the $N^2$ evolution exhibited alternating layers of positive and negative tendencies.
+
+Outside of the eye, the $N^2$ evolution exhibited alternating layers of positive and negative tendencies.
 Near and above 18 km existed an upward-sloping region of decreasing $N^2$ that extended out to the 180-km radius.
 In this region, neither vertical turbulence nor radiation exhibited negative $N^2$ tendencies; advection was the only forcing for destabilization.
-Immediately below this layer was a region of increasing $N^2$, which sloped upward from 17 km near the 30-km radius to just below 18 km outside of the 100 km radius.
+Immediately below this layer was a region of increasing $N^2$, which sloped upward from 17 km near the 30-km radius to just below 18 km outside of the 100-km radius.
 Advection and vertical turbulence both contributed to this positive $N^2$ tendency, with advection playing an important role below about 17.5 km and and turbulence playing an important role above.
-The sum of advection and turbulence (Fig.~\ref{fig:stab-24-48}e) reveals two discontiguous regions of increasing $N^2$ rather than one contiguous region.
+The sum of advection and turbulence (Fig.~\ref{fig:stab-24-48}e) reveals two discontiguous regions of increasing $N^2$ in the 17-18-km layer rather than one contiguous region.
 The addition of radiation to these two terms, however, (Fig.~\ref{fig:stab-24-48}f) provides the link between these two regions, indicating that radiation also plays a role in strengthening the stable layer just above the tropopause.
-Below 17 km, a horizontally-extensive layer of decreasing $N^2$ also was forced by a combination of advection, vertical turbulence, and radiation.
-The sum of advection and vertical turbulence accounts only for two isolated regions of decreasing $N^2$ in this layer, and actually forces stabilization in part of the region.
-For example, just above 16 km in the 150-200-km radial band, the sum of advection and vertical turbulence forces an increase in $N^2$.
-Likewise, throughout most of the 30-60-km radial band in this layer, advection and vertical turbulence combine to force near-zero or positive $N^2$ tendencies.
-Radiative tendencies overcome this forcing for stabilization in both of these regions to produce the radially-extensive region of destabilization just below the tropopause.
+In the 16-17-km layer, a horizontally-extensive layer of decreasing $N^2$ also was forced by a combination of advection, vertical turbulence, and radiation.
+The sum of advection and vertical turbulence accounts for only a portion of the decreasing $N^2$ in this layer, and actually indicates forcing for stabilization near the 50-km radius and outside of the 130-km radius.
+Radiative tendencies overcome this forcing for stabilization in both of these regions to produce the radially-extensive region of destabilization observed just below the tropopause.
 
@@
 
-Dunion et al. speculate that the diurnal pulse only occurs in mature storms. Maybe the development of the near-tropopause stable layer could partially explain the reason for this.
+Diurnal variability of of static stability in the upper troposphere is an interesting area of future research.
+
 % text...

### 2018-02-08 paper.tex
Added a lot to the Results and Discussion sections and changed Figures.

@@
 \paragraph{48-72 hours}
-The third day of the simulation marked a dramatic change in the structure of the tropopause-layer static stability tendencies.
-During this time, static stability increased markedly in an upward-sloping region within the 30-60-km radial band (Fig.~\ref{fig:stab-48-72}a), and also increased within the 16.75-17.5-km layer out to at least the 200-km radius.
-As this layer stabilized, the layer immediately below it destabilized in a broad region extending from 60-200 km.
-Examination of the contribution from total advection (Fig.~\ref{fig:stab-48-72}b) reveals that advection no longer dominates the static stability tendencies.
-Instead, a combination of vertical turbulence (Fig.~\ref{fig:stab-48-72}c) and radiation (Fig.~\ref{fig:stab-48-72}d) overcomes the destabilizing influence of advection to create the layer of increasing static stability.
-Meanwhile, the destabilizing influence of vertical turbulence in a broad region below 17 km combines with a small region of destabilization due to radiation in the 50-120-km radial band combine to destabilize the layer below 16.5 km in the 50-200-km radial band.
-Comparing the sum of advection and vertical turbulence (Fig.~\ref{fig:stab-48-72}e) to the sum of advection, vertical turbulence, and radiation (Fig.~\ref{fig:stab-48-72}f) reveals that radiation plays a fundamental role in the re-strengthening of the lower-stratospheric stable layer during this time.
+After the storm's maximum wind speed leveled off near 80 m s\textsuperscript{-1}, the magnitude of the static stability tendencies within the eye decreased to near zero (Fig.~\ref{fig:stab-48-72}a).
 
-\paragraph{72-96 hours}
+Outside of the eye, however, $N^2$ continued to increase just above the tropopause and decrease just below.
+The sum of advection and vertical turbulence (Fig.~\ref{fig:stab-48-72}e) indicates that the increase of $N^2$ observed in the 17-18-km layer and inside of the 80-km radius cannot be attributed to these processes, since the sum of these two terms provided forcing for destabilization.
+Instead, radiation (Fig.~\ref{fig:stab-48-72}d), provided the forcing for stabilization in this region.
+Outside of the 80-km radius, both advection (Fig.~\ref{fig:stab-48-72}b) and vertical turbulence (Fig.~\ref{fig:stab-48-72}c) provided forcing for stabilization near the 18-km level.
+The sum of the two terms indicates increasing $N^2$ near the 18-km level everywhere outside of the 80-km radius, but this stabilization is slightly weaker in the 90-120-km radial band than the observed value.
+The addition of radiation (Fig.~\ref{fig:stab-48-72}f) provides the extra forcing for stabilization required to account for the observed increase in $N^2$.
+Outside of the 120-km radius, the region of radiative forcing for stabilization slopes downward, and the increase in $N^2$ observed near 18 km can be explained entirely by a combination of advection and vertical turbulence.
+The layer of decreasing $N^@$ observed near 17 km was forced primarily by vertical turbulence and radiation.
+Within most of this region, advection provided strong forcing for stabilization, but this forcing was outweighed by the negative $N^@$ tendencies induced by a combination of vertical turbulence and radiation.
 
   \section{Discussion}
+
+  \subsection{The role of advection}
+
+Advection played an important role in the tropopause-layer $N^2$ evolution at all stages of intensification.
+To investigate the advective processes more closely, the individual contributions of horizontal and vertical advection are shown for all three time periods in Figs.
+\ref{fig:adv-00-24}-\ref{fig:adv-48-72}, along with the corresponding time-mean velocities and $\theta$.
+In each of the three time periods, the $N^2$ tendencies due to the two advective components exhibit strong cancellation, consistent with flow that is nearly isentropic.
+There are, however, some regions in which flow crosses $\theta$ surfaces; this flow accounts for all non-zero $N^2$ tendencies due to advection in the budget analyses.
+
+  \paragraph{0-24 hours}
+During the first day of the simulation, horizontal advection (Fig. \ref{fig:adv-00-24}a) generally forced a decrease in $N^2$ below 17 km and an increase in $N^2$ above.
+The mean radial velocity during this period (Fig.
+\ref{fig:adv-00-24}c) reveals a region of outflow at and below 17 km and near-zero radial velocity above, with a layer of strong vertical wind shear straddling the tropopause.
+The slight downward slope with radius of the $\theta$ surfaces near the tropopause (meaning that $\theta$ increases with radius) implies that the outflow in this layer locally acted to decrease $\theta$.
+This negative $\theta$ tendency must decrease with height within the region of strong vertical wind shear and approach zero as the radial velocity diminishes to zero near 17 km.
+These tendencies thus yielded an increase in the vertical gradient of $\theta$ above 17 km, which implies an increase in $N^2$, as was seen in Fig. \ref{fig:adv-00-24}a.
+Note that although the radial gradient of $\theta$ was stronger in the 15-16-km layer than it was closer to the tropopause, the vertical shear of the radial wind was much smaller there, yielding a smaller $N^2$ tendency due to horizontal advection.
+
+Notably, there existed strong $N^2$ tendencies due to horizontal advection inside of the 30-km radius even though the mean radial velocity in that region was near zero.
+Close examination of the radial velocity at each output time step reveals the presence of inward-propagating waves in the lower stratosphere.
+These waves amplified upon reaching r=0 and forced strong but highly transient $\theta$ tendencies due to advective processes.
+Thus, although the radial velocity perturbations associated with these waves averaged out to zero, the non-linear effect of these waves on the $N^2$ field remained.
+
+The $N^2$ tendencies forced by horizontal advection were completely canceled out by vertical advective tendencies (Fig. \ref{fig:adv-00-24}b).
+As was seen in Fig.
+\ref{fig:stab-00-24}b, the sum of the two terms yielded a layer of increasing $N^2$ below 17 km and decreasing $N^2$ above, meaning that vertical advective processes dominated the $N^2$ tendency during the initial spin-up period.
 
@@
 \begin{figure*}[ht]
-\centerline{\includegraphics[width=39pc]{figures/u.png}}
-\caption{Radial velocity (m s\textsuperscript{-1}; filled contours), potential temperature (K; thick black contours), and cold point tropopause height (orange lines) averaged over (a) 0-24 hours, (b) 24-48 hours, and (c) 48-72 hours.}
-\label{fig:u}
+\centerline{\includegraphics[width=39pc]{figures/h000-h024-adv.png}}
+\caption{The contribution to the change in $N^2$ over the 0-24-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 hr)\textsuperscript{-1}) by (a) horizontal advection and (b) vertical advection.
+(c) The radial velocity (m s\textsuperscript{-1}; filled contours), potential temperature (K; thick black contours), and cold-point tropopause height (orange line) averaged over the 0-24-hour period.
+(d) The vertical velocity (cm s\textsuperscript{-1}; filled contours), potential temperature (K; thick black contours), and cold-point tropopause height (orange line) averaged over the 0-24-hour period.}
+\label{fig:adv-00-24}
+\end{figure*}
+
+%FIGURE 8%
+%\begin{figure*}[ht]
+%\centerline{\includegraphics[width=39pc]{figures/u.png}}
+%\caption{Radial velocity (m s\textsuperscript{-1}; filled contours), potential temperature (K; thick black contours), and cold point tropopause height (orange lines) averaged over (a) 0-24 hours, (b) 24-48 hours, and (c) 48-72 hours.}
+%\label{fig:u}
+%\end{figure*}
+
+%FIGURE 9%
+\begin{figure*}[ht]
+\centerline{\includegraphics[width=39pc]{figures/h024-h048-adv.png}}
+\caption{As in Fig. \ref{fig:adv-00-24}, but for the 24-48-hour period.}
+\label{fig:adv-24-48}
 \end{figure*}
@@
 %FIGURE 9%
+%\begin{figure*}[ht]
+%\centerline{\includegraphics[width=39pc]{figures/w.png}}
+%\caption{Vertical velocity (cm s\textsuperscript{-1}; filled contours), potential temperature (K; thick black contours), and cold point tropopause height (orange lines) averaged over (a) 0-24 hours, (b) 24-48 hours, and (c) 48-72 hours.}
+%\label{fig:w}
+%\end{figure*}
+
+%FIGURE 10%
 \begin{figure*}[ht]
-\centerline{\includegraphics[width=39pc]{figures/w.png}}
-\caption{Vertical velocity (cm s\textsuperscript{-1}; filled contours), potential temperature (K; thick black contours), and cold point tropopause height (orange lines) averaged over (a) 0-24 hours, (b) 24-48 hours, and (c) 48-72 hours.}
-\label{fig:w}
+\centerline{\includegraphics[width=39pc]{figures/h048-h072-adv.png}}
+\caption{As in Fig. \ref{fig:adv-00-24}, but for the 48-72-hour period.}
+\label{fig:adv-48-72}
 \end{figure*}
 
-%FIGURE 10%
+%FIGURE 11%
 \begin{figure*}[ht]
@@
 
-%FIGURE 11%
+%FIGURE 12%
 \begin{figure*}[ht]
@@
 
-%FIGURE 12%
+%FIGURE 13%
 \begin{figure*}[ht]
@@
 \caption{Vertical eddy diffusivity (m\textsuperscript{2} s\textsuperscript{-2}; filled contours), cold point tropopause height (cyan lines), and radial velocity (m s\textsuperscript{-1}; thick black lines) averaged over (a) 0-24 hours, (b) 24-48 hours, and (c) 48-72 hours.}
-\label{fig:radten}
+\label{fig:diff}
 \end{figure*}

### 2018-02-14 paper.tex
Added to Discussion section and removed 0-24-hour period from Role of Advection subsection.

@@
 
-\title{Tropopause Evolution in a Rapidly Intensifying Tropical Cyclone: A Static Stability Budget Analysis}
+\title{Tropopause Evolution in a Rapidly Intensifying Tropical Cyclone: A Static Stability Budget Analysis in an Idealized, Axisymmetric Framework}
 
@@
 Each term on the right-hand side of Eq. \ref{eq:dthetadt} represents a $\theta$ budget variable, each of which is output directly by the model every minute.
-HADV and VADV are the radial and vertical advective tendencies, HTURB and VTURB are the radial and vertical tendencies from the turbulence parameterization, MP is the tendency from the microphysics scheme, RAD is the tendency from the radiation scheme, and DISS is the tendency due to turbulent dissipation.
+HADV and VADV are the radial and vertical advective tendencies\footnote{These terms include the tendencies due to diffusion that are implicit in the fifth-order advection scheme.}, HTURB and VTURB are the radial and vertical tendencies from the turbulence parameterization, MP is the tendency from the microphysics scheme, RAD is the tendency from the radiation scheme, and DISS is the tendency due to turbulent dissipation.
 This equation neglects Rayleigh damping, since this term is zero everywhere below 25 km, and the analysis domain does not extend to that level.
@@
 The layer of decreasing $N^@$ observed near 17 km was forced primarily by vertical turbulence and radiation.
-Within most of this region, advection provided strong forcing for stabilization, but this forcing was outweighed by the negative $N^@$ tendencies induced by a combination of vertical turbulence and radiation.
+Within most of this region, advection provided strong forcing for stabilization, but this forcing was outweighed by the negative $N^2$ tendencies induced by a combination of vertical turbulence and radiation.
 
@@
 
-  \paragraph{0-24 hours}
-During the first day of the simulation, horizontal advection (Fig. \ref{fig:adv-00-24}a) generally forced a decrease in $N^2$ below 17 km and an increase in $N^2$ above.
-The mean radial velocity during this period (Fig.
+Some insight gan be gained by considering the vertical gradient of the advective $\theta$ tendency:
+   \begin{equation} \label{eq:advtend}
+   \left(\frac{\partial}{\partial z}\frac{\partial \theta}{\partial t}\right)_{adv} = -u\frac{\partial}{\partial r}\frac{\partial \theta}{\partial z}-w\frac{\partial}{\partial z}\frac{\partial \theta}{\partial z}-\frac{\partial u}{\partial z}\frac{\partial \theta}{\partial r}-\frac{\partial w}{\partial z}\frac{\partial \theta}{\partial z}.
+   \end{equation}
+
+The first two terms on the right-hand side of Eq.
+\ref{eq:advtend} represent advection of static stability by the radial and vertical wind, respectively.
+The third and fourth terms represent, respectively, the tilting of isentropes in the presence of vertical wind shear, and the spreading or compaction of isentropes through divergence of the vertical wind.
+Each of these terms plays a part in the $N^2$ evolution in every day of the simulation; in the subsequent sub-sections, we will focus on the RI period and the quasi-steady-state period after RI.
+
+%  \paragraph{0-24 hours}
+%During the first day of the simulation, horizontal advection (Fig. \ref{fig:adv-00-24}a) generally forced a decrease in $N^2$ below 17 km and an increase in $N^2$ above.
+%The mean radial velocity during this period (Fig.
 \ref{fig:adv-00-24}c) reveals a region of outflow at and below 17 km and near-zero radial velocity above, with a layer of strong vertical wind shear straddling the tropopause.
-The slight downward slope with radius of the $\theta$ surfaces near the tropopause (meaning that $\theta$ increases with radius) implies that the outflow in this layer locally acted to decrease $\theta$.
-This negative $\theta$ tendency must decrease with height within the region of strong vertical wind shear and approach zero as the radial velocity diminishes to zero near 17 km.
-These tendencies thus yielded an increase in the vertical gradient of $\theta$ above 17 km, which implies an increase in $N^2$, as was seen in Fig. \ref{fig:adv-00-24}a.
-Note that although the radial gradient of $\theta$ was stronger in the 15-16-km layer than it was closer to the tropopause, the vertical shear of the radial wind was much smaller there, yielding a smaller $N^2$ tendency due to horizontal advection.
+%The slight downward slope with radius of the $\theta$ surfaces near the tropopause (i.e.
+$\partial\theta/\partial r > 0$), together with strong vertical wind shear ($\partial u/\partial z < 0$) in this layer, acts to force an increase in the vertical gradient of $\theta$ above 17 km through the third term on the right-hand side of Eq.
+\ref{eq:advtend}.
+%This negative $\theta$ tendency must decrease with height within the region of strong vertical wind shear and approach zero as the radial velocity diminishes to zero near 17 km.
+%These tendencies thus yielded an increase in the vertical gradient of $\theta$ above 17 km, which implies an increase in $N^2$, as was seen in Fig. \ref{fig:adv-00-24}a.
+%Note that although the radial gradient of $\theta$ was stronger in the 15-16-km layer than it was closer to the tropopause, the vertical shear of the radial wind was much smaller there, yielding a smaller $N^2$ tendency due to horizontal advection.
+%
+%Notably, there existed strong $N^2$ tendencies due to horizontal advection inside of the 30-km radius even though the mean radial velocity in that region was near zero.
+%Close examination of the radial velocity at each output time step reveals the presence of inward-propagating waves in the lower stratosphere.
+%These waves amplified upon reaching r=0 and forced strong but highly transient $\theta$ tendencies due to advective processes.
+%Thus, although the radial velocity perturbations associated with these waves averaged out to zero, the non-linear effect of these waves on the $N^2$ field remained.
+%
+%The $N^2$ tendencies forced by horizontal advection were completely canceled out by vertical advective tendencies (Fig. \ref{fig:adv-00-24}b).
+%As was seen in Fig.
+\ref{fig:stab-00-24}b, the sum of the two terms yielded a layer of increasing $N^2$ below 17 km and decreasing $N^2$ above, meaning that vertical advective processes dominated the $N^2$ tendency during the initial spin-up period.
+%Most of the upper troposphere contained mean ascent during this time, with the magnitude of the ascent decreasing with height.
+%This decrease in upward motion with height forces a convergence of isentropic surfaces, which implies a positive $N^2$ tendency in this region, as was observed in Fig. \ref{fig:adv-00-24}b.
+%Some weak descent at and just above the tropopause, meanwhile, forces a slight divergence of isentropes in the 17-18-km layer and a concomitant decrease in $N^2$.
+%Surprisingly, the 0-20-km radius was characterized by mean ascent, even up to the 21-km level.
+%Inward-propagating waves, upon reaching r=0, induced dipoles of strong upward and downward vertical motion.
+%For reasons that remain unclear, the regions of ascent tended to last longer than the regions of subsidence induced by these waves, which is responsible for the dominance of ascent in the mean.
+%In this region of mean ascent, changes in the vertical gradint of mean vertical velocity are responsible for alternating regions of positive and negative $N^2$ tendencies.
+%
+%HOVMOLLER OF w IN THE LOWER STRATOSPHERE??
 
-Notably, there existed strong $N^2$ tendencies due to horizontal advection inside of the 30-km radius even though the mean radial velocity in that region was near zero.
-Close examination of the radial velocity at each output time step reveals the presence of inward-propagating waves in the lower stratosphere.
-These waves amplified upon reaching r=0 and forced strong but highly transient $\theta$ tendencies due to advective processes.
-Thus, although the radial velocity perturbations associated with these waves averaged out to zero, the non-linear effect of these waves on the $N^2$ field remained.
-
-The $N^2$ tendencies forced by horizontal advection were completely canceled out by vertical advective tendencies (Fig. \ref{fig:adv-00-24}b).
-As was seen in Fig.
-\ref{fig:stab-00-24}b, the sum of the two terms yielded a layer of increasing $N^2$ below 17 km and decreasing $N^2$ above, meaning that vertical advective processes dominated the $N^2$ tendency during the initial spin-up period.
+   \paragraph{RI period: 24-48 hours}
+During the RI period, strong radial and vertical circulations developed near the tropopause, which forced high-magnitude $N^2$ tendencies due to advection (Fig. \ref{fig:adv-24-48}a,b).
+A layer of strong outflow developed at and below the tropopause during this period, with the outflow maximum curving from the 14-km level at the 45-km radius to just below the 16-km level at the 180-km radius (Fig.
+\ref{fig:adv-24-48c}).
 
@@
 \caption{Twenty-four-hour averages of squared Brunt-V{\"a}is{\"a}l{\"a} frequency (10\textsuperscript{-4} s\textsuperscript{-2}) over the first four days of the simulation.
-Orange lines represent the cold-point tropopause determined by the mean temperature field over the same time periods.}
+Orange lines represent the cold-point tropopause averaged over the same time periods.}
 \label{fig:n2-24hr-avgs}
@@
 \begin{figure*}[ht]
-\centerline{\includegraphics[width=39pc]{figures/qtot.png}}
-\caption{Total condensate mixing ratio (g kg\textsuperscript{-1}) and cold point tropopause height (orange lines) averaged over (a) 0-24 hours, (b) 24-48 hours, and (c) 48-72 hours.}
-\label{fig:qtot}
+\centerline{\includegraphics[width=27pc]{figures/qi+radten.png}}
+\caption{Ice mixing ratio (g kg\textsuperscript{-1}) and cold point tropopause height (orange lines) averaged over (a) 0-24 hours, (c) 24-48 hours, and (e) 48-72 hours.
+Radiative heating rate (K hr\textsuperscript{-1}) and cold point tropopause height (orange lines) averaged over (b) 0-24 hours, (d) 24-48 hours, and (f) 48-72 hours.}
+\label{fig:qi+radten}
 \end{figure*}
@@
 %FIGURE 12%
-\begin{figure*}[ht]
-\centerline{\includegraphics[width=39pc]{figures/radten.png}}
-\caption{Radiative heating rate (K hr\textsuperscript{-1}) and cold point tropopause height (orange lines) averaged over (a) 0-24 hours, (b) 24-48 hours, and (c) 48-72 hours.}
-\label{fig:radten}
-\end{figure*}
-
-%FIGURE 13%
 \begin{figure*}[ht]

### 2018-02-20 paper.tex
Some changes to figure captions and started writing appendix.

@@
 High-altitude dropsonde observations taken during the Tropical Cyclone Intensity (TCI) experiment captured this RI in unprecedented detail \citep{DoyleTCI}.
-These observations revealed remarkable changes in the structure of the cold-point tropopause and upper-level static stability as the storm intensified \citep{DuranMolinari2018}.
+These observations revealed dramatic changes in the structure of the cold-point tropopause and upper-level static stability as the storm intensified \citep{DuranMolinari2018}.
 
@@
 Their results are consistent with the evolution observed over the inner core of Hurricane Patricia, in which the tropopause height increased and the tropopause temperature warmed throughout RI \citep{DuranMolinari2018}.
-The simulations of \cite{OhnoSatoh2015} suggested that the development of an upper-level warm core within the eye acted to decrease the static stability near the tropopause.
-Although the mechanisms that drive this static stability evolution have not been examined explicitly, the potential temperature ($\theta$) budget analysis of \cite{SternZhang2013} examined the development of the TC warm core.
-They found that radial and vertical advection both play important roles in warm core development throughout RI, with subgrid-scale diffusion becoming particularly important during the later stage of RI.
+
+The idealized simulations of \cite{OhnoSatoh2015} suggested that the development of an upper-level warm core near the TC storm center acted to decrease the static stability near the tropopause.
+Although the mechanisms that drive this static stability evolution have not been examined explicitly, \cite{SternZhang2013} described the development of the TC warm core using a potential temperature ($\theta$) budget analysis.
+They found that radial and vertical advection both played important roles in warm core development throughout RI, and subgrid-scale diffusion became particularly important during the later stage of RI.
+To our knowledge, the only paper that has examined the static stability evolution in a TC is KEPERT ET AL ##########################################
 
@@
 
-Advection played an important role in the tropopause-layer $N^2$ evolution at all stages of intensification.
-To investigate the advective processes more closely, the individual contributions of horizontal and vertical advection are shown for all three time periods in Figs.
-\ref{fig:adv-00-24}-\ref{fig:adv-48-72}, along with the corresponding time-mean velocities and $\theta$.
-In each of the three time periods, the $N^2$ tendencies due to the two advective components exhibit strong cancellation, consistent with flow that is nearly isentropic.
-There are, however, some regions in which flow crosses $\theta$ surfaces; this flow accounts for all non-zero $N^2$ tendencies due to advection in the budget analyses.
+Advection played an important role in the tropopause-layer $N^2$ evolution at all stages of intensification, but for brevity, this section will focus only on the RI period.
+To investigate the advective processes more closely, the individual contributions of horizontal and vertical advection during the RI period are shown in Fig.
+\ref{fig:adv-24-48}, along with the corresponding time-mean radial and vertical velocities and $\theta$.
+The $N^2$ tendencies due to the two advective components (Fig. \ref{fig:adv-24-48}a,b) exhibit strong cancellation, consistent with flow that is nearly isentropic.
+There are, however, some regions in which flow crosses $\theta$ surfaces; this flow accounts for all non-zero $N^2$ tendencies due to advection previously seen in Fig. \ref{fig:stab-24-48}b.
 
-Some insight gan be gained by considering the vertical gradient of the advective $\theta$ tendency:
+Some insight can be gained by considering the time tendency of the vertical $\theta$ gradient due to advection:
    \begin{equation} \label{eq:advtend}
-   \left(\frac{\partial}{\partial z}\frac{\partial \theta}{\partial t}\right)_{adv} = -u\frac{\partial}{\partial r}\frac{\partial \theta}{\partial z}-w\frac{\partial}{\partial z}\frac{\partial \theta}{\partial z}-\frac{\partial u}{\partial z}\frac{\partial \theta}{\partial r}-\frac{\partial w}{\partial z}\frac{\partial \theta}{\partial z}.
+   \left(\frac{\partial}{\partial t}\frac{\partial \theta}{\partial z}\right)_{adv} = -u\frac{\partial}{\partial r}\frac{\partial \theta}{\partial z}-w\frac{\partial}{\partial z}\frac{\partial \theta}{\partial z}-\frac{\partial u}{\partial z}\frac{\partial \theta}{\partial r}-\frac{\partial w}{\partial z}\frac{\partial \theta}{\partial z}.
    \end{equation}
 
-The first two terms on the right-hand side of Eq.
-\ref{eq:advtend} represent advection of static stability by the radial and vertical wind, respectively.
+The first two terms on the right-hand side of Eq. \ref{eq:advtend} represent advection of static stability by the radial and vertical wind, respectively.
 The third and fourth terms represent, respectively, the tilting of isentropes in the presence of vertical wind shear, and the spreading or compaction of isentropes through divergence of the vertical wind.
-Each of these terms plays a part in the $N^2$ evolution in every day of the simulation; in the subsequent sub-sections, we will focus on the RI period and the quasi-steady-state period after RI.
 
@@
 
-   \paragraph{RI period: 24-48 hours}
+%   \paragraph{RI period: 24-48 hours}
 During the RI period, strong radial and vertical circulations developed near the tropopause, which forced high-magnitude $N^2$ tendencies due to advection (Fig. \ref{fig:adv-24-48}a,b).
-A layer of strong outflow developed at and below the tropopause during this period, with the outflow maximum curving from the 14-km level at the 45-km radius to just below the 16-km level at the 180-km radius (Fig.
-\ref{fig:adv-24-48c}).
+A layer of strong outflow developed at and below the tropopause during this period, with the outflow maximum (dashed cyan line) curving from the 14-km level at the 50-km radius to just below the 16-km level outside of the 80-km radius (Fig.
+\ref{fig:adv-24-48}c).
+The cyan line, by definition, represents the level at which the vertial gradient of radial velocity switched signs, with $\partial u/\partial z>0$ below the line and $\partial u/\partial z<0$ above.
+Notably, the $N^2$ tendency due to horizontal advection (Fig.
+\ref{fig:adv-24-48}a) also tended to switch signs very near this line, with stabilization below the outflow maximum and destabilization above.
+This suggests that vertical wind shear above and below the outflow maximum played an important role in the $N^2$ tendency during this time.
+Examination of the third term on the right-hand side of Eq.
+\ref{eq:advtend} reveals that tilting of isentropes within these shear layers contributed to the strong $N^2$ tendencies that flanked the outflow maximum.
+Outside of the eye and eyewall, isentropes generally sloped upward with radius, which means that $\theta$ decreased outward ($\partial \theta/\partial r<0$).
+Thus, wherever $\partial u/\partial z>0$, the tilting term forced an increase in $N^2$, and wherever $\partial u/\partial z<0$, the tilting term forced a decrease in $N^2$.
+This is precisely the structure seen in Fig. \ref{fig:adv-24-48}a, which suggests that the tilting term
+
+Meanwhile in the lower stratosphere, a thin layer of 2-4 m s\textsuperscript{-1} inflow developed a few hundred meters above the tropopause.
 
@@
 % Use \appendix if there is only one appendix.
-%\appendix
+\appendix
 
@@
 %% Appendix title is necessary! For appendix title:
-%\appendixtitle{}
+\appendixtitle{Sensitivity experiments}
+The simulations exhibited some sentivity to the initial thermodynamic profile and the prescribed vertical mixing length.
+Although the details of the intensification and the tropopause-layer $N^2$ evolution varied when these quantities were changed, the conclusions of the paper remain unchanged.
 
 %%% Appendix section numbering (note, skip \section and begin with \subsection)
-% \subsection{First primary heading}
+ \subsection{Sensitivity to the initial thermodynamic profile}
+A number of sensitivity experiments were conducted using a variety of initial soundings.
+Changing the initial temperature and humidity profiles affected the timing of the onset of organized deep convection and the rapidity of intensification.
+In all simulations, however, convection eventually penetrated to the tropopause, at which time vertical turbulence and radiation combined with advection to adjust the $N^2$ profile toward that which was observed in the control run.
+By the end of the RI period in every simulation, all three proesses were actively modifying the $N^2$ profile near the tropopause.
 
-% \subsubsection{First secondary heading}
+ \subsection{Sensitivity to the vertical mixing length}
+The extent of parameterized turbulent mixing is highly dependent on a prescribed length scale.
+Since there is no theoretical or observational guidance for the selection of this mixing length, the value used in the control run (100 m) is based on the sensitivity experiments of BRYAN 2012????
+Since the vertical eddy viscosity varies linearly with the vertical mixing length, prescribing a smaller mixing length produces smaller $\theta$ tendencies due to turbulence.
+Even with a mixing length on the low end of those tested by BRYAN 2012????, however, turbulence still plays a role in the tropopause-layer $N^2$ evolution.
+FIG #### shows the $N^2$ evolution in a simulation identical to the control run, except with a vertical mixing length of 50 m rather than 100 m.
+DESCRIPTION OF THE FIGURE
 
@@
 \centerline{\includegraphics[width=39pc]{figures/mod+bud+res.png}}
-\caption{Left panels: Twenty-four-hour changes in squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$; 10\textsuperscript{-4} s\textsuperscript{-2}) over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, (d) 72-96 hours.
-Middle Panels: The $N^2$ change over the same time periods computed using Eq.
-\ref{eq:budgetchange}.
+\caption{Left panels: Twenty-four-hour changes in squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$; 10\textsuperscript{-4} s\textsuperscript{-2}) over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours.
+Middle Panels: The $N^2$ change over the same time periods computed using Eqs. \ref{eq:dn2dt}-\ref{eq:budgetchange}, %together with Eqs. \ref{eq:dn2dt}, \ref{eq:dthetadt}.
 Right Panels: The budget residual over the same time periods, computed by subtracting the budget change (middle column) from the model change (left column).}
@@
 \centerline{\includegraphics[width=39pc]{figures/n2-24hr-avgs.png}}
-\caption{Twenty-four-hour averages of squared Brunt-V{\"a}is{\"a}l{\"a} frequency (10\textsuperscript{-4} s\textsuperscript{-2}) over the first four days of the simulation.
+\caption{Twenty-four-hour averages of squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$; 10\textsuperscript{-4} s\textsuperscript{-2}) over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours.
 Orange lines represent the cold-point tropopause averaged over the same time periods.}
@@
 \centerline{\includegraphics[width=19pc]{figures/AVG_budterms.png}}
-\caption{Time series of the contribution of each of the budget terms to the time tendency of the squared Brunt-V{\"a}is{\"a}l{\"a} frequency (N\textsuperscript{2}; 10\textsuperscript{-4} s\textsuperscript{-2}).
-For each budget term, the absolute value of the N\textsuperscript{2} tendency is averaged temporally over 1-hour periods (using output every minute), and spatially in a region extending from 0 to 200 km radius and 14 to 21 km altitude.}
+\caption{Time series of the contribution of each of the budget terms to the time tendency of the squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$; 10\textsuperscript{-4} s\textsuperscript{-2}).
+For each budget term, the absolute value of the $N^2$ tendency is averaged temporally over 1-hour periods (using output every minute), and spatially in a region extending from 0 to 200 km radius and 14 to 21 km altitude.}
 \label{fig:avgbudterms}
@@
 \centerline{\includegraphics[width=27pc]{figures/h000-h024-budgetterms.png}}
-\caption{(a) Total change in N\textsuperscript{2} over the 0-24-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 hr)\textsuperscript{-1}) and the contributions to that change from (b) the sum of horizontal and vertical advection, (c) vertical turbulence, (d) longwave and shortwave radiation, (e) the sum of horizontal advection, vertical advection, and vertical turublence, and (f) the sum of horizontal advection, vertical advection, vertical turbulence, and longwave and shortwave radiation.}
+\caption{(a) Total change in $N^2$ over the 0-24-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 hr)\textsuperscript{-1}) and the contributions to that change from (b) the sum of horizontal and vertical advection, (c) vertical turbulence, (d) longwave and shortwave radiation, (e) the sum of horizontal advection, vertical advection, and vertical turublence, and (f) the sum of horizontal advection, vertical advection, vertical turbulence, and longwave and shortwave radiation.}
 \label{fig:stab-00-24}
@@
 %FIGURE 8%
-\begin{figure*}[ht]
-\centerline{\includegraphics[width=39pc]{figures/h000-h024-adv.png}}
-\caption{The contribution to the change in $N^2$ over the 0-24-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 hr)\textsuperscript{-1}) by (a) horizontal advection and (b) vertical advection.
+%\begin{figure*}[ht]
+%\centerline{\includegraphics[width=39pc]{figures/h000-h024-adv.png}}
+%\caption{The contribution to the change in $N^2$ over the 0-24-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 hr)\textsuperscript{-1}) by (a) horizontal advection and (b) vertical advection.
 (c) The radial velocity (m s\textsuperscript{-1}; filled contours), potential temperature (K; thick black contours), and cold-point tropopause height (orange line) averaged over the 0-24-hour period.
 (d) The vertical velocity (cm s\textsuperscript{-1}; filled contours), potential temperature (K; thick black contours), and cold-point tropopause height (orange line) averaged over the 0-24-hour period.}
-\label{fig:adv-00-24}
-\end{figure*}
+%\label{fig:adv-00-24}
+%\end{figure*}
 
@@
 %\centerline{\includegraphics[width=39pc]{figures/u.png}}
-%\caption{Radial velocity (m s\textsuperscript{-1}; filled contours), potential temperature (K; thick black contours), and cold point tropopause height (orange lines) averaged over (a) 0-24 hours, (b) 24-48 hours, and (c) 48-72 hours.}
+%\caption{Radial velocity (m s\textsuperscript{-1}; filled contours), potential temperature (K; thick black contours), and cold-point tropopause height (orange lines) averaged over (a) 0-24 hours, (b) 24-48 hours, and (c) 48-72 hours.}
 %\label{fig:u}
@@
 
-%FIGURE 9%
+%FIGURE 8%
 \begin{figure*}[ht]
 \centerline{\includegraphics[width=39pc]{figures/h024-h048-adv.png}}
-\caption{As in Fig. \ref{fig:adv-00-24}, but for the 24-48-hour period.}
+\caption{The contribution to the change in $N^2$ over the 24-48-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 hr)\textsuperscript{-1}) by (a) horizontal advection and (b) vertical advection.
+(c) The radial velocity (m s\textsuperscript{-1}; filled contours), potential temperature (K; thick black contours), cold-point tropopause height (orange line), and level of maximum outflow (dashed cyan line) averaged over the 24-48-hour period.
+(d) The vertical velocity (cm s\textsuperscript{-1}; filled contours), potential temperature (K; thick black contours), and cold-point tropopause height (orange line) averaged over the 24-48-hour period.}
+%\caption{As in Fig. \ref{fig:adv-00-24}, but for the 24-48-hour period.}
 \label{fig:adv-24-48}
@@
 %\centerline{\includegraphics[width=39pc]{figures/w.png}}
-%\caption{Vertical velocity (cm s\textsuperscript{-1}; filled contours), potential temperature (K; thick black contours), and cold point tropopause height (orange lines) averaged over (a) 0-24 hours, (b) 24-48 hours, and (c) 48-72 hours.}
+%\caption{Vertical velocity (cm s\textsuperscript{-1}; filled contours), potential temperature (K; thick black contours), and cold-point tropopause height (orange lines) averaged over (a) 0-24 hours, (b) 24-48 hours, and (c) 48-72 hours.}
 %\label{fig:w}
@@
 %FIGURE 10%
-\begin{figure*}[ht]
-\centerline{\includegraphics[width=39pc]{figures/h048-h072-adv.png}}
-\caption{As in Fig. \ref{fig:adv-00-24}, but for the 48-72-hour period.}
-\label{fig:adv-48-72}
-\end{figure*}
+%\begin{figure*}[ht]
+%\centerline{\includegraphics[width=39pc]{figures/h048-h072-adv.png}}
+%\caption{As in Fig. \ref{fig:adv-00-24}, but for the 48-72-hour period.}
+%\label{fig:adv-48-72}
+%\end{figure*}
 
@@
 \centerline{\includegraphics[width=27pc]{figures/qi+radten.png}}
-\caption{Ice mixing ratio (g kg\textsuperscript{-1}) and cold point tropopause height (orange lines) averaged over (a) 0-24 hours, (c) 24-48 hours, and (e) 48-72 hours.
-Radiative heating rate (K hr\textsuperscript{-1}) and cold point tropopause height (orange lines) averaged over (b) 0-24 hours, (d) 24-48 hours, and (f) 48-72 hours.}
+\caption{Ice mixing ratio (g kg\textsuperscript{-1}) and cold-point tropopause height (orange lines) averaged over (a) 0-24 hours, (c) 24-48 hours, and (e) 48-72 hours.
+Radiative heating rate (K hr\textsuperscript{-1}) and cold-point tropopause height (orange lines) averaged over (b) 0-24 hours, (d) 24-48 hours, and (f) 48-72 hours.}
 \label{fig:qi+radten}
@@
 \centerline{\includegraphics[width=39pc]{figures/khvten.png}}
-\caption{Vertical eddy diffusivity (m\textsuperscript{2} s\textsuperscript{-2}; filled contours), cold point tropopause height (cyan lines), and radial velocity (m s\textsuperscript{-1}; thick black lines) averaged over (a) 0-24 hours, (b) 24-48 hours, and (c) 48-72 hours.}
+\caption{Vertical eddy diffusivity (m\textsuperscript{2} s\textsuperscript{-2}; filled contours), cold-point tropopause height (cyan lines), and radial velocity (m s\textsuperscript{-1}; thick black lines) averaged over (a) 0-24 hours, (b) 24-48 hours, and (c) 48-72 hours.}
 \label{fig:diff}

### 2018-02-20 paper.tex
Wrote a complete draft of the Abstract.

@@
 
-\abstract{We have some cool results!}
+\abstract{Idealized simulations of an intense axisymmetric tropical cyclone (TC) reveal considerable changes in the tropopause-layer static stability during rapid intensification (RI).
+During RI, static stability near the tropopause decreased over the eye.
+This destabilization was associated with a rise in the cold-point tropopause height by up to 4 km at the storm center.
+Outside of the eye, meanwhile, the cold-point tropopause remained near its initial level, and the static stability increased considerably in the layer immediately above it.
+These results are consistent with recent observations collected during the RI of Hurricane Patricia (2015).
+
+A static stability budget analysis reveals that horizontal and vertical advection both contribute to the static stability tendencies at all times throughout the upper troposphere and lower stratosphere.
+Advection is particularly important within the eye, where is acts to destabilize the layer near and above the cold-point tropopause.
+Outside of the eye, a strong radial-vertical circulation develops during RI, with outflow below the tropopause and inflow above.
+Turbulence induced by strong vertical wind shear above and below the upper-tropospheric outflow maximum provides forcing for both stabilization and destabilization in the tropopause layer.
+Meanwhile, as organized convection reaches the tropopause, radiative heating tendencies at the top of the cirrus canopy act to destabilize the upper troposphere and stabilize the lower stratosphere.
+This combination of turbulent mixing and radiative heating plays an important role in the development of the strong stable layer immediately above the cold-point tropopause.
+
+The resuts suggest that turbulence and radiation both play fundamental roles in the upper-level static stability evolution of TCs.
+The conclusions are robust to changes in the initial thermodynamic profile and prescribed vertical mixing length within a reasonable range of values.}
 
@@
 
-The idealized simulations of \cite{OhnoSatoh2015} suggested that the development of an upper-level warm core near the TC storm center acted to decrease the static stability near the tropopause.
+Idealized simulations of a TC analyzed by \cite{OhnoSatoh2015} suggested that the development of an upper-level warm core near the TC storm center acted to decrease the static stability near the tropopause (see their Fig.
+).
 Although the mechanisms that drive this static stability evolution have not been examined explicitly, \cite{SternZhang2013} described the development of the TC warm core using a potential temperature ($\theta$) budget analysis.
 They found that radial and vertical advection both played important roles in warm core development throughout RI, and subgrid-scale diffusion became particularly important during the later stage of RI.
-To our knowledge, the only paper that has examined the static stability evolution in a TC is KEPERT ET AL ##########################################
-
-The analysis herein is based upon that of \cite{SternZhang2013}, except using a static stability budget similar to that of \cite{Kepertetal2016} rather than a $\theta$ budget.
+To our knowledge, the only paper that has examined explicitly the static stability evolution in a modeled TC is \cite{Kepertetal2016}, but their analysis was limited to the boundary layer.
+The analysis herein is based upon that of \cite{SternZhang2013}, except using a static stability budget similar to that of \cite{Kepertetal2016}, with a focus on the upper troposphere and lower stratosphere.
 
@@
 Each term on the right-hand side of Eq. \ref{eq:dthetadt} represents a $\theta$ budget variable, each of which is output directly by the model every minute.
-HADV and VADV are the radial and vertical advective tendencies\footnote{These terms include the tendencies due to diffusion that are implicit in the fifth-order advection scheme.}, HTURB and VTURB are the radial and vertical tendencies from the turbulence parameterization, MP is the tendency from the microphysics scheme, RAD is the tendency from the radiation scheme, and DISS is the tendency due to turbulent dissipation.
+HADV and VADV are the radial and vertical advective tendencies\footnote{These terms include the tendencies due to the diffusion that is implicit in the fifth-order advection scheme.}, HTURB and VTURB are the radial and vertical tendencies from the turbulence parameterization, MP is the tendency from the microphysics scheme, RAD is the tendency from the radiation scheme, and DISS is the tendency due to turbulent dissipation.
 This equation neglects Rayleigh damping, since this term is zero everywhere below 25 km, and the analysis domain does not extend to that level.
@@
 For this figure, each of the budget terms is computed using the method described in Section 3, except with 1-hour averaging intervals instead of 24-hour intervals.
-The absolute values of these tendencies are then averaged over a radius-height domain surrounding the tropopause and plotted as a time series\footnote{It will be seeen in subsequent figures that each of the terms contributes both positively and negatively to the N\textsuperscript{2} tendency within the analysis domain.
+The absolute values of these tendencies are then averaged over a radius-height domain surrounding the tropopause and plotted as a time series\footnote{It will be seeen in subsequent figures that each of the terms contributes both positively and negatively to the $N^2$ tendency within the analysis domain.
 Thus, taking an average over the domain tends to wash out the positive and negative contributions.
@@
  \subsection{Sensitivity to the vertical mixing length}
-The extent of parameterized turbulent mixing is highly dependent on a prescribed length scale.
-Since there is no theoretical or observational guidance for the selection of this mixing length, the value used in the control run (100 m) is based on the sensitivity experiments of BRYAN 2012????
+The intensity of parameterized turbulence is highly dependent on a prescribed length scale.
+Since there is no theoretical or observational guidance for the selection of this mixing length, the value used in the control run (100 m) is based on the sensitivity experiments of \cite{Bryan2012}.
 Since the vertical eddy viscosity varies linearly with the vertical mixing length, prescribing a smaller mixing length produces smaller $\theta$ tendencies due to turbulence.
-Even with a mixing length on the low end of those tested by BRYAN 2012????, however, turbulence still plays a role in the tropopause-layer $N^2$ evolution.
-FIG #### shows the $N^2$ evolution in a simulation identical to the control run, except with a vertical mixing length of 50 m rather than 100 m.
+Even with a mixing length on the low end of those tested by \cite{Bryan2012}, however, turbulence still plays a role in the tropopause-layer $N^2$ evolution.
+FIG shows the $N^2$ evolution in a simulation identical to the control run, except with a vertical mixing length of 50 m rather than 100 m.
 DESCRIPTION OF THE FIGURE

### 2018-02-21 paper.tex
Modified the Abstract and expanded the advection section of the Discussion.

@@
 
-\abstract{Idealized simulations of an intense axisymmetric tropical cyclone (TC) reveal considerable changes in the tropopause-layer static stability during rapid intensification (RI).
-During RI, static stability near the tropopause decreased over the eye.
-This destabilization was associated with a rise in the cold-point tropopause height by up to 4 km at the storm center.
-Outside of the eye, meanwhile, the cold-point tropopause remained near its initial level, and the static stability increased considerably in the layer immediately above it.
-These results are consistent with recent observations collected during the RI of Hurricane Patricia (2015).
-
-A static stability budget analysis reveals that horizontal and vertical advection both contribute to the static stability tendencies at all times throughout the upper troposphere and lower stratosphere.
-Advection is particularly important within the eye, where is acts to destabilize the layer near and above the cold-point tropopause.
-Outside of the eye, a strong radial-vertical circulation develops during RI, with outflow below the tropopause and inflow above.
-Turbulence induced by strong vertical wind shear above and below the upper-tropospheric outflow maximum provides forcing for both stabilization and destabilization in the tropopause layer.
-Meanwhile, as organized convection reaches the tropopause, radiative heating tendencies at the top of the cirrus canopy act to destabilize the upper troposphere and stabilize the lower stratosphere.
-This combination of turbulent mixing and radiative heating plays an important role in the development of the strong stable layer immediately above the cold-point tropopause.
-
-The resuts suggest that turbulence and radiation both play fundamental roles in the upper-level static stability evolution of TCs.
-The conclusions are robust to changes in the initial thermodynamic profile and prescribed vertical mixing length within a reasonable range of values.}
+\abstract{Large changes in tropopause-layer static stability are observed during the rapid intensification (RI) of an idealized, axisymmetric tropical cyclone (TC).
+Over the eye, static stability near the tropopause decreases and the cold-point tropopause height rises by up to 4 km at the storm center.
+Outside of the eye, static stability immediately above the cold-point tropopause increases considerably, and the tropopause remains near its initial level.
+A budget analysis reveals that advection contributes to the static stability tendencies at all times throughout the upper troposphere and lower stratosphere.
+Advection is particularly important within the eye, where it acts to destabilize the layer near and above the cold-point tropopause.
+Outside of the eye, a radial-vertical circulation develops during RI, with strong outflow below the tropopause and weak inflow above.
+Vertical wind shear above and below the upper-tropospheric outflow maximum induces turbulence, which provides forcing for both destabilization and stabilization in the tropopause layer.
+Meanwhile, as organized convection reaches the tropopause, radiative heating tendencies at the top of the cirrus canopy generally act to destabilize the upper troposphere and stabilize the lower stratosphere.
+Turbulent mixing and radiative heating combine to play an important role in the development of the strong stable layer immediately above the cold-point tropopause during RI.
+The results suggest that turbulence and radiation, alongside advection, play fundamental roles in the upper-level static stability evolution of TCs.}
+%The conclusions are robust to changes in the initial thermodynamic profile and prescribed vertical mixing length within a reasonable range of values.}
 
@@
 Outside of the 120-km radius, the region of radiative forcing for stabilization slopes downward, and the increase in $N^2$ observed near 18 km can be explained entirely by a combination of advection and vertical turbulence.
-The layer of decreasing $N^@$ observed near 17 km was forced primarily by vertical turbulence and radiation.
+The layer of decreasing $N^2$ observed near 17 km was forced primarily by vertical turbulence and radiation.
 Within most of this region, advection provided strong forcing for stabilization, but this forcing was outweighed by the negative $N^2$ tendencies induced by a combination of vertical turbulence and radiation.
@@
 
-Advection played an important role in the tropopause-layer $N^2$ evolution at all stages of intensification, but for brevity, this section will focus only on the RI period.
+Advection played an important role in the tropopause-layer $N^2$ evolution at all stages of intensification, but for brevity, this section will focus only on the RI (24-48-hour) period.
 To investigate the advective processes more closely, the individual contributions of horizontal and vertical advection during the RI period are shown in Fig.
@@
 The first two terms on the right-hand side of Eq. \ref{eq:advtend} represent advection of static stability by the radial and vertical wind, respectively.
+These terms cannot create a maximum or a minimum; they only act to rearrange the static stability field.
+Since the goal of this analysis is to understand the processes responsible for the creation of maxima and minima in $N^2$, these two terms will not be examined.
 The third and fourth terms represent, respectively, the tilting of isentropes in the presence of vertical wind shear, and the spreading or compaction of isentropes through divergence of the vertical wind.
+Since these terms involve gradients of velocities, they can create or eliminate local maxima or minima in static stability. This section will focus on these two terms.
 
@@
 Outside of the eye and eyewall, isentropes generally sloped upward with radius, which means that $\theta$ decreased outward ($\partial \theta/\partial r<0$).
-Thus, wherever $\partial u/\partial z>0$, the tilting term forced an increase in $N^2$, and wherever $\partial u/\partial z<0$, the tilting term forced a decrease in $N^2$.
-This is precisely the structure seen in Fig. \ref{fig:adv-24-48}a, which suggests that the tilting term
+Thus, wherever $\partial u/\partial z>0$, the tilting term must force an increase in $N^2$, and wherever $\partial u/\partial z<0$, the tilting term must force a decrease in $N^2$.
+This is precisely the structure seen in Fig. \ref{fig:adv-24-48}a, which suggests that the tilting term might be important near the outflow jet.
 
-Meanwhile in the lower stratosphere, a thin layer of 2-4 m s\textsuperscript{-1} inflow developed a few hundred meters above the tropopause.
+Advection of $N^2$ by the radial wind (first term on the right-hand side of Eq. \ref{eq:advtend}) also acts within the outflow jet.
+For example, horizontal advection provided forcing for destabilization at the 16-km level almost everywhere inside of the 140-km radius.
+Outside of this radius near 16 km, however, existed a region of forcing for stabilization.
+This switch in signs was a consequence of a reversal of the radial graident of mean $N^2$ near the 140-km radius (Fig. \ref{fig:n2-24hr-avgs}b).
+Inside of that radius, $(\partial/\partial r)(\partial \theta/\partial z) > 0$ and $u > 0$, which corresponds to forcing for destabilization in Eq.
+\ref{eq:advtend}; outside of that radius $(\partial/\partial r)(\partial \theta/\partial z) < 0$ and $u > 0$, which corresponds to forcing for stabilization.
+
+The relative imporance of the first and third terms on the right-hand side of Eq.
+\ref{eq:advtend} is difficult to ascertain, but the structure of the mean radial velocity, $\theta$, and $N^2$ fields suggests that both terms are contributing within the outflow layer.
+
+Meanwhile in the lower stratosphere, a thin layer of 2-4 m s\textsuperscript{-1} inflow developed a few hundred meters above the tropopause, similar to that which was observed in Hurricane Patricia (2015; \citeauthor{DuranMolinari2018} \citeyear{DuranMolinari2018}).
+Since the isentropes in this layer slope slightly upward with radius (i.e. $\partial \theta/\partial r < 0$), this inflow acts to import lower $\theta$ air to inner radii.
+There also existed strong radial gradients of mean $N^2$ in this layer during this time (Fig. \ref{fig:n2-24hr-avgs}b), so the inflow layer must have acted to rearrange $N^2$.
+This rearrangement could not have been responsible for the overall increase in $N^2$ during this period, however.
+If horizontal advection contributed to the strengthening stable layer just above the tropopause, it must have been through the tilting term.
+The inflow maximum near the 18-km level represents the level at which the sign of $\partial u/\partial z$ reverses, with $\partial u/\partial z < 0$ below and $\partial u/\partial z > 0$ above.
+The third term on the right-hand side of Eq.
+\ref{eq:advtend} suggests that the tilting of isentropes should act to destabilize the layer below the inflow maximum and stabilize the layer above, and this was observed in Fig.
+\ref{fig:adv-24-48}a.
 

### 2018-02-21 paper.tex
Began and finished most of the radiative heating section of the Discussion.

@@
 
+  \subsection{The role of radiation}
+During the initial spin-up period (0-24 hours; \ref{fig:qi+radten}a), convection was not deep enough to deposit large quantities of ice near the tropopause in the mean.
+Due to the lack of ice particles, the radiative heating tendencies during this period (\ref{fig:qi+radten}b) were relatively small and confined to the region above a few particularly strong convective towers.
+During RI (24-48 hours; \ref{fig:qu+radten}b), the eyewall updraft strengthened and a radially-extensive cirrus canopy developed near the tropopause.
+The enhanced vertical gradient of ice mixing ratio at the top of the cirrus canopy induced strong diurnal-mean radiative cooling near the tropopause (\ref{fig:qi+radten}d).
+This cooling exceeded 0.6 K h\textsuperscript{-1} in some places and sloped downward from the lower stratosphere into the upper troposphere, following the top of the cirrus canopy.
+A small radiative warming maximum also appeared outside of the 140-km radius below this region of cooling.
+These results broadly agree with those of \citeauthor{buetal} (\citeyear{buetal}; see their Fig.
+11a), whose CM1 simulations 0.3 K net diurnally-averaged radiative cooling at the top of the cirrus canopy and radiative warming within the cloud maximized near the 200-km radius.
+The broad region of radiative cooling acted to destabilize the layer below the cooling maximum and stabilize the layer above, which can be seen in Fig. \ref{fig:h024-048}d.
+The small area of net radiative heating outside of the 140-km radius enhanced the destabilization in this region and produced a thin layer of stabilization in the 15-16-km layer.
+
+At steady-state strong radiative cooling remained near the tropopause at inner radii, sloping downward with the top of the cirrus canopy to below the tropopause at outer radii.
+Cooling rates exceeded 1 K h\textsuperscript{-1} just above the tropopause between the 30 and 70 km radii.
+These cooling rates exceeded those observed by \cite{buetal}, a discrepancy that is likely a consequence of their larger vertical grid spacing (625 m) compared to that used here (250 m), with a possible a contribution from differing radiation schemes\footnote{\cite{buetal} employed the NASA-Goddard radiation scheme for their CM1 simulations, whereas RRTMG is used in the present paper.
+They did use the RRTMG radiation scheme alongside the Thompson microphysics parameterization for their HWRF simulations, but those simulations also produced smaller radiative tendencies than those seen here (see their Fig.
+5a), suggesting that vertical resolution accounts for most of the difference in radiative heating rates.}
+
+  \subsection{The role of turbulent mixing}
+
 Radiative heating and turbulence viscosity figures?
@@
 Diurnal variability of of static stability in the upper troposphere is an interesting area of future research.
+
+Bu et al.
+did not see a lower-stratospheric inflow layer, likely due to their 625-m grid spacing.
+If we want to resolve properly the radiative cooling at the top of the cirrus canopy and the lower-stratospheric inflow layer, we must have sufficient vertical resolution in the tropopause layer.
+Our 100-m grid spacing here may not even be sufficient, given how shallow the layer is!
 
@@
 \centerline{\includegraphics[width=27pc]{figures/h000-h024-budgetterms.png}}
-\caption{(a) Total change in $N^2$ over the 0-24-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 hr)\textsuperscript{-1}) and the contributions to that change from (b) the sum of horizontal and vertical advection, (c) vertical turbulence, (d) longwave and shortwave radiation, (e) the sum of horizontal advection, vertical advection, and vertical turublence, and (f) the sum of horizontal advection, vertical advection, vertical turbulence, and longwave and shortwave radiation.}
+\caption{(a) Total change in $N^2$ over the 0-24-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 h)\textsuperscript{-1}) and the contributions to that change from (b) the sum of horizontal and vertical advection, (c) vertical turbulence, (d) longwave and shortwave radiation, (e) the sum of horizontal advection, vertical advection, and vertical turublence, and (f) the sum of horizontal advection, vertical advection, vertical turbulence, and longwave and shortwave radiation.}
 \label{fig:stab-00-24}
@@
 \centerline{\includegraphics[width=39pc]{figures/h024-h048-adv.png}}
-\caption{The contribution to the change in $N^2$ over the 24-48-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 hr)\textsuperscript{-1}) by (a) horizontal advection and (b) vertical advection.
+\caption{The contribution to the change in $N^2$ over the 24-48-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 h)\textsuperscript{-1}) by (a) horizontal advection and (b) vertical advection.
 (c) The radial velocity (m s\textsuperscript{-1}; filled contours), potential temperature (K; thick black contours), cold-point tropopause height (orange line), and level of maximum outflow (dashed cyan line) averaged over the 24-48-hour period.
@@
 \caption{Ice mixing ratio (g kg\textsuperscript{-1}) and cold-point tropopause height (orange lines) averaged over (a) 0-24 hours, (c) 24-48 hours, and (e) 48-72 hours.
-Radiative heating rate (K hr\textsuperscript{-1}) and cold-point tropopause height (orange lines) averaged over (b) 0-24 hours, (d) 24-48 hours, and (f) 48-72 hours.}
+Radiative heating rate (K h\textsuperscript{-1}) and cold-point tropopause height (orange lines) averaged over (b) 0-24 hours, (d) 24-48 hours, and (f) 48-72 hours.}
 \label{fig:qi+radten}

### 2018-02-21 paper.tex
Finished radiation section of Discussion and started turbulent mixing section.

@@
 During the initial spin-up period (0-24 hours; \ref{fig:qi+radten}a), convection was not deep enough to deposit large quantities of ice near the tropopause in the mean.
-Due to the lack of ice particles, the radiative heating tendencies during this period (\ref{fig:qi+radten}b) were relatively small and confined to the region above a few particularly strong convective towers.
-During RI (24-48 hours; \ref{fig:qu+radten}b), the eyewall updraft strengthened and a radially-extensive cirrus canopy developed near the tropopause.
+Due to the lack of ice particles, the radiative heating tendencies during this period (Fig.
+\ref{fig:qi+radten}b) were relatively small and confined to the region above a few particularly strong convective towers.
+During RI (24-48 hours; Fig. \ref{fig:qi+radten}b), the eyewall updraft strengthened and a radially-extensive cirrus canopy developed near the tropopause.
 The enhanced vertical gradient of ice mixing ratio at the top of the cirrus canopy induced strong diurnal-mean radiative cooling near the tropopause (\ref{fig:qi+radten}d).
@@
 11a), whose CM1 simulations 0.3 K net diurnally-averaged radiative cooling at the top of the cirrus canopy and radiative warming within the cloud maximized near the 200-km radius.
-The broad region of radiative cooling acted to destabilize the layer below the cooling maximum and stabilize the layer above, which can be seen in Fig. \ref{fig:h024-048}d.
+The broad region of radiative cooling acted to destabilize the layer below the cooling maximum and stabilize the layer above, which can be seen in Fig. \ref{fig:stab-24-48}d.
 The small area of net radiative heating outside of the 140-km radius enhanced the destabilization in this region and produced a thin layer of stabilization in the 15-16-km layer.
 
-At steady-state strong radiative cooling remained near the tropopause at inner radii, sloping downward with the top of the cirrus canopy to below the tropopause at outer radii.
-Cooling rates exceeded 1 K h\textsuperscript{-1} just above the tropopause between the 30 and 70 km radii.
+After the TC's RI period completed (48-72 hours; Fig.
+\ref{fig:qi+radten}f), strong radiative cooling remained near the tropopause at inner radii, sloping downward with the top of the cirrus canopy to below the tropopause at outer radii.
+Cooling rates exceeded 1 K h\textsuperscript{-1} just above the tropopause between the 30- and 70-km radii.
 These cooling rates exceeded those observed by \cite{buetal}, a discrepancy that is likely a consequence of their larger vertical grid spacing (625 m) compared to that used here (250 m), with a possible a contribution from differing radiation schemes\footnote{\cite{buetal} employed the NASA-Goddard radiation scheme for their CM1 simulations, whereas RRTMG is used in the present paper.
 They did use the RRTMG radiation scheme alongside the Thompson microphysics parameterization for their HWRF simulations, but those simulations also produced smaller radiative tendencies than those seen here (see their Fig.
-5a), suggesting that vertical resolution accounts for most of the difference in radiative heating rates.}
+5a), suggesting that vertical resolution accounts for most of the difference in radiative heating rates.}.
+Time-mean radiative warming spread from 30- to 160-km radius within the cirrus canopy.
+The existence of radiative cooling overlying radiative warming in this region led to radiatively-forced destabilization at and below the tropopause, as was observed in Fig. \ref{fig:stab-48-72}d.
+Below the warming layer existed a region of forcing for stabilization, while a much stronger region of forcing for destabilization existed above the cooling maximum in the lower stratosphere.
+
+The results herein suggest that radiative heating tendencies played an important role in destabilizing the upper troposphere and stabilizing the lower stratosphere after the cirrus canopy developed and persisted during and after RI.
 
@@
 
-Radiative heating and turbulence viscosity figures?
-
-Discuss how turbulence increases the static stability in some regions --> vertical gradients of turblence intensity.
+Although vertical turbulence always acts to eliminate vertical gradients of $\theta$, this adjustment toward a neutral state only occurs where the mixing takes place.
+If turbulence occurs in a stably-stratified layer, it will act to decrease $\theta$ at the top of the layer and increase it below.
+Just above and just below the mixed layer, however, the $\theta$ profile remains undisturbed.
+Consequently, although turbulent mixing acts to decrease $\partial \theta/\partial z$ in the layer in which it is occurring, it actually increases $\partial \theta/\partial z$ just below and just above the layer.
+These vertical gradients of turbulent mixing are quite important, particularly on the flanks of the upper-tropospheric outflow jet.
 
@@
 Our 100-m grid spacing here may not even be sufficient, given how shallow the layer is!
+Did my no-CRF simulation show a lower-stratospheric inflow layer?? If not, that's strong evidence supporting the role of radiation in producing the desceding inflow layer above the tropopause.
 
@@
 We also thank Jeffrey Kepert, Robert Fovell, and Erika Navarro for helpful conversations related to this work.
-ADD GRANT NUMBER
+This research was supported by NSF Grant \#1636799.
 

### 2018-02-22 paper.tex
Added reference to vertically-implicit, Crank-Nicholson diffusion scheme and made a few minor changes throughout.

@@
 This formulation allows for realistically-large horizontal mixing lengths near the hurricane's inner core, consistent with the results of \cite{Bryan2012}, while not over-representing horizontal turbulence in convection at outer radii.
-Vertical turbulence was parameterized using the formulation of \citeauthor{MarkowskiBryan2016} (\citeyear{MarkowskiBryan2016}, their Eq. 6), using an asymptotic vertical mixing length of 100 m.
+Vertical turbulence was parameterized using the formulation of \citeauthor{MarkowskiBryan2016} (\citeyear{MarkowskiBryan2016}, their Eq.
+6), using an asymptotic vertical mixing length of 100 m and a vertically implicit Crank-Nicholson scheme.
 A Rayleigh damping layer was applied outside of the 2900-km radius and above the 25-km level to prevent spurious gravity wave reflection at the model boundaries.
@@
 \centerline{\includegraphics[width=39pc]{figures/mod+bud+res.png}}
-\caption{Left panels: Twenty-four-hour changes in squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$; 10\textsuperscript{-4} s\textsuperscript{-2}) over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours.
+\caption{Left panels: Twenty-four-hour changes in squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$; 10\textsuperscript{-4} s\textsuperscript{-2}) over (top row) 0-24 hours, (middle row) 24-48 hours, (bottom row) 48-72 hours.
 Middle Panels: The $N^2$ change over the same time periods computed using Eqs. \ref{eq:dn2dt}-\ref{eq:budgetchange}, %together with Eqs. \ref{eq:dn2dt}, \ref{eq:dthetadt}.

### 2018-02-27 paper.tex
Added Appendix figures and expanded a lot of the Discussion and some of the Appendix.

@@
 Over the eye, static stability near the tropopause decreases and the cold-point tropopause height rises by up to 4 km at the storm center.
-Outside of the eye, static stability immediately above the cold-point tropopause increases considerably, and the tropopause remains near its initial level.
-A budget analysis reveals that advection contributes to the static stability tendencies at all times throughout the upper troposphere and lower stratosphere.
+Outside of the eye, static stability increases considerably just above the cold-point tropopause, and the tropopause remains near its initial level.\\
+\indent A budget analysis reveals that advection contributes to the static stability tendencies at all times throughout the upper troposphere and lower stratosphere.
 Advection is particularly important within the eye, where it acts to destabilize the layer near and above the cold-point tropopause.
@@
 
-Idealized simulations of a TC analyzed by \cite{OhnoSatoh2015} suggested that the development of an upper-level warm core near the TC storm center acted to decrease the static stability near the tropopause (see their Fig.
-).
+Idealized simulations of a TC analyzed by \cite{OhnoSatoh2015} suggested that the development of an upper-level warm core near the TC storm center acted to decrease the static stability near the tropopause (compare their Figs.
+9,10).
 Although the mechanisms that drive this static stability evolution have not been examined explicitly, \cite{SternZhang2013} described the development of the TC warm core using a potential temperature ($\theta$) budget analysis.
@@
 The remaining two processes - microphysics and dissipative heating (Fig.~\ref{fig:avgbudterms}, orange and light green lines, respectively) - lie atop one another near zero.
+Although the latent heating term can be quite large in the eyewall region, it is negligible everywhere outside of the eyewall, as are the effects of dissipative heating.
 These time series indicate that, at all times, three budget terms dominate the tropopause-layer static stability tendency: advection, vertical turbulence, and radiation.
@@
 Although these tendencies extended out to the 200-km radius, they were particularly pronounced at innermost radii.
-A comparison of the contributions of advection (Fig.~\ref{fig:stab-00-24}b), vertical turbulence (Fig.~\ref{fig:stab-00-24}c), and radiation (Fig.~\ref{fig:stab-00-24}d) reveals that advection is primarily responsible for the change in static stability during this period.
-Although vertical turbulence acts in opposition to advection (i.e.
-it acts to stabilize regions that advection acts to destabilize), the magnitude of the advective tendencies is larger, particularly at the innermost radii.
-The sum of advection and vertical turbulence (Fig.~\ref{fig:stab-00-24}e) almost exactly replicates the static stability tendencies above 17 km.
-Radiative tendencies (Fig.~\ref{fig:stab-00-24}d) act to destabilize the layer below about 16 km and stabilize the layer between 16 and 17 km.
+A comparison of the contributions of advection (Fig.~\ref{fig:stab-00-24}b), vertical turbulence (Fig.~\ref{fig:stab-00-24}c), and radiation (Fig.~\ref{fig:stab-00-24}d) reveals that advection was primarily responsible for the change in static stability during this period.
+Although vertical turbulence acted in opposition to advection (i.e.
+it acted to stabilize regions that advection acted to destabilize), the magnitude of the advective tendencies was larger, particularly at the innermost radii.
+The sum of advection and vertical turbulence (Fig.~\ref{fig:stab-00-24}e) almost exactly replicated the static stability tendencies above 17 km.
+Radiative tendencies. meanwhile, (Fig.~\ref{fig:stab-00-24}d) acted to destabilize the layer below about 16 km and stabilize the layer between 16 and 17 km.
 The sum of advection, vertical turbulence, and radiation (Fig.~\ref{fig:stab-00-24}f) reproduces the total change in $N^2$ almost exactly.
-
-...Explain this in the context of radial and vertical velocities...
-...See Stern and Zhang, Page 84, Section 3d...
-...Add mention of total condensate and radiative heating tendencies as it relates to statbility tendency due to rad...
 
@@
 
-TWO REGIONS WHERE Panel (f) differs from panel (a): 30-60 km radial band below 16 km, which is actually canceled out by a vertical gradient of latent heating, and the thin region of strong stabilization between 15-17.5 km near r=30 km, which is canceled out by horizontal turbulence.
+The sum of advection, vertical turbulence, and radiation (Fig.
+\ref{fig:stab-24-48}f) once again closely follows the observed $N^2$ variability, except in portions of the eyewall where the neglect of latent heating and horizontal turbulence introduces some differences.
 
@@
 The $N^2$ tendencies due to the two advective components (Fig. \ref{fig:adv-24-48}a,b) exhibit strong cancellation, consistent with flow that is nearly isentropic.
-There are, however, some regions in which flow crosses $\theta$ surfaces; this flow accounts for all non-zero $N^2$ tendencies due to advection previously seen in Fig. \ref{fig:stab-24-48}b.
+There are, however, many regions in which flow crosses $\theta$ surfaces; this flow accounts for all non-zero $N^2$ tendencies due to advection previously seen in Fig. \ref{fig:stab-24-48}b.
+
+%The eye was characterized by stabilization below 16 km and destabilization in the 16-17-km and 18-19-km layers.
+%Comparing Fig.
+\ref{fig:stab-24-48}b to \ref{fig:adv-24-48}a,b reveals that the stabilization below 16 km in the eye was forced by vertical advection, as was the region of destabilization in the 18-19-km layer.
+%Meanwhile, the destabilization that occurred in the 16-17-km layer was forced by a combination and radial and vertial advection.
+
+%Outside of the eye, the layer below about 15.5 km was dominated by stabilization.
+%Outside of the 50-km radius, horizontal advection provided the forcing for this stabilization, while inside of the 50-km radius, vertical advection was responsible.
+%Above this layer existed a layer of destabilization near the 16-km level, which was forced by horizontal advection.
 
@@
 These terms cannot create a maximum or a minimum; they only act to rearrange the static stability field.
-Since the goal of this analysis is to understand the processes responsible for the creation of maxima and minima in $N^2$, these two terms will not be examined.
+%Since the goal of this analysis is to understand the processes responsible for the creation of maxima and minima in $N^2$, these two terms will not be examined.
 The third and fourth terms represent, respectively, the tilting of isentropes in the presence of vertical wind shear, and the spreading or compaction of isentropes through divergence of the vertical wind.
-Since these terms involve gradients of velocities, they can create or eliminate local maxima or minima in static stability. This section will focus on these two terms.
+Since these terms involve gradients of velocities, they can create or eliminate local maxima or minima in static stability.% This section will focus on these two terms.
 
@@
 \ref{fig:adv-24-48}c).
-The cyan line, by definition, represents the level at which the vertial gradient of radial velocity switched signs, with $\partial u/\partial z>0$ below the line and $\partial u/\partial z<0$ above.
-Notably, the $N^2$ tendency due to horizontal advection (Fig.
-\ref{fig:adv-24-48}a) also tended to switch signs very near this line, with stabilization below the outflow maximum and destabilization above.
-This suggests that vertical wind shear above and below the outflow maximum played an important role in the $N^2$ tendency during this time.
+The cyan line, by definition, represents the level at which the vertical gradient of radial velocity switched signs, with $\partial u/\partial z>0$ below the line and $\partial u/\partial z<0$ above.
+Notably, the $N^2$ tendency due to horizontal advection (Fig. \ref{fig:adv-24-48}a) also tended to switch signs at this line, with stabilization below the outflow maximum and destabilization above.
+%This suggests that vertical wind shear above and below the outflow maximum played an important role in the $N^2$ tendency during this time.
 Examination of the third term on the right-hand side of Eq.
-\ref{eq:advtend} reveals that tilting of isentropes within these shear layers contributed to the strong $N^2$ tendencies that flanked the outflow maximum.
+\ref{eq:advtend} suggests that tilting of isentropes within these shear layers contributed to the strong $N^2$ tendencies that flanked the outflow maximum.
 Outside of the eye and eyewall, isentropes generally sloped upward with radius, which means that $\theta$ decreased outward ($\partial \theta/\partial r<0$).
-Thus, wherever $\partial u/\partial z>0$, the tilting term must force an increase in $N^2$, and wherever $\partial u/\partial z<0$, the tilting term must force a decrease in $N^2$.
-This is precisely the structure seen in Fig. \ref{fig:adv-24-48}a, which suggests that the tilting term might be important near the outflow jet.
+Thus, wherever $\partial u/\partial z>0$, the tilting term must force an increase in $N^2$, and wherever $\partial u/\partial z<0$, the tilting term must force a decrease in $N^2$, which is precisely the structure seen in Fig.
+\ref{fig:adv-24-48}a.
 
-Advection of $N^2$ by the radial wind (first term on the right-hand side of Eq. \ref{eq:advtend}) also acts within the outflow jet.
+Advection of $N^2$ by the radial wind (first term on the right-hand side of Eq. \ref{eq:advtend}) also acted within the outflow jet.
 For example, horizontal advection provided forcing for destabilization at the 16-km level almost everywhere inside of the 140-km radius.
@@
 
-Meanwhile in the lower stratosphere, a thin layer of 2-4 m s\textsuperscript{-1} inflow developed a few hundred meters above the tropopause, similar to that which was observed in Hurricane Patricia (2015; \citeauthor{DuranMolinari2018} \citeyear{DuranMolinari2018}).
-Since the isentropes in this layer slope slightly upward with radius (i.e. $\partial \theta/\partial r < 0$), this inflow acts to import lower $\theta$ air to inner radii.
-There also existed strong radial gradients of mean $N^2$ in this layer during this time (Fig. \ref{fig:n2-24hr-avgs}b), so the inflow layer must have acted to rearrange $N^2$.
-This rearrangement could not have been responsible for the overall increase in $N^2$ during this period, however.
-If horizontal advection contributed to the strengthening stable layer just above the tropopause, it must have been through the tilting term.
-The inflow maximum near the 18-km level represents the level at which the sign of $\partial u/\partial z$ reverses, with $\partial u/\partial z < 0$ below and $\partial u/\partial z > 0$ above.
-The third term on the right-hand side of Eq.
-\ref{eq:advtend} suggests that the tilting of isentropes should act to destabilize the layer below the inflow maximum and stabilize the layer above, and this was observed in Fig.
+Meanwhile in the lower stratosphere, a thin layer of 2-4 m s\textsuperscript{-1} inflow developed a few hundred meters above the tropopause, similar to that which was observed in Hurricane Patricia (2015; \citeauthor{DuranMolinari2018} \citeyear{DuranMolinari2018}) and in previous modeling studies (e.g.
+\citeauthor{OhnoSatoh2015} \citeyear{OhnoSatoh2015}; \citeauthor{Kieuetal} \citeyear{Kieuetal}).
+Since the isentropes in this layer sloped slightly upward with radius (i.e. $\partial \theta/\partial r < 0$), this inflow acted to import lower $\theta$ air from outer radii to inner radii.
+%There also existed strong radial gradients of mean $N^2$ in this layer during this time (Fig. \ref{fig:n2-24hr-avgs}b), so the inflow layer must have acted to rearrange $N^2$.
+%This rearrangement could not have been responsible for the overall increase in $N^2$ during this period, however.
+%If horizontal advection contributed to the strengthening stable layer just above the tropopause, it must have been through the tilting term.
+%The inflow maximum near the 18-km level represents the level at which the sign of $\partial u/\partial z$ reverses, with $\partial u/\partial z < 0$ below and $\partial u/\partial z > 0$ above.
+%The third term on the right-hand side of Eq.
+\ref{eq:advtend} shows that the tilting of isentropes should act to destabilize the layer below the inflow maximum and stabilize the layer above, which is precisely what was observed outside of the 80-km radius in Fig.
 \ref{fig:adv-24-48}a.
+Decreasing $\theta$ near the inflow maximum acted to destabilize the layer below the inflow maximum and stabilize the layer above (Fig. \ref{fig:adv-24-48}a).
+
+Vertical advection also played an important role in the tropopause-layer static stability evolution.
+Within the eye, subsidence dominated below 17 km, while mean ascent existed near the storm center above 17 km\footnote{Close examination of the model output revealed that this mean ascent was forced by the interaction of inward-propagating waves with the boundary at r=0.
+When a wave reached r=0, a dipole of vertical velocity resulted, with ascent above and subsidence below.
+For reasons that remain unclear, the regions of ascent were more persistent than the regions of subsidence, which resulted in mean ascent near r=0 in the lower stratosphere.}.
+Although the magnitude of the subsidence was larger at lower altitudes, $\partial \theta/\partial z$ was smaller there.
+Because $\partial \theta/\partial z$ was smaller, the subsidence at lower levels could not accomplish as much warming as the subsidence at higher levels in the eye, consistent with the results of \cite{SternZhang2013}.
+
+Outside of the eye, ascent dominated the troposphere, while a 1.5-km-deep layer of descent existed immediately above the tropopause.
+This region of descent
 
@@
 Cooling rates exceeded 1 K h\textsuperscript{-1} just above the tropopause between the 30- and 70-km radii.
-These cooling rates exceeded those observed by \cite{buetal}, a discrepancy that is likely a consequence of their larger vertical grid spacing (625 m) compared to that used here (250 m), with a possible a contribution from differing radiation schemes\footnote{\cite{buetal} employed the NASA-Goddard radiation scheme for their CM1 simulations, whereas RRTMG is used in the present paper.
-They did use the RRTMG radiation scheme alongside the Thompson microphysics parameterization for their HWRF simulations, but those simulations also produced smaller radiative tendencies than those seen here (see their Fig.
-5a), suggesting that vertical resolution accounts for most of the difference in radiative heating rates.}.
+These cooling rates exceeded those observed by \cite{buetal}, a discrepancy that is a consequence of their larger vertical grid spacing (625 m) compared to that used here (250 m), along with a contribution from differing radiation schemes\footnote{\cite{buetal} employed the NASA-Goddard radiation scheme for their CM1 simulations, whereas RRTMG is used in the present paper.
+A simulation using NASA-Goddard radiation and 625-m vertical grid spacing produced maximum radiative cooling rates of 0.3 K h\textsuperscript{-1}, which agrees with the rates in \cite{buetal}.
+Another simulation using 625-m vertical grid spacing and RRTMG radiation produced cooling rates of up to 0.6 K h\textsuperscript{-1}.}.
 Time-mean radiative warming spread from 30- to 160-km radius within the cirrus canopy.
@@
 
+%An interesting result of the budget analysis was that turbulent mixing acted to increase static stability in some regions of the storm.
 Although vertical turbulence always acts to eliminate vertical gradients of $\theta$, this adjustment toward a neutral state only occurs where the mixing takes place.
@@
 
-Diurnal variability of of static stability in the upper troposphere is an interesting area of future research.
+Fig. \ref{fig:diff} reveals that two distinct maxima of vertial eddy diffusivity developed in the tropopause layer as the storm intensified.
+Comparison of these turbulent regions to the $N^2$ tendencies in Figs.
+\ref{fig:stab-24-48}c and \ref{fig:stab-48-72}c reveals that the layers in which vertical eddy diffusivity maximized corresponded to layers of destabiliztion due to vertical turbulence.
+Just outside of these layers, however, vertical turbulence acted to increase $N^2$.
+The large vertical gradient of vertical eddy diffusivity near the tropopause played an important role in developing the lower-stratospheric stable layer during RI.
+This supports the hypothesized role of turbulence in setting the outflow-layer $\theta$ stratification in \cite{RotunnoEmanuel}.
 
-Bu et al.
-did not see a lower-stratospheric inflow layer, likely due to their 625-m grid spacing.
-If we want to resolve properly the radiative cooling at the top of the cirrus canopy and the lower-stratospheric inflow layer, we must have sufficient vertical resolution in the tropopause layer.
-Our 100-m grid spacing here may not even be sufficient, given how shallow the layer is!
-Did my no-CRF simulation show a lower-stratospheric inflow layer?? If not, that's strong evidence supporting the role of radiation in producing the desceding inflow layer above the tropopause.
+  \section{Conclusions}
+
+The simulated $N^2$ evolution shown herein closely matched that observed during the RI of Hurricane Patricia (2015).
+Three processes dominated the $N^2$ variability in the upper troposphere and lower stratosphere: advection, radiation, and vertical turbulence.
+Radiation and vertical turbulence played particularly important roles in developing the strong $N^2$ maximum just above the cold-point tropopause during RI.
+Since these two processes are parameterized, and radiation closely depends on yet another parameterized process (microphysics), the tropopause-layer $N^2$ variability could be quite sensitive to the assumptions inherent to parameterizations used.
+A number of sensitivity experiments revealed that the details of the $N^2$ evolution were sensitive to the selection of the microphysics scheme, the vertical turbulence length scale, and the vertical grid spacing.
+All of the simulations, however, did develop an elevated tropopause over the eye that corresponded to decreasing static stability and, outside of the eye, an $N^2$ maximum immediately above the tropopause.
+
+Comparison to previous work revealed that small vertical grid spacing is necessary to resolve the shallow layer of radiative cooling at the top of the cirrus canopy.
+Increasing the vertical grid spacing decreased the magnitude of the radiative cooling and produced a weaker, but deeper lower-stratospheric stable layer.
+
+In this paper, all of the variables were averaged over a full diurnal cycle to eliminate the effects of diurnal variability and isolate the overall storm evolution.
+Diurnal variations in static stability near the tropopause are potentially of interest with respect to the tropical cyclone diurnal cycle, however, and will be the subject of future work.
 
@@
 
+As an example, 24-hour averages of $N^2$ are plotted in Fig.
+\ref{fig:n2-1000km} for a simulation that was identical to that used in this paper, except the initial sounding was determined by averaging every grid point within 1000 km of TC Patricia's storm center at 18 UTC 21 October 2015 instead of averaging only within the 100-km radius.
+Although the lower-stratospheric stable layer developed more slowly and was weaker than that shown in Fig.
+\ref{fig:n2-24hr-avgs}, the overall evolution was quite similar and the same budget terms dominated the static stability evolution (not shown).
+
  \subsection{Sensitivity to the vertical mixing length}
-The intensity of parameterized turbulence is highly dependent on a prescribed length scale.
-Since there is no theoretical or observational guidance for the selection of this mixing length, the value used in the control run (100 m) is based on the sensitivity experiments of \cite{Bryan2012}.
-Since the vertical eddy viscosity varies linearly with the vertical mixing length, prescribing a smaller mixing length produces smaller $\theta$ tendencies due to turbulence.
-Even with a mixing length on the low end of those tested by \cite{Bryan2012}, however, turbulence still plays a role in the tropopause-layer $N^2$ evolution.
-FIG shows the $N^2$ evolution in a simulation identical to the control run, except with a vertical mixing length of 50 m rather than 100 m.
-DESCRIPTION OF THE FIGURE
+The rate of turbulent mixing in the Smagorinsky scheme used herein is highly dependent on a prescribed length scale.
+The vertical mixing length used in this paper (100 m) was based on the sensitivity experiments of \cite{Bryan2012}.
+Prescribing a smaller mixing length produces smaller $\theta$ tendencies due to turbulence, but even with a mixing length on the low end of those tested by \cite{Bryan2012}, turbulence still played an important role in the tropopause-layer $N^2$ evolution.
+Fig.
+\ref{fig:turb-50m} shows the 24-hour-averaged contributions of turbulent mixing to the $N^2$ evolution from a simulation identical to that used in this paper, except with a vertical mixing length of 50 m.
+At all times, vertical turbulence still played an important role in the tropopause-layer static stability evolution, particularly during the latter stages of RI (48-72 hours).
 
@@
 \begin{figure*}[ht]
-\centerline{\includegraphics[width=27pc]{figures/h000-h024-budgetterms.png}}
+\centerline{\includegraphics[width=39pc]{figures/h000-h024-budgetterms.png}}
+\end{figure*}
+\begin{figure}
 \caption{(a) Total change in $N^2$ over the 0-24-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 h)\textsuperscript{-1}) and the contributions to that change from (b) the sum of horizontal and vertical advection, (c) vertical turbulence, (d) longwave and shortwave radiation, (e) the sum of horizontal advection, vertical advection, and vertical turublence, and (f) the sum of horizontal advection, vertical advection, vertical turbulence, and longwave and shortwave radiation.}
 \label{fig:stab-00-24}
-\end{figure*}
+\end{figure}
 
@@
 \begin{figure*}[ht]
-\centerline{\includegraphics[width=27pc]{figures/h024-h048-budgetterms.png}}
+\centerline{\includegraphics[width=39pc]{figures/h024-h048-budgetterms.png}}
 \caption{As in Fig.~\ref{fig:stab-00-24}, but for the 24-48-hour period.}
@@
 \begin{figure*}[ht]
-\centerline{\includegraphics[width=27pc]{figures/h048-h072-budgetterms.png}}
+\centerline{\includegraphics[width=39pc]{figures/h048-h072-budgetterms.png}}
 \caption{As in Fig.~\ref{fig:stab-00-24}, but for the 48-72-hour period.}
@@
 
-%FIGURE 11%
+%FIGURE 9%
 \begin{figure*}[ht]
-\centerline{\includegraphics[width=27pc]{figures/qi+radten.png}}
+\centerline{\includegraphics[width=39pc]{figures/qi+radten.png}}
+\end{figure*}
+\begin{figure}
 \caption{Ice mixing ratio (g kg\textsuperscript{-1}) and cold-point tropopause height (orange lines) averaged over (a) 0-24 hours, (c) 24-48 hours, and (e) 48-72 hours.
@@
 \label{fig:qi+radten}
-\end{figure*}
+\end{figure}
 
-%FIGURE 12%
+%FIGURE 10%
 \begin{figure*}[ht]
@@
 \label{fig:diff}
+\end{figure*}
+
+%FIGURE A1%
+\begin{figure*}[ht]
+\centerline{\includegraphics[width=39pc]{figures/n2-1000km.png}}
+\appendcaption{A1}{Twenty-four-hour averages of squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$; 10\textsuperscript{-4} s\textsuperscript{-2}) over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, and (d) 72-96 hours for the simulation described in Appendix Aa.
+Orange lines represent the cold-point tropopause averged over the same time periods.}
+\label{fig:n2-1000km}
+\end{figure*}
+
+%FIGURE A2%
+\begin{figure*}[ht]
+\centerline{\includegraphics[width=39pc]{figures/turb-50m.png}}
+\appendcaption{A2}{The contribution of vertical turbulence to the $N^2$ variability (10\textsuperscript{-4} s\textsuperscript{-2} (24 h)\textsuperscript{-1}) averaged over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, and (d) 72-96 hours for the simulation described in Appendix Ab.}
+\label{fig:turb-50m}
 \end{figure*}

### 2018-02-28 paper.tex
FIRST DRAFT SENT TO JOHN

@@
 For simplicity, however, only Eq.
-\ref{eq:n2dry} will be employed for the budget computations herein\footnote{The validity of this approximation will be substantiated later in this section.}.
+\ref{eq:n2dry} will be employed for the budget computations \footnote{The validity of this approximation will be substantiated later in this section.}.
 
@@
 Each term on the right-hand side of Eq. \ref{eq:dthetadt} represents a $\theta$ budget variable, each of which is output directly by the model every minute.
-HADV and VADV are the radial and vertical advective tendencies\footnote{These terms include the tendencies due to the diffusion that is implicit in the fifth-order advection scheme.}, HTURB and VTURB are the radial and vertical tendencies from the turbulence parameterization, MP is the tendency from the microphysics scheme, RAD is the tendency from the radiation scheme, and DISS is the tendency due to turbulent dissipation.
+HADV and VADV are the radial and vertical advective tendencies\footnote{These terms include the tendencies due to implicit diffusion in the fifth-order finite differencing scheme.}, HTURB and VTURB are the tendencies from the horizontal and vertical turbulence parameterizations, MP is the tendency from the microphysics scheme, RAD is the tendency from the radiation scheme, and DISS is the tendency due to turbulent dissipation.
 This equation neglects Rayleigh damping, since this term is zero everywhere below 25 km, and the analysis domain does not extend to that level.
@@
 
-Eqs. \ref{eq:budgetchange}-\ref{eq:residual} are plotted for four consecutive 24-hour periods in Fig. \ref{fig:mod+bud+res}.
+Eqs. \ref{eq:budgetchange}-\ref{eq:residual} are plotted for three consecutive 24-hour periods in Fig. \ref{fig:mod+bud+res}.
 For this and all subsequent radial-vertical cross sections, a 1-2-1 smoother is applied once in the radial direction to eliminate $2\Delta r$ noise that appears in some of the raw model output and calculated fields.
@@
 Although the contribution from horizontal turbulence (Fig.~\ref{fig:avgbudterms}, purple line) becomes more important after 48 hours, it is confined to a very small region immediately surrounding the eyewall tangential velocity maximum (not shown), and is negligible throughout the rest of the tropopause layer.
-The remaining two processes - microphysics and dissipative heating (Fig.~\ref{fig:avgbudterms}, orange and light green lines, respectively) - lie atop one another near zero.
+The two remaining processes - microphysics and dissipative heating (Fig.~\ref{fig:avgbudterms}, orange and light green lines, respectively) - lie atop one another near zero.
 Although the latent heating term can be quite large in the eyewall region, it is negligible everywhere outside of the eyewall, as are the effects of dissipative heating.
-These time series indicate that, at all times, three budget terms dominate the tropopause-layer static stability tendency: advection, vertical turbulence, and radiation.
+
+The preceding analysis indicates that, at all times, three budget terms dominate the tropopause-layer static stability tendency: advection, vertical turbulence, and radiation.
 Variations in the magnitude and spatial structure of these terms drive the static stability changes depicted in Fig.~\ref{fig:mod+bud+res}; subsequent sections will focus on these variations and what causes them.
@@
 The sum of advection and vertical turbulence (Fig.~\ref{fig:stab-00-24}e) almost exactly replicated the static stability tendencies above 17 km.
-Radiative tendencies. meanwhile, (Fig.~\ref{fig:stab-00-24}d) acted to destabilize the layer below about 16 km and stabilize the layer between 16 and 17 km.
+Radiative tendencies, meanwhile, (Fig.~\ref{fig:stab-00-24}d) acted to destabilize the layer below about 16 km and stabilize the layer between 16 and 17 km.
 The sum of advection, vertical turbulence, and radiation (Fig.~\ref{fig:stab-00-24}f) reproduces the total change in $N^2$ almost exactly.
@@
 
-Some insight can be gained by considering the time tendency of the vertical $\theta$ gradient due to advection:
-   \begin{equation} \label{eq:advtend}
-   \left(\frac{\partial}{\partial t}\frac{\partial \theta}{\partial z}\right)_{adv} = -u\frac{\partial}{\partial r}\frac{\partial \theta}{\partial z}-w\frac{\partial}{\partial z}\frac{\partial \theta}{\partial z}-\frac{\partial u}{\partial z}\frac{\partial \theta}{\partial r}-\frac{\partial w}{\partial z}\frac{\partial \theta}{\partial z}.
-   \end{equation}
+%Some insight can be gained by considering the time tendency of the vertical $\theta$ gradient due to advection:
+%   \begin{equation} \label{eq:advtend}
+%   \left(\frac{\partial}{\partial t}\frac{\partial \theta}{\partial z}\right)_{adv} = -u\frac{\partial}{\partial r}\frac{\partial \theta}{\partial z}-w\frac{\partial}{\partial z}\frac{\partial \theta}{\partial z}-\frac{\partial u}{\partial z}\frac{\partial \theta}{\partial r}-\frac{\partial w}{\partial z}\frac{\partial \theta}{\partial z}.
+%   \end{equation}
 
-The first two terms on the right-hand side of Eq. \ref{eq:advtend} represent advection of static stability by the radial and vertical wind, respectively.
-These terms cannot create a maximum or a minimum; they only act to rearrange the static stability field.
+%The first two terms on the right-hand side of Eq. \ref{eq:advtend} represent advection of static stability by the radial and vertical wind, respectively.
+%These terms cannot create a maximum or a minimum; they only act to rearrange the static stability field.
 %Since the goal of this analysis is to understand the processes responsible for the creation of maxima and minima in $N^2$, these two terms will not be examined.
-The third and fourth terms represent, respectively, the tilting of isentropes in the presence of vertical wind shear, and the spreading or compaction of isentropes through divergence of the vertical wind.
-Since these terms involve gradients of velocities, they can create or eliminate local maxima or minima in static stability.% This section will focus on these two terms.
+%The third and fourth terms represent, respectively, the tilting of isentropes in the presence of vertical wind shear, and the spreading or compaction of isentropes through divergence of the vertical wind.
+%Since these terms involve gradients of velocities, they can create or eliminate local maxima or minima in static stability.% This section will focus on these two terms.
 
@@
 \ref{fig:adv-24-48}c).
-The cyan line, by definition, represents the level at which the vertical gradient of radial velocity switched signs, with $\partial u/\partial z>0$ below the line and $\partial u/\partial z<0$ above.
-Notably, the $N^2$ tendency due to horizontal advection (Fig. \ref{fig:adv-24-48}a) also tended to switch signs at this line, with stabilization below the outflow maximum and destabilization above.
+%The cyan line, by definition, represents the level at which the vertical gradient of radial velocity switched signs, with $\partial u/\partial z>0$ below the line and $\partial u/\partial z<0$ above.
+Notably, the $N^2$ tendency due to horizontal advection (Fig. \ref{fig:adv-24-48}a) tended to switch signs at this line, with stabilization below the outflow maximum and destabilization above.
 %This suggests that vertical wind shear above and below the outflow maximum played an important role in the $N^2$ tendency during this time.
-Examination of the third term on the right-hand side of Eq.
+%Examination of the third term on the right-hand side of Eq.
 \ref{eq:advtend} suggests that tilting of isentropes within these shear layers contributed to the strong $N^2$ tendencies that flanked the outflow maximum.
-Outside of the eye and eyewall, isentropes generally sloped upward with radius, which means that $\theta$ decreased outward ($\partial \theta/\partial r<0$).
-Thus, wherever $\partial u/\partial z>0$, the tilting term must force an increase in $N^2$, and wherever $\partial u/\partial z<0$, the tilting term must force a decrease in $N^2$, which is precisely the structure seen in Fig.
+Outside of the eye and eyewall, isentropes generally sloped upward with radius.
+Vertical wind shear acting on these upward-sloping isentropes should act to tilt them into the vertical above the outflow maximum, thereby decreasing $\partial \theta/\partial z$, and tilt them to be more horizontal below the outflow maximum, thereby increasing $\partial \theta/\partial z$.
+This mechanism is the same as that discussed in \cite{TrierSharman}, and is consistent with the change in sign of the $N^2$ tendency at the level of maximum outflow.
+%Thus, wherever $\partial u/\partial z>0$, the tilting term must force an increase in $N^2$, and wherever $\partial u/\partial z<0$, the tilting term must force a decrease in $N^2$, which is precisely the structure seen in Fig.
 \ref{fig:adv-24-48}a.
 
-Advection of $N^2$ by the radial wind (first term on the right-hand side of Eq. \ref{eq:advtend}) also acted within the outflow jet.
-For example, horizontal advection provided forcing for destabilization at the 16-km level almost everywhere inside of the 140-km radius.
-Outside of this radius near 16 km, however, existed a region of forcing for stabilization.
-This switch in signs was a consequence of a reversal of the radial graident of mean $N^2$ near the 140-km radius (Fig. \ref{fig:n2-24hr-avgs}b).
-Inside of that radius, $(\partial/\partial r)(\partial \theta/\partial z) > 0$ and $u > 0$, which corresponds to forcing for destabilization in Eq.
+%Advection of $N^2$ by the radial wind (first term on the right-hand side of Eq. \ref{eq:advtend}) also acted within the outflow jet.
+%For example, horizontal advection provided forcing for destabilization at the 16-km level almost everywhere inside of the 140-km radius.
+%Outside of this radius near 16 km, however, existed a region of forcing for stabilization.
+%This switch in signs was a consequence of a reversal of the radial graident of mean $N^2$ near the 140-km radius (Fig. \ref{fig:n2-24hr-avgs}b).
+%Inside of that radius, $(\partial/\partial r)(\partial \theta/\partial z) > 0$ and $u > 0$, which corresponds to forcing for destabilization in Eq.
 \ref{eq:advtend}; outside of that radius $(\partial/\partial r)(\partial \theta/\partial z) < 0$ and $u > 0$, which corresponds to forcing for stabilization.
-
-The relative imporance of the first and third terms on the right-hand side of Eq.
+%
+%The relative imporance of the first and third terms on the right-hand side of Eq.
 \ref{eq:advtend} is difficult to ascertain, but the structure of the mean radial velocity, $\theta$, and $N^2$ fields suggests that both terms are contributing within the outflow layer.
@@
 \ref{fig:adv-24-48}a.
-Decreasing $\theta$ near the inflow maximum acted to destabilize the layer below the inflow maximum and stabilize the layer above (Fig. \ref{fig:adv-24-48}a).
+Since the negative $\theta$ tendencies maximized at the level of maximum inflow, the layer layer below the inflow maximum destabilized and the layer above stabilized (Fig. \ref{fig:adv-24-48}a).
+
+Curiously, horizontal advection contributed to the $N^2$ tendency everywhere within the eye, even though the mean radial velocity was near zero.
+Close examination of the model output revealed that these tendencies were forced by advective processes associated with inward-propagating waves.
+%Close examination of the model output revealed that this mean ascent was forced by the interaction of inward-propagating waves with the boundary at r=0.
+Although the radial velocity perturbations induced by these waves averaged out to zero, the advective tendencies forced by the radial velocity perturbations did not.
+Additionally, when these waves reached r=0, a dipole of vertical velocity resulted, with ascent above and subsidence below.
+For reasons that remain unclear, the regions of ascent were more persistent than the regions of subsidence, which resulted in the mean ascent observed near r=0 above 17 km in Fig.
+\ref{fig:adv-24-48}b.
 
 Vertical advection also played an important role in the tropopause-layer static stability evolution.
-Within the eye, subsidence dominated below 17 km, while mean ascent existed near the storm center above 17 km\footnote{Close examination of the model output revealed that this mean ascent was forced by the interaction of inward-propagating waves with the boundary at r=0.
-When a wave reached r=0, a dipole of vertical velocity resulted, with ascent above and subsidence below.
-For reasons that remain unclear, the regions of ascent were more persistent than the regions of subsidence, which resulted in mean ascent near r=0 in the lower stratosphere.}.
+Within the eye, subsidence dominated below 17 km, while mean ascent existed near the storm center above 17 km.
 Although the magnitude of the subsidence was larger at lower altitudes, $\partial \theta/\partial z$ was smaller there.
 Because $\partial \theta/\partial z$ was smaller, the subsidence at lower levels could not accomplish as much warming as the subsidence at higher levels in the eye, consistent with the results of \cite{SternZhang2013}.
+As a result, vertical advection within the eye acted to stabilize the layer below 16 km during RI.
 
 Outside of the eye, ascent dominated the troposphere, while a 1.5-km-deep layer of descent existed immediately above the tropopause.
-This region of descent
+These regions of ascent and descent converged just above the tropopause; this convergence acted to compact the isentropes in this layer and increase the static stability.
+Above the lower-stratospheric subsidence maximum, meanwhile, vertical advection acted to decrease $N^2$.
+In the troposphere, vertical advection acted to increase $N^2$ within the eyewall region and above the vertical velocity maximum at larger radii.
+Outside of the eyewall and below the vertical velocity maximum, meanwhile, vertical advection acted to decrease $N^2$.
+
+Comparing the $N^2$ tendencies due to horizontal (Fig.
+\ref{fig:adv-24-48}a) and vertical (Fig.
+\ref{fig:adv-24-48}b) advection to the total advective tendency seen in Fig.
+\ref{fig:stab-24-48}b reveals that horizontal advective tendencies dominated the troposphere, while vertical advective tendencies dominated the layer near and above the tropopause.
+Thus, tilting of isentropes in the vicinity of the upper-tropospheric outflow maximum appears to be the most important process governing the $N^2$ tendency in the troposphere, whereas convergence of vertical velocity appears to be the most important process near the tropopause.
 
@@
 During RI (24-48 hours; Fig. \ref{fig:qi+radten}b), the eyewall updraft strengthened and a radially-extensive cirrus canopy developed near the tropopause.
-The enhanced vertical gradient of ice mixing ratio at the top of the cirrus canopy induced strong diurnal-mean radiative cooling near the tropopause (\ref{fig:qi+radten}d).
+The enhanced vertical gradient of ice mixing ratio at the top of the cirrus canopy induced strong diurnal-mean radiative cooling near the tropopause (Fig. \ref{fig:qi+radten}d).
 This cooling exceeded 0.6 K h\textsuperscript{-1} in some places and sloped downward from the lower stratosphere into the upper troposphere, following the top of the cirrus canopy.
@@
 These results broadly agree with those of \citeauthor{buetal} (\citeyear{buetal}; see their Fig.
-11a), whose CM1 simulations 0.3 K net diurnally-averaged radiative cooling at the top of the cirrus canopy and radiative warming within the cloud maximized near the 200-km radius.
+11a), whose CM1 simulations produced a 0.3 K diurnally-averaged radiative cooling at the top of the cirrus canopy and radiative warming within the cloud that maximized near the 200-km radius.
 The broad region of radiative cooling acted to destabilize the layer below the cooling maximum and stabilize the layer above, which can be seen in Fig. \ref{fig:stab-24-48}d.
-The small area of net radiative heating outside of the 140-km radius enhanced the destabilization in this region and produced a thin layer of stabilization in the 15-16-km layer.
+The small area of net radiative heating outside of the 140-km radius enhanced the destabilization above 16 km in this region and produced a thin layer of stabilization in the 15-16-km layer.
 
@@
 A simulation using NASA-Goddard radiation and 625-m vertical grid spacing produced maximum radiative cooling rates of 0.3 K h\textsuperscript{-1}, which agrees with the rates in \cite{buetal}.
-Another simulation using 625-m vertical grid spacing and RRTMG radiation produced cooling rates of up to 0.6 K h\textsuperscript{-1}.}.
+Another simulation using 625-m vertical grid spacing and RRTMG radiation produced cooling rates of up to 0.6 K h\textsuperscript{-1}, which is consistent with the WRF simulations of \cite{buetal}.}.
 Time-mean radiative warming spread from 30- to 160-km radius within the cirrus canopy.
 The existence of radiative cooling overlying radiative warming in this region led to radiatively-forced destabilization at and below the tropopause, as was observed in Fig. \ref{fig:stab-48-72}d.
-Below the warming layer existed a region of forcing for stabilization, while a much stronger region of forcing for destabilization existed above the cooling maximum in the lower stratosphere.
+Below the warming layer existed a region of forcing for stabilization, while a much stronger region of forcing for stabilization existed in the lower stratosphere, above the cooling maximum.
 
-The results herein suggest that radiative heating tendencies played an important role in destabilizing the upper troposphere and stabilizing the lower stratosphere after the cirrus canopy developed and persisted during and after RI.
+The results herein suggest that radiative heating tendencies played an important role in destabilizing the upper troposphere and stabilizing the lower stratosphere after the cirrus canopy developed.
 
@@
 Radiation and vertical turbulence played particularly important roles in developing the strong $N^2$ maximum just above the cold-point tropopause during RI.
-Since these two processes are parameterized, and radiation closely depends on yet another parameterized process (microphysics), the tropopause-layer $N^2$ variability could be quite sensitive to the assumptions inherent to parameterizations used.
-A number of sensitivity experiments revealed that the details of the $N^2$ evolution were sensitive to the selection of the microphysics scheme, the vertical turbulence length scale, and the vertical grid spacing.
-All of the simulations, however, did develop an elevated tropopause over the eye that corresponded to decreasing static stability and, outside of the eye, an $N^2$ maximum immediately above the tropopause.
+Since these two processes are parameterized, and radiation closely depends on yet another parameterized process (microphysics), the tropopause-layer $N^2$ variability could be quite sensitive to the assumptions inherent to the parameterizations used.
+A better understanding of the microphysical characteristics of the TC cirrus canopy, its interaction with radiation, and outflow-layer turbulence is critical to understanding the tropopause-layer $N^2$ evolution.
+%A number of sensitivity experiments revealed that the details of the $N^2$ evolution were sensitive to the selection of the radiation scheme, the vertical turbulence length scale, and the vertical grid spacing.
+%All of the simulations, however, did develop an elevated tropopause over the eye that corresponded to decreasing static stability and, outside of the eye, an $N^2$ maximum immediately above the tropopause.
 
-Comparison to previous work revealed that small vertical grid spacing is necessary to resolve the shallow layer of radiative cooling at the top of the cirrus canopy.
-Increasing the vertical grid spacing decreased the magnitude of the radiative cooling and produced a weaker, but deeper lower-stratospheric stable layer.
+%Comparison to previous work revealed that small vertical grid spacing is necessary to resolve the shallow layer of radiative cooling at the top of the cirrus canopy.
+%Increasing the vertical grid spacing decreased the magnitude of the radiative cooling and produced a weaker, but deeper lower-stratospheric stable layer.
 
@@
 As an example, 24-hour averages of $N^2$ are plotted in Fig.
-\ref{fig:n2-1000km} for a simulation that was identical to that used in this paper, except the initial sounding was determined by averaging every grid point within 1000 km of TC Patricia's storm center at 18 UTC 21 October 2015 instead of averaging only within the 100-km radius.
+A1 for a simulation that was identical to that used in this paper, except the initial sounding was determined by averaging every grid point within 1000 km of TC Patricia's storm center at 18 UTC 21 October 2015 instead of averaging only within the 100-km radius.
 Although the lower-stratospheric stable layer developed more slowly and was weaker than that shown in Fig.
-\ref{fig:n2-24hr-avgs}, the overall evolution was quite similar and the same budget terms dominated the static stability evolution (not shown).
+\ref{fig:n2-24hr-avgs}, the overall evolution was quite similar and the same budget terms dominated the static stability evolution.
 
@@
 Prescribing a smaller mixing length produces smaller $\theta$ tendencies due to turbulence, but even with a mixing length on the low end of those tested by \cite{Bryan2012}, turbulence still played an important role in the tropopause-layer $N^2$ evolution.
-Fig.
-\ref{fig:turb-50m} shows the 24-hour-averaged contributions of turbulent mixing to the $N^2$ evolution from a simulation identical to that used in this paper, except with a vertical mixing length of 50 m.
+Fig. A2 shows the 24-hour-averaged contributions of turbulent mixing to the $N^2$ evolution from a simulation identical to that used in this paper, except with a vertical mixing length of 50 m.
 At all times, vertical turbulence still played an important role in the tropopause-layer static stability evolution, particularly during the latter stages of RI (48-72 hours).

### 2018-03-03 paper.tex

@@
 \indent A budget analysis reveals that advection contributes to the static stability tendencies at all times throughout the upper troposphere and lower stratosphere.
-Advection is particularly important within the eye, where it acts to destabilize the layer near and above the cold-point tropopause.
+Differential advection is particularly important within the eye, where it acts to destabilize the layer near and above the cold-point tropopause.
 Outside of the eye, a radial-vertical circulation develops during RI, with strong outflow below the tropopause and weak inflow above.
@@
 
-At tropical storm intensity, shortly before RI commenced, a strong inversion layer existed just above Patricia's cold-point tropopause, which was located near 17.2 km.
+At tropical storm intensity, shortly before RI commenced, a strong inversion layer existed just above the cold-point tropopause.
 During the first half of the RI period, this inversion layer weakened throughout Patricia's inner core, with the weakening most pronounced over the developing eye.
-By the time the storm reached its maximum intensity, the inversion layer over the eye had disappeared almost completely, which was accompanied by an increase in the tropopause height to a level at or above the highest-available dropsonde data point (18.3 km) at two locations.
-Meanwhile over the eyewall region, the static stability re-strengthened and the tropopause was limited to a level at or below 17.5 km.
-The mechanisms that led to these changes in upper-level static stability and tropopause height are the subject of the current paper.
+By the time the storm reached its maximum intensity of 95 m s\textsuperscript{-1}, the inversion layer over the eye had disappeared almost completely, which was accompanied by a greater than 1-km increase in the tropopause height.
+Meanwhile over the eyewall region, the static stability increased and the tropopause remained near its initial level.
+The mechanisms that might have led to this tropopause-layer variability will be investigated in the current paper using idealized simulations.
 
-Despite the importance of tropopause-layer thermodynamics in theoretical models of hurricanes (\citeauthor{EmanuelRotunno2011} \citeyear{EmanuelRotunno2011}; \citeauthor{Emanuel2012} \citeyear{Emanuel2012}), few papers have examined the upper-tropospheric evolution of TCs.
-\cite{KomaromiDoyle2017} found that stronger TCs tended to have a higher and warmer tropopause over their inner core than weaker TCs.
+Despite the importance of tropopause-layer thermodynamics in theoretical models of hurricanes (\citeauthor{EmanuelRotunno2011} \citeyear{EmanuelRotunno2011}; \citeauthor{Emanuel2012} \citeyear{Emanuel2012}), most observational studies of the upper-tropospheric structure of TCs are decades old.
+Recently, however, \cite{KomaromiDoyle2017} found that stronger TCs tended to have a higher and warmer tropopause over their inner core than weaker TCs.
 Their results are consistent with the evolution observed over the inner core of Hurricane Patricia, in which the tropopause height increased and the tropopause temperature warmed throughout RI \citep{DuranMolinari2018}.
 
-Idealized simulations of a TC analyzed by \cite{OhnoSatoh2015} suggested that the development of an upper-level warm core near the TC storm center acted to decrease the static stability near the tropopause (compare their Figs.
+Idealized simulations of a TC analyzed by \cite{OhnoSatoh2015} suggested that the development of an upper-level warm core near the 13-km level acted to decrease the static stability near the tropopause within the eye (compare their Figs.
 9,10).
-Although the mechanisms that drive this static stability evolution have not been examined explicitly, \cite{SternZhang2013} described the development of the TC warm core using a potential temperature ($\theta$) budget analysis.
+Although the mechanisms that might drive this static stability evolution have not been examined explicitly, \cite{SternZhang2013} described the development of the TC warm core using a potential temperature ($\theta$) budget analysis.
 They found that radial and vertical advection both played important roles in warm core development throughout RI, and subgrid-scale diffusion became particularly important during the later stage of RI.
@@
 1773), with a prescribed mixing length that varied linearly from 100 m at a surface pressure of 1015 hPa to 1000 m at a surface pressure of 900 hPa.
-This formulation allows for realistically-large horizontal mixing lengths near the hurricane's inner core, consistent with the results of \cite{Bryan2012}, while not over-representing horizontal turbulence in convection at outer radii.
-Vertical turbulence was parameterized using the formulation of \citeauthor{MarkowskiBryan2016} (\citeyear{MarkowskiBryan2016}, their Eq.
-6), using an asymptotic vertical mixing length of 100 m and a vertically implicit Crank-Nicholson scheme.
+Vertical turbulence was parameterized using the formulation of \citeauthor{MarkowskiBryan2016} (\citeyear{MarkowskiBryan2016}, their Eq. 6), using an asymptotic vertical mixing length of 100 m.
 A Rayleigh damping layer was applied outside of the 2900-km radius and above the 25-km level to prevent spurious gravity wave reflection at the model boundaries.
-Microphysical processes were parameterized using the \cite{Thompson} microphysics scheme and radiative heating tendencies were computed every two minutes using the Rapid Radiative Transfer Model for GCMs (RRTMG) longwave and shortwave schemes \citep{Iacono}.
+Microphysical processes were parameterized using the \cite{Thompson} scheme and radiative heating tendencies were computed every two minutes using the Rapid Radiative Transfer Model for GCMs (RRTMG) longwave and shortwave schemes \citep{Iacono}.
 The initial temperature and humidity field was horizontally homogeneous and determined by averaging all Climate Forecast System Reanalysis (CFSR) grid points within 100 km of Patricia's center of circulation at 18 UTC 21 October 2015.
@@
 After this RI, the storm continued to intensify more slowly until the maximum 10-m wind speed reached 89 m s\textsuperscript{-1} and the minimum sea-level pressure reached its minimum of 846 mb, 81 hours into the simulation.
-Hurricane Patricia (red stars) exhibited a similar intensity evolution, with an RI period leading to a maximum 10-m wind speed of 95 m s\textsuperscript{-1} and a minimum sea-level pressure of 872 hPa.
-Despite the limitations of the axisymmetric framework, the extraordinary intensity of Hurricane Patricia and the rapidity of its intensification makes Patricia a particularly good candidate for axisymmetric analysis.
+Hurricane Patricia (red stars) exhibited a similar intensity evolution prior to its landfall, with an RI period leading to a maximum 10-m wind speed of 95 m s\textsuperscript{-1} and a minimum sea-level pressure of 872 hPa.
 

### 2018-03-04 paper.tex
Begin first round of revisions using both my comments and John's comments on first draft.

@@
 
-The static stability can be expressed as the squared Brunt V{\"a}is{\"a}l{\"a} frequency:
+The static stability can be expressed as the squared Brunt-V{\"a}is{\"a}l{\"a} frequency:
    \begin{equation} \label{eq:n2moist}
@@
 
-To compute $N^2$, CM1 uses Eq.\ref{eq:n2moist} in saturated environments and Eq.
+To compute $N^2$, CM1 uses Eq.
+\ref{eq:n2moist} in saturated environments and Eq.
 \ref{eq:n2dry} in sub-saturated environments.
 For simplicity, however, only Eq.
-\ref{eq:n2dry} will be employed for the budget computations \footnote{The validity of this approximation will be substantiated later in this section.}.
+\ref{eq:n2dry} will be employed for the budget computations\footnote{The validity of this approximation will be substantiated later in this section.}.
 
@@
 Each term on the right-hand side of Eq. \ref{eq:dthetadt} represents a $\theta$ budget variable, each of which is output directly by the model every minute.
-HADV and VADV are the radial and vertical advective tendencies\footnote{These terms include the tendencies due to implicit diffusion in the fifth-order finite differencing scheme.}, HTURB and VTURB are the tendencies from the horizontal and vertical turbulence parameterizations, MP is the tendency from the microphysics scheme, RAD is the tendency from the radiation scheme, and DISS is the tendency due to turbulent dissipation.
-This equation neglects Rayleigh damping, since this term is zero everywhere below 25 km, and the analysis domain does not extend to that level.
+HADV and VADV are the radial and vertical advective tendencies\footnote{These terms include the tendencies due to implicit diffusion in the fifth-order finite differencing scheme, which are output separately from the advection terms in CM1.}, HTURB and VTURB are the tendencies from the horizontal and vertical turbulence parameterizations, MP is the tendency from the microphysics scheme, RAD is the tendency from the radiation scheme, and DISS is the tendency due to turbulent dissipation.
+This equation neglects Rayleigh damping, since the entire analysis domain is outside of the regions where damping is applied.
 Each term in Eq. \ref{eq:dthetadt} is substituted for ${\partial \theta}/{\partial t}$ in Eq. \ref{eq:dn2dt}, yielding the contribution of each budget term to the static stability tendency.
@@
 
-Eqs. \ref{eq:budgetchange}-\ref{eq:residual} are plotted for three consecutive 24-hour periods in Fig. \ref{fig:mod+bud+res}.
+Eqs. \ref{eq:budgetchange}-\ref{eq:residual} are plotted for three consecutive 24-hour periods in Fig.~\ref{fig:mod+bud+res}.
 For this and all subsequent radial-vertical cross sections, a 1-2-1 smoother is applied once in the radial direction to eliminate $2\Delta r$ noise that appears in some of the raw model output and calculated fields.
-The left column of Fig.~\ref{fig:mod+bud+res} depicts the model changes (Eq.
-\ref{eq:modelchange}), the center column depicts the budget changes (Eq.
-\ref{eq:budgetchange}), and the right column depicts the residuals (Eq.
-\ref{eq:residual}).
+      The left column of Fig.~\ref{fig:mod+bud+res} depicts the model changes computed using Eq.
+\ref{eq:modelchange}, along with Eq.
+\ref{eq:n2moist} in saturated environments and Eq.
+\ref{eq:n2dry} in subsaturated environments.
+The center column depicts the budget changes computed using Eq. \ref{eq:budgetchange} along with Eq. \ref{eq:n2dry} throughout the domain.
+Thus, the left column includes the effect of moisture in the $N^2$ computations, whereas the center column neglects moisture.
+The right column depicts the residuals, computed using Eq. \ref{eq:residual} (i.e. the left column minus the center column.)
 In every 24-hour period, the budget changes are nearly identical to the model changes, which is reflected in the near-zero residuals in the right column.
-This indicates that the budget accurately represents the model variability, which implies that the neglect of moisture in the budget computation introduces negligible error within the anaysis domain\footnote{This is not the case in the lower- and mid-troposphere, where the residual actually exceeds the budget variability in many places, likely due to the neglect of moisture; thus we limit this analysis to the upper troposphere and lower stratosphere.}.
+This indicates that the budget accurately represents the model variability, which implies that the neglect of moisture in the budget computation introduces negligible error within the anaysis domain\footnote{This is not the case in the lower- and mid-troposphere, where the residual actually exceeds the budget tendencies in many places, likely due to the neglect of moisture; thus we limit this analysis to the upper troposphere and lower stratosphere.}.
 
@@
 To determine which of the budget terms are most important, a time series of the contribution of each of the budget terms in Eq.
-\ref{eq:dthetadt} to the tropopause-layer static stability tendency is plotted in Fig.
-\ref{fig:avgbudterms}.
+\ref{eq:dthetadt} to the tropopause-layer static stability tendency is plotted in Fig.~\ref{fig:avgbudterms}.
 For this figure, each of the budget terms is computed using the method described in Section 3, except with 1-hour averaging intervals instead of 24-hour intervals.
-The absolute values of these tendencies are then averaged over a radius-height domain surrounding the tropopause and plotted as a time series\footnote{It will be seeen in subsequent figures that each of the terms contributes both positively and negatively to the $N^2$ tendency within the analysis domain.
+The absolute values of these tendencies are then averaged over the radius-height domain of the plots shown in Fig.~\ref{fig:mod+bud+res} and plotted as a time series\footnote{It will be seeen in subsequent figures that each of the terms contributes both positively and negatively to the $N^2$ tendency within the analysis domain.
 Thus, taking an average over the domain tends to wash out the positive and negative contributions.
@@
 Advection (Fig.~\ref{fig:avgbudterms}, red line) plays an important role in the mean tropopause-layer static stability tendency at all times, and vertical turbulence (Fig.~\ref{fig:avgbudterms}, blue line) and radiation (Fig.~\ref{fig:avgbudterms}, dark green line) also contribute significantly.
-%both become important after 48 hours.
-Although the contribution from horizontal turbulence (Fig.~\ref{fig:avgbudterms}, purple line) becomes more important after 48 hours, it is confined to a very small region immediately surrounding the eyewall tangential velocity maximum (not shown), and is negligible throughout the rest of the tropopause layer.
-The two remaining processes - microphysics and dissipative heating (Fig.~\ref{fig:avgbudterms}, orange and light green lines, respectively) - lie atop one another near zero.
-Although the latent heating term can be quite large in the eyewall region, it is negligible everywhere outside of the eyewall, as are the effects of dissipative heating.
+The remaining three processes - horizontal turbulence, microphysics, and dissipative heating - lie atop one another near zero.
+Although the horizontal turbulence and microphysics terms can be quite large in the eyewall region, they are negligible everywhere outside of the eyewall, and do not play important roles in the mesoscale tropopause variability.
+Dissipative heating, meanwhile, is relatively small everywhere.
+%Although the contribution from horizontal turbulence (Fig.~\ref{fig:avgbudterms}, purple line) becomes more important after 48 hours, it is confined to a very small region immediately surrounding the eyewall tangential velocity maximum (not shown), and is negligible throughout the rest of the tropopause layer.
+%The two remaining processes - microphysics and dissipative heating (Fig.~\ref{fig:avgbudterms}, orange and light green lines, respectively) - lie atop one another near zero.
+%Although the latent heating term can be quite large in the eyewall region, it is negligible everywhere outside of the eyewall, as are the effects of dissipative heating.
 
@@
 
-The average $N^2$ over the first day of the simulation (Fig.~\ref{fig:n2-24hr-avgs}a) indicates the presence of a weak static stability maximum just above the cold-point tropopause.
-Over the subsequent 24 hours, during the RI period, the static stability within and above this layer decreased near the storm center (Fig.~\ref{fig:n2-24hr-avgs}b).
+The average $N^2$ over the first day of the simulation (Fig.~\ref{fig:n2-24hr-avgs}a) indicates the presence of a weak $N^2$ maximum just above the cold-point tropopause.
+Over the subsequent 24 hours, during the RI period, the $N^2$ within and above this layer decreased near the storm center (Fig.~\ref{fig:n2-24hr-avgs}b).
 This decreasing $N^2$ corresponded to an increase in the tropopause height within the developing eye, maximized at the storm center.
-Outside of the eye, meanwhile, the tropopause height decresed over the eyewall region (25-60-km radius) and increased only slightly outside of the 60-km radius.
+Outside of the eye, meanwhile, the tropopause height decreased over the eyewall region (25-60-km radius) and increased only slightly outside of the 60-km radius.
 In this outer region, the $N^2$ maximum just above the tropopause strengthened during RI.
@@
 This $N^2$ evolution closely follows that observed in Hurricane Patricia (2015; \citeauthor{DuranMolinari2018} \citeyear{DuranMolinari2018}).
-The mechanisms that led to these static stability changes will be investigated in the subsequent sections.
+The mechanisms that led to these $N^2$ changes will be investigated in the subsequent sections.
 
@@
 \paragraph{0-24 hours}
-The weakening of the lower-stratospheric static stability maximum during the initial spin-up period is reflected in the total $N^2$ budget change over this time (Fig.~\ref{fig:stab-00-24}a).
+The weakening of the lower-stratospheric $N^2$ maximum during the initial spin-up period is reflected in the total $N^2$ budget change over this time (Fig.~\ref{fig:stab-00-24}a).
 The 17-18-km layer was characterized by decreasing $N^2$ (purple shading), maximizing at the storm center.
-The layer immediately below the tropopause, meanwhile, saw strengthening $N^2$ during this time period.
+The layer immediately below the tropopause, meanwhile, saw increasing $N^2$ during this time period.
 Although these tendencies extended out to the 200-km radius, they were particularly pronounced at innermost radii.
-A comparison of the contributions of advection (Fig.~\ref{fig:stab-00-24}b), vertical turbulence (Fig.~\ref{fig:stab-00-24}c), and radiation (Fig.~\ref{fig:stab-00-24}d) reveals that advection was primarily responsible for the change in static stability during this period.
+A comparison of the contributions of advection (Fig.~\ref{fig:stab-00-24}b), vertical turbulence (Fig.~\ref{fig:stab-00-24}c), and radiation (Fig.~\ref{fig:stab-00-24}d) reveals that advection was the primary drive of the $N^2$ tendency during this period.
 Although vertical turbulence acted in opposition to advection (i.e.
@@
 
-The sum of advection, vertical turbulence, and radiation (Fig.
-\ref{fig:stab-24-48}f) once again closely follows the observed $N^2$ variability, except in portions of the eyewall where the neglect of latent heating and horizontal turbulence introduces some differences.
+The sum of advection, vertical turbulence, and radiation (Fig.~\ref{fig:stab-24-48}f) once again closely follows the observed $N^2$ variability, except lower in the eyewall where the neglect of latent heating and horizontal turbulence introduces some differences.
 
@@
 Outside of the 80-km radius, both advection (Fig.~\ref{fig:stab-48-72}b) and vertical turbulence (Fig.~\ref{fig:stab-48-72}c) provided forcing for stabilization near the 18-km level.
-The sum of the two terms indicates increasing $N^2$ near the 18-km level everywhere outside of the 80-km radius, but this stabilization is slightly weaker in the 90-120-km radial band than the observed value.
+The sum of the two terms (Fig.~\ref{fig:stab-48-72}e) indicates increasing $N^2$ near the 18-km level everywhere outside of the 80-km radius, but this stabilization is slightly weaker in the 90-120-km radial band than the observed value.
 The addition of radiation (Fig.~\ref{fig:stab-48-72}f) provides the extra forcing for stabilization required to account for the observed increase in $N^2$.
@@
 Advection played an important role in the tropopause-layer $N^2$ evolution at all stages of intensification, but for brevity, this section will focus only on the RI (24-48-hour) period.
-To investigate the advective processes more closely, the individual contributions of horizontal and vertical advection during the RI period are shown in Fig.
-\ref{fig:adv-24-48}, along with the corresponding time-mean radial and vertical velocities and $\theta$.
-The $N^2$ tendencies due to the two advective components (Fig. \ref{fig:adv-24-48}a,b) exhibit strong cancellation, consistent with flow that is nearly isentropic.
-There are, however, many regions in which flow crosses $\theta$ surfaces; this flow accounts for all non-zero $N^2$ tendencies due to advection previously seen in Fig. \ref{fig:stab-24-48}b.
+To investigate the advective processes more closely, the individual contributions of horizontal and vertical advection during the RI period are shown in Fig.~\ref{fig:adv-24-48}, along with the corresponding time-mean radial and vertical velocities and $\theta$.
+The $N^2$ tendencies due to the two advective components (Fig.~\ref{fig:adv-24-48}a,b) exhibit strong cancellation, consistent with flow that is nearly isentropic.
+There are, however, many regions in which flow crosses $\theta$ surfaces; this flow accounts for all non-zero $N^2$ tendencies due to advection previously seen in Fig.~\ref{fig:stab-24-48}b.
 
 %The eye was characterized by stabilization below 16 km and destabilization in the 16-17-km and 18-19-km layers.
-%Comparing Fig.
-\ref{fig:stab-24-48}b to \ref{fig:adv-24-48}a,b reveals that the stabilization below 16 km in the eye was forced by vertical advection, as was the region of destabilization in the 18-19-km layer.
+%Comparing Fig.~\ref{fig:stab-24-48}b to \ref{fig:adv-24-48}a,b reveals that the stabilization below 16 km in the eye was forced by vertical advection, as was the region of destabilization in the 18-19-km layer.
 %Meanwhile, the destabilization that occurred in the 16-17-km layer was forced by a combination and radial and vertial advection.
@@
 %  \paragraph{0-24 hours}
-%During the first day of the simulation, horizontal advection (Fig. \ref{fig:adv-00-24}a) generally forced a decrease in $N^2$ below 17 km and an increase in $N^2$ above.
-%The mean radial velocity during this period (Fig.
-\ref{fig:adv-00-24}c) reveals a region of outflow at and below 17 km and near-zero radial velocity above, with a layer of strong vertical wind shear straddling the tropopause.
+%During the first day of the simulation, horizontal advection (Fig.~\ref{fig:adv-00-24}a) generally forced a decrease in $N^2$ below 17 km and an increase in $N^2$ above.
+%The mean radial velocity during this period (Fig.~\ref{fig:adv-00-24}c) reveals a region of outflow at and below 17 km and near-zero radial velocity above, with a layer of strong vertical wind shear straddling the tropopause.
 %The slight downward slope with radius of the $\theta$ surfaces near the tropopause (i.e.
@@
 %This negative $\theta$ tendency must decrease with height within the region of strong vertical wind shear and approach zero as the radial velocity diminishes to zero near 17 km.
-%These tendencies thus yielded an increase in the vertical gradient of $\theta$ above 17 km, which implies an increase in $N^2$, as was seen in Fig. \ref{fig:adv-00-24}a.
+%These tendencies thus yielded an increase in the vertical gradient of $\theta$ above 17 km, which implies an increase in $N^2$, as was seen in Fig.~\ref{fig:adv-00-24}a.
 %Note that although the radial gradient of $\theta$ was stronger in the 15-16-km layer than it was closer to the tropopause, the vertical shear of the radial wind was much smaller there, yielding a smaller $N^2$ tendency due to horizontal advection.
@@
 %
-%The $N^2$ tendencies forced by horizontal advection were completely canceled out by vertical advective tendencies (Fig. \ref{fig:adv-00-24}b).
-%As was seen in Fig.
-\ref{fig:stab-00-24}b, the sum of the two terms yielded a layer of increasing $N^2$ below 17 km and decreasing $N^2$ above, meaning that vertical advective processes dominated the $N^2$ tendency during the initial spin-up period.
+%The $N^2$ tendencies forced by horizontal advection were completely canceled out by vertical advective tendencies (Fig.~\ref{fig:adv-00-24}a.
+%Note that although the radial gradient of $\theta$ was stronger in the 15-16-km layer than it was closer to the tropopause, the vertical shear of the radial wind was much smaller there, yielding a smaller $N^2$ tendency due to horizontal advection.
+%
+%Notably, there existed strong $N^2$ tendencies due to horizontal advection inside of the 30-km radius even though the mean radial velocity in that region was near zero.
+%Close examination of the radial velocity at each output time step reveals the presence of inward-propagating waves in the lower stratosphere.
+%These waves amplified upon reaching r=0 and forced strong but highly transient $\theta$ tendencies due to advective processes.
+%Thus, although the radial velocity perturbations associated with these waves averaged out to zero, the non-linear effect of these waves on the $N^2$ field remained.
+%
+%The $N^2$ tendencies forced by horizontal advection were completely canceled out by vertical advective tendencies (\ref{fig:adv-00-24}b).
+%As was seen in Fig.~\ref{fig:stab-00-24}b, the sum of the two terms yielded a layer of increasing $N^2$ below 17 km and decreasing $N^2$ above, meaning that vertical advective processes dominated the $N^2$ tendency during the initial spin-up period.
 %Most of the upper troposphere contained mean ascent during this time, with the magnitude of the ascent decreasing with height.
-%This decrease in upward motion with height forces a convergence of isentropic surfaces, which implies a positive $N^2$ tendency in this region, as was observed in Fig. \ref{fig:adv-00-24}b.
+%This decrease in upward motion with height forces a convergence of isentropic surfaces, which implies a positive $N^2$ tendency in this region, as was observed in Fig.~\ref{fig:adv-00-24}b.
 %Some weak descent at and just above the tropopause, meanwhile, forces a slight divergence of isentropes in the 17-18-km layer and a concomitant decrease in $N^2$.
@@
 %   \paragraph{RI period: 24-48 hours}
-During the RI period, strong radial and vertical circulations developed near the tropopause, which forced high-magnitude $N^2$ tendencies due to advection (Fig. \ref{fig:adv-24-48}a,b).
-A layer of strong outflow developed at and below the tropopause during this period, with the outflow maximum (dashed cyan line) curving from the 14-km level at the 50-km radius to just below the 16-km level outside of the 80-km radius (Fig.
-\ref{fig:adv-24-48}c).
+During the RI period, strong radial and vertical circulations developed near the tropopause (Fig.~\ref{fig:adv-24-48}c,d), which forced high-magnitude $N^2$ tendencies due to advection (Fig.~\ref{fig:adv-24-48}a,b).
+A layer of strong outflow formed at and below the tropopause during this period, with the outflow maximum (dashed cyan line) curving from the 14-km level at the 50-km radius to just below the 16-km level outside of the 80-km radius (Fig.~\ref{fig:adv-24-48}c).
 %The cyan line, by definition, represents the level at which the vertical gradient of radial velocity switched signs, with $\partial u/\partial z>0$ below the line and $\partial u/\partial z<0$ above.
-Notably, the $N^2$ tendency due to horizontal advection (Fig. \ref{fig:adv-24-48}a) tended to switch signs at this line, with stabilization below the outflow maximum and destabilization above.
+Notably, the $N^2$ tendency due to horizontal advection (Fig.~\ref{fig:adv-24-48}a) tended to switch signs at this line, with stabilization below the outflow maximum and destabilization above.
 %This suggests that vertical wind shear above and below the outflow maximum played an important role in the $N^2$ tendency during this time.
@@
 This mechanism is the same as that discussed in \cite{TrierSharman}, and is consistent with the change in sign of the $N^2$ tendency at the level of maximum outflow.
-%Thus, wherever $\partial u/\partial z>0$, the tilting term must force an increase in $N^2$, and wherever $\partial u/\partial z<0$, the tilting term must force a decrease in $N^2$, which is precisely the structure seen in Fig.
-\ref{fig:adv-24-48}a.
+%Thus, wherever $\partial u/\partial z>0$, the tilting term must force an increase in $N^2$, and wherever $\partial u/\partial z<0$, the tilting term must force a decrease in $N^2$, which is precisely the structure seen in Fig.~\ref{fig:adv-24-48}a.
 
@@
 %Outside of this radius near 16 km, however, existed a region of forcing for stabilization.
-%This switch in signs was a consequence of a reversal of the radial graident of mean $N^2$ near the 140-km radius (Fig. \ref{fig:n2-24hr-avgs}b).
+%This switch in signs was a consequence of a reversal of the radial graident of mean $N^2$ near the 140-km radius (Fig.~\ref{fig:n2-24hr-avgs}b).
 %Inside of that radius, $(\partial/\partial r)(\partial \theta/\partial z) > 0$ and $u > 0$, which corresponds to forcing for destabilization in Eq.
@@
 Since the isentropes in this layer sloped slightly upward with radius (i.e. $\partial \theta/\partial r < 0$), this inflow acted to import lower $\theta$ air from outer radii to inner radii.
-%There also existed strong radial gradients of mean $N^2$ in this layer during this time (Fig. \ref{fig:n2-24hr-avgs}b), so the inflow layer must have acted to rearrange $N^2$.
+%There also existed strong radial gradients of mean $N^2$ in this layer during this time (Fig.~\ref{fig:n2-24hr-avgs}b), so the inflow layer must have acted to rearrange $N^2$.
 %This rearrangement could not have been responsible for the overall increase in $N^2$ during this period, however.
@@
 %The third term on the right-hand side of Eq.
-\ref{eq:advtend} shows that the tilting of isentropes should act to destabilize the layer below the inflow maximum and stabilize the layer above, which is precisely what was observed outside of the 80-km radius in Fig.
-\ref{fig:adv-24-48}a.
-Since the negative $\theta$ tendencies maximized at the level of maximum inflow, the layer layer below the inflow maximum destabilized and the layer above stabilized (Fig. \ref{fig:adv-24-48}a).
+\ref{eq:advtend} shows that the tilting of isentropes should act to destabilize the layer below the inflow maximum and stabilize the layer above, which is precisely what was observed outside of the 80-km radius in Fig.~\ref{fig:adv-24-48}a.
+Since the negative $\theta$ tendencies maximized at the level of maximum inflow, the layer below the inflow maximum destabilized and the layer above stabilized (Fig.~\ref{fig:adv-24-48}a).
 
@@
 Although the radial velocity perturbations induced by these waves averaged out to zero, the advective tendencies forced by the radial velocity perturbations did not.
-Additionally, when these waves reached r=0, a dipole of vertical velocity resulted, with ascent above and subsidence below.
-For reasons that remain unclear, the regions of ascent were more persistent than the regions of subsidence, which resulted in the mean ascent observed near r=0 above 17 km in Fig.
-\ref{fig:adv-24-48}b.
+Additionally, when these waves reached r=0, a dipole of vertical velocity resulted, with ascent above and descent below.
+For reasons that remain unclear, the regions of ascent were more persistent than the regions of descent, which resulted in the mean ascent observed near r=0 above 17 km in Fig.~\ref{fig:adv-24-48}b.
 
@@
 
-Outside of the eye, ascent dominated the troposphere, while a 1.5-km-deep layer of descent existed immediately above the tropopause.
+Outside of the 27-km radius, ascent dominated the troposphere, while a 1.5-km-deep layer of descent existed immediately above the tropopause.
 These regions of ascent and descent converged just above the tropopause; this convergence acted to compact the isentropes in this layer and increase the static stability.
 Above the lower-stratospheric subsidence maximum, meanwhile, vertical advection acted to decrease $N^2$.
-In the troposphere, vertical advection acted to increase $N^2$ within the eyewall region and above the vertical velocity maximum at larger radii.
+In the troposphere, differential vertical advection increased $N^2$ within the eyewall region and above the vertical velocity maximum at larger radii.
 Outside of the eyewall and below the vertical velocity maximum, meanwhile, vertical advection acted to decrease $N^2$.
 
-Comparing the $N^2$ tendencies due to horizontal (Fig.
-\ref{fig:adv-24-48}a) and vertical (Fig.
-\ref{fig:adv-24-48}b) advection to the total advective tendency seen in Fig.
-\ref{fig:stab-24-48}b reveals that horizontal advective tendencies dominated the troposphere, while vertical advective tendencies dominated the layer near and above the tropopause.
+Comparing the $N^2$ tendencies forced by horizontal (Fig.~\ref{fig:adv-24-48}a) and vertical (Fig.~\ref{fig:adv-24-48}b) advection to the total advective tendency seen in Fig.~\ref{fig:stab-24-48}b reveals that horizontal advective tendencies dominated the troposphere, while vertical advective tendencies dominated the layer near and above the tropopause.
 Thus, tilting of isentropes in the vicinity of the upper-tropospheric outflow maximum appears to be the most important process governing the $N^2$ tendency in the troposphere, whereas convergence of vertical velocity appears to be the most important process near the tropopause.
@@
   \subsection{The role of radiation}
-During the initial spin-up period (0-24 hours; \ref{fig:qi+radten}a), convection was not deep enough to deposit large quantities of ice near the tropopause in the mean.
-Due to the lack of ice particles, the radiative heating tendencies during this period (Fig.
-\ref{fig:qi+radten}b) were relatively small and confined to the region above a few particularly strong convective towers.
-During RI (24-48 hours; Fig. \ref{fig:qi+radten}b), the eyewall updraft strengthened and a radially-extensive cirrus canopy developed near the tropopause.
-The enhanced vertical gradient of ice mixing ratio at the top of the cirrus canopy induced strong diurnal-mean radiative cooling near the tropopause (Fig. \ref{fig:qi+radten}d).
+During the initial spin-up period (0-24 hours; Fig.~\ref{fig:qi+radten}a), convection was not deep enough to deposit large quantities of ice near the tropopause to create a persistent cirrus canopy.
+Due to the lack of ice particles, the radiative heating tendencies during this period (Fig.~\ref{fig:qi+radten}b) were relatively small and confined to the region above a few particularly strong, although transient, convective towers.
+During RI (24-48 hours; Fig.~\ref{fig:qi+radten}b), the eyewall updraft strengthened and a radially-extensive cirrus canopy developed near the tropopause.
+The enhanced vertical gradient of ice mixing ratio at the top of the cirrus canopy induced strong diurnal-mean radiative cooling near the tropopause (Fig.~\ref{fig:qi+radten}d).
 This cooling exceeded 0.6 K h\textsuperscript{-1} in some places and sloped downward from the lower stratosphere into the upper troposphere, following the top of the cirrus canopy.
@@
 These results broadly agree with those of \citeauthor{buetal} (\citeyear{buetal}; see their Fig.
-11a), whose CM1 simulations produced a 0.3 K diurnally-averaged radiative cooling at the top of the cirrus canopy and radiative warming within the cloud that maximized near the 200-km radius.
-The broad region of radiative cooling acted to destabilize the layer below the cooling maximum and stabilize the layer above, which can be seen in Fig. \ref{fig:stab-24-48}d.
+11a), whose CM1 simulations produced a 0.3 K h\textsuperscript{-1} diurnally-averaged radiative cooling at the top of the cirrus canopy and radiative warming within the cloud that maximized near the 200-km radius.
+This broad region of radiative cooling acted to destabilize the layer below the cooling maximum and stabilize the layer above, which can be seen in Fig.~\ref{fig:stab-24-48}d.
 The small area of net radiative heating outside of the 140-km radius enhanced the destabilization above 16 km in this region and produced a thin layer of stabilization in the 15-16-km layer.
 
-After the TC's RI period completed (48-72 hours; Fig.
-\ref{fig:qi+radten}f), strong radiative cooling remained near the tropopause at inner radii, sloping downward with the top of the cirrus canopy to below the tropopause at outer radii.
+After the TC's RI period completed (48-72 hours; Fig.~\ref{fig:qi+radten}f), strong radiative cooling remained near the tropopause at inner radii, sloping downward with the top of the cirrus canopy to below the tropopause at outer radii.
 Cooling rates exceeded 1 K h\textsuperscript{-1} just above the tropopause between the 30- and 70-km radii.
-These cooling rates exceeded those observed by \cite{buetal}, a discrepancy that is a consequence of their larger vertical grid spacing (625 m) compared to that used here (250 m), along with a contribution from differing radiation schemes\footnote{\cite{buetal} employed the NASA-Goddard radiation scheme for their CM1 simulations, whereas RRTMG is used in the present paper.
-A simulation using NASA-Goddard radiation and 625-m vertical grid spacing produced maximum radiative cooling rates of 0.3 K h\textsuperscript{-1}, which agrees with the rates in \cite{buetal}.
-Another simulation using 625-m vertical grid spacing and RRTMG radiation produced cooling rates of up to 0.6 K h\textsuperscript{-1}, which is consistent with the WRF simulations of \cite{buetal}.}.
+This value is more than three times the maximum cooling rate of 0.3 K h\textsuperscript{-1} observed by \cite{buetal}, a discrepancy that is a consequence of their larger vertical grid spacing compared to that used here, along with a contribution from differing radiation schemes.
+%\cite{buetal} employed the NASA-Goddard radiation scheme in their CM1 simulations, whereas RRTMG is used in the present paper.
+To compare our results to those of \cite{buetal}, we ran a simulation identical to that described in Section 2, except using the NASA-Goddard radiation scheme and 625-m vertical grid spacing, to match those of \cite{buetal}.
+This simulation produced a maximum radiative cooling rate of 0.3 K h\textsuperscript{-1}, which agrees with that shown in \cite{buetal}.
+Another simulation using 625-m vertical grid spacing and RRTMG radiation produced cooling rates of up to 0.6 K h\textsuperscript{-1}, which is consistent with the WRF simulations of \cite{buetal}.
+This suggests that vertical grid spacing smaller than 625 m is necessary to resolve properly the radiative cooling at the top of the cirrus canopy, and that the results can be quite sensitive to the radiation scheme used.
+
 Time-mean radiative warming spread from 30- to 160-km radius within the cirrus canopy.
-The existence of radiative cooling overlying radiative warming in this region led to radiatively-forced destabilization at and below the tropopause, as was observed in Fig. \ref{fig:stab-48-72}d.
-Below the warming layer existed a region of forcing for stabilization, while a much stronger region of forcing for stabilization existed in the lower stratosphere, above the cooling maximum.
+The existence of radiative cooling overlying radiative warming in this region led to radiatively-forced destabilization at and below the tropopause, as was observed in Fig.~\ref{fig:stab-48-72}d.
+Beneath the warming layer existed a region of forcing for stabilization, while a much stronger region of forcing for stabilization existed in the lower stratosphere, above the cooling maximum.
 
@@
 
-Fig. \ref{fig:diff} reveals that two distinct maxima of vertial eddy diffusivity developed in the tropopause layer as the storm intensified.
+Two distinct maxima of vertical eddy diffusivity developed in the tropopause layer as the storm intensified (Fig.~\ref{fig:diff}).
 Comparison of these turbulent regions to the $N^2$ tendencies in Figs.
@@
 \appendixtitle{Sensitivity experiments}
-The simulations exhibited some sentivity to the initial thermodynamic profile and the prescribed vertical mixing length.
+The simulations exhibited some sensitivity to the initial thermodynamic profile and the prescribed vertical mixing length.
 Although the details of the intensification and the tropopause-layer $N^2$ evolution varied when these quantities were changed, the conclusions of the paper remain unchanged.
@@
 In all simulations, however, convection eventually penetrated to the tropopause, at which time vertical turbulence and radiation combined with advection to adjust the $N^2$ profile toward that which was observed in the control run.
-By the end of the RI period in every simulation, all three proesses were actively modifying the $N^2$ profile near the tropopause.
+By the end of the RI period in every simulation, all three processes were actively modifying the $N^2$ profile near the tropopause.
 
 As an example, 24-hour averages of $N^2$ are plotted in Fig.
-A1 for a simulation that was identical to that used in this paper, except the initial sounding was determined by averaging every grid point within 1000 km of TC Patricia's storm center at 18 UTC 21 October 2015 instead of averaging only within the 100-km radius.
-Although the lower-stratospheric stable layer developed more slowly and was weaker than that shown in Fig.
-\ref{fig:n2-24hr-avgs}, the overall evolution was quite similar and the same budget terms dominated the static stability evolution.
+A1 for a simulation that was identical to that used in this paper, except the initial sounding was determined by averaging every CFSR grid point within 1000 km of TC Patricia's storm center at 18 UTC 21 October 2015 instead of averaging only within the 100-km radius.
+Although the lower-stratospheric stable layer developed more slowly and was weaker than that shown in Fig.~\ref{fig:n2-24hr-avgs}, the overall evolution was quite similar and the same budget terms dominated the $N^2$ evolution.
 
@@
 Fig. A2 shows the 24-hour-averaged contributions of turbulent mixing to the $N^2$ evolution from a simulation identical to that used in this paper, except with a vertical mixing length of 50 m.
-At all times, vertical turbulence still played an important role in the tropopause-layer static stability evolution, particularly during the latter stages of RI (48-72 hours).
+At all times, vertical turbulence still played an important role in the tropopause-layer $N^2$ evolution, particularly during the latter stages of RI (48-72 hours).
 
@@
 \centerline{\includegraphics[width=19pc]{figures/vmax+pmin.png}}
-\caption{The maximum 10-m wind speed (top panel; m s\textsuperscript{-1}) and minimum sea-level pressure (bottom panel; hPa) in the simulated storm (blue lines) and from Hurricane Patricia's best track (red stars).}
+\caption{The maximum 10-m wind speed (top panel; m s\textsuperscript{-1}) and minimum sea-level pressure (bottom panel; hPa) in the simulated storm (blue lines; plotted every minute) and from Hurricane Patricia's best track (red stars; plotted every six hours beginning at the time Patricia attained tropical storm intensity).
+The rapid weakening during the later stage of Patricia's lifetime was induced by landfall.}
 \label{fig:vmax+pmin}
@@
 \centerline{\includegraphics[width=39pc]{figures/mod+bud+res.png}}
-\caption{Left panels: Twenty-four-hour changes in squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$; 10\textsuperscript{-4} s\textsuperscript{-2}) over (top row) 0-24 hours, (middle row) 24-48 hours, (bottom row) 48-72 hours.
+\caption{Left panels: Twenty-four-hour changes in squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$; 10\textsuperscript{-4} s\textsuperscript{-2}) computed using Eq.~\ref{eq:modelchange} over (top row) 0-24 hours, (middle row) 24-48 hours, (bottom row) 48-72 hours.
 Middle Panels: The $N^2$ change over the same time periods computed using Eqs. \ref{eq:dn2dt}-\ref{eq:budgetchange}, %together with Eqs. \ref{eq:dn2dt}, \ref{eq:dthetadt}.
@@
 %FIGURE 3%
+\begin{figure}[ht]
+\centerline{\includegraphics[width=19pc]{figures/AVG_budterms.png}}
+\caption{Time series of the contribution of each of the budget terms to the time tendency of the squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$; 10\textsuperscript{-4} s\textsuperscript{-2}).
+For each budget term, the absolute value of the $N^2$ tendency is averaged temporally over 1-hour periods (using output every minute), and spatially in a region extending from 0 to 200 km radius and 14 to 21 km altitude.}
+\label{fig:avgbudterms}
+\end{figure}
+
+%FIGURE 4%
 \begin{figure*}[ht]
@@
 
-%FIGURE 4%
-\begin{figure}[ht]
-\centerline{\includegraphics[width=19pc]{figures/AVG_budterms.png}}
-\caption{Time series of the contribution of each of the budget terms to the time tendency of the squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$; 10\textsuperscript{-4} s\textsuperscript{-2}).
-For each budget term, the absolute value of the $N^2$ tendency is averaged temporally over 1-hour periods (using output every minute), and spatially in a region extending from 0 to 200 km radius and 14 to 21 km altitude.}
-\label{fig:avgbudterms}
-\end{figure}
-
 %FIGURE 5%
@@
 \begin{figure}
-\caption{(a) Total change in $N^2$ over the 0-24-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 h)\textsuperscript{-1}) and the contributions to that change from (b) the sum of horizontal and vertical advection, (c) vertical turbulence, (d) longwave and shortwave radiation, (e) the sum of horizontal advection, vertical advection, and vertical turublence, and (f) the sum of horizontal advection, vertical advection, vertical turbulence, and longwave and shortwave radiation.}
+\caption{(a) Total change in $N^2$ over the 0-24-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 h)\textsuperscript{-1}) and the contributions to that change from (b) the sum of horizontal and vertical advection, (c) vertical turbulence, (d) longwave and shortwave radiation, (e) the sum of horizontal advection, vertical advection, and vertical turbulence, and (f) the sum of horizontal advection, vertical advection, vertical turbulence, and longwave and shortwave radiation.}
 \label{fig:stab-00-24}
@@
 \centerline{\includegraphics[width=39pc]{figures/h024-h048-adv.png}}
-\caption{The contribution to the change in $N^2$ over the 24-48-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 h)\textsuperscript{-1}) by (a) horizontal advection and (b) vertical advection.
+\caption{The contributions to the change in $N^2$ over the 24-48-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 h)\textsuperscript{-1}) by (a) horizontal advection and (b) vertical advection.
 (c) The radial velocity (m s\textsuperscript{-1}; filled contours), potential temperature (K; thick black contours), cold-point tropopause height (orange line), and level of maximum outflow (dashed cyan line) averaged over the 24-48-hour period.
@@
 \appendcaption{A1}{Twenty-four-hour averages of squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$; 10\textsuperscript{-4} s\textsuperscript{-2}) over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, and (d) 72-96 hours for the simulation described in Appendix Aa.
-Orange lines represent the cold-point tropopause averged over the same time periods.}
+Orange lines represent the cold-point tropopause averaged over the same time periods.}
 \label{fig:n2-1000km}

### 2018-03-04 paper.tex
Add tropopause height to stability budget figures to aid in discussion of physical processes.

@@
 Middle Panels: The $N^2$ change over the same time periods computed using Eqs. \ref{eq:dn2dt}-\ref{eq:budgetchange}, %together with Eqs. \ref{eq:dn2dt}, \ref{eq:dthetadt}.
-Right Panels: The budget residual over the same time periods, computed by subtracting the budget change (middle column) from the model change (left column).}
+Right Panels: The budget residual over the same time periods, computed by subtracting the budget change (middle column) from the model change (left column).
+Orange lines represent the cold-point tropopause height averaged over the same time periods.}
 \label{fig:mod+bud+res}
@@
 \caption{Twenty-four-hour averages of squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$; 10\textsuperscript{-4} s\textsuperscript{-2}) over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours.
-Orange lines represent the cold-point tropopause averaged over the same time periods.}
+Orange lines represent the cold-point tropopause height averaged over the same time periods.}
 \label{fig:n2-24hr-avgs}
@@
 \begin{figure}
-\caption{(a) Total change in $N^2$ over the 0-24-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 h)\textsuperscript{-1}) and the contributions to that change from (b) the sum of horizontal and vertical advection, (c) vertical turbulence, (d) longwave and shortwave radiation, (e) the sum of horizontal advection, vertical advection, and vertical turbulence, and (f) the sum of horizontal advection, vertical advection, vertical turbulence, and longwave and shortwave radiation.}
+\caption{(a) Total change in $N^2$ over the 0-24-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 h)\textsuperscript{-1}) and the contributions to that change from (b) the sum of horizontal and vertical advection, (c) vertical turbulence, (d) longwave and shortwave radiation, (e) the sum of horizontal advection, vertical advection, and vertical turbulence, and (f) the sum of horizontal advection, vertical advection, vertical turbulence, and longwave and shortwave radiation.
+Orange lines represent the cold-point tropopause height averaged over the 0-24-hour period.}
 \label{fig:stab-00-24}
@@
 \appendcaption{A1}{Twenty-four-hour averages of squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$; 10\textsuperscript{-4} s\textsuperscript{-2}) over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, and (d) 72-96 hours for the simulation described in Appendix Aa.
-Orange lines represent the cold-point tropopause averaged over the same time periods.}
+Orange lines represent the cold-point tropopause height averaged over the same time periods.}
 \label{fig:n2-1000km}
@@
 \centerline{\includegraphics[width=39pc]{figures/turb-50m.png}}
-\appendcaption{A2}{The contribution of vertical turbulence to the $N^2$ variability (10\textsuperscript{-4} s\textsuperscript{-2} (24 h)\textsuperscript{-1}) averaged over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, and (d) 72-96 hours for the simulation described in Appendix Ab.}
+\appendcaption{A2}{The contribution of vertical turbulence to the $N^2$ variability (10\textsuperscript{-4} s\textsuperscript{-2} (24 h)\textsuperscript{-1}) averaged over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, and (d) 72-96 hours for the simulation described in Appendix Ab.
+Orange lines represent the cold-point tropopause height averaged over the same time periods.}
 \label{fig:turb-50m}

### 2018-03-05 paper.tex
Change discussion of N^2 budget figures in Results section so that it references the tropopause height in most places rather than height levels. Also change Fig. A2 to include tropopause height.

@@
 The weakening of the lower-stratospheric $N^2$ maximum during the initial spin-up period is reflected in the total $N^2$ budget change over this time (Fig.~\ref{fig:stab-00-24}a).
-The 17-18-km layer was characterized by decreasing $N^2$ (purple shading), maximizing at the storm center.
-The layer immediately below the tropopause, meanwhile, saw increasing $N^2$ during this time period.
+The layer just above the cold-point tropopause was characterized by decreasing $N^2$ (purple shading), maximizing at the storm center.
+At and immediately below the tropopause, meanwhile, saw increasing $N^2$ during this time period.
 Although these tendencies extended out to the 200-km radius, they were particularly pronounced at innermost radii.
-A comparison of the contributions of advection (Fig.~\ref{fig:stab-00-24}b), vertical turbulence (Fig.~\ref{fig:stab-00-24}c), and radiation (Fig.~\ref{fig:stab-00-24}d) reveals that advection was the primary drive of the $N^2$ tendency during this period.
+A comparison of the contributions of advection (Fig.~\ref{fig:stab-00-24}b), vertical turbulence (Fig.~\ref{fig:stab-00-24}c), and radiation (Fig.~\ref{fig:stab-00-24}d) reveals that advection was the primary driver of the $N^2$ tendency during this period, acting to stabilize near and just below the tropopause and destabilize above.
 Although vertical turbulence acted in opposition to advection (i.e.
 it acted to stabilize regions that advection acted to destabilize), the magnitude of the advective tendencies was larger, particularly at the innermost radii.
-The sum of advection and vertical turbulence (Fig.~\ref{fig:stab-00-24}e) almost exactly replicated the static stability tendencies above 17 km.
+The sum of advection and vertical turbulence (Fig.~\ref{fig:stab-00-24}e) almost exactly replicated the static stability tendencies above the tropopause.
 Radiative tendencies, meanwhile, (Fig.~\ref{fig:stab-00-24}d) acted to destabilize the layer below about 16 km and stabilize the layer between 16 and 17 km.
@@
 \paragraph{24-48 hours}
-During the RI period, $N^2$ within the eye generally decreased above 16 km and increased below (Fig.~\ref{fig:stab-24-48}a).
+During the RI period, $N^2$ within the eye generally decreased above 16 km and increased below (Fig.~\ref{fig:stab-24-48}a), with the destabilization above 16 km maximizing near the level of the mean cold-point tropopause.
 These tendencies at the innermost radii were driven almost entirely by advection (Fig.~\ref{fig:stab-24-48}b); vertical turbulence (Fig.~\ref{fig:stab-24-48}c) and radiation (Fig.~\ref{fig:stab-24-48}d) contributed negligibly to the static stability tendencies in this region.
@@
 Near and above 18 km existed an upward-sloping region of decreasing $N^2$ that extended out to the 180-km radius.
-In this region, neither vertical turbulence nor radiation exhibited negative $N^2$ tendencies; advection was the only forcing for destabilization.
-Immediately below this layer was a region of increasing $N^2$, which sloped upward from 17 km near the 30-km radius to just below 18 km outside of the 100-km radius.
+In this region, neither vertical turbulence nor radiation exhibited negative $N^2$ tendencies; advection was the only forcing for this destabilization.
+Immediately below this layer, just above the cold-point tropopause, was a region of increasing $N^2$ that sloped upward from 17 km near the 30-km radius to just below 18 km outside of the 100-km radius.
 Advection and vertical turbulence both contributed to this positive $N^2$ tendency, with advection playing an important role below about 17.5 km and and turbulence playing an important role above.
@@
 The addition of radiation to these two terms, however, (Fig.~\ref{fig:stab-24-48}f) provides the link between these two regions, indicating that radiation also plays a role in strengthening the stable layer just above the tropopause.
-In the 16-17-km layer, a horizontally-extensive layer of decreasing $N^2$ also was forced by a combination of advection, vertical turbulence, and radiation.
+In the 16-17-km layer, just below the cold-point tropopause, a horizontally-extensive layer of destabilization also was forced by a combination of advection, vertical turbulence, and radiation.
 The sum of advection and vertical turbulence accounts for only a portion of the decreasing $N^2$ in this layer, and actually indicates forcing for stabilization near the 50-km radius and outside of the 130-km radius.
@@
 
-The sum of advection, vertical turbulence, and radiation (Fig.~\ref{fig:stab-24-48}f) once again closely follows the observed $N^2$ variability, except lower in the eyewall where the neglect of latent heating and horizontal turbulence introduces some differences.
+The sum of advection, vertical turbulence, and radiation (Fig.~\ref{fig:stab-24-48}f) once again closely follows the observed $N^2$ variability, except in the eyewall region, where the neglect of latent heating and horizontal turbulence introduces some differences.
 
@@
 
-Outside of the eye, however, $N^2$ continued to increase just above the tropopause and decrease just below.
+Outside of the eye, however, $N^2$ continued to decrease at and just below the tropopause and increase above it.
 The sum of advection and vertical turbulence (Fig.~\ref{fig:stab-48-72}e) indicates that the increase of $N^2$ observed in the 17-18-km layer and inside of the 80-km radius cannot be attributed to these processes, since the sum of these two terms provided forcing for destabilization.
@@
 Outside of the 120-km radius, the region of radiative forcing for stabilization slopes downward, and the increase in $N^2$ observed near 18 km can be explained entirely by a combination of advection and vertical turbulence.
-The layer of decreasing $N^2$ observed near 17 km was forced primarily by vertical turbulence and radiation.
+The layer of decreasing $N^2$ observed near the tropopause was forced primarily by vertical turbulence and radiation.
 Within most of this region, advection provided strong forcing for stabilization, but this forcing was outweighed by the negative $N^2$ tendencies induced by a combination of vertical turbulence and radiation.

### 2018-03-05 paper.tex
Commit at time of printing of second draft. Make a few more changes before submitting to John.

@@
    \end{equation}
-where the potential temperature tendency, $\partial \theta/\partial t$, can be written:
+where the potential temperature tendency, $\partial \theta/\partial t$, can be written, following \cite{Bryan2017}:
    \begin{equation} \label{eq:dthetadt}
-   \frac{\partial \theta}{\partial t} = HADV+VADV+HTURB+VTURB+MP+RAD+DISS 
+%   \frac{\partial \theta}{\partial t} = HADV+VADV+HTURB+VTURB+MP+RAD+DISS 
+   \frac{\partial \theta}{\partial t} = -u\frac{\partial\theta}{\partial r}-w\frac{\partial \theta}{\partial z}+HTURB+VTURB+MP+RAD+DISS
    \end{equation}
-Each term on the right-hand side of Eq. \ref{eq:dthetadt} represents a $\theta$ budget variable, each of which is output directly by the model every minute.
-HADV and VADV are the radial and vertical advective tendencies\footnote{These terms include the tendencies due to implicit diffusion in the fifth-order finite differencing scheme, which are output separately from the advection terms in CM1.}, HTURB and VTURB are the tendencies from the horizontal and vertical turbulence parameterizations, MP is the tendency from the microphysics scheme, RAD is the tendency from the radiation scheme, and DISS is the tendency due to turbulent dissipation.
+Each term on the right-hand side of Eq.~\ref{eq:dthetadt} represents a $\theta$ budget variable, each of which is output directly by the model every minute.
+Since the first term on the right-hand side of Eq.~\ref{eq:dn2dt} is larger than the second term throughout most of the tropopause layer (not shown), the contribution of each of the terms in Eq.~\ref{eq:dthetadt} to the $N^2$ tendency can be interpreted in light of a vertical gradient of each term.
+
+Taking the vertical gradient of the first two terms on the right-hand side yields the time tendency of the vertical $\theta$ gradient due to horizontal and vertical advection\footnote{These terms include the tendencies due to implicit diffusion in the fifth-order finite differencing scheme, which are separated from the advection terms in the CM1 budget output}:
+
+   \begin{equation} \label{eq:advtend}
+   \left(\frac{\partial}{\partial t}\frac{\partial \theta}{\partial z}\right)_{adv} = -u\frac{\partial}{\partial r}\frac{\partial \theta}{\partial z}-w\frac{\partial}{\partial z}\frac{\partial \theta}{\partial z}-\frac{\partial u}{\partial z}\frac{\partial \theta}{\partial r}-\frac{\partial w}{\partial z}\frac{\partial \theta}{\partial z}.
+   \end{equation}
+The first two terms on the right-hand side of Eq.~\ref{eq:advtend} represent advection of static stability by the radial and vertical wind, respectively.
+These terms act to rearrange the static stability field, but cannot strengthen or weaken static stability maxima or minima.
+The third and fourth terms on the right-hand side of Eq.~\ref{eq:advtend} represent, respectively, the tilting of isentropes in the presence of vertical wind shear and the stretching or squashing of isentropes by vertical gradients of vertical velocity.
+Since these terms involve velocity gradients, they can act to strengthen or weaken static stability maxima or minima through differential advection.
+For example, since the $\theta$ of the air flowing out of the eyewall into the upper-tropospheric outflow layer increases as the TC intensifies, $\theta$ increases locally within the outflow layer.
+This acts to increase $\partial \theta/\partial z$ below the outflow maximum and decrease $\partial \theta/\partial z$ above, thereby modifying the static stability field.
+Similarly, the decay of updrafts with height at the top of convective towers can act to increase $\partial \theta/\partial z$ through squashing of isentropes.
+
+Returning to Eq.~\ref{eq:dthetadt}, HTURB and VTURB are the tendencies from the horizontal and vertical turbulence parameterizations, MP is the tendency from the microphysics scheme, RAD is the tendency from the radiation scheme, and DISS is the tendency due to turbulent dissipation.
 This equation neglects Rayleigh damping, since the entire analysis domain is outside of the regions where damping is applied.

### 2018-03-06 paper.tex
SECOND DRAFT SENT TO JOHN

@@
 
-At tropical storm intensity, shortly before RI commenced, a strong inversion layer existed just above the cold-point tropopause.
+When Patricia was at tropical storm intensity, shortly before RI commenced, a strong inversion layer existed just above the cold-point tropopause.
 During the first half of the RI period, this inversion layer weakened throughout Patricia's inner core, with the weakening most pronounced over the developing eye.
@@
 Although hurricanes simulated in an axisymmetric framework tend to be more intense than those observed in nature, the intensity evolution of this simulation matches reasonably well with that observed in Hurricane Patricia.
-After an initial spin-up period of about 20 hours, the modeled storm (Fig.\ref{fig:vmax+pmin}, blue lines) began an RI period that lasted approximately 30 hours.
-After this RI, the storm continued to intensify more slowly until the maximum 10-m wind speed reached 89 m s\textsuperscript{-1} and the minimum sea-level pressure reached its minimum of 846 mb, 81 hours into the simulation.
+After an initial spin-up period of about 20 hours, the modeled storm (Fig.~\ref{fig:vmax+pmin}, blue lines) began an RI period that lasted approximately 30 hours.
+After this RI, the storm continued to intensify more slowly until the maximum 10-m wind speed reached 89 m s\textsuperscript{-1} and the sea-level pressure reached its minimum of 846 hPa, 81 hours into the simulation.
 Hurricane Patricia (red stars) exhibited a similar intensity evolution prior to its landfall, with an RI period leading to a maximum 10-m wind speed of 95 m s\textsuperscript{-1} and a minimum sea-level pressure of 872 hPa.
@@
 
-Taking the vertical gradient of the first two terms on the right-hand side yields the time tendency of the vertical $\theta$ gradient due to horizontal and vertical advection\footnote{These terms include the tendencies due to implicit diffusion in the fifth-order finite differencing scheme, which are separated from the advection terms in the CM1 budget output}:
+Taking the vertical gradient of the first two terms on the right-hand side of Eq.~\ref{eq:dthetadt} yields the time tendency of the vertical $\theta$ gradient due to horizontal and vertical advection\footnote{These terms include the tendencies due to implicit diffusion in the fifth-order finite differencing scheme, which are separated from the advection terms in the CM1 budget output}:
 
@@
 These terms act to rearrange the static stability field, but cannot strengthen or weaken static stability maxima or minima.
-The third and fourth terms on the right-hand side of Eq.~\ref{eq:advtend} represent, respectively, the tilting of isentropes in the presence of vertical wind shear and the stretching or squashing of isentropes by vertical gradients of vertical velocity.
+The third and fourth terms on the right-hand side of Eq.~\ref{eq:advtend} represent, respectively, the tilting of isentropes in the presence of vertical wind shear, and the stretching or squashing of isentropes by vertical gradients of vertical velocity.
 Since these terms involve velocity gradients, they can act to strengthen or weaken static stability maxima or minima through differential advection.
@@
 
-Returning to Eq.~\ref{eq:dthetadt}, HTURB and VTURB are the tendencies from the horizontal and vertical turbulence parameterizations, MP is the tendency from the microphysics scheme, RAD is the tendency from the radiation scheme, and DISS is the tendency due to turbulent dissipation.
-This equation neglects Rayleigh damping, since the entire analysis domain is outside of the regions where damping is applied.
+Returning to Eq.~\ref{eq:dthetadt}, HTURB and VTURB are the $\theta$ tendencies from the horizontal and vertical turbulence parameterizations, MP is the tendency from the microphysics scheme, RAD is the tendency from the radiation scheme, and DISS is the tendency due to turbulent dissipation.
+This equation neglects Rayleigh damping, since the entire analysis domain lies outside of the regions where damping is applied.
 Each term in Eq. \ref{eq:dthetadt} is substituted for ${\partial \theta}/{\partial t}$ in Eq. \ref{eq:dn2dt}, yielding the contribution of each budget term to the static stability tendency.
@@
       The left column of Fig.~\ref{fig:mod+bud+res} depicts the model changes computed using Eq.
-\ref{eq:modelchange}, along with Eq.
-\ref{eq:n2moist} in saturated environments and Eq.
+\ref{eq:modelchange}, together with Eq.~\ref{eq:n2moist} in saturated environments and Eq.
 \ref{eq:n2dry} in subsaturated environments.
-The center column depicts the budget changes computed using Eq. \ref{eq:budgetchange} along with Eq. \ref{eq:n2dry} throughout the domain.
+The center column depicts the budget changes computed using Eq. \ref{eq:budgetchange} together with Eq.~\ref{eq:n2dry} throughout the entire domain.
 Thus, the left column includes the effect of moisture in the $N^2$ computations, whereas the center column neglects moisture.
@@
 The average $N^2$ over the first day of the simulation (Fig.~\ref{fig:n2-24hr-avgs}a) indicates the presence of a weak $N^2$ maximum just above the cold-point tropopause.
-Over the subsequent 24 hours, during the RI period, the $N^2$ within and above this layer decreased near the storm center (Fig.~\ref{fig:n2-24hr-avgs}b).
+Over the subsequent 24 hours, during the RI period, the $N^2$ within and above this layer decreased within the 25-km radius (Fig.~\ref{fig:n2-24hr-avgs}b).
 This decreasing $N^2$ corresponded to an increase in the tropopause height within the developing eye, maximized at the storm center.
@@
 
-Outside of the eye, however, $N^2$ continued to decrease at and just below the tropopause and increase above it.
+Outside of the eye, however, $N^2$ continued to decrease in the layer immediately sorrounding the tropopause.
 The sum of advection and vertical turbulence (Fig.~\ref{fig:stab-48-72}e) indicates that the increase of $N^2$ observed in the 17-18-km layer and inside of the 80-km radius cannot be attributed to these processes, since the sum of these two terms provided forcing for destabilization.
-Instead, radiation (Fig.~\ref{fig:stab-48-72}d), provided the forcing for stabilization in this region.
-Outside of the 80-km radius, both advection (Fig.~\ref{fig:stab-48-72}b) and vertical turbulence (Fig.~\ref{fig:stab-48-72}c) provided forcing for stabilization near the 18-km level.
+Instead, radiation (Fig.~\ref{fig:stab-48-72}d) provided the forcing for stabilization in this region.
+Outside of the 80-km radius, both advection (Fig.~\ref{fig:stab-48-72}b) and vertical turbulence (Fig.~\ref{fig:stab-48-72}c) provided forcing for stabilization near and just above the 18-km level.
 The sum of the two terms (Fig.~\ref{fig:stab-48-72}e) indicates increasing $N^2$ near the 18-km level everywhere outside of the 80-km radius, but this stabilization is slightly weaker in the 90-120-km radial band than the observed value.
-The addition of radiation (Fig.~\ref{fig:stab-48-72}f) provides the extra forcing for stabilization required to account for the observed increase in $N^2$.
-Outside of the 120-km radius, the region of radiative forcing for stabilization slopes downward, and the increase in $N^2$ observed near 18 km can be explained entirely by a combination of advection and vertical turbulence.
+The addition of radiation (Fig.~\ref{fig:stab-48-72}f) provided the extra forcing for stabilization required to account for the observed increase in $N^2$.
+Outside of the 120-km radius, the region of radiative forcing for stabilization sloped downward, and the increase in $N^2$ observed near 18 km can be explained entirely by a combination of advection and vertical turbulence.
 The layer of decreasing $N^2$ observed near the tropopause was forced primarily by vertical turbulence and radiation.
@@
 To investigate the advective processes more closely, the individual contributions of horizontal and vertical advection during the RI period are shown in Fig.~\ref{fig:adv-24-48}, along with the corresponding time-mean radial and vertical velocities and $\theta$.
-The $N^2$ tendencies due to the two advective components (Fig.~\ref{fig:adv-24-48}a,b) exhibit strong cancellation, consistent with flow that is nearly isentropic.
-There are, however, many regions in which flow crosses $\theta$ surfaces; this flow accounts for all non-zero $N^2$ tendencies due to advection previously seen in Fig.~\ref{fig:stab-24-48}b.
+The $N^2$ tendencies due to the two advective components (Fig.~\ref{fig:adv-24-48}a,b) exhibited strong cancellation, consistent with flow that was nearly isentropic.
+There were, however, many regions in which flow crossed $\theta$ surfaces; this flow accounted for all non-zero $N^2$ tendencies due to advection previously seen in Fig.~\ref{fig:stab-24-48}b.
 
@@
 \ref{eq:advtend} suggests that tilting of isentropes within these shear layers contributed to the strong $N^2$ tendencies that flanked the outflow maximum.
-Outside of the eye and eyewall, isentropes generally sloped upward with radius.
-Vertical wind shear acting on these upward-sloping isentropes should act to tilt them into the vertical above the outflow maximum, thereby decreasing $\partial \theta/\partial z$, and tilt them to be more horizontal below the outflow maximum, thereby increasing $\partial \theta/\partial z$.
-This mechanism is the same as that discussed in \cite{TrierSharman}, and is consistent with the change in sign of the $N^2$ tendency at the level of maximum outflow.
+This is consistent with the outflow layer carrying air with increasingly large $\theta$ from the eyewall to large radii as the storm intensified.
+This increase in $\theta$ maximized near the outflow maximum, which acted to decrease $\partial \theta/\partial z$ above the outflow maximum and increase it below.
+%Outside of the eye and eyewall, isentropes generally sloped upward with radius.
+%Vertical wind shear acting on these upward-sloping isentropes should act to tilt them into the vertical above the outflow maximum, thereby decreasing $\partial \theta/\partial z$, and tilt them to be more horizontal below the outflow maximum, thereby increasing $\partial \theta/\partial z$.
+This mechanism is the same as that discussed in \cite{TrierSharman}, in which vertical wind shear in the outflow layer of a mesoscale convective system acted to modify the upper-tropospheric static stability through differential advection of isentropes.
 %Thus, wherever $\partial u/\partial z>0$, the tilting term must force an increase in $N^2$, and wherever $\partial u/\partial z<0$, the tilting term must force a decrease in $N^2$, which is precisely the structure seen in Fig.~\ref{fig:adv-24-48}a.
@@
 
-Curiously, horizontal advection contributed to the $N^2$ tendency everywhere within the eye, even though the mean radial velocity was near zero.
+Curiously, horizontal advection contributed to the $N^2$ tendency everywhere within the eye, even though the mean radial velocity there was near zero.
 Close examination of the model output revealed that these tendencies were forced by advective processes associated with inward-propagating waves.
@@
 Above the lower-stratospheric subsidence maximum, meanwhile, vertical advection acted to decrease $N^2$.
-In the troposphere, differential vertical advection increased $N^2$ within the eyewall region and above the vertical velocity maximum at larger radii.
-Outside of the eyewall and below the vertical velocity maximum, meanwhile, vertical advection acted to decrease $N^2$.
+Below the tropopause, differential vertical advection increased $N^2$ within the eyewall region and also at larger radii above the vertical velocity maximum at larger radii.
+Outside of the eyewall and below the vertical velocity maximum, meanwhile, differential vertical advection acted to decrease $N^2$.
 
@@
   \subsection{The role of radiation}
-During the initial spin-up period (0-24 hours; Fig.~\ref{fig:qi+radten}a), convection was not deep enough to deposit large quantities of ice near the tropopause to create a persistent cirrus canopy.
+During the initial spin-up period (0-24 hours; Fig.~\ref{fig:qi+radten}a), convection was not deep enough to deposit large quantities of ice near the tropopause and create a persistent cirrus canopy.
 Due to the lack of ice particles, the radiative heating tendencies during this period (Fig.~\ref{fig:qi+radten}b) were relatively small and confined to the region above a few particularly strong, although transient, convective towers.
-During RI (24-48 hours; Fig.~\ref{fig:qi+radten}b), the eyewall updraft strengthened and a radially-extensive cirrus canopy developed near the tropopause.
+During RI (24-48 hours), the eyewall updraft strengthened and a radially-extensive cirrus canopy developed near the tropopause (Fig.~\ref{fig:qi+radten}c).
 The enhanced vertical gradient of ice mixing ratio at the top of the cirrus canopy induced strong diurnal-mean radiative cooling near the tropopause (Fig.~\ref{fig:qi+radten}d).
@@
 
-After the TC's RI period completed (48-72 hours; Fig.~\ref{fig:qi+radten}f), strong radiative cooling remained near the tropopause at inner radii, sloping downward with the top of the cirrus canopy to below the tropopause at outer radii.
+After the TC's RI period completed (48-72 hours), strong radiative cooling remained near the tropopause at inner radii (Fig.~\ref{fig:qi+radten}f), sloping downward with the top of the cirrus canopy to below the tropopause at outer radii.
 Cooling rates exceeded 1 K h\textsuperscript{-1} just above the tropopause between the 30- and 70-km radii.
@@
 To compare our results to those of \cite{buetal}, we ran a simulation identical to that described in Section 2, except using the NASA-Goddard radiation scheme and 625-m vertical grid spacing, to match those of \cite{buetal}.
-This simulation produced a maximum radiative cooling rate of 0.3 K h\textsuperscript{-1}, which agrees with that shown in \cite{buetal}.
-Another simulation using 625-m vertical grid spacing and RRTMG radiation produced cooling rates of up to 0.6 K h\textsuperscript{-1}, which is consistent with the WRF simulations of \cite{buetal}.
+This simulation produced a maximum 24-hour-average radiative cooling rate of 0.3 K h\textsuperscript{-1}, which agrees with that shown in \cite{buetal}.
+Another simulation using 625-m vertical grid spacing and RRTMG radiation produced 24-hour-average cooling rates of up to 0.6 K h\textsuperscript{-1}, which is consistent with the WRF simulations of \cite{buetal}.
 This suggests that vertical grid spacing smaller than 625 m is necessary to resolve properly the radiative cooling at the top of the cirrus canopy, and that the results can be quite sensitive to the radiation scheme used.
 
-Time-mean radiative warming spread from 30- to 160-km radius within the cirrus canopy.
+Meanwhile below the tropopause, time-mean radiative warming spread from 30- to 160-km radius within the cirrus canopy.
 The existence of radiative cooling overlying radiative warming in this region led to radiatively-forced destabilization at and below the tropopause, as was observed in Fig.~\ref{fig:stab-48-72}d.

### 2018-03-07 paper.tex
Address John's comments on budget comtributions time series on page 9. Removed crossed-out words.

@@
 In every 24-hour period, the budget changes are nearly identical to the model changes, which is reflected in the near-zero residuals in the right column.
-This indicates that the budget accurately represents the model variability, which implies that the neglect of moisture in the budget computation introduces negligible error within the anaysis domain\footnote{This is not the case in the lower- and mid-troposphere, where the residual actually exceeds the budget tendencies in many places, likely due to the neglect of moisture; thus we limit this analysis to the upper troposphere and lower stratosphere.}.
+This indicates that the budget accurately represents the model variability, which implies that the neglect of moisture in the budget computation introduces negligible error within the analysis domain\footnote{This is not the case in the lower- and mid-troposphere, where the residual actually exceeds the budget tendencies in many places, likely due to the neglect of moisture; thus we limit this analysis to the upper troposphere and lower stratosphere.}.
 
@@
 Advection (Fig.~\ref{fig:avgbudterms}, red line) plays an important role in the mean tropopause-layer static stability tendency at all times, and vertical turbulence (Fig.~\ref{fig:avgbudterms}, blue line) and radiation (Fig.~\ref{fig:avgbudterms}, dark green line) also contribute significantly.
-The remaining three processes - horizontal turbulence, microphysics, and dissipative heating - lie atop one another near zero.
-Although the horizontal turbulence and microphysics terms can be quite large in the eyewall region, they are negligible everywhere outside of the eyewall, and do not play important roles in the mesoscale tropopause variability.
-Dissipative heating, meanwhile, is relatively small everywhere.
-%Although the contribution from horizontal turbulence (Fig.~\ref{fig:avgbudterms}, purple line) becomes more important after 48 hours, it is confined to a very small region immediately surrounding the eyewall tangential velocity maximum (not shown), and is negligible throughout the rest of the tropopause layer.
-%The two remaining processes - microphysics and dissipative heating (Fig.~\ref{fig:avgbudterms}, orange and light green lines, respectively) - lie atop one another near zero.
-%Although the latent heating term can be quite large in the eyewall region, it is negligible everywhere outside of the eyewall, as are the effects of dissipative heating.
+The remaining three processes - horizontal turbulence, microphysics, and dissipative heating -  are negligible everywhere outside of the eyewall, and do not play important roles in the mesoscale tropopause variability.
 

### 2018-03-07 paper.tex
Force newline after paragraph labels in Results section using command \mbox{}\ and and indent the first paragraph using \indent command, per John's comment on Page 10.

@@
 
-\paragraph{0-24 hours}
-The weakening of the lower-stratospheric $N^2$ maximum during the initial spin-up period is reflected in the total $N^2$ budget change over this time (Fig.~\ref{fig:stab-00-24}a).
+\paragraph{0-24 hours}\mbox{}\\
+\indent The weakening of the lower-stratospheric $N^2$ maximum during the initial spin-up period is reflected in the total $N^2$ budget change over this time (Fig.~\ref{fig:stab-00-24}a).
 The layer just above the cold-point tropopause was characterized by decreasing $N^2$ (purple shading), maximizing at the storm center.
@@
 
-\paragraph{24-48 hours}
-During the RI period, $N^2$ within the eye generally decreased above 16 km and increased below (Fig.~\ref{fig:stab-24-48}a), with the destabilization above 16 km maximizing near the level of the mean cold-point tropopause.
+\paragraph{24-48 hours}\mbox{}\\
+\indent During the RI period, $N^2$ within the eye generally decreased above 16 km and increased below (Fig.~\ref{fig:stab-24-48}a), with the destabilization above 16 km maximizing near the level of the mean cold-point tropopause.
 These tendencies at the innermost radii were driven almost entirely by advection (Fig.~\ref{fig:stab-24-48}b); vertical turbulence (Fig.~\ref{fig:stab-24-48}c) and radiation (Fig.~\ref{fig:stab-24-48}d) contributed negligibly to the static stability tendencies in this region.
@@
 
-\paragraph{48-72 hours}
-After the storm's maximum wind speed leveled off near 80 m s\textsuperscript{-1}, the magnitude of the static stability tendencies within the eye decreased to near zero (Fig.~\ref{fig:stab-48-72}a).
+\paragraph{48-72 hours}\mbox{}\\
+\indent After the storm's maximum wind speed leveled off near 80 m s\textsuperscript{-1}, the magnitude of the static stability tendencies within the eye decreased to near zero (Fig.~\ref{fig:stab-48-72}a).
 

### 2018-03-07 paper.tex
Address specific comments on Pages 10-12

@@
 Static stability outside of the eye, meanwhile, continued to increase just above the cold-point tropopause.
-This $N^2$ evolution closely follows that observed in Hurricane Patricia (2015; \citeauthor{DuranMolinari2018} \citeyear{DuranMolinari2018}).
+This $N^2$ evolution closely follows that observed in Hurricane Patricia (2015; \citeauthor{DuranMolinari2018} \citeyear{DuranMolinari2018}, see their Fig. 4).
 The mechanisms that led to these $N^2$ changes will be investigated in the subsequent sections.
@@
 \paragraph{0-24 hours}\mbox{}\\
-\indent The weakening of the lower-stratospheric $N^2$ maximum during the initial spin-up period is reflected in the total $N^2$ budget change over this time (Fig.~\ref{fig:stab-00-24}a).
+\indent The initial spin-up period was characterized by a steady increase of the maximum wind speed from 11 m s\textsuperscript{-1} to 22 m s\textsuperscript{-1} (Fig.~\ref{fig:vmax+pmin}a, blue line), an intensification rate that closely matched that of TC Patricia (Fig.~\ref{fig:vmax+pmin}a, red stars).
+The weakening of the lower-stratospheric $N^2$ maximum during this period is reflected in the total $N^2$ budget change over this time (Fig.~\ref{fig:stab-00-24}a).
 The layer just above the cold-point tropopause was characterized by decreasing $N^2$ (purple shading), maximizing at the storm center.
@@
 Radiative tendencies, meanwhile, (Fig.~\ref{fig:stab-00-24}d) acted to destabilize the layer below about 16 km and stabilize the layer between 16 and 17 km.
-The sum of advection, vertical turbulence, and radiation (Fig.~\ref{fig:stab-00-24}f) reproduces the total change in $N^2$ almost exactly.
+The sum of advection, vertical turbulence, and radiation (Fig.~\ref{fig:stab-00-24}f) reproduced the total change in $N^2$ almost exactly.
 
 \paragraph{24-48 hours}\mbox{}\\
-\indent During the RI period, $N^2$ within the eye generally decreased above 16 km and increased below (Fig.~\ref{fig:stab-24-48}a), with the destabilization above 16 km maximizing near the level of the mean cold-point tropopause.
-These tendencies at the innermost radii were driven almost entirely by advection (Fig.~\ref{fig:stab-24-48}b); vertical turbulence (Fig.~\ref{fig:stab-24-48}c) and radiation (Fig.~\ref{fig:stab-24-48}d) contributed negligibly to the static stability tendencies in this region.
+\indent During the RI period, the maximum wind speed increased from 22 m s\textsuperscript{-1} to 80 m s\textsuperscript{-1}.
+Over this time, $N^2$ within the eye generally decreased above 16 km and increased below (Fig.~\ref{fig:stab-24-48}a), with the destabilization above 16 km maximizing near the level of the mean cold-point tropopause.
+These tendencies at the innermost radii were driven almost entirely by advection (Fig.~\ref{fig:stab-24-48}b).
+Vertical turbulence (Fig.~\ref{fig:stab-24-48}c) and radiation (Fig.~\ref{fig:stab-24-48}d) contributed negligibly to the static stability tendencies in this region.
 

### 2018-03-07 paper.tex
Fix typo on Page 17 and make dashed lines darker in Vmax+Pmin figure.

@@
 Comparison of these turbulent regions to the $N^2$ tendencies in Figs.
-\ref{fig:stab-24-48}c and \ref{fig:stab-48-72}c reveals that the layers in which vertical eddy diffusivity maximized corresponded to layers of destabiliztion due to vertical turbulence.
+\ref{fig:stab-24-48}c and \ref{fig:stab-48-72}c reveals that the layers in which vertical eddy diffusivity maximized corresponded to layers of destabilization due to vertical turbulence.
 Just outside of these layers, however, vertical turbulence acted to increase $N^2$.

### 2018-03-08 paper.tex
A few changes...

@@
 
+Using a high-resolution dropsonde dataset collected during the Tropical Cyclone Intensity experiment (TCI; \citeauthor{DoyleTCI} \citeyear{DoyleTCI}), \cite{DuranMolinari2018} observed dramatic changes in tropopause structure during the rapid intensification (RI) of Hurricane Patricia (2015).
+The goal of the present paper is to analyze the processes that might have produced the upper-tropospheric and lower-stratospheric fluctuations observed in Patricia using an idealized axisymmetric simulation.
+
 After undergoing a remarkably rapid intensification (RI), Hurricane Patricia (2015) set a new record as the strongest tropical cyclone (TC) ever observed in the Western Hemisphere (\citeauthor{Kimberlainetal2016} \citeyear{Kimberlainetal2016}; \citeauthor{Rogersetal2017} \citeyear{Rogersetal2017}).
-High-altitude dropsonde observations taken during the Tropical Cyclone Intensity (TCI) experiment captured this RI in unprecedented detail \citep{DoyleTCI}.
-These observations revealed dramatic changes in the structure of the cold-point tropopause and upper-level static stability as the storm intensified \citep{DuranMolinari2018}.
-
-When Patricia was at tropical storm intensity, shortly before RI commenced, a strong inversion layer existed just above the cold-point tropopause.
+%High-altitude dropsonde observations taken during the Tropical Cyclone Intensity (TCI) experiment captured this RI in unprecedented detail \citep{DoyleTCI}.
+TCI dropsonde observations collected during this RI period revealed dramatic changes in the cold-point tropopause height and upper-level static stability \citep{DuranMolinari2018}.
+In particular, when Patricia was at tropical storm intensity shortly before RI commenced, a strong inversion layer existed just above the cold-point tropopause.
 During the first half of the RI period, this inversion layer weakened throughout Patricia's inner core, with the weakening most pronounced over the developing eye.
@@
 Meanwhile over the eyewall region, the static stability increased and the tropopause remained near its initial level.
-The mechanisms that might have led to this tropopause-layer variability will be investigated in the current paper using idealized simulations.
+%The mechanisms that might have led to this tropopause-layer variability will be investigated in the current paper using idealized simulations.
 

### 2018-03-09 paper.tex
Change Abstract, add mention of radiation and vertical turbulence to Introduction per John's comment, and make a few other changes.

@@
 \indent A budget analysis reveals that advection contributes to the static stability tendencies at all times throughout the upper troposphere and lower stratosphere.
-Differential advection is particularly important within the eye, where it acts to destabilize the layer near and above the cold-point tropopause.
+Within the eye, differential advection plays a particularly important role in destabilizing the layer near and above the cold-point tropopause.
 Outside of the eye, a radial-vertical circulation develops during RI, with strong outflow below the tropopause and weak inflow above.
@@
 They found that radial and vertical advection both played important roles in warm core development throughout RI, and subgrid-scale diffusion became particularly important during the later stage of RI.
+
+Other processes that can modify the static stability in the upper troposphere of TCs include radiative heating within and near the top of the cirrus canopy and shear-induced turbulent mixing near the outflow jet.
 To our knowledge, the only paper that has examined explicitly the static stability evolution in a modeled TC is \cite{Kepertetal2016}, but their analysis was limited to the boundary layer.
@@
 After an initial spin-up period of about 20 hours, the modeled storm (Fig.~\ref{fig:vmax+pmin}, blue lines) began an RI period that lasted approximately 30 hours.
-After this RI, the storm continued to intensify more slowly until the maximum 10-m wind speed reached 89 m s\textsuperscript{-1} and the sea-level pressure reached its minimum of 846 hPa, 81 hours into the simulation.
+After this RI, the storm continued to intensify more slowly until the maximum 10-m wind speed reached 89 m s\textsuperscript{-1} and the sea-level pressure reached its minimum of 846 hPa 81 hours into the simulation.
 Hurricane Patricia (red stars) exhibited a similar intensity evolution prior to its landfall, with an RI period leading to a maximum 10-m wind speed of 95 m s\textsuperscript{-1} and a minimum sea-level pressure of 872 hPa.
@@
 For simplicity, however, only Eq.
-\ref{eq:n2dry} will be employed for the budget computations\footnote{The validity of this approximation will be substantiated later in this section.}.
+\ref{eq:n2dry} will be employed for the budget computations throughout the entire domain\footnote{The validity of this approximation will be substantiated later in this section.}.
 
@@
 Each term on the right-hand side of Eq.~\ref{eq:dthetadt} represents a $\theta$ budget variable, each of which is output directly by the model every minute.
-Since the first term on the right-hand side of Eq.~\ref{eq:dn2dt} is larger than the second term throughout most of the tropopause layer (not shown), the contribution of each of the terms in Eq.~\ref{eq:dthetadt} to the $N^2$ tendency can be interpreted in light of a vertical gradient of each term.
+
+The first term on the right-hand side of Eq. ~\ref{eq:dn2dt} is larger than the second term throughout most of the tropopause layer (not shown).
+Consequently, the contribution of each of the terms in Eq.~\ref{eq:dthetadt} to the $N^2$ tendency can be interpreted in light of a vertical gradient of each term.
+%Since the first term on the right-hand side of Eq.~\ref{eq:dn2dt} is larger than the second term throughout most of the tropopause layer (not shown), the contribution of each of the terms in Eq.~\ref{eq:dthetadt} to the $N^2$ tendency can be interpreted in light of a vertical gradient of each term.
 
@@
 Since these terms involve velocity gradients, they can act to strengthen or weaken static stability maxima or minima through differential advection.
-For example, since the $\theta$ of the air flowing out of the eyewall into the upper-tropospheric outflow layer increases as the TC intensifies, $\theta$ increases locally within the outflow layer.
-This acts to increase $\partial \theta/\partial z$ below the outflow maximum and decrease $\partial \theta/\partial z$ above, thereby modifying the static stability field.
-Similarly, the decay of updrafts with height at the top of convective towers can act to increase $\partial \theta/\partial z$ through squashing of isentropes.
+%For example, since the $\theta$ of the air flowing out of the eyewall into the upper-tropospheric outflow layer increases as the TC intensifies, $\theta$ increases locally within the outflow layer.
+%This acts to increase $\partial \theta/\partial z$ below the outflow maximum and decrease $\partial \theta/\partial z$ above, thereby modifying the static stability field.
+%Similarly, the decay of updrafts with height at the top of convective towers can act to increase $\partial \theta/\partial z$ through squashing of isentropes.
 
@@
 For this and all subsequent radial-vertical cross sections, a 1-2-1 smoother is applied once in the radial direction to eliminate $2\Delta r$ noise that appears in some of the raw model output and calculated fields.
-      The left column of Fig.~\ref{fig:mod+bud+res} depicts the model changes computed using Eq.
-\ref{eq:modelchange}, together with Eq.~\ref{eq:n2moist} in saturated environments and Eq.
+      The left column of Fig.~\ref{fig:mod+bud+res} depicts the model changes computed using Eq.~\ref{eq:modelchange}, together with Eq.~\ref{eq:n2moist} in saturated environments and Eq.
 \ref{eq:n2dry} in subsaturated environments.

### 2018-03-19 paper.tex
Added Figs. 11 and 12, along with their descriptions.

@@
 Since these terms involve velocity gradients, they can act to strengthen or weaken static stability maxima or minima through differential advection.
+Unless otherwise stated, the "advection" term in this paper indicates the sum of the terms in Eq.~\ref{eq:advtend}.
 %For example, since the $\theta$ of the air flowing out of the eyewall into the upper-tropospheric outflow layer increases as the TC intensifies, $\theta$ increases locally within the outflow layer.
@@
 The $N^2$ tendencies due to the two advective components (Fig.~\ref{fig:adv-24-48}a,b) exhibited strong cancellation, consistent with flow that was nearly isentropic.
-There were, however, many regions in which flow crossed $\theta$ surfaces; this flow accounted for all non-zero $N^2$ tendencies due to advection previously seen in Fig.~\ref{fig:stab-24-48}b.
+There existed, however, a large region near the tropopause in which the total advective tendency was nonzero (Fig.~\ref{fig:stab-24-48}b).
+These nonzero tendencies were related to the development of the TC's seconary circulation as it intensified.
 
@@
 Although vertical turbulence always acts to eliminate vertical gradients of $\theta$, this adjustment toward a neutral state only occurs where the mixing takes place.
-If turbulence occurs in a stably-stratified layer, it will act to decrease $\theta$ at the top of the layer and increase it below.
+Fig.~\ref{fig:schematic} depicts the effect of turbulent mixing on the $\theta$ profile of an initially stably-stratified layer.
+At the initial time in this idealized case, $\theta$ increases with height at a constant rate (Fig.~\ref{fig:schematic}, left panel).
+The imposition of tubulence (blue hatching) adjusts the $\theta$ profile within the mixed layer toward a constant value equal to the mean value of that layer in the initial state (Fig.~\ref{fig:schematic}, right panel).
+%If turbulence occurs in a stably-stratified layer, it will act to decrease $\theta$ at the top of the layer and increase it at the bottom.
 Just above and just below the mixed layer, however, the $\theta$ profile remains undisturbed.
@@
 Radiation and vertical turbulence played particularly important roles in developing the strong $N^2$ maximum just above the cold-point tropopause during RI.
-Since these two processes are parameterized, and radiation closely depends on yet another parameterized process (microphysics), the tropopause-layer $N^2$ variability could be quite sensitive to the assumptions inherent to the parameterizations used.
+
+To put the $N^2$ variability observed near the tropopause into context, Fig.~\ref{fig:fulltrop} depicts the model change in $N^2$ over the RI period from 0 to 21 km altitude, along with the vertical eddy diffusivity and the radiative heating rate.
+It is clear that the largest changes in $N^2$ occurred in a relatively shallow layer immediately surrounding the tropopause (Fig.~\ref{fig:fulltrop}a).
+This shalow layer also contained the largest diurnally-averaged radiative heating tendencies found anywhere in the domain (Fig.~\ref{fig:fulltrop}c).
+%The largest diurnally-averaged radiative heating tendencies found anywhere in the domain also were contained within this relatively shallow layer (Fig.~\ref{fig:fulltrop}c).
+Values of vertical eddy diffusivity larger than any found outside of the boundary layer also resided in the upper troposphere (Fig.~\ref{fig:fulltrop}b).
+%The upper troposphere also contained a deep layer of vertical eddy diffusivity values larger than those found anywhere outside of the boundary layer.
+The results herein suggest that this tubulence not only develops as a response to the presence of small static stability and large vertical wind shear, as discussed by \cite{Molinarietal} and \cite{DuranMolinari2016}, but also can actively increase the static stability in highly localized regions just above and below the mixed layers.
+
+Since two of the most important processes contributing to the $N^2$ variability are parameterized, and one (radiation) closely depends on yet another parameterized process (microphysics), the tropopause-layer $N^2$ variability could be quite sensitive to the assumptions inherent to the parameterizations used.
 A better understanding of the microphysical characteristics of the TC cirrus canopy, its interaction with radiation, and outflow-layer turbulence is critical to understanding the tropopause-layer $N^2$ evolution.
+
 %A number of sensitivity experiments revealed that the details of the $N^2$ evolution were sensitive to the selection of the radiation scheme, the vertical turbulence length scale, and the vertical grid spacing.
@@
 In this paper, all of the variables were averaged over a full diurnal cycle to eliminate the effects of diurnal variability and isolate the overall storm evolution.
-Diurnal variations in static stability near the tropopause are potentially of interest with respect to the tropical cyclone diurnal cycle, however, and will be the subject of future work.
+Diurnal variations in static stability near the tropopause are potentially of interest with respect to the tropical cyclone diurnal cycle, and will be the subject of future work.
 
@@
 \begin{figure*}[ht]
+\centerline{\includegraphics[width=39pc]{figures/Schematic2.png}}
+\caption{Idealized schematic diagram of turbulent mixing in a stably-stratified layer.
+At the initial time (left panel), potential temperature increases with height at a constant rate (thick black line).
+The imposition of turbulence within a portion of the layer (blue hatching) adjusts the potential temperature profile toward the mean initial value of that layer.
+After a period of mixing (right panel) the potential temperature in the mixed layer does not vary with height, but just above and just below the mixed layer, it rapidly increases with height.}
+\label{fig:schematic}
+\end{figure*}
+
+%FIGURE 11%
+\begin{figure*}[ht]
 \centerline{\includegraphics[width=39pc]{figures/khvten.png}}
@@
 \end{figure*}
+
+%FIGURE 12%
+\begin{figure*}[ht]
+\centerline{\includegraphics[width=19pc]{figures/fulltrop.png}}
+\end{figure*}
+\begin{figure}
+\caption{(Top panel) Change in $N^2$ over the 24-48-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 h)\textsuperscript{-1}) directly output by the model for the 0-21-km layer.
+(Middle panel) Vertical eddy diffusivity (m\textsuperscript{2} s\textsuperscript{-2} averaged over the same time period.
+(Bottom panel) Radiative heating rate (K h\textsuperscript{-1}) averaged over the same time period.}
+\label{fig:fulltrop}
+\end{figure}
 

### 2018-03-19 paper.tex
THIRD DRAFT SUBMITTED TO JOHN.

@@
 Since these terms involve velocity gradients, they can act to strengthen or weaken static stability maxima or minima through differential advection.
-Unless otherwise stated, the "advection" term in this paper indicates the sum of the terms in Eq.~\ref{eq:advtend}.
+Unless otherwise stated, any reference to "advection" in this paper indicates the sum of all of the terms in Eq.~\ref{eq:advtend}.
 %For example, since the $\theta$ of the air flowing out of the eyewall into the upper-tropospheric outflow layer increases as the TC intensifies, $\theta$ increases locally within the outflow layer.
@@
 %An interesting result of the budget analysis was that turbulent mixing acted to increase static stability in some regions of the storm.
-Although vertical turbulence always acts to eliminate vertical gradients of $\theta$, this adjustment toward a neutral state only occurs where the mixing takes place.
+%Although vertical turbulence always acts to eliminate vertical gradients of $\theta$, this adjustment toward a neutral state only occurs where the mixing takes place.
 Fig.~\ref{fig:schematic} depicts the effect of turbulent mixing on the $\theta$ profile of an initially stably-stratified layer.
@@
 It is clear that the largest changes in $N^2$ occurred in a relatively shallow layer immediately surrounding the tropopause (Fig.~\ref{fig:fulltrop}a).
-This shalow layer also contained the largest diurnally-averaged radiative heating tendencies found anywhere in the domain (Fig.~\ref{fig:fulltrop}c).
+This shallow layer also contained the largest diurnally-averaged radiative heating tendencies found anywhere in the domain (Fig.~\ref{fig:fulltrop}c).
 %The largest diurnally-averaged radiative heating tendencies found anywhere in the domain also were contained within this relatively shallow layer (Fig.~\ref{fig:fulltrop}c).
@@
 \caption{(Top panel) Change in $N^2$ over the 24-48-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 h)\textsuperscript{-1}) directly output by the model for the 0-21-km layer.
-(Middle panel) Vertical eddy diffusivity (m\textsuperscript{2} s\textsuperscript{-2} averaged over the same time period.
+(Middle panel) Vertical eddy diffusivity (m\textsuperscript{2} s\textsuperscript{-2}) averaged over the same time period.
 (Bottom panel) Radiative heating rate (K h\textsuperscript{-1}) averaged over the same time period.}

### 2018-03-21 paper.tex
Modify abstract per John's comments. Currently 246 words.

@@
 Outside of the eye, static stability increases considerably just above the cold-point tropopause, and the tropopause remains near its initial level.\\
-\indent A budget analysis reveals that advection contributes to the static stability tendencies at all times throughout the upper troposphere and lower stratosphere.
+\indent A budget analysis reveals that the advection term, which includes differential advection of potential temperature and direct advection of static stability, is important throughout the upper troposphere and lower stratosphere.
 Within the eye, differential advection plays a particularly important role in destabilizing the layer near and above the cold-point tropopause.
 Outside of the eye, a radial-vertical circulation develops during RI, with strong outflow below the tropopause and weak inflow above.
-Vertical wind shear above and below the upper-tropospheric outflow maximum induces turbulence, which provides forcing for both destabilization and stabilization in the tropopause layer.
+The upper-tropospheric outflow layer exports high potential temperature ($\theta$) air from the eyewall to large radii in the upper troposphere.
+This increase in $\theta$ forces stabilization below the outfow jet and destabilization above.
+Vertical wind shear above and below the upper-tropospheric outflow maximum induces vertical gradients of turbulence, which also modify the vertical stability profile.
 Meanwhile, as organized convection reaches the tropopause, radiative heating tendencies at the top of the cirrus canopy generally act to destabilize the upper troposphere and stabilize the lower stratosphere.
-Turbulent mixing and radiative heating combine to play an important role in the development of the strong stable layer immediately above the cold-point tropopause during RI.
-The results suggest that turbulence and radiation, alongside advection, play fundamental roles in the upper-level static stability evolution of TCs.}
+Turbulent mixing and radiative heating combine to play an important role in the development of the strong stable layer immediately above the cold-point tropopause during RI.}
+%The results suggest that turbulence and radiation, alongside advection, play fundamental roles in the upper-level static stability evolution of TCs.}
 %The conclusions are robust to changes in the initial thermodynamic profile and prescribed vertical mixing length within a reasonable range of values.}
@@
 To our knowledge, the only paper that has examined explicitly the static stability evolution in a modeled TC is \cite{Kepertetal2016}, but their analysis was limited to the boundary layer.
-The analysis herein is based upon that of \cite{SternZhang2013}, except using a static stability budget similar to that of \cite{Kepertetal2016}, with a focus on the upper troposphere and lower stratosphere.
+The analysis herein is based upon that of \cite{SternZhang2013}, except using a static stability budget similar to that of \cite{Kepertetal2016}, with a focus on the upper-tropospheric and lower-stratospheric evolution during RI.
 

### 2018-03-21 paper.tex
Remove Appendix, per discussion with John.

@@
 % Use \appendix if there is only one appendix.
-\appendix
+%\appendix
 
@@
 %% Appendix title is necessary! For appendix title:
-\appendixtitle{Sensitivity experiments}
-The simulations exhibited some sensitivity to the initial thermodynamic profile and the prescribed vertical mixing length.
-Although the details of the intensification and the tropopause-layer $N^2$ evolution varied when these quantities were changed, the conclusions of the paper remain unchanged.
-
-%%% Appendix section numbering (note, skip \section and begin with \subsection)
- \subsection{Sensitivity to the initial thermodynamic profile}
-A number of sensitivity experiments were conducted using a variety of initial soundings.
-Changing the initial temperature and humidity profiles affected the timing of the onset of organized deep convection and the rapidity of intensification.
-In all simulations, however, convection eventually penetrated to the tropopause, at which time vertical turbulence and radiation combined with advection to adjust the $N^2$ profile toward that which was observed in the control run.
-By the end of the RI period in every simulation, all three processes were actively modifying the $N^2$ profile near the tropopause.
-
-As an example, 24-hour averages of $N^2$ are plotted in Fig.
+%\appendixtitle{Sensitivity experiments}
+%The simulations exhibited some sensitivity to the initial thermodynamic profile and the prescribed vertical mixing length.
+%Although the details of the intensification and the tropopause-layer $N^2$ evolution varied when these quantities were changed, the conclusions of the paper remain unchanged.
+%
+%%%% Appendix section numbering (note, skip \section and begin with \subsection)
+% \subsection{Sensitivity to the initial thermodynamic profile}
+%A number of sensitivity experiments were conducted using a variety of initial soundings.
+%Changing the initial temperature and humidity profiles affected the timing of the onset of organized deep convection and the rapidity of intensification.
+%In all simulations, however, convection eventually penetrated to the tropopause, at which time vertical turbulence and radiation combined with advection to adjust the $N^2$ profile toward that which was observed in the control run.
+%By the end of the RI period in every simulation, all three processes were actively modifying the $N^2$ profile near the tropopause.
+%
+%As an example, 24-hour averages of $N^2$ are plotted in Fig.
 A1 for a simulation that was identical to that used in this paper, except the initial sounding was determined by averaging every CFSR grid point within 1000 km of TC Patricia's storm center at 18 UTC 21 October 2015 instead of averaging only within the 100-km radius.
-Although the lower-stratospheric stable layer developed more slowly and was weaker than that shown in Fig.~\ref{fig:n2-24hr-avgs}, the overall evolution was quite similar and the same budget terms dominated the $N^2$ evolution.
-
- \subsection{Sensitivity to the vertical mixing length}
-The rate of turbulent mixing in the Smagorinsky scheme used herein is highly dependent on a prescribed length scale.
-The vertical mixing length used in this paper (100 m) was based on the sensitivity experiments of \cite{Bryan2012}.
-Prescribing a smaller mixing length produces smaller $\theta$ tendencies due to turbulence, but even with a mixing length on the low end of those tested by \cite{Bryan2012}, turbulence still played an important role in the tropopause-layer $N^2$ evolution.
-Fig. A2 shows the 24-hour-averaged contributions of turbulent mixing to the $N^2$ evolution from a simulation identical to that used in this paper, except with a vertical mixing length of 50 m.
-At all times, vertical turbulence still played an important role in the tropopause-layer $N^2$ evolution, particularly during the latter stages of RI (48-72 hours).
+%Although the lower-stratospheric stable layer developed more slowly and was weaker than that shown in Fig.~\ref{fig:n2-24hr-avgs}, the overall evolution was quite similar and the same budget terms dominated the $N^2$ evolution.
+%
+% \subsection{Sensitivity to the vertical mixing length}
+%The rate of turbulent mixing in the Smagorinsky scheme used herein is highly dependent on a prescribed length scale.
+%The vertical mixing length used in this paper (100 m) was based on the sensitivity experiments of \cite{Bryan2012}.
+%Prescribing a smaller mixing length produces smaller $\theta$ tendencies due to turbulence, but even with a mixing length on the low end of those tested by \cite{Bryan2012}, turbulence still played an important role in the tropopause-layer $N^2$ evolution.
+%Fig. A2 shows the 24-hour-averaged contributions of turbulent mixing to the $N^2$ evolution from a simulation identical to that used in this paper, except with a vertical mixing length of 50 m.
+%At all times, vertical turbulence still played an important role in the tropopause-layer $N^2$ evolution, particularly during the latter stages of RI (48-72 hours).
 

### 2018-03-21 paper.tex
Remove Appendix figures.

@@
 
-%FIGURE A1%
-\begin{figure*}[ht]
-\centerline{\includegraphics[width=39pc]{figures/n2-1000km.png}}
-\appendcaption{A1}{Twenty-four-hour averages of squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$; 10\textsuperscript{-4} s\textsuperscript{-2}) over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, and (d) 72-96 hours for the simulation described in Appendix Aa.
+%%FIGURE A1%
+%\begin{figure*}[ht]
+%\centerline{\includegraphics[width=39pc]{figures/n2-1000km.png}}
+%\appendcaption{A1}{Twenty-four-hour averages of squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$; 10\textsuperscript{-4} s\textsuperscript{-2}) over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, and (d) 72-96 hours for the simulation described in Appendix Aa.
 Orange lines represent the cold-point tropopause height averaged over the same time periods.}
-\label{fig:n2-1000km}
-\end{figure*}
-
-%FIGURE A2%
-\begin{figure*}[ht]
-\centerline{\includegraphics[width=39pc]{figures/turb-50m.png}}
-\appendcaption{A2}{The contribution of vertical turbulence to the $N^2$ variability (10\textsuperscript{-4} s\textsuperscript{-2} (24 h)\textsuperscript{-1}) averaged over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, and (d) 72-96 hours for the simulation described in Appendix Ab.
+%\label{fig:n2-1000km}
+%\end{figure*}
+%
+%%FIGURE A2%
+%\begin{figure*}[ht]
+%\centerline{\includegraphics[width=39pc]{figures/turb-50m.png}}
+%\appendcaption{A2}{The contribution of vertical turbulence to the $N^2$ variability (10\textsuperscript{-4} s\textsuperscript{-2} (24 h)\textsuperscript{-1}) averaged over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, and (d) 72-96 hours for the simulation described in Appendix Ab.
 Orange lines represent the cold-point tropopause height averaged over the same time periods.}
-\label{fig:turb-50m}
-\end{figure*}
+%\label{fig:turb-50m}
+%\end{figure*}
 

### 2018-03-21 paper.tex
Address the rest of John's comments except those on the figures.

@@
 
-Idealized simulations of a TC analyzed by \cite{OhnoSatoh2015} suggested that the development of an upper-level warm core near the 13-km level acted to decrease the static stability near the tropopause within the eye (compare their Figs.
-9,10).
-Although the mechanisms that might drive this static stability evolution have not been examined explicitly, \cite{SternZhang2013} described the development of the TC warm core using a potential temperature ($\theta$) budget analysis.
+An idealized simulations of a TC analyzed by \cite{OhnoSatoh2015} suggested that the development of an upper-level warm core near the 13-km level acted to decrease the static stability near the tropopause within the eye.
+During the early stage of development in their simulation (their Fig. 9), static stability above 16 km was large at all radii.
+However, after the storm's intensification, the static stability above 16 km within the eye was markedly smaller (their Fig. 10c).
+Although the mechanisms that might drive this static stability evolution have not been examined explicitly it might be related to the development of an upper-tropospheric warm care within the eye.
+\cite{SternZhang2013} described the development of the TC warm core using a potential temperature ($\theta$) budget analysis.
+Although the warm anomaly in their simulation maximized in the mid-levels, they also note that a secondary warming maximum existed in the 12-14-km layer.
 They found that radial and vertical advection both played important roles in warm core development throughout RI, and subgrid-scale diffusion became particularly important during the later stage of RI.
+The warming of the upper troposophere by these advective and diffusive processes could contribute to a decrease in static stability near the tropoopause within the eye.
+Other processes that can modify the static stability in the upper troposphere of TCs include radiative heating within and near the top of the cirrus canopy and shear-induced turbulent mixing near the outflow jet.
 
-Other processes that can modify the static stability in the upper troposphere of TCs include radiative heating within and near the top of the cirrus canopy and shear-induced turbulent mixing near the outflow jet.
 To our knowledge, the only paper that has examined explicitly the static stability evolution in a modeled TC is \cite{Kepertetal2016}, but their analysis was limited to the boundary layer.
@@
 \indent The initial spin-up period was characterized by a steady increase of the maximum wind speed from 11 m s\textsuperscript{-1} to 22 m s\textsuperscript{-1} (Fig.~\ref{fig:vmax+pmin}a, blue line), an intensification rate that closely matched that of TC Patricia (Fig.~\ref{fig:vmax+pmin}a, red stars).
-The weakening of the lower-stratospheric $N^2$ maximum during this period is reflected in the total $N^2$ budget change over this time (Fig.~\ref{fig:stab-00-24}a).
+The weakening of the lower-stratospheric static stability maximum during this period is reflected in the total $N^2$ budget change over this time (Fig.~\ref{fig:stab-00-24}a).
 The layer just above the cold-point tropopause was characterized by decreasing $N^2$ (purple shading), maximizing at the storm center.
-At and immediately below the tropopause, meanwhile, saw increasing $N^2$ during this time period.
+At and immediately below the tropopause, meanwhile, existed increasing $N^2$ during this time period.
 Although these tendencies extended out to the 200-km radius, they were particularly pronounced at innermost radii.
@@
 Advection and vertical turbulence both contributed to this positive $N^2$ tendency, with advection playing an important role below about 17.5 km and and turbulence playing an important role above.
-The sum of advection and turbulence (Fig.~\ref{fig:stab-24-48}e) reveals two discontiguous regions of increasing $N^2$ in the 17-18-km layer rather than one contiguous region.
+The sum of advection and turbulence (Fig.~\ref{fig:stab-24-48}e) reveals two separate regions of increasing $N^2$ in the 17-18-km layer rather than one contiguous region.
 The addition of radiation to these two terms, however, (Fig.~\ref{fig:stab-24-48}f) provides the link between these two regions, indicating that radiation also plays a role in strengthening the stable layer just above the tropopause.
@@
 The enhanced vertical gradient of ice mixing ratio at the top of the cirrus canopy induced strong diurnal-mean radiative cooling near the tropopause (Fig.~\ref{fig:qi+radten}d).
-This cooling exceeded 0.6 K h\textsuperscript{-1} in some places and sloped downward from the lower stratosphere into the upper troposphere, following the top of the cirrus canopy.
+This cooling exceeded 0.6 K h\textsuperscript{-1} (14.4 K day\textsuperscript{-1}) in some places and sloped downward from the lower stratosphere into the upper troposphere, following the top of the cirrus canopy.
 A small radiative warming maximum also appeared outside of the 140-km radius below this region of cooling.
@@
 After the TC's RI period completed (48-72 hours), strong radiative cooling remained near the tropopause at inner radii (Fig.~\ref{fig:qi+radten}f), sloping downward with the top of the cirrus canopy to below the tropopause at outer radii.
-Cooling rates exceeded 1 K h\textsuperscript{-1} just above the tropopause between the 30- and 70-km radii.
-This value is more than three times the maximum cooling rate of 0.3 K h\textsuperscript{-1} observed by \cite{buetal}, a discrepancy that is a consequence of their larger vertical grid spacing compared to that used here, along with a contribution from differing radiation schemes.
+Cooling rates exceeded 1 K h\textsuperscript{-1} (24 K day\textsuperscript{-1}) just above the tropopause between the 30- and 70-km radii.
+This value is more than three times the maximum cooling rate of 0.3 K h\textsuperscript{-1} observed by \cite{buetal}, a difference that is a consequence of their larger vertical grid spacing compared to that used here, along with a contribution from differing radiation schemes.
 %\cite{buetal} employed the NASA-Goddard radiation scheme in their CM1 simulations, whereas RRTMG is used in the present paper.
@@
 
-The results herein suggest that radiative heating tendencies played an important role in destabilizing the upper troposphere and stabilizing the lower stratosphere after the cirrus canopy developed.
+The results herein suggest that, after the cirrus canopy developed, radiative heating tendencies considerably destabilized the upper troposphere and stabilized the lower stratosphere.
 
@@
 Fig.~\ref{fig:schematic} depicts the effect of turbulent mixing on the $\theta$ profile of an initially stably-stratified layer.
-At the initial time in this idealized case, $\theta$ increases with height at a constant rate (Fig.~\ref{fig:schematic}, left panel).
-The imposition of tubulence (blue hatching) adjusts the $\theta$ profile within the mixed layer toward a constant value equal to the mean value of that layer in the initial state (Fig.~\ref{fig:schematic}, right panel).
+At the initial time in this schematic, $\theta$ is assumed to increase with height at a constant rate (Fig.~\ref{fig:schematic}, left panel).
+The imposition of turbulence (blue hatching) adjusts the $\theta$ profile within the mixed layer toward a constant value equal to the mean value of that layer in the initial state (Fig.~\ref{fig:schematic}, right panel).
 %If turbulence occurs in a stably-stratified layer, it will act to decrease $\theta$ at the top of the layer and increase it at the bottom.
@@
 The large vertical gradient of vertical eddy diffusivity near the tropopause played an important role in developing the lower-stratospheric stable layer during RI.
-This supports the hypothesized role of turbulence in setting the outflow-layer $\theta$ stratification in \cite{RotunnoEmanuel}.
+These results support the hypothesized role of turbulence in setting the outflow-layer $\theta$ stratification in \cite{RotunnoEmanuel}.
 
@@
 The simulated $N^2$ evolution shown herein closely matched that observed during the RI of Hurricane Patricia (2015).
-Three processes dominated the $N^2$ variability in the upper troposphere and lower stratosphere: advection, radiation, and vertical turbulence.
+Three $N^2$ budget terms dominated in the upper troposphere and lower stratosphere: advection, radiation, and vertical turbulence.
 Radiation and vertical turbulence played particularly important roles in developing the strong $N^2$ maximum just above the cold-point tropopause during RI.
 
-To put the $N^2$ variability observed near the tropopause into context, Fig.~\ref{fig:fulltrop} depicts the model change in $N^2$ over the RI period from 0 to 21 km altitude, along with the vertical eddy diffusivity and the radiative heating rate.
-It is clear that the largest changes in $N^2$ occurred in a relatively shallow layer immediately surrounding the tropopause (Fig.~\ref{fig:fulltrop}a).
+To put the $N^2$ variability observed near the tropopause into context, Fig.~\ref{fig:fulltrop} depicts the model change in $N^2$ over the RI period (hours 24-48) from 0 to 21 km altitude, along with the vertical eddy diffusivity and the radiative heating rate.
+The largest changes in $N^2$ occurred in a relatively shallow layer immediately surrounding the tropopause (Fig.~\ref{fig:fulltrop}a).
 This shallow layer also contained the largest diurnally-averaged radiative heating tendencies found anywhere in the domain (Fig.~\ref{fig:fulltrop}c).
@@
 %The upper troposphere also contained a deep layer of vertical eddy diffusivity values larger than those found anywhere outside of the boundary layer.
-The results herein suggest that this tubulence not only develops as a response to the presence of small static stability and large vertical wind shear, as discussed by \cite{Molinarietal} and \cite{DuranMolinari2016}, but also can actively increase the static stability in highly localized regions just above and below the mixed layers.
+The results herein suggest that this turbulence not only develops as a response to the presence of small static stability and large vertical wind shear, as discussed by \cite{Molinarietal} and \cite{DuranMolinari2016}, but also can actively increase the static stability in highly localized regions just above and below the mixed layers.
 
@@
 We also thank Jeffrey Kepert, Robert Fovell, and Erika Navarro for helpful conversations related to this work.
-This research was supported by NSF Grant \#1636799.
+This research was supported by NSF grant AGS-1636799 and Office of Naval Research Grant N000141712110 as a part of the TCI Departmental Research Initiative.
 

### 2018-03-22 paper.tex
Change caption of Fig. 5 to include description of green and purple shading, per John's comment.
Changed all figures per John's suggestions.

@@
 \caption{(a) Total change in $N^2$ over the 0-24-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 h)\textsuperscript{-1}) and the contributions to that change from (b) the sum of horizontal and vertical advection, (c) vertical turbulence, (d) longwave and shortwave radiation, (e) the sum of horizontal advection, vertical advection, and vertical turbulence, and (f) the sum of horizontal advection, vertical advection, vertical turbulence, and longwave and shortwave radiation.
+Green shading indicates regions of stabilization and purple shading indicates regions of destabilization.
 Orange lines represent the cold-point tropopause height averaged over the 0-24-hour period.}
@@
 \centerline{\includegraphics[width=39pc]{figures/Schematic2.png}}
-\caption{Idealized schematic diagram of turbulent mixing in a stably-stratified layer.
-At the initial time (left panel), potential temperature increases with height at a constant rate (thick black line).
+   \caption{Schematic diagram of the effect of turbulent mixing on the vertical profile of potential temperature ($\theta$).
+At the initial time (left panel), potential temperature is assumed to increase with height at a constant rate (thick black line).
 The imposition of turbulence within a portion of the layer (blue hatching) adjusts the potential temperature profile toward the mean initial value of that layer.

### 2018-03-22 paper.tex
Modify Abstract per my comments.

@@
 Within the eye, differential advection plays a particularly important role in destabilizing the layer near and above the cold-point tropopause.
-Outside of the eye, a radial-vertical circulation develops during RI, with strong outflow below the tropopause and weak inflow above.
-The upper-tropospheric outflow layer exports high potential temperature ($\theta$) air from the eyewall to large radii in the upper troposphere.
+Outside of the eye, the upper-tropospheric outflow layer exports high potential temperature ($\theta$) air from the eyewall to large radii in the upper troposphere.
 This increase in $\theta$ forces stabilization below the outfow jet and destabilization above.
-Vertical wind shear above and below the upper-tropospheric outflow maximum induces vertical gradients of turbulence, which also modify the vertical stability profile.
-Meanwhile, as organized convection reaches the tropopause, radiative heating tendencies at the top of the cirrus canopy generally act to destabilize the upper troposphere and stabilize the lower stratosphere.
-Turbulent mixing and radiative heating combine to play an important role in the development of the strong stable layer immediately above the cold-point tropopause during RI.}
+Vertical wind shear above and below the outflow maximum induces vertical gradients of turbulence, which also modify the vertical stability profile.
+Meanwhile, radiative heating tendencies at the top of the cirrus canopy generally act to destabilize the upper troposphere and stabilize the lower stratosphere.
+These turbulent and radiative processes combine to play an important role in the development of the strong stable layer immediately above the cold-point tropopause during RI.}
 %The results suggest that turbulence and radiation, alongside advection, play fundamental roles in the upper-level static stability evolution of TCs.}
@@
 The warming of the upper troposophere by these advective and diffusive processes could contribute to a decrease in static stability near the tropoopause within the eye.
-Other processes that can modify the static stability in the upper troposphere of TCs include radiative heating within and near the top of the cirrus canopy and shear-induced turbulent mixing near the outflow jet.
+
+Outside of the eye, in the presence of cirrus clouds, vertical gradients of radiative heating also can modify the tropopause-layer static stability.
+\cite{Buetal} note the existence of a shallow region of diurnal-mean net radiative cooling at the top of the TC cirrus canopy (see their Figs. 5, 11).
+This shallow region of cooling could act to destabilize the layer just below the top of the cirrus canopy and stabilize the layer immediately above.
+If the top of the cirrus canopy lies close to the tropopause, these radiative processes could contribute to a stabilization of the lower stratosphere, as was observed in Hurricane Patricia. 
+%Other processes that can modify the static stability in the upper troposphere of TCs include radiative heating within and near the top of the cirrus canopy and shear-induced turbulent mixing near the outflow jet.
 
@@
 \indent After the storm's maximum wind speed leveled off near 80 m s\textsuperscript{-1}, the magnitude of the static stability tendencies within the eye decreased to near zero (Fig.~\ref{fig:stab-48-72}a).
-
-Outside of the eye, however, $N^2$ continued to decrease in the layer immediately sorrounding the tropopause.
-The sum of advection and vertical turbulence (Fig.~\ref{fig:stab-48-72}e) indicates that the increase of $N^2$ observed in the 17-18-km layer and inside of the 80-km radius cannot be attributed to these processes, since the sum of these two terms provided forcing for destabilization.
-Instead, radiation (Fig.~\ref{fig:stab-48-72}d) provided the forcing for stabilization in this region.
+Outside of the eye, however, $N^2$ continued to decrease in the layer immediately sorrounding the tropopause and increase just above.
+The sum of advection and vertical turbulence (Fig.~\ref{fig:stab-48-72}e) indicates that these two processes account for most of the destabilization near the tropopause and some of the stabilization near the 18-km altitude.
+Below the tropopause, however, these two terms provided strong forcing for stabilization that was not observed in the budget change (Fig.~\ref{fig:stab-48-72}a).
+Radiation (Fig.~\ref{fig:stab-48-72}d), which generally forced stabilization above 17 km and destabilization below, balanced out this forcing for stabilization in the upper troposphere.
+In the eyewall region (30-80-km radius), advection and vertical turbulence combined to force destabilization in the 17-18-km layer (Fig.~\ref{fig:stab-48-72}e), which was not observed in the budget change (Fig.~\ref{fig:stab-48-72}a).
+Radiation provided strong forcing for stabilization, which outweighed this effect and produced net stabilization in a portion of this region.
 Outside of the 80-km radius, both advection (Fig.~\ref{fig:stab-48-72}b) and vertical turbulence (Fig.~\ref{fig:stab-48-72}c) provided forcing for stabilization near and just above the 18-km level.
@@
 Outside of the 120-km radius, the region of radiative forcing for stabilization sloped downward, and the increase in $N^2$ observed near 18 km can be explained entirely by a combination of advection and vertical turbulence.
-The layer of decreasing $N^2$ observed near the tropopause was forced primarily by vertical turbulence and radiation.
-Within most of this region, advection provided strong forcing for stabilization, but this forcing was outweighed by the negative $N^2$ tendencies induced by a combination of vertical turbulence and radiation.
 
@@
 A small radiative warming maximum also appeared outside of the 140-km radius below this region of cooling.
-These results broadly agree with those of \citeauthor{buetal} (\citeyear{buetal}; see their Fig.
+These results broadly agree with those of \citeauthor{Buetal} (\citeyear{Buetal}; see their Fig.
 11a), whose CM1 simulations produced a 0.3 K h\textsuperscript{-1} diurnally-averaged radiative cooling at the top of the cirrus canopy and radiative warming within the cloud that maximized near the 200-km radius.
@@
 Cooling rates exceeded 1 K h\textsuperscript{-1} (24 K day\textsuperscript{-1}) just above the tropopause between the 30- and 70-km radii.
-This value is more than three times the maximum cooling rate of 0.3 K h\textsuperscript{-1} observed by \cite{buetal}, a difference that is a consequence of their larger vertical grid spacing compared to that used here, along with a contribution from differing radiation schemes.
-%\cite{buetal} employed the NASA-Goddard radiation scheme in their CM1 simulations, whereas RRTMG is used in the present paper.
-To compare our results to those of \cite{buetal}, we ran a simulation identical to that described in Section 2, except using the NASA-Goddard radiation scheme and 625-m vertical grid spacing, to match those of \cite{buetal}.
-This simulation produced a maximum 24-hour-average radiative cooling rate of 0.3 K h\textsuperscript{-1}, which agrees with that shown in \cite{buetal}.
-Another simulation using 625-m vertical grid spacing and RRTMG radiation produced 24-hour-average cooling rates of up to 0.6 K h\textsuperscript{-1}, which is consistent with the WRF simulations of \cite{buetal}.
+This value is more than three times the maximum cooling rate of 0.3 K h\textsuperscript{-1} observed by \cite{Buetal}, a difference that is a consequence of their larger vertical grid spacing compared to that used here, along with a contribution from differing radiation schemes.
+%\cite{Buetal} employed the NASA-Goddard radiation scheme in their CM1 simulations, whereas RRTMG is used in the present paper.
+To compare our results to those of \cite{Buetal}, we ran a simulation identical to that described in Section 2, except using the NASA-Goddard radiation scheme and 625-m vertical grid spacing, to match those of \cite{Buetal}.
+This simulation produced a maximum 24-hour-average radiative cooling rate of 0.3 K h\textsuperscript{-1}, which agrees with that shown in \cite{Buetal}.
+Another simulation using 625-m vertical grid spacing and RRTMG radiation produced 24-hour-average cooling rates of up to 0.6 K h\textsuperscript{-1}, which is consistent with the WRF simulations of \cite{Buetal}.
 This suggests that vertical grid spacing smaller than 625 m is necessary to resolve properly the radiative cooling at the top of the cirrus canopy, and that the results can be quite sensitive to the radiation scheme used.

### 2018-03-22 paper.tex
Modify all sections after abstract per my comments.

@@
 
-Despite the importance of tropopause-layer thermodynamics in theoretical models of hurricanes (\citeauthor{EmanuelRotunno2011} \citeyear{EmanuelRotunno2011}; \citeauthor{Emanuel2012} \citeyear{Emanuel2012}), most observational studies of the upper-tropospheric structure of TCs are decades old.
+Despite the importance of tropopause-layer thermodynamics in theoretical models of hurricanes (\citeauthor{EmanuelRotunno2011} \citeyear{EmanuelRotunno2011}; \citeauthor{Emanuel2012} \citeyear{Emanuel2012}), most observational studies of the upper-tropospheric structure of TCs are decades old\footnote{An in-depth review of these papers can be found in \cite{DuranMolinari2018}.}.
 Recently, however, \cite{KomaromiDoyle2017} found that stronger TCs tended to have a higher and warmer tropopause over their inner core than weaker TCs.
@@
 
-An idealized simulations of a TC analyzed by \cite{OhnoSatoh2015} suggested that the development of an upper-level warm core near the 13-km level acted to decrease the static stability near the tropopause within the eye.
-During the early stage of development in their simulation (their Fig. 9), static stability above 16 km was large at all radii.
-However, after the storm's intensification, the static stability above 16 km within the eye was markedly smaller (their Fig. 10c).
-Although the mechanisms that might drive this static stability evolution have not been examined explicitly it might be related to the development of an upper-tropospheric warm care within the eye.
+An idealized simulation of a TC analyzed by \cite{OhnoSatoh2015} suggested that the development of an upper-level warm core near the 13-km level acted to decrease the static stability near the tropopause within the eye.
+During the early stage of development in their simulation, large static stability existed above 16 km at all radii (their Fig. 9c).
+However, after the storm's intensification, the static stability within the eye above 16 km was markedly smaller (their Fig. 10c).
+Although the mechanisms that might drive this static stability evolution have not been examined explicitly, it might be related to the development of an upper-tropospheric warm care within the eye.
 \cite{SternZhang2013} described the development of the TC warm core using a potential temperature ($\theta$) budget analysis.
-Although the warm anomaly in their simulation maximized in the mid-levels, they also note that a secondary warming maximum existed in the 12-14-km layer.
-They found that radial and vertical advection both played important roles in warm core development throughout RI, and subgrid-scale diffusion became particularly important during the later stage of RI.
-The warming of the upper troposophere by these advective and diffusive processes could contribute to a decrease in static stability near the tropoopause within the eye.
+Although the warm anomaly in their simulation maximized in the mid-levels, they also note that a secondary warming maximum also existed in the 12-14-km layer.
+They found that radial and vertical advection both played important roles in this warm core development throughout RI, and subgrid-scale diffusion became particularly important during the later stage of RI.
+The warming of the upper troposophere by these advective and diffusive processes could contribute to a decrease in static stability near the tropoopause within the eye by decreasing the vertical $\theta$ gradient.
 
@@
 A Rayleigh damping layer was applied outside of the 2900-km radius and above the 25-km level to prevent spurious gravity wave reflection at the model boundaries.
-Microphysical processes were parameterized using the \cite{Thompson} scheme and radiative heating tendencies were computed every two minutes using the Rapid Radiative Transfer Model for GCMs (RRTMG) longwave and shortwave schemes \citep{Iacono}.
+Microphysical processes were parameterized using the \cite{Thompson} scheme, and radiative heating tendencies were computed every two minutes using the Rapid Radiative Transfer Model for GCMs (RRTMG) longwave and shortwave schemes \citep{Iacono}.
 The initial temperature and humidity field was horizontally homogeneous and determined by averaging all Climate Forecast System Reanalysis (CFSR) grid points within 100 km of Patricia's center of circulation at 18 UTC 21 October 2015.
@@
 Although hurricanes simulated in an axisymmetric framework tend to be more intense than those observed in nature, the intensity evolution of this simulation matches reasonably well with that observed in Hurricane Patricia.
-After an initial spin-up period of about 20 hours, the modeled storm (Fig.~\ref{fig:vmax+pmin}, blue lines) began an RI period that lasted approximately 30 hours.
+After an initial spin-up period of about 20 hours, the modeled storm (Fig.~\ref{fig:vmax+pmin}, blue lines) began an RI period that lasted approximately 18 hours.
 After this RI, the storm continued to intensify more slowly until the maximum 10-m wind speed reached 89 m s\textsuperscript{-1} and the sea-level pressure reached its minimum of 846 hPa 81 hours into the simulation.
@@
 
-Taking the vertical gradient of the first two terms on the right-hand side of Eq.~\ref{eq:dthetadt} yields the time tendency of the vertical $\theta$ gradient due to horizontal and vertical advection\footnote{These terms include the tendencies due to implicit diffusion in the fifth-order finite differencing scheme, which are separated from the advection terms in the CM1 budget output}:
+Taking the vertical gradient of the first two terms on the right-hand side of Eq.~\ref{eq:dthetadt} yields the time tendency of the vertical $\theta$ gradient due to horizontal and vertical advection\footnote{These terms include the tendencies due to implicit diffusion in the fifth-order finite differencing scheme, which are separated from the advection terms in the CM1 version 19.4 budget output.}:
 
@@
 The layer just above the cold-point tropopause was characterized by decreasing $N^2$ (purple shading), maximizing at the storm center.
-At and immediately below the tropopause, meanwhile, existed increasing $N^2$ during this time period.
+At and immediately below the tropopause, meanwhile, $N^2$ increased during this time period (green shading).
 Although these tendencies extended out to the 200-km radius, they were particularly pronounced at innermost radii.
@@
 \paragraph{24-48 hours}\mbox{}\\
-\indent During the RI period, the maximum wind speed increased from 22 m s\textsuperscript{-1} to 80 m s\textsuperscript{-1}.
+\indent During the RI period, the maximum wind speed increased from 22 m s\textsuperscript{-1} to 80 m s\textsuperscript{-1} (Fig.~\ref{fig:vmax+pmin}a).
 Over this time, $N^2$ within the eye generally decreased above 16 km and increased below (Fig.~\ref{fig:stab-24-48}a), with the destabilization above 16 km maximizing near the level of the mean cold-point tropopause.
@@
 \paragraph{48-72 hours}\mbox{}\\
-\indent After the storm's maximum wind speed leveled off near 80 m s\textsuperscript{-1}, the magnitude of the static stability tendencies within the eye decreased to near zero (Fig.~\ref{fig:stab-48-72}a).
+\indent After the storm's maximum wind speed leveled off near 80 m s\textsuperscript{-1} (Fig.~\ref{fig:vmax+pmin}a), the magnitude of the static stability tendencies within the eye decreased to near zero (Fig.~\ref{fig:stab-48-72}a).
 Outside of the eye, however, $N^2$ continued to decrease in the layer immediately sorrounding the tropopause and increase just above.
@@
 There existed, however, a large region near the tropopause in which the total advective tendency was nonzero (Fig.~\ref{fig:stab-24-48}b).
-These nonzero tendencies were related to the development of the TC's seconary circulation as it intensified.
+These nonzero tendencies were related to the development of the TC's secondary circulation as the storm intensified.
 
@@
 %Vertical wind shear acting on these upward-sloping isentropes should act to tilt them into the vertical above the outflow maximum, thereby decreasing $\partial \theta/\partial z$, and tilt them to be more horizontal below the outflow maximum, thereby increasing $\partial \theta/\partial z$.
-This mechanism is the same as that discussed in \cite{TrierSharman}, in which vertical wind shear in the outflow layer of a mesoscale convective system acted to modify the upper-tropospheric static stability through differential advection of isentropes.
+This mechanism is the same as that discussed in \cite{TrierSharman}, in which vertical wind shear in the outflow layer of a mesoscale convective system modified the upper-tropospheric static stability through differential advection of isentropes.
 %Thus, wherever $\partial u/\partial z>0$, the tilting term must force an increase in $N^2$, and wherever $\partial u/\partial z<0$, the tilting term must force a decrease in $N^2$, which is precisely the structure seen in Fig.~\ref{fig:adv-24-48}a.
@@
 Additionally, when these waves reached r=0, a dipole of vertical velocity resulted, with ascent above and descent below.
-For reasons that remain unclear, the regions of ascent were more persistent than the regions of descent, which resulted in the mean ascent observed near r=0 above 17 km in Fig.~\ref{fig:adv-24-48}b.
+For reasons that remain unclear, the regions of ascent were more persistent than the regions of descent, which resulted in the mean ascent observed near r=0 above 17 km in Fig.~\ref{fig:adv-24-48}d.
 
@@
 Because $\partial \theta/\partial z$ was smaller, the subsidence at lower levels could not accomplish as much warming as the subsidence at higher levels in the eye, consistent with the results of \cite{SternZhang2013}.
-As a result, vertical advection within the eye acted to stabilize the layer below 16 km during RI.
+As a result, vertical advection within the eye stabilized the layer below 16 km during RI.
 
-Outside of the 27-km radius, ascent dominated the troposphere, while a 1.5-km-deep layer of descent existed immediately above the tropopause.
+Outside of the 27-km radius, ascent dominated the troposphere, while a 1-1.5-km-deep layer of descent existed immediately above the tropopause.
 These regions of ascent and descent converged just above the tropopause; this convergence acted to compact the isentropes in this layer and increase the static stability.
-Above the lower-stratospheric subsidence maximum, meanwhile, vertical advection acted to decrease $N^2$.
+Above the lower-stratospheric subsidence maximum, meanwhile, vertical advection decreased $N^2$.
 Below the tropopause, differential vertical advection increased $N^2$ within the eyewall region and also at larger radii above the vertical velocity maximum at larger radii.
@@
 Comparing the $N^2$ tendencies forced by horizontal (Fig.~\ref{fig:adv-24-48}a) and vertical (Fig.~\ref{fig:adv-24-48}b) advection to the total advective tendency seen in Fig.~\ref{fig:stab-24-48}b reveals that horizontal advective tendencies dominated the troposphere, while vertical advective tendencies dominated the layer near and above the tropopause.
-Thus, tilting of isentropes in the vicinity of the upper-tropospheric outflow maximum appears to be the most important process governing the $N^2$ tendency in the troposphere, whereas convergence of vertical velocity appears to be the most important process near the tropopause.
+Thus, tilting of isentropes in the vicinity of the upper-tropospheric outflow maximum appears to be the most important advective process governing the $N^2$ tendency in the troposphere, whereas convergence of vertical velocity appears to be the most important advective process near the tropopause.
 
@@
 %\cite{Buetal} employed the NASA-Goddard radiation scheme in their CM1 simulations, whereas RRTMG is used in the present paper.
-To compare our results to those of \cite{Buetal}, we ran a simulation identical to that described in Section 2, except using the NASA-Goddard radiation scheme and 625-m vertical grid spacing, to match those of \cite{Buetal}.
+To compare our results to theirs, we ran a simulation identical to that described in Section 2, except using the NASA-Goddard radiation scheme and 625-m vertical grid spacing, to match those of \cite{Buetal}.
 This simulation produced a maximum 24-hour-average radiative cooling rate of 0.3 K h\textsuperscript{-1}, which agrees with that shown in \cite{Buetal}.
-Another simulation using 625-m vertical grid spacing and RRTMG radiation produced 24-hour-average cooling rates of up to 0.6 K h\textsuperscript{-1}, which is consistent with the WRF simulations of \cite{Buetal}.
+Another simulation using 625-m vertical grid spacing and RRTMG radiation produced 24-hour-average cooling rates of up to 0.6 K h\textsuperscript{-1}.
 This suggests that vertical grid spacing smaller than 625 m is necessary to resolve properly the radiative cooling at the top of the cirrus canopy, and that the results can be quite sensitive to the radiation scheme used.
@@
 %Although vertical turbulence always acts to eliminate vertical gradients of $\theta$, this adjustment toward a neutral state only occurs where the mixing takes place.
-Fig.~\ref{fig:schematic} depicts the effect of turbulent mixing on the $\theta$ profile of an initially stably-stratified layer.
+Fig.~\ref{fig:schematic} depicts the effect of turbulent mixing on the vertical $\theta$ profile of an initially stably-stratified layer.
 At the initial time in this schematic, $\theta$ is assumed to increase with height at a constant rate (Fig.~\ref{fig:schematic}, left panel).
@@
 Consequently, although turbulent mixing acts to decrease $\partial \theta/\partial z$ in the layer in which it is occurring, it actually increases $\partial \theta/\partial z$ just below and just above the layer.
-These vertical gradients of turbulent mixing are quite important, particularly on the flanks of the upper-tropospheric outflow jet.
+Vertical gradients of turbulent mixing like those depicted here are quite important, particularly on the flanks of the upper-tropospheric outflow jet.
 
@@
 Three $N^2$ budget terms dominated in the upper troposphere and lower stratosphere: advection, radiation, and vertical turbulence.
+Advection dominated within the eye, where it provided forcing for destabilization.
 Radiation and vertical turbulence played particularly important roles in developing the strong $N^2$ maximum just above the cold-point tropopause during RI.

### 2018-03-26 paper.tex
Correct c_p_m to c_{pm} in gamma_m equation.
Some minor changes to Introduction and a typo correct.

@@
 
-Using a high-resolution dropsonde dataset collected during the Tropical Cyclone Intensity experiment (TCI; \citeauthor{DoyleTCI} \citeyear{DoyleTCI}), \cite{DuranMolinari2018} observed dramatic changes in tropopause structure during the rapid intensification (RI) of Hurricane Patricia (2015).
+Using a high-resolution dropsonde dataset collected during the Tropical Cyclone Intensity Experiment (TCI; \citeauthor{DoyleTCI} \citeyear{DoyleTCI}), \cite{DuranMolinari2018} observed dramatic changes in tropopause structure during the rapid intensification (RI) of Hurricane Patricia (2015).
 The goal of the present paper is to analyze the processes that might have produced the upper-tropospheric and lower-stratospheric fluctuations observed in Patricia using an idealized axisymmetric simulation.
@@
 Although the mechanisms that might drive this static stability evolution have not been examined explicitly, it might be related to the development of an upper-tropospheric warm care within the eye.
+
 \cite{SternZhang2013} described the development of the TC warm core using a potential temperature ($\theta$) budget analysis.
-Although the warm anomaly in their simulation maximized in the mid-levels, they also note that a secondary warming maximum also existed in the 12-14-km layer.
-They found that radial and vertical advection both played important roles in this warm core development throughout RI, and subgrid-scale diffusion became particularly important during the later stage of RI.
-The warming of the upper troposophere by these advective and diffusive processes could contribute to a decrease in static stability near the tropoopause within the eye by decreasing the vertical $\theta$ gradient.
+Although the warm anomaly in their simulation maximized in the mid-levels, they noted that a secondary warming maximum also existed in the 12-14-km layer.
+Radial and vertical advection both played important roles in this warm core development throughout RI, and subgrid-scale diffusion became particularly important during the later stage of RI.
+The warming of the upper troposophere by these advective and diffusive processes could decrease the vertical $\theta$ gradient, thereby contributing to a decrease in static stability near the tropoopause within the eye.
 
 Outside of the eye, in the presence of cirrus clouds, vertical gradients of radiative heating also can modify the tropopause-layer static stability.
-\cite{Buetal} note the existence of a shallow region of diurnal-mean net radiative cooling at the top of the TC cirrus canopy (see their Figs. 5, 11).
+\cite{Buetal} noted the existence of a shallow region of diurnal-mean net radiative cooling at the top of the TC cirrus canopy (see their Figs. 5, 11).
 This shallow region of cooling could act to destabilize the layer just below the top of the cirrus canopy and stabilize the layer immediately above.
@@
    \begin{equation} \label{eq:gamma_m}
-   \Gamma_m = g(1+q_t)\left(\frac{1+L_vq_s/R_dT}{c_p_m +L_v\partial q_s/\partial T}\right),
+      \Gamma_m = g(1+q_t)\left(\frac{1+L_vq_s/R_dT}{c_{pm}+L_v\partial q_s/\partial T}\right),
    \end {equation}
@@
 \indent After the storm's maximum wind speed leveled off near 80 m s\textsuperscript{-1} (Fig.~\ref{fig:vmax+pmin}a), the magnitude of the static stability tendencies within the eye decreased to near zero (Fig.~\ref{fig:stab-48-72}a).
-Outside of the eye, however, $N^2$ continued to decrease in the layer immediately sorrounding the tropopause and increase just above.
+Outside of the eye, however, $N^2$ continued to decrease in the layer immediately surrounding the tropopause and increase just above.
 The sum of advection and vertical turbulence (Fig.~\ref{fig:stab-48-72}e) indicates that these two processes account for most of the destabilization near the tropopause and some of the stabilization near the 18-km altitude.

### 2018-03-26 paper.tex
Copy figures used in paper to the directory in which paper.tex file is located and clean up Figures section of paper.tex.

@@
 \begin{figure}[ht]
-\centerline{\includegraphics[width=19pc]{figures/vmax+pmin.png}}
+\centerline{\includegraphics[width=19pc]{vmax+pmin.png}}
 \caption{The maximum 10-m wind speed (top panel; m s\textsuperscript{-1}) and minimum sea-level pressure (bottom panel; hPa) in the simulated storm (blue lines; plotted every minute) and from Hurricane Patricia's best track (red stars; plotted every six hours beginning at the time Patricia attained tropical storm intensity).
@@
 \begin{figure}[ht]
-\centerline{\includegraphics[width=39pc]{figures/mod+bud+res.png}}
+\centerline{\includegraphics[width=39pc]{mod+bud+res.png}}
 \caption{Left panels: Twenty-four-hour changes in squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$; 10\textsuperscript{-4} s\textsuperscript{-2}) computed using Eq.~\ref{eq:modelchange} over (top row) 0-24 hours, (middle row) 24-48 hours, (bottom row) 48-72 hours.
@@
 \begin{figure}[ht]
-\centerline{\includegraphics[width=19pc]{figures/AVG_budterms.png}}
+\centerline{\includegraphics[width=19pc]{AVG_budterms.png}}
 \caption{Time series of the contribution of each of the budget terms to the time tendency of the squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$; 10\textsuperscript{-4} s\textsuperscript{-2}).
@@
 \begin{figure*}[ht]
-\centerline{\includegraphics[width=39pc]{figures/n2-24hr-avgs.png}}
+\centerline{\includegraphics[width=39pc]{n2-24hr-avgs.png}}
 \caption{Twenty-four-hour averages of squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$; 10\textsuperscript{-4} s\textsuperscript{-2}) over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours.
@@
 \begin{figure*}[ht]
-\centerline{\includegraphics[width=39pc]{figures/h000-h024-budgetterms.png}}
+\centerline{\includegraphics[width=39pc]{h000-h024-budgetterms.png}}
 \end{figure*}
@@
 \begin{figure*}[ht]
-\centerline{\includegraphics[width=39pc]{figures/h024-h048-budgetterms.png}}
+\centerline{\includegraphics[width=39pc]{h024-h048-budgetterms.png}}
 \caption{As in Fig.~\ref{fig:stab-00-24}, but for the 24-48-hour period.}
@@
 \begin{figure*}[ht]
-\centerline{\includegraphics[width=39pc]{figures/h048-h072-budgetterms.png}}
+\centerline{\includegraphics[width=39pc]{h048-h072-budgetterms.png}}
 \caption{As in Fig.~\ref{fig:stab-00-24}, but for the 48-72-hour period.}
@@
 %FIGURE 8%
-%\begin{figure*}[ht]
-%\centerline{\includegraphics[width=33pc]{figures/h072-h096-budgetterms.png}}
-%\caption{As in Fig.~\ref{fig:stab-48-72}, but for the 72-96-hour period.}
-%\label{fig:stab-72-96}
-%\end{figure*}
-
-%FIGURE 8%
-%\begin{figure*}[ht]
-%\centerline{\includegraphics[width=39pc]{figures/h000-h024-adv.png}}
-%\caption{The contribution to the change in $N^2$ over the 0-24-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 hr)\textsuperscript{-1}) by (a) horizontal advection and (b) vertical advection.
-(c) The radial velocity (m s\textsuperscript{-1}; filled contours), potential temperature (K; thick black contours), and cold-point tropopause height (orange line) averaged over the 0-24-hour period.
-(d) The vertical velocity (cm s\textsuperscript{-1}; filled contours), potential temperature (K; thick black contours), and cold-point tropopause height (orange line) averaged over the 0-24-hour period.}
-%\label{fig:adv-00-24}
-%\end{figure*}
-
-%FIGURE 8%
-%\begin{figure*}[ht]
-%\centerline{\includegraphics[width=39pc]{figures/u.png}}
-%\caption{Radial velocity (m s\textsuperscript{-1}; filled contours), potential temperature (K; thick black contours), and cold-point tropopause height (orange lines) averaged over (a) 0-24 hours, (b) 24-48 hours, and (c) 48-72 hours.}
-%\label{fig:u}
-%\end{figure*}
-
-%FIGURE 8%
 \begin{figure*}[ht]
-\centerline{\includegraphics[width=39pc]{figures/h024-h048-adv.png}}
+\centerline{\includegraphics[width=39pc]{h024-h048-adv.png}}
 \caption{The contributions to the change in $N^2$ over the 24-48-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 h)\textsuperscript{-1}) by (a) horizontal advection and (b) vertical advection.
@@
 (d) The vertical velocity (cm s\textsuperscript{-1}; filled contours), potential temperature (K; thick black contours), and cold-point tropopause height (orange line) averaged over the 24-48-hour period.}
-%\caption{As in Fig. \ref{fig:adv-00-24}, but for the 24-48-hour period.}
 \label{fig:adv-24-48}
@@
 %FIGURE 9%
-%\begin{figure*}[ht]
-%\centerline{\includegraphics[width=39pc]{figures/w.png}}
-%\caption{Vertical velocity (cm s\textsuperscript{-1}; filled contours), potential temperature (K; thick black contours), and cold-point tropopause height (orange lines) averaged over (a) 0-24 hours, (b) 24-48 hours, and (c) 48-72 hours.}
-%\label{fig:w}
-%\end{figure*}
-
-%FIGURE 10%
-%\begin{figure*}[ht]
-%\centerline{\includegraphics[width=39pc]{figures/h048-h072-adv.png}}
-%\caption{As in Fig. \ref{fig:adv-00-24}, but for the 48-72-hour period.}
-%\label{fig:adv-48-72}
-%\end{figure*}
-
-%FIGURE 9%
 \begin{figure*}[ht]
-\centerline{\includegraphics[width=39pc]{figures/qi+radten.png}}
+\centerline{\includegraphics[width=39pc]{qi+radten.png}}
 \end{figure*}
@@
 \begin{figure*}[ht]
-\centerline{\includegraphics[width=39pc]{figures/Schematic2.png}}
+\centerline{\includegraphics[width=39pc]{Schematic2.png}}
    \caption{Schematic diagram of the effect of turbulent mixing on the vertical profile of potential temperature ($\theta$).
@@
 \begin{figure*}[ht]
-\centerline{\includegraphics[width=39pc]{figures/khvten.png}}
+\centerline{\includegraphics[width=39pc]{khvten.png}}
 \caption{Vertical eddy diffusivity (m\textsuperscript{2} s\textsuperscript{-2}; filled contours), cold-point tropopause height (cyan lines), and radial velocity (m s\textsuperscript{-1}; thick black lines) averaged over (a) 0-24 hours, (b) 24-48 hours, and (c) 48-72 hours.}
@@
 \begin{figure*}[ht]
-\centerline{\includegraphics[width=19pc]{figures/fulltrop.png}}
+\centerline{\includegraphics[width=19pc]{fulltrop.png}}
 \end{figure*}

### 2018-03-26 paper.tex
Make some minor changes to Figure calls to be consistent with AMS guidelines.
Correct typos.

@@
 Radial and vertical advection both played important roles in this warm core development throughout RI, and subgrid-scale diffusion became particularly important during the later stage of RI.
-The warming of the upper troposophere by these advective and diffusive processes could decrease the vertical $\theta$ gradient, thereby contributing to a decrease in static stability near the tropoopause within the eye.
+The warming of the upper troposphere by these advective and diffusive processes could decrease the vertical $\theta$ gradient, thereby contributing to a decrease in static stability near the tropopause within the eye.
 
@@
 For this figure, each of the budget terms is computed using the method described in Section 3, except with 1-hour averaging intervals instead of 24-hour intervals.
-The absolute values of these tendencies are then averaged over the radius-height domain of the plots shown in Fig.~\ref{fig:mod+bud+res} and plotted as a time series\footnote{It will be seeen in subsequent figures that each of the terms contributes both positively and negatively to the $N^2$ tendency within the analysis domain.
+The absolute values of these tendencies are then averaged over the radius-height domain of the plots shown in Fig.~\ref{fig:mod+bud+res} and plotted as a time series\footnote{It will be seen in subsequent figures that each of the terms contributes both positively and negatively to the $N^2$ tendency within the analysis domain.
 Thus, taking an average over the domain tends to wash out the positive and negative contributions.
@@
 %Comparing Fig.~\ref{fig:stab-24-48}b to \ref{fig:adv-24-48}a,b reveals that the stabilization below 16 km in the eye was forced by vertical advection, as was the region of destabilization in the 18-19-km layer.
-%Meanwhile, the destabilization that occurred in the 16-17-km layer was forced by a combination and radial and vertial advection.
+%Meanwhile, the destabilization that occurred in the 16-17-km layer was forced by a combination and radial and vertical advection.
 
@@
 %For reasons that remain unclear, the regions of ascent tended to last longer than the regions of subsidence induced by these waves, which is responsible for the dominance of ascent in the mean.
-%In this region of mean ascent, changes in the vertical gradint of mean vertical velocity are responsible for alternating regions of positive and negative $N^2$ tendencies.
+%In this region of mean ascent, changes in the vertical gradient of mean vertical velocity are responsible for alternating regions of positive and negative $N^2$ tendencies.
 %
@@
 %Outside of this radius near 16 km, however, existed a region of forcing for stabilization.
-%This switch in signs was a consequence of a reversal of the radial graident of mean $N^2$ near the 140-km radius (Fig.~\ref{fig:n2-24hr-avgs}b).
+%This switch in signs was a consequence of a reversal of the radial gradient of mean $N^2$ near the 140-km radius (Fig.~\ref{fig:n2-24hr-avgs}b).
 %Inside of that radius, $(\partial/\partial r)(\partial \theta/\partial z) > 0$ and $u > 0$, which corresponds to forcing for destabilization in Eq.
@@
 %
-%The relative imporance of the first and third terms on the right-hand side of Eq.
+%The relative importance of the first and third terms on the right-hand side of Eq.
 \ref{eq:advtend} is difficult to ascertain, but the structure of the mean radial velocity, $\theta$, and $N^2$ fields suggests that both terms are contributing within the outflow layer.
@@
 %FIGURE 2%
-\begin{figure}[ht]
+\begin{figure*}[ht]
 \centerline{\includegraphics[width=39pc]{mod+bud+res.png}}
@@
 \label{fig:mod+bud+res}
-\end{figure}
+\end{figure*}
 
@@
 %FIGURE 9%
-\begin{figure*}[ht]
+\begin{figure}[ht]
 \centerline{\includegraphics[width=39pc]{qi+radten.png}}
-\end{figure*}
+\end{figure}
 \begin{figure}
@@
 %FIGURE 11%
-\begin{figure*}[ht]
+\begin{figure}[ht]
 \centerline{\includegraphics[width=39pc]{khvten.png}}
@@
 \label{fig:diff}
-\end{figure*}
+\end{figure}
 
 %FIGURE 12%
-\begin{figure*}[ht]
+\begin{figure}[ht]
 \centerline{\includegraphics[width=19pc]{fulltrop.png}}
-\end{figure*}
+\end{figure}
 \begin{figure}

### 2018-03-26 paper.tex
Small change to abstract (move definition of theta to earlier in the paragraph.

@@
 Outside of the eye, static stability increases considerably just above the cold-point tropopause, and the tropopause remains near its initial level.\\
-\indent A budget analysis reveals that the advection term, which includes differential advection of potential temperature and direct advection of static stability, is important throughout the upper troposphere and lower stratosphere.
+\indent A budget analysis reveals that the advection term, which includes differential advection of potential temperature ($\theta$) and direct advection of static stability, is important throughout the upper troposphere and lower stratosphere.
 Within the eye, differential advection plays a particularly important role in destabilizing the layer near and above the cold-point tropopause.
-Outside of the eye, the upper-tropospheric outflow layer exports high potential temperature ($\theta$) air from the eyewall to large radii in the upper troposphere.
+Outside of the eye, the upper-tropospheric outflow layer exports high-$\theta$ air from the eyewall to large radii in the upper troposphere.
 This increase in $\theta$ forces stabilization below the outfow jet and destabilization above.

### 2018-07-09 paper.tex
Correct typo in abstract.
Add Emanuel and Rotunno (2011) citation and correct parenthetical to reflect this. Correct typo ('warm care').

--- 2018-03-26 paper.tex
@@
 
-After undergoing a remarkably rapid intensification (RI), Hurricane Patricia (2015) set a new record as the strongest tropical cyclone (TC) ever observed in the Western Hemisphere (\citeauthor{Kimberlainetal2016} \citeyear{Kimberlainetal2016}; \citeauthor{Rogersetal2017} \citeyear{Rogersetal2017}).
+After undergoing a remarkably rapid intensification (RI), Hurricane Patricia (2015) attained the strongest wind speed ever recorded in a tropical cyclone (TC) (\citeauthor{Kimberlainetal2016} \citeyear{Kimberlainetal2016}; \citeauthor{Rogersetal2017} \citeyear{Rogersetal2017}).
 %High-altitude dropsonde observations taken during the Tropical Cyclone Intensity (TCI) experiment captured this RI in unprecedented detail \citep{DoyleTCI}.
@@
 However, after the storm's intensification, the static stability within the eye above 16 km was markedly smaller (their Fig. 10c).
-Although the mechanisms that might drive this static stability evolution have not been examined explicitly, it might be related to the development of an upper-tropospheric warm care within the eye.
+Although the mechanisms that might drive this static stability evolution have not been examined explicitly, it might be related to the development of an upper-tropospheric warm core within the eye.
 
@@
 %Since relative humidity measurements were unreliable at temperatures below -40\textdegree C \citep{BellTCI}, relative humidity was set equal to 50\% above 11.5 km (the level above which temperature dropped below -40\textdegree C).
-The vortex described in \citeauthor{RotunnoEmanuel} (\citeyear{RotunnoEmanuel}, their Eq. 37) was used to initialize the wind field, setting all parameters equal to the values used therein.
+The vortex described in \citeauthor{RotunnoEmanuel1987} (\citeyear{RotunnoEmanuel1987}, their Eq. 37) was used to initialize the wind field, setting all parameters equal to the values used therein.
 
@@
 The large vertical gradient of vertical eddy diffusivity near the tropopause played an important role in developing the lower-stratospheric stable layer during RI.
-These results support the hypothesized role of turbulence in setting the outflow-layer $\theta$ stratification in \cite{RotunnoEmanuel}.
+These results support the hypothesized role of turbulence in setting the outflow-layer $\theta$ stratification in \cite{EmanuelRotunno2011}.
 

### 2018-07-10 paper.tex
Begin addressing Reviewer 1's more minor comments.

@@
 
-\abstract{Large changes in tropopause-layer static stability are observed during the rapid intensification (RI) of an idealized, axisymmetric tropical cyclone (TC).
+\abstract{Large changes in tropopause-layer static stability are examined during the rapid intensification (RI) of a tropical cyclone (TC) in an idealized, axisymmetric simulation.
 Over the eye, static stability near the tropopause decreases and the cold-point tropopause height rises by up to 4 km at the storm center.
@@
 Vertical wind shear above and below the outflow maximum induces vertical gradients of turbulence, which also modify the vertical stability profile.
-Meanwhile, radiative heating tendencies at the top of the cirrus canopy generally act to destabilize the upper troposphere and stabilize the lower stratosphere.
+Meanwhile, radiative cooling tendencies at the top of the cirrus canopy generally act to destabilize the upper troposphere and stabilize the lower stratosphere.
 These turbulent and radiative processes combine to play an important role in the development of the strong stable layer immediately above the cold-point tropopause during RI.}
@@
 TCI dropsonde observations collected during this RI period revealed dramatic changes in the cold-point tropopause height and upper-level static stability \citep{DuranMolinari2018}.
-In particular, when Patricia was at tropical storm intensity shortly before RI commenced, a strong inversion layer existed just above the cold-point tropopause.
+In particular, when Patricia was at tropical storm intensity shortly before RI commenced, a strong inversion layer existed just above the cold-point tropopause (see their Fig. 4a).
 During the first half of the RI period, this inversion layer weakened throughout Patricia's inner core, with the weakening most pronounced over the developing eye.
-By the time the storm reached its maximum intensity of 95 m s\textsuperscript{-1}, the inversion layer over the eye had disappeared almost completely, which was accompanied by a greater than 1-km increase in the tropopause height.
+By the time the storm reached its maximum best-track intensity of 95 m s\textsuperscript{-1}, the inversion layer over the eye had disappeared almost completely (see their Fig.
+4d), which was accompanied by a greater than 1-km increase in the tropopause height.
 Meanwhile over the eyewall region, the static stability increased and the tropopause remained near its initial level.
@@
 The equations of motion were integrated on a 3000-km-wide, 30-km-deep axisymmetric grid with 1-km horizontal and 250-m vertical grid spacing.
-The computations were performed on an \textit{f}-plane at 15\textdegree{N} latitude, over a sea surface with constant temperature of 30.5\textdegree C, which matches that observed near Hurricane Patricia (2015; \citeauthor{Kimberlainetal2016} \citeyear{Kimberlainetal2016}).
+The computations were performed on an \textit{f}-plane at 15\textdegree{N} latitude, over a sea surface with constant temperature of 30.5\textdegree C, which is based on that analyzed near Hurricane Patricia (2015; \citeauthor{Kimberlainetal2016} \citeyear{Kimberlainetal2016}).
 Horizontal turbulence was parameterized using the Smagorinsky scheme described in \citeauthor{BryanRotunno2009} (\citeyear{BryanRotunno2009}, pg.
 1773), with a prescribed mixing length that varied linearly from 100 m at a surface pressure of 1015 hPa to 1000 m at a surface pressure of 900 hPa.
-Vertical turbulence was parameterized using the formulation of \citeauthor{MarkowskiBryan2016} (\citeyear{MarkowskiBryan2016}, their Eq. 6), using an asymptotic vertical mixing length of 100 m.
+Vertical turbulence was parameterized using the formulation of \citeauthor{MarkowskiBryan2016} (\citeyear{MarkowskiBryan2016}, their Eq.
+6), using an asymptotic vertical mixing length of 100 m, which is the default setup for hurricane simulations in CM1.
 A Rayleigh damping layer was applied outside of the 2900-km radius and above the 25-km level to prevent spurious gravity wave reflection at the model boundaries.
@@
 where $L_v$ is the latent heat of vaporization and $c_{pm}$ is the specific heat of moist air at constant pressure.
-In the tropopause layer, $q_s$, ${\partial q_s}/{\partial T}$, and ${\partial q_t}/{\partial z}$ approach zero. In this limiting case, Eq. \ref{eq:n2moist} reduces to:
+In the tropopause layer, $q_s$, $q_t$, ${\partial q_s}/{\partial T}$, and ${\partial q_t}/{\partial z}$ approach zero. In this limiting case, Eq. \ref{eq:n2moist} reduces to:
    \begin{equation} \label{eq:n2dry}

### 2018-07-11 paper.tex
Address a few more of Reviewer 1's comments (#6,8,10,18,19).

@@
 4d), which was accompanied by a greater than 1-km increase in the tropopause height.
-Meanwhile over the eyewall region, the static stability increased and the tropopause remained near its initial level.
+Meanwhile over the eyewall region, the static stability remained large and the tropopause stayed near its initial level.
 %The mechanisms that might have led to this tropopause-layer variability will be investigated in the current paper using idealized simulations.
@@
 This shallow region of cooling could act to destabilize the layer just below the top of the cirrus canopy and stabilize the layer immediately above.
-If the top of the cirrus canopy lies close to the tropopause, these radiative processes could contribute to a stabilization of the lower stratosphere, as was observed in Hurricane Patricia. 
+If the top of the cirrus canopy lies close to the tropopause, these radiative processes could contribute to a stabilization of the lower stratosphere. 
 %Other processes that can modify the static stability in the upper troposphere of TCs include radiative heating within and near the top of the cirrus canopy and shear-induced turbulent mixing near the outflow jet.
@@
 
-Taking the time derivative of Eq. \ref{eq:n2dry} yields the static stability tendency:
+Taking the time derivative of Eq. \ref{eq:n2dry} and switching the order of differentiation yields the static stability tendency:
    \begin{equation} \label{eq:dn2dt}
@@
 The first term on the right-hand side of Eq. ~\ref{eq:dn2dt} is larger than the second term throughout most of the tropopause layer (not shown).
-Consequently, the contribution of each of the terms in Eq.~\ref{eq:dthetadt} to the $N^2$ tendency can be interpreted in light of a vertical gradient of each term.
+Consequently, the contribution of each of the terms in Eq.~\ref{eq:dthetadt} to the $N^2$ tendency can be interpreted in terms of a vertical gradient of each term.
 %Since the first term on the right-hand side of Eq.~\ref{eq:dn2dt} is larger than the second term throughout most of the tropopause layer (not shown), the contribution of each of the terms in Eq.~\ref{eq:dthetadt} to the $N^2$ tendency can be interpreted in light of a vertical gradient of each term.
@@
 
- \subsection{Static stability evolution}
+ \subsection{Static stability and tropopause evolution}
 
@@
 The tropopause height increased to nearly 21 km at the storm center and sloped sharply downward to 16.3 km on the inner edge of the eyewall, near the 30 km radius.
+A local minimum in tropopause height manifested near the eye-eyewall interface, similar to that observed in Hurricane Patricia (see \citeauthor{DuranMolinari2018} \citeyear{DuranMolinari2018}, Figs.
+4f-h), although the authors of that paper cautioned that these local minima could be quite sensitive to small fluctuations in temperature.
+%The authors cautioned that, due to the presence of a nearly isothermal layer at this location (\citeauthor{DuranMolinari2018} \citeyear{DuranMolinari2018}, Figs.
+4b-d), the tropopause height could be quite sensitive to small fluctuations in temperature or to sensor error.
+The presence of a local minimum at this location in these 24-hour averages, however, suggests that this tropopause depression on the outer edge of the eye could be a robust, persistent feature.
 Static stability outside of the eye, meanwhile, continued to increase just above the cold-point tropopause.

### 2018-07-30 paper.tex
Address a few more reviewer comments.

@@
 
-The static stability can be expressed as the squared Brunt-V{\"a}is{\"a}l{\"a} frequency:
+Following \cite{Bryan2017}, the static stability can be expressed as the squared Brunt-V{\"a}is{\"a}l{\"a} frequency:
    \begin{equation} \label{eq:n2moist}
@@
 
-To compute $N^2$, CM1 uses Eq.
-\ref{eq:n2moist} in saturated environments and Eq.
-\ref{eq:n2dry} in sub-saturated environments.
-For simplicity, however, only Eq.
-\ref{eq:n2dry} will be employed for the budget computations throughout the entire domain\footnote{The validity of this approximation will be substantiated later in this section.}.
+Eq. \ref{eq:n2moist} is the appropriate expression for $N^2$ in moist environments, whereas Eq. \ref{eq:n2dry} applies strictly in the absence of moisture.
+Although the tropopause layer is not completely dry, moisture is small enough there for Eq.
+\ref{eq:n2dry} to be a good approximation of $N^2$ in the the budget computation\footnote{The validity of this approximation will be substantiated later in this section.}.
 
@@
 Each term in Eq. \ref{eq:dthetadt} is substituted for ${\partial \theta}/{\partial t}$ in Eq. \ref{eq:dn2dt}, yielding the contribution of each budget term to the static stability tendency.
-These terms are summed, yielding an instantaneous "budget change" in $N^2$ every minute.
+These terms are summed, yielding an instantaneous ``budget change" in $N^2$ every minute.
 The budget changes are then averaged over 24-hour periods and compared to the total model change in $N^2$ over that same time period, i.e.:
@@
 
-Eqs. \ref{eq:budgetchange}-\ref{eq:residual} are plotted for three consecutive 24-hour periods in Fig.~\ref{fig:mod+bud+res}.
+Eqs. \ref{eq:budgetchange}-\ref{eq:residual} are evaluated for three consecutive 24-hour periods in Fig.~\ref{fig:mod+bud+res}.
 For this and all subsequent radial-vertical cross sections, a 1-2-1 smoother is applied once in the radial direction to eliminate $2\Delta r$ noise that appears in some of the raw model output and calculated fields.

### 2018-07-30 paper.tex
Addressed a number of reviewer comments.

@@
 4d), which was accompanied by a greater than 1-km increase in the tropopause height.
-Meanwhile over the eyewall region, the static stability remained large and the tropopause stayed near its initial level.
+Meanwhile outside of the eye, the static stability remained large and the tropopause stayed near its initial level.
 %The mechanisms that might have led to this tropopause-layer variability will be investigated in the current paper using idealized simulations.
@@
 
-Taking the vertical gradient of the first two terms on the right-hand side of Eq.~\ref{eq:dthetadt} yields the time tendency of the vertical $\theta$ gradient due to horizontal and vertical advection\footnote{These terms include the tendencies due to implicit diffusion in the fifth-order finite differencing scheme, which are separated from the advection terms in the CM1 version 19.4 budget output.}:
+Taking the vertical gradient of the first two terms on the right-hand side of Eq.~\ref{eq:dthetadt} yields the time tendency of the vertical $\theta$ gradient due to horizontal and vertical advection:%\footnote{These terms include the tendencies due to implicit diffusion in the fifth-order finite differencing scheme, which are separated from the advection terms in the CM1 version 19.4 budget output.}
 
@@
 Since these terms involve velocity gradients, they can act to strengthen or weaken static stability maxima or minima through differential advection.
-Unless otherwise stated, any reference to "advection" in this paper indicates the sum of all of the terms in Eq.~\ref{eq:advtend}.
+Unless otherwise stated, any reference to ``advection" in this paper indicates the sum of all of the terms in Eq.~\ref{eq:advtend}.
 %For example, since the $\theta$ of the air flowing out of the eyewall into the upper-tropospheric outflow layer increases as the TC intensifies, $\theta$ increases locally within the outflow layer.
@@
 These terms are summed, yielding an instantaneous ``budget change" in $N^2$ every minute.
-The budget changes are then averaged over 24-hour periods and compared to the total model change in $N^2$ over that same time period, i.e.:
+The budget changes are then averaged over 24-hour (1440-minute) periods, multiplied by the length of the time period, and compared to the total model change in $N^2$ over that same time period, i.e.:
    \begin{equation} \label{eq:budgetchange}
-   \Delta N^2_{budget} = \frac{1}{\delta t}\sum_{t=t_0}^{t_0+\delta t} \left.\frac{\partial N^2}{\partial t}\right\vert_t
+   \Delta N^2_{budget} = \frac{\delta t}{1440}\sum_{t=t_0}^{1440} \left.\frac{\partial N^2}{\partial t}\right\vert_t
    \end{equation}
@@
 \ref{eq:n2dry} in subsaturated environments.
-The center column depicts the budget changes computed using Eq. \ref{eq:budgetchange} together with Eq.~\ref{eq:n2dry} throughout the entire domain.
+The center column depicts the budget changes computed using Eq. \ref{eq:budgetchange} together with Eq.~\ref{eq:dn2dt} throughout the entire domain.
 Thus, the left column includes the effect of moisture in the $N^2$ computations, whereas the center column neglects moisture.
@@
 The average $N^2$ over the first day of the simulation (Fig.~\ref{fig:n2-24hr-avgs}a) indicates the presence of a weak $N^2$ maximum just above the cold-point tropopause.
-Over the subsequent 24 hours, during the RI period, the $N^2$ within and above this layer decreased within the 25-km radius (Fig.~\ref{fig:n2-24hr-avgs}b).
+Over the subsequent 24 hours, during the RI period, the $N^2$ maximum weakened within the 25-km radius (Fig.~\ref{fig:n2-24hr-avgs}b).
 This decreasing $N^2$ corresponded to an increase in the tropopause height within the developing eye, maximized at the storm center.
-Outside of the eye, meanwhile, the tropopause height decreased over the eyewall region (25-60-km radius) and increased only slightly outside of the 60-km radius.
-In this outer region, the $N^2$ maximum just above the tropopause strengthened during RI.
+Just outside of the eye, meanwhile, the tropopause height decreased within the 25-60-km radial band, and increased only slightly outside of the 60-km radius.
+Everywhere outside of the eye, the $N^2$ maximum just above the tropopause strengthened during RI.
 These trends continued as the storm's intensity leveled off in the 48-72-hour period (Fig.~\ref{fig:n2-24hr-avgs}c).
@@
 Static stability outside of the eye, meanwhile, continued to increase just above the cold-point tropopause.
-This $N^2$ evolution closely follows that observed in Hurricane Patricia (2015; \citeauthor{DuranMolinari2018} \citeyear{DuranMolinari2018}, see their Fig. 4).
+This $N^2$ evolution resembles that observed in Hurricane Patricia (2015; \citeauthor{DuranMolinari2018} \citeyear{DuranMolinari2018}, see their Fig. 4).
 The mechanisms that led to these $N^2$ changes will be investigated in the subsequent sections.
@@
 \paragraph{0-24 hours}\mbox{}\\
-\indent The initial spin-up period was characterized by a steady increase of the maximum wind speed from 11 m s\textsuperscript{-1} to 22 m s\textsuperscript{-1} (Fig.~\ref{fig:vmax+pmin}a, blue line), an intensification rate that closely matched that of TC Patricia (Fig.~\ref{fig:vmax+pmin}a, red stars).
+\indent The initial spin-up period was characterized by a steady increase of the maximum wind speed from 11 m s\textsuperscript{-1} to 22 m s\textsuperscript{-1} (Fig.~\ref{fig:vmax+pmin}a, blue line).
 The weakening of the lower-stratospheric static stability maximum during this period is reflected in the total $N^2$ budget change over this time (Fig.~\ref{fig:stab-00-24}a).
-The layer just above the cold-point tropopause was characterized by decreasing $N^2$ (purple shading), maximizing at the storm center.
+The layer just above the cold-point tropopause was characterized by decreasing $N^2$ (purple shading), maximizing in magnitude at the storm center.
 At and immediately below the tropopause, meanwhile, $N^2$ increased during this time period (green shading).
@@
 Outside of the eye, the $N^2$ evolution exhibited alternating layers of positive and negative tendencies.
-Near and above 18 km existed an upward-sloping region of decreasing $N^2$ that extended out to the 180-km radius.
+Near and above 18 km existed an outward-sloping region of decreasing $N^2$ that extended out to the 180-km radius.
 In this region, neither vertical turbulence nor radiation exhibited negative $N^2$ tendencies; advection was the only forcing for this destabilization.
-Immediately below this layer, just above the cold-point tropopause, was a region of increasing $N^2$ that sloped upward from 17 km near the 30-km radius to just below 18 km outside of the 100-km radius.
+Immediately below this layer, just above the cold-point tropopause, was a region of increasing $N^2$ that sloped outward from 17 km near the 30-km radius to just below 18 km outside of the 100-km radius.
 Advection and vertical turbulence both contributed to this positive $N^2$ tendency, with advection playing an important role below about 17.5 km and and turbulence playing an important role above.
@@
 Radiative tendencies overcome this forcing for stabilization in both of these regions to produce the radially-extensive region of destabilization observed just below the tropopause.
-
 The sum of advection, vertical turbulence, and radiation (Fig.~\ref{fig:stab-24-48}f) once again closely follows the observed $N^2$ variability, except in the eyewall region, where the neglect of latent heating and horizontal turbulence introduces some differences.
@@
 Radiation (Fig.~\ref{fig:stab-48-72}d), which generally forced stabilization above 17 km and destabilization below, balanced out this forcing for stabilization in the upper troposphere.
-In the eyewall region (30-80-km radius), advection and vertical turbulence combined to force destabilization in the 17-18-km layer (Fig.~\ref{fig:stab-48-72}e), which was not observed in the budget change (Fig.~\ref{fig:stab-48-72}a).
+Within the 30-80-km radial band, advection and vertical turbulence combined to force destabilization in the 17-18-km layer (Fig.~\ref{fig:stab-48-72}e), which was not observed in the budget change (Fig.~\ref{fig:stab-48-72}a).
 Radiation provided strong forcing for stabilization, which outweighed this effect and produced net stabilization in a portion of this region.

### 2018-08-04 paper.tex

@@
 Outside of the eye, static stability increases considerably just above the cold-point tropopause, and the tropopause remains near its initial level.\\
-\indent A budget analysis reveals that the advection term, which includes differential advection of potential temperature and direct advection of static stability, is important throughout the upper troposphere and lower stratosphere.
+\indent A budget analysis reveals that the advection term, which includes differential advection of potential temperature ($\theta$) and direct advection of static stability, is important throughout the upper troposphere and lower stratosphere.
 Within the eye, differential advection plays a particularly important role in destabilizing the layer near and above the cold-point tropopause.
-Outside of the eye, the upper-tropospheric outflow layer exports high potential temperature ($\theta$) air from the eyewall to large radii in the upper troposphere.
-This increase in $\theta$ forces stabilization below the outfow jet and destabilization above.
+Outside of the eye, the upper-tropospheric outflow layer exports high-$\theta$ air from the eyewall to large radii in the upper troposphere.
+This increase in $\theta$ forces stabilization below the outflow jet and destabilization above.
 Vertical wind shear above and below the outflow maximum induces vertical gradients of turbulence, which also modify the vertical stability profile.

### 2018-08-06 paper.tex
Addressed a number of Reviewer 1's comments.

@@
 
-\cite{SternZhang2013} described the development of the TC warm core using a potential temperature ($\theta$) budget analysis.
+\cite{SternZhang2013} described the development of the TC warm core in a three-dimensional framework using a potential temperature ($\theta$) budget analysis.
 Although the warm anomaly in their simulation maximized in the mid-levels, they noted that a secondary warming maximum also existed in the 12-14-km layer.
-Radial and vertical advection both played important roles in this warm core development throughout RI, and subgrid-scale diffusion became particularly important during the later stage of RI.
-The warming of the upper troposphere by these advective and diffusive processes could decrease the vertical $\theta$ gradient, thereby contributing to a decrease in static stability near the tropopause within the eye.
+In the midlevels, radial and vertical advection both played important roles in the development of the warm core, with the eddy component of radial advection dominating over the mean component.
+In the upper levels, however, only the mean component of vertical advection was important for warm-core development.
+Horizontal diffusion became particularly important near the outer edge of the eye during the later stage of RI; these diffusive tendencies produced regions of warming below regions of cooling (see \citeauthor{SternZhang2013} \citeyear{SternZhang2013}, their Fig.
+7t), which would act to decrease the vertical $\theta$ gradient.
+Potential temperature tendencies associated with these advective and diffusive processes could contribute to a decrease in static stability near the tropopause within the eye.
 
@@
 After this RI, the storm continued to intensify more slowly until the maximum 10-m wind speed reached 89 m s\textsuperscript{-1} and the sea-level pressure reached its minimum of 846 hPa 81 hours into the simulation.
-Hurricane Patricia (red stars) exhibited a similar intensity evolution prior to its landfall, with an RI period leading to a maximum 10-m wind speed of 95 m s\textsuperscript{-1} and a minimum sea-level pressure of 872 hPa.
+Hurricane Patricia (red stars) exhibited a similar intensity evolution prior to its landfall, with an RI period leading to a maximum 10-m wind speed of 95 m s\textsuperscript{-1} and a minimum sea-level pressure of 872 hPa\footnote{Note that in Fig.
+1, plotting of Patricia's wind speed begins when it attained tropical-storm strength at 00 UTC 21 October 2015, rather than its first best-track entry.
+This was done to shift Patricia's RI period in the plot so that it occurs near the same time as modeled storm's RI period.}.
 
@@
 For this and all subsequent radial-vertical cross sections, a 1-2-1 smoother is applied once in the radial direction to eliminate $2\Delta r$ noise that appears in some of the raw model output and calculated fields.
-      The left column of Fig.~\ref{fig:mod+bud+res} depicts the model changes computed using Eq.~\ref{eq:modelchange}, together with Eq.~\ref{eq:n2moist} in saturated environments and Eq.
-\ref{eq:n2dry} in subsaturated environments.
-The center column depicts the budget changes computed using Eq. \ref{eq:budgetchange} together with Eq.~\ref{eq:dn2dt} throughout the entire domain.
+      The left column of Fig.~\ref{fig:mod+bud+res} depicts the model changes computed using Eq.~\ref{eq:modelchange}, together with Eq.~\ref{eq:n2moist} in saturated environments.
+The center column depicts the budget changes computed using Eq. \ref{eq:budgetchange}, together with Eq.~\ref{eq:dn2dt} throughout the entire domain.
 Thus, the left column includes the effect of moisture in the $N^2$ computations, whereas the center column neglects moisture.
@@
 The sum of advection and vertical turbulence accounts for only a portion of the decreasing $N^2$ in this layer, and actually indicates forcing for stabilization near the 50-km radius and outside of the 130-km radius.
-Radiative tendencies overcome this forcing for stabilization in both of these regions to produce the radially-extensive region of destabilization observed just below the tropopause.
-The sum of advection, vertical turbulence, and radiation (Fig.~\ref{fig:stab-24-48}f) once again closely follows the observed $N^2$ variability, except in the eyewall region, where the neglect of latent heating and horizontal turbulence introduces some differences.
+Radiative tendencies overcome this forcing for stabilization in both of these regions to produce the radially-extensive region of destabilization just below the tropopause.
+The sum of advection, vertical turbulence, and radiation (Fig.~\ref{fig:stab-24-48}f) once again closely follows the total $N^2$ variability, except in the eyewall region, where the neglect of latent heating and horizontal turbulence introduces some differences.
 
@@
 The sum of advection and vertical turbulence (Fig.~\ref{fig:stab-48-72}e) indicates that these two processes account for most of the destabilization near the tropopause and some of the stabilization near the 18-km altitude.
-Below the tropopause, however, these two terms provided strong forcing for stabilization that was not observed in the budget change (Fig.~\ref{fig:stab-48-72}a).
+Below the tropopause, however, these two terms provided strong forcing for stabilization that did not manifest in the budget change (Fig.~\ref{fig:stab-48-72}a).
 Radiation (Fig.~\ref{fig:stab-48-72}d), which generally forced stabilization above 17 km and destabilization below, balanced out this forcing for stabilization in the upper troposphere.
-Within the 30-80-km radial band, advection and vertical turbulence combined to force destabilization in the 17-18-km layer (Fig.~\ref{fig:stab-48-72}e), which was not observed in the budget change (Fig.~\ref{fig:stab-48-72}a).
+Within the 30-80-km radial band, advection and vertical turbulence combined to force destabilization in the 17-18-km layer (Fig.~\ref{fig:stab-48-72}e), which did not manifest in the budget change (Fig.~\ref{fig:stab-48-72}a).
 Radiation provided strong forcing for stabilization, which outweighed this effect and produced net stabilization in a portion of this region.
 Outside of the 80-km radius, both advection (Fig.~\ref{fig:stab-48-72}b) and vertical turbulence (Fig.~\ref{fig:stab-48-72}c) provided forcing for stabilization near and just above the 18-km level.
-The sum of the two terms (Fig.~\ref{fig:stab-48-72}e) indicates increasing $N^2$ near the 18-km level everywhere outside of the 80-km radius, but this stabilization is slightly weaker in the 90-120-km radial band than the observed value.
-The addition of radiation (Fig.~\ref{fig:stab-48-72}f) provided the extra forcing for stabilization required to account for the observed increase in $N^2$.
-Outside of the 120-km radius, the region of radiative forcing for stabilization sloped downward, and the increase in $N^2$ observed near 18 km can be explained entirely by a combination of advection and vertical turbulence.
+The sum of the two terms (Fig.~\ref{fig:stab-48-72}e) indicates increasing $N^2$ near the 18-km level everywhere outside of the 80-km radius, but this stabilization is slightly weaker in the 90-120-km radial band than the total budget tendency.
+The addition of radiation (Fig.~\ref{fig:stab-48-72}f) provided the extra forcing for stabilization required to account for the total increase in $N^2$.
+Outside of the 120-km radius, the region of radiative forcing for stabilization sloped downward, and the increase in $N^2$ that appeared near 18 km can be explained entirely by a combination of advection and vertical turbulence.
 
@@
 There existed, however, a large region near the tropopause in which the total advective tendency was nonzero (Fig.~\ref{fig:stab-24-48}b).
-These nonzero tendencies were related to the development of the TC's secondary circulation as the storm intensified.
+These nonzero tendencies, which were partially canceled by turbulence tendencies, were related to the development of the TC's secondary circulation as the storm intensified.
 
@@
 \ref{eq:advtend} suggests that tilting of isentropes within these shear layers contributed to the strong $N^2$ tendencies that flanked the outflow maximum.
-This is consistent with the outflow layer carrying air with increasingly large $\theta$ from the eyewall to large radii as the storm intensified.
-This increase in $\theta$ maximized near the outflow maximum, which acted to decrease $\partial \theta/\partial z$ above the outflow maximum and increase it below.
-%Outside of the eye and eyewall, isentropes generally sloped upward with radius.
-%Vertical wind shear acting on these upward-sloping isentropes should act to tilt them into the vertical above the outflow maximum, thereby decreasing $\partial \theta/\partial z$, and tilt them to be more horizontal below the outflow maximum, thereby increasing $\partial \theta/\partial z$.
+%This is consistent with the outflow layer carrying air with increasingly large $\theta$ from the eyewall to large radii as the storm intensified.
+%This increase in $\theta$ maximized near the outflow maximum, which acted to decrease $\partial \theta/\partial z$ above the outflow maximum and increase it below.
+Outside of the eye and eyewall, isentropes generally sloped upward with radius (Fig. \ref{fig:adv-24-48}c, black lines).
+Vertical wind shear acting on these upward-sloping isentropes should act to tilt them into the vertical above the outflow maximum, thereby decreasing $\partial \theta/\partial z$, and tilt them to be more horizontal below the outflow maximum, thereby increasing $\partial \theta/\partial z$.
 This mechanism is the same as that discussed in \cite{TrierSharman}, in which vertical wind shear in the outflow layer of a mesoscale convective system modified the upper-tropospheric static stability through differential advection of isentropes.
-%Thus, wherever $\partial u/\partial z>0$, the tilting term must force an increase in $N^2$, and wherever $\partial u/\partial z<0$, the tilting term must force a decrease in $N^2$, which is precisely the structure seen in Fig.~\ref{fig:adv-24-48}a.
+Thus, wherever $\partial u/\partial z>0$, the tilting term must force an increase in $N^2$, and wherever $\partial u/\partial z<0$, the tilting term must force a decrease in $N^2$, which is precisely the structure seen in Fig.~\ref{fig:adv-24-48}a.
 
-%Advection of $N^2$ by the radial wind (first term on the right-hand side of Eq. \ref{eq:advtend}) also acted within the outflow jet.
-%For example, horizontal advection provided forcing for destabilization at the 16-km level almost everywhere inside of the 140-km radius.
-%Outside of this radius near 16 km, however, existed a region of forcing for stabilization.
-%This switch in signs was a consequence of a reversal of the radial gradient of mean $N^2$ near the 140-km radius (Fig.~\ref{fig:n2-24hr-avgs}b).
-%Inside of that radius, $(\partial/\partial r)(\partial \theta/\partial z) > 0$ and $u > 0$, which corresponds to forcing for destabilization in Eq.
-\ref{eq:advtend}; outside of that radius $(\partial/\partial r)(\partial \theta/\partial z) < 0$ and $u > 0$, which corresponds to forcing for stabilization.
+Advection of $N^2$ by the radial wind (first term on the right-hand side of Eq. \ref{eq:advtend}) also acted within the outflow jet.
+For example, horizontal advection provided forcing for destabilization at the 16-km level almost everywhere inside of the 140-km radius.
+Outside of this radius near 16 km, however, existed a region of forcing for stabilization.
+This switch in signs can be explained by a reversal of the radial gradient of mean $N^2$ near the 140-km radius (Fig.~\ref{fig:n2-24hr-avgs}b).
+Inside of that radius, $(\partial/\partial r)(\partial \theta/\partial z) > 0$ and $u > 0$, which corresponds to forcing for destabilization in Eq.
+\ref{eq:advtend}; outside of that radius, $(\partial/\partial r)(\partial \theta/\partial z) < 0$ and $u > 0$, which corresponds to forcing for stabilization.
 %
-%The relative importance of the first and third terms on the right-hand side of Eq.
+The relative importance of the first and third terms on the right-hand side of Eq.
 \ref{eq:advtend} is difficult to ascertain, but the structure of the mean radial velocity, $\theta$, and $N^2$ fields suggests that both terms are contributing within the outflow layer.
 
-Meanwhile in the lower stratosphere, a thin layer of 2-4 m s\textsuperscript{-1} inflow developed a few hundred meters above the tropopause, similar to that which was observed in Hurricane Patricia (2015; \citeauthor{DuranMolinari2018} \citeyear{DuranMolinari2018}) and in previous modeling studies (e.g.
+Meanwhile in the lower stratosphere, a thin layer of 2--4 m s\textsuperscript{-1} inflow developed about one km above the tropopause, similar to that which was observed in Hurricane Patricia (2015; \citeauthor{DuranMolinari2018} \citeyear{DuranMolinari2018}) and in previous modeling studies (e.g.
 \citeauthor{OhnoSatoh2015} \citeyear{OhnoSatoh2015}; \citeauthor{Kieuetal} \citeyear{Kieuetal}).
@@
 \ref{eq:advtend} shows that the tilting of isentropes should act to destabilize the layer below the inflow maximum and stabilize the layer above, which is precisely what was observed outside of the 80-km radius in Fig.~\ref{fig:adv-24-48}a.
-Since the negative $\theta$ tendencies maximized at the level of maximum inflow, the layer below the inflow maximum destabilized and the layer above stabilized (Fig.~\ref{fig:adv-24-48}a).
+Since the negative $\theta$ tendencies maximized at the level of maximum inflow, radial advection provided forcing for  destabilization below the inflow maximum and stabilization above (Fig.~\ref{fig:adv-24-48}a).
 
@@
 Additionally, when these waves reached r=0, a dipole of vertical velocity resulted, with ascent above and descent below.
-For reasons that remain unclear, the regions of ascent were more persistent than the regions of descent, which resulted in the mean ascent observed near r=0 above 17 km in Fig.~\ref{fig:adv-24-48}d.
+For reasons that remain unclear, the regions of ascent were more persistent than the regions of descent in the lower stratosphere, which resulted in the mean ascent that manifested near r=0 above 17 km in Fig.~\ref{fig:adv-24-48}d.
+The dynamics that force this mean stratospheric ascent near r=0, and its potential consequences, are left for future work.
 
 Vertical advection also played an important role in the tropopause-layer static stability evolution.
-Within the eye, subsidence dominated below 17 km, while mean ascent existed near the storm center above 17 km.
 Although the magnitude of the subsidence was larger at lower altitudes, $\partial \theta/\partial z$ was smaller there.
@@
 Above the lower-stratospheric subsidence maximum, meanwhile, vertical advection decreased $N^2$.
-Below the tropopause, differential vertical advection increased $N^2$ within the eyewall region and also at larger radii above the vertical velocity maximum at larger radii.
-Outside of the eyewall and below the vertical velocity maximum, meanwhile, differential vertical advection acted to decrease $N^2$.
+Below the tropopause, differential vertical advection increased $N^2$ within the eyewall region, where upward vertical velocity decreased rapidly with height.
+Outside of the eyewall below 16 km, meanwhile, the vertical gradient of vertical velocity was smaller, and as a result, the $N^2$ tendencies due to vertical advection were weaker.
 
@@
 
-After the TC's RI period completed (48-72 hours), strong radiative cooling remained near the tropopause at inner radii (Fig.~\ref{fig:qi+radten}f), sloping downward with the top of the cirrus canopy to below the tropopause at outer radii.
+After the TC's RI period completed (48-72 hours), strong radiative cooling remained near the tropopause at inner radii (Fig.~\ref{fig:qi+radten}f), sloping downward with the top of the cirrus canopy to below the tropopause at outer radii
+
 Cooling rates exceeded 1 K h\textsuperscript{-1} (24 K day\textsuperscript{-1}) just above the tropopause between the 30- and 70-km radii.
-This value is more than three times the maximum cooling rate of 0.3 K h\textsuperscript{-1} observed by \cite{Buetal}, a difference that is a consequence of their larger vertical grid spacing compared to that used here, along with a contribution from differing radiation schemes.
+This value is more than three times the maximum cooling rate of 0.3 K h\textsuperscript{-1} noted by \cite{Buetal}, a difference that is a consequence of their larger vertical grid spacing compared to that used here, along with a contribution from differing radiation schemes.
 %\cite{Buetal} employed the NASA-Goddard radiation scheme in their CM1 simulations, whereas RRTMG is used in the present paper.
@@
 This suggests that vertical grid spacing smaller than 625 m is necessary to resolve properly the radiative cooling at the top of the cirrus canopy, and that the results can be quite sensitive to the radiation scheme used.
+A more in-depth analysis of this sensitivity to vertical grid spacing and radiation scheme are left to future work; it is possible that a vertical grid spacing even smaller than 250 m is necessary to resolve cloud-top radiative tendencies.
 
-Meanwhile below the tropopause, time-mean radiative warming spread from 30- to 160-km radius within the cirrus canopy.
-The existence of radiative cooling overlying radiative warming in this region led to radiatively-forced destabilization at and below the tropopause, as was observed in Fig.~\ref{fig:stab-48-72}d.
+Meanwhile below the tropopause, time-mean radiative warming was present between the 30- to 160-km radius within the cirrus canopy.
+The existence of radiative cooling overlying radiative warming in this region led to radiatively-forced destabilization at and below the tropopause, as was depicted in Fig.~\ref{fig:stab-48-72}d.
 Beneath the warming layer existed a region of forcing for stabilization, while a much stronger region of forcing for stabilization existed in the lower stratosphere, above the cooling maximum.
 
-The results herein suggest that, after the cirrus canopy developed, radiative heating tendencies considerably destabilized the upper troposphere and stabilized the lower stratosphere.
+The results herein suggest that, after the cirrus canopy developed, radiative heating tendencies considerably destabilized the upper troposphere and stabilized the lower stratosphere at inner radii.
+At larger radii, the downward slope of these tendencies with radius produced a region of radiative forcing for stabilization just below the tropopause.
+The departure of the cirrus canopy from the tropopause at these large radii (Figs.
+\ref{fig:qi+radten}c,e) suggests that, in this region, the tropopause did not exert a strong control on the height of the cirrus canopy.
+Other processes, such as the precipitaton of ice particles, caused a lowering of the cirrus canopy that adjusted the location of the radiative forcing relative to the tropopause.
 
@@
 
-The simulated $N^2$ evolution shown herein closely matched that observed during the RI of Hurricane Patricia (2015).
+The simulated $N^2$ evolution shown herein closely resembled that observed during the RI of Hurricane Patricia (2015).
 Three $N^2$ budget terms dominated in the upper troposphere and lower stratosphere: advection, radiation, and vertical turbulence.
@@
 
-To put the $N^2$ variability observed near the tropopause into context, Fig.~\ref{fig:fulltrop} depicts the model change in $N^2$ over the RI period (hours 24-48) from 0 to 21 km altitude, along with the vertical eddy diffusivity and the radiative heating rate.
+To put the $N^2$ variability seen near the tropopause into context, Fig.~\ref{fig:fulltrop} depicts the model change in $N^2$ over the RI period (hours 24-48) from 0 to 21 km altitude, along with the vertical eddy diffusivity and the radiative heating rate.
 The largest changes in $N^2$ occurred in a relatively shallow layer immediately surrounding the tropopause (Fig.~\ref{fig:fulltrop}a).
@@
 \centerline{\includegraphics[width=39pc]{mod+bud+res.png}}
-\caption{Left panels: Twenty-four-hour changes in squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$; 10\textsuperscript{-4} s\textsuperscript{-2}) computed using Eq.~\ref{eq:modelchange} over (top row) 0-24 hours, (middle row) 24-48 hours, (bottom row) 48-72 hours.
-Middle Panels: The $N^2$ change over the same time periods computed using Eqs. \ref{eq:dn2dt}-\ref{eq:budgetchange}, %together with Eqs. \ref{eq:dn2dt}, \ref{eq:dthetadt}.
+\caption{Left panels: Twenty-four-hour changes in squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$; 10\textsuperscript{-4} s\textsuperscript{-2}) computed using Eq.~\ref{eq:modelchange}, together with Eq.
+1, over (top row) 0-24 hours, (middle row) 24-48 hours, (bottom row) 48-72 hours.
+Middle Panels: The $N^2$ change over the same time periods computed using Eqs. 3-\ref{eq:budgetchange}.
 Right Panels: The budget residual over the same time periods, computed by subtracting the budget change (middle column) from the model change (left column).
-Orange lines represent the cold-point tropopause height averaged over the same time periods.}
+Orange lines represent the cold-point tropopause height averaged over the same time periods (i.e., the tropopause is determined every minute, and these tropopause heights are averaged over 24 hours.)}
 \label{fig:mod+bud+res}

### 2018-08-09 paper.tex
Address Reviewer 1's commen #50.

@@
 The large vertical gradient of vertical eddy diffusivity near the tropopause played an important role in developing the lower-stratospheric stable layer during RI.
-These results support the hypothesized role of turbulence in setting the outflow-layer $\theta$ stratification in \cite{EmanuelRotunno2011}.
+These results support the hypothesized role of turbulence in setting the outflow-layer $\theta$ stratification in \cite{EmanuelRotunno2011}, although more experiments with different turbulence parameterizations are needed to prove this conclusively.
 

### 2018-08-14 paper.tex
Address all reviewer comments except Reviewer 1's major comment and Reviewer 2's paragraph comments and minor points 1 and 4.

--- 2018-08-06 paper.tex
@@
 These trends continued as the storm's intensity leveled off in the 48-72-hour period (Fig.~\ref{fig:n2-24hr-avgs}c).
-The tropopause height increased to nearly 21 km at the storm center and sloped sharply downward to 16.3 km on the inner edge of the eyewall, near the 30 km radius.
-A local minimum in tropopause height manifested near the eye-eyewall interface, similar to that observed in Hurricane Patricia (see \citeauthor{DuranMolinari2018} \citeyear{DuranMolinari2018}, Figs.
+The tropopause height increased to nearly 21 km at the storm center and sloped sharply downward to 16.3 km on the outer edge of the eye, near the 30 km radius.
+A local minimum in tropopause height manifested near the outer edge of the eye, similar to that observed in Hurricane Patricia (see \citeauthor{DuranMolinari2018} \citeyear{DuranMolinari2018}, Figs.
 4f-h), although the authors of that paper cautioned that these local minima could be quite sensitive to small fluctuations in temperature.
@@
 Radiative tendencies overcome this forcing for stabilization in both of these regions to produce the radially-extensive region of destabilization just below the tropopause.
-The sum of advection, vertical turbulence, and radiation (Fig.~\ref{fig:stab-24-48}f) once again closely follows the total $N^2$ variability, except in the eyewall region, where the neglect of latent heating and horizontal turbulence introduces some differences.
+The sum of advection, vertical turbulence, and radiation (Fig.~\ref{fig:stab-24-48}f) once again closely follows the total $N^2$ variability, except in the 25--70-km radial band, where the neglect of latent heating and horizontal turbulence introduces some differences.
 
@@
 Comparison of these turbulent regions to the $N^2$ tendencies in Figs.
-\ref{fig:stab-24-48}c and \ref{fig:stab-48-72}c reveals that the layers in which vertical eddy diffusivity maximized corresponded to layers of destabilization due to vertical turbulence.
+\ref{fig:stab-24-48}c and \ref{fig:stab-48-72}c reveals that layers characterized by large vertical gradients of vertical eddy diffusivity corresponded to layers of destabilization due to vertical turbulence.
 Just outside of these layers, however, vertical turbulence acted to increase $N^2$.
 The large vertical gradient of vertical eddy diffusivity near the tropopause played an important role in developing the lower-stratospheric stable layer during RI.
-These results support the hypothesized role of turbulence in setting the outflow-layer $\theta$ stratification in \cite{EmanuelRotunno2011}.
+These results support the hypothesized role of turbulence in setting the outflow-layer $\theta$ stratification in \cite{EmanuelRotunno2011}, although more experiments with different turbulence parameterizations are needed to investigate this problem more closely.
 
@@
 In this paper, all of the variables were averaged over a full diurnal cycle to eliminate the effects of diurnal variability and isolate the overall storm evolution.
-Diurnal variations in static stability near the tropopause are potentially of interest with respect to the tropical cyclone diurnal cycle, and will be the subject of future work.
+Diurnal variations in static stability near the tropopause are potentially of interest with respect to the tropical cyclone diurnal cycle.
+A preliminary investigation using an ensemble of CM1 simulations suggests that the static stability at the top of the cirrus canopy peaks in the early afternoon and decreases overnight (Sarah Ditchek, personal communication).
+The mechanisms that produce this diurnal cycle of static stability, and its potential consequences, are the subject of future work.
 
@@
 \acknowledgments
-We are indebted to George Bryan for his continued development and support of Cloud Model 1.
-We also thank Jeffrey Kepert, Robert Fovell, and Erika Navarro for helpful conversations related to this work.
+This work constituted a portion of the lead author's Ph.D. dissertation, which benefited greatly from the guidance of committee members Kristen Corbosiero, Robert Fovell, Brian Tang, and Ryan Torn.
+We thank George Bryan for his continued development and support of Cloud Model 1, and Jeffrey Kepert and Erika Duran for helpful conversations related to this work.
+Comments and recommendations from Kerry Emanuel and two anonymous reviewers considerably improved a previous version of this manuscript.
 This research was supported by NSF grant AGS-1636799 and Office of Naval Research Grant N000141712110 as a part of the TCI Departmental Research Initiative.
@@
 \caption{Twenty-four-hour averages of squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$; 10\textsuperscript{-4} s\textsuperscript{-2}) over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours.
+Thick black contours are overlayed every 5x10\textsuperscript{-4} s\textsuperscript{-2}, starting at 5x10\textsuperscript{-4} s\textsuperscript{-2}.
 Orange lines represent the cold-point tropopause height averaged over the same time periods.}

### 2018-08-15 paper.tex
REVISED VERSION SUBMITTED TO JOHN.

@@
 
-\authors{Patrick Duran\correspondingauthor{Department of Atmospheric and Environmental Sciences, University at Albany, State University of New York, 1400 Washington Avenue, Albany, NY.} and John Molinari}
+\authors{Patrick Duran\correspondingauthor{Patrick Duran, University of Alabama in Huntsville, 320 Sparkman Dr.
+NW, Huntsville, AL 35805.}\thanks{Current affiliation: Earth System Science Center, University of Alabama in Huntsville} and John Molinari}
 
@@
 
-\email{pduran2008@gmail.com}
+\email{patrick.duran@uah.edu}
 
@@
 % and identify it as the capsule. Example: This is the end of the abstract. (Capsule Summary) This is the capsule summary. 
-
-\abstract{Large changes in tropopause-layer static stability are examined during the rapid intensification (RI) of a tropical cyclone (TC) in an idealized, axisymmetric simulation.
-Over the eye, static stability near the tropopause decreases and the cold-point tropopause height rises by up to 4 km at the storm center.
+\abstract{Large changes in tropopause-layer static stability are examined during the rapid intensification (RI) of a simulated tropical cyclone (TC).
+Over the eye, static stability near the tropopause decreases and the cold-point tropopause rises by up to 4 km at the storm center.
 Outside of the eye, static stability increases considerably just above the cold-point tropopause, and the tropopause remains near its initial level.\\
 \indent A budget analysis reveals that the advection term, which includes differential advection of potential temperature ($\theta$) and direct advection of static stability, is important throughout the upper troposphere and lower stratosphere.
-Within the eye, differential advection plays a particularly important role in destabilizing the layer near and above the cold-point tropopause.
-Outside of the eye, the upper-tropospheric outflow layer exports high-$\theta$ air from the eyewall to large radii in the upper troposphere.
-This increase in $\theta$ forces stabilization below the outflow jet and destabilization above.
-Vertical wind shear above and below the outflow maximum induces vertical gradients of turbulence, which also modify the vertical stability profile.
+Advection is particularly important within the eye, where it acts to destabilize the layer near and above the cold-point tropopause.
+Outside of the eye, a radial-vertical circulation develops during RI, with strong outflow below the tropopause and weak inflow above.
+Differential advection of $\theta$ near the outflow jet provides forcing for stabilization below the outflow maximum and destabilization above.
+Vertical wind shear induces turbulence on the flanks of the outflow maximum, which also modifies the vertical stability profile.
 Meanwhile, radiative cooling tendencies at the top of the cirrus canopy generally act to destabilize the upper troposphere and stabilize the lower stratosphere.
-These turbulent and radiative processes combine to play an important role in the development of the strong stable layer immediately above the cold-point tropopause during RI.}
+%These turbulent and radiative processes combine to play an important role in the development of the strong stable layer immediately above the cold-point tropopause during RI.
+The results suggest that turbulence and radiation, alongside advection, play fundamental roles in the upper-level static stability evolution of TCs.}
+
+%\abstract{Large changes in tropopause-layer static stability are examined during the rapid intensification (RI) of a tropical cyclone (TC) in an idealized, axisymmetric simulation.
+%Over the eye, static stability near the tropopause decreases and the cold-point tropopause height rises by up to 4 km at the storm center.
+%Outside of the eye, static stability increases considerably just above the cold-point tropopause, and the tropopause remains near its initial level.\\
+%\indent A budget analysis reveals that the advection term, which includes differential advection of potential temperature ($\theta$) and direct advection of static stability, is important throughout the upper troposphere and lower stratosphere.
+%Within the eye, differential advection plays a particularly important role in destabilizing the layer near and above the cold-point tropopause.
+%Outside of the eye, the upper-tropospheric outflow layer exports high-$\theta$ air from the eyewall to large radii in the upper troposphere.
+%This increase in $\theta$ forces stabilization below the outflow jet and destabilization above.
+%Vertical wind shear above and below the outflow maximum induces vertical gradients of turbulence, which also modify the vertical stability profile.
+%Meanwhile, radiative cooling tendencies at the top of the cirrus canopy generally act to destabilize the upper troposphere and stabilize the lower stratosphere.
+%These turbulent and radiative processes combine to play an important role in the development of the strong stable layer immediately above the cold-point tropopause during RI.}
 %The results suggest that turbulence and radiation, alongside advection, play fundamental roles in the upper-level static stability evolution of TCs.}
 %The conclusions are robust to changes in the initial thermodynamic profile and prescribed vertical mixing length within a reasonable range of values.}
-
 \begin{document}
@@
 
-After undergoing a remarkably rapid intensification (RI), Hurricane Patricia (2015) attained the strongest wind speed ever recorded in a tropical cyclone (TC) (\citeauthor{Kimberlainetal2016} \citeyear{Kimberlainetal2016}; \citeauthor{Rogersetal2017} \citeyear{Rogersetal2017}).
+After undergoing a remarkably rapid intensification, Hurricane Patricia (2015) attained the strongest wind speed ever recorded in a tropical cyclone (TC) (\citeauthor{Kimberlainetal2016} \citeyear{Kimberlainetal2016}; \citeauthor{Rogersetal2017} \citeyear{Rogersetal2017}).
 %High-altitude dropsonde observations taken during the Tropical Cyclone Intensity (TCI) experiment captured this RI in unprecedented detail \citep{DoyleTCI}.
@@
 During the early stage of development in their simulation, large static stability existed above 16 km at all radii (their Fig. 9c).
-However, after the storm's intensification, the static stability within the eye above 16 km was markedly smaller (their Fig. 10c).
+After the storm's intensification, however, the static stability within the eye above 16 km was markedly smaller (their Fig. 10c).
 Although the mechanisms that might drive this static stability evolution have not been examined explicitly, it might be related to the development of an upper-tropospheric warm core within the eye.
@@
 If the top of the cirrus canopy lies close to the tropopause, these radiative processes could contribute to a stabilization of the lower stratosphere.
+
+In addition to the direct effect of radiative cooling on the tropopause-layer static stability, this cooling also could exert an indirect effect by modifying the storm's radial--vertical circulation.
+\cite{Durranetal2009} described the circulation that develops in response to radiative heating within tropopause-layer cirrus clouds.
+The heating induces upward motion through the heat source, inflow below the heat source, and outflow above.
+\cite{Dinhetal2010} showed that these circulations act to spread cirrus clouds laterally, which then would feed back onto the radiative tendencies.
+Although the cloud-top radiative cooling played a negligible role in the radiatively-induced storm expansion observed by \cite{Buetal} and \cite{Fovelletal2016}, it did modify the circulation near the cloud top.
+In particular, it drove weak inflow above the cooling maximum and outflow below, along with subsidence within the region of cooling (see \citeauthor{Fovelletal2016} \citeyear{Fovelletal2016}, Fig.
+21).
+Although these circulations were weak, their persistence could have driven differential advection of $\theta$, as discussed by \cite{ChenZhang2013} and \cite{ChenGopalakrishnan2015},  which could modify the tropopause-layer static stability.
+
+The existence of a diurnal cycle of TC convection has been well established in recent literature (e.g., \citeauthor{Kossin2002} \citeyear{Kossin2002}; \citeauthor{Dunionetal2014} \citeyear{Dunionetal2014}; \citeauthor{BowmanFowler2015} \citeyear{BowmanFowler2015}).
+Since this cycle exhibits a convective maximum overnight and in the early morning, and a convective minimum in the afternoon, radiative heating tendencies are a natural suspect in its evolution.
+The idealized simulations of \cite{NavarroHakim2016} implicate periodic oscillations of upper-level radiative heating in the evolution of the TC diurnal cycle.
+Their results exhibit characteristics of an inertia--gravity wave response with an outward-propagating horizontal phase speed of 9.8 m s\textsuperscript{-1}, which is consistent with the outward motion of the diurnal pulse observed by \cite{Dunionetal2014}.
+If the diurnal pulse is, indeed, an outward-propagating inertia--gravity wave, the upper-tropospheric static stability profile could have implications for the characteristics of its propagation.
+
 %Other processes that can modify the static stability in the upper troposphere of TCs include radiative heating within and near the top of the cirrus canopy and shear-induced turbulent mixing near the outflow jet.
@@
 
-Although hurricanes simulated in an axisymmetric framework tend to be more intense than those observed in nature, the intensity evolution of this simulation matches reasonably well with that observed in Hurricane Patricia.
+Although hurricanes simulated in an axisymmetric framework tend to be more intense than those observed in nature, the intensity evolution of this simulation matches reasonably well with that observed in Hurricane Patricia\footnote{Although the intensities of the storms are comparable, the simplifications inherent to this modeling framework --- particularly axisymmetry and a lack of atmosphere--ocean coupling --- mean that the processes contributing to intensification probably are quite different.}.
 After an initial spin-up period of about 20 hours, the modeled storm (Fig.~\ref{fig:vmax+pmin}, blue lines) began an RI period that lasted approximately 18 hours.
@@
 A local minimum in tropopause height manifested near the outer edge of the eye, similar to that observed in Hurricane Patricia (see \citeauthor{DuranMolinari2018} \citeyear{DuranMolinari2018}, Figs.
-4f-h), although the authors of that paper cautioned that these local minima could be quite sensitive to small fluctuations in temperature.
+4f-h).
+% although the authors of that paper cautioned that these local minima could be quite sensitive to small fluctuations in temperature.
 %The authors cautioned that, due to the presence of a nearly isothermal layer at this location (\citeauthor{DuranMolinari2018} \citeyear{DuranMolinari2018}, Figs.
 4b-d), the tropopause height could be quite sensitive to small fluctuations in temperature or to sensor error.
-The presence of a local minimum at this location in these 24-hour averages, however, suggests that this tropopause depression on the outer edge of the eye could be a robust, persistent feature.
+The presence of a local minimum at this location in these 24-hour averages suggests that this tropopause depression on the outer edge of the eye could be a robust, persistent feature.
 Static stability outside of the eye, meanwhile, continued to increase just above the cold-point tropopause.
@@
 This mechanism is the same as that discussed in \cite{TrierSharman}, in which vertical wind shear in the outflow layer of a mesoscale convective system modified the upper-tropospheric static stability through differential advection of isentropes.
-Thus, wherever $\partial u/\partial z>0$, the tilting term must force an increase in $N^2$, and wherever $\partial u/\partial z<0$, the tilting term must force a decrease in $N^2$, which is precisely the structure seen in Fig.~\ref{fig:adv-24-48}a.
+Thus, wherever $\partial u/\partial z>0$, the tilting term must force an increase in $N^2$, and wherever $\partial u/\partial z<0$, the tilting term must force a decrease in $N^2$, which is the structure seen in Fig.~\ref{fig:adv-24-48}a.
 
@@
 
-After the TC's RI period completed (48-72 hours), strong radiative cooling remained near the tropopause at inner radii (Fig.~\ref{fig:qi+radten}f), sloping downward with the top of the cirrus canopy to below the tropopause at outer radii
-
+After the TC's RI period completed (48-72 hours), strong radiative cooling remained near the tropopause at inner radii (Fig.~\ref{fig:qi+radten}f), sloping downward with the top of the cirrus canopy to below the tropopause at outer radii.
 Cooling rates exceeded 1 K h\textsuperscript{-1} (24 K day\textsuperscript{-1}) just above the tropopause between the 30- and 70-km radii.
@@
 This suggests that vertical grid spacing smaller than 625 m is necessary to resolve properly the radiative cooling at the top of the cirrus canopy, and that the results can be quite sensitive to the radiation scheme used.
-A more in-depth analysis of this sensitivity to vertical grid spacing and radiation scheme are left to future work; it is possible that a vertical grid spacing even smaller than 250 m is necessary to resolve cloud-top radiative tendencies.
+A more in-depth analysis of this sensitivity to vertical grid spacing and radiation scheme is left to future work; it is possible that a vertical grid spacing even smaller than 250 m is necessary to resolve cloud-top radiative tendencies.
 
@@
 \ref{fig:qi+radten}c,e) suggests that, in this region, the tropopause did not exert a strong control on the height of the cirrus canopy.
-Other processes, such as the precipitaton of ice particles, caused a lowering of the cirrus canopy that adjusted the location of the radiative forcing relative to the tropopause.
+Other processes, such as the precipitaton of ice particles, must have caused this lowering of the cirrus canopy.
+
+  \subsubsection{Sensitivity to cloud-radiative forcing}
+
+To analyze more closely the effect of cloud-radiative forcing on the $N^2$ evolution, a simulation identical to that described in Section 2 was run, except the interaction between condensate and radiation was prohibited (as was described in \citeauthor{Buetal} \citeyear{Buetal} and \citeauthor{Fovelletal2016} \citeyear{Fovelletal2016}).
+The intensity evolution of this simulation (Fig.
+\ref{fig:vmax-norad}, blue line) compares well with that of the simulation described in Section 2 (Fig.
+\ref{fig:vmax-norad}, red line), except the storm without cloud-radiative forcing took longer to begin its RI period.
+Twenty-four-hour averages of $N^2$ reveal a similar overall evolution in the two simulations (compare Figs.
+\ref{fig:n2-24hr-avgs},\ref{fig:n2-norad}), except the lower-stratospheric $N^2$ maximum does not become as strong in the simulation without cloud-radiative forcing.
+The magnitude of the sum of the advection and turbulence terms immediately surrounding the tropopause in this simulation (Fig.
+\ref{fig:budgetterms-norad}e) is not as large as that in the full-radiation simulation (Fig.
+\ref{fig:stab-48-72}e).
+This suggests that radiative heating tendencies near the cloud top affect the radial-vertical circulation there, which then feeds back on to the advection and turbulence terms.
+The smaller turbulence and advective tendencies, combined with the near-zero radiative heating tendencies (Fig.
+\ref{fig:budgetterms-norad}d), leads to a smaller lower-stratospheric stabilization tendency (compare Figs.
+\ref{fig:stab-48-72}a,\ref{fig:budgetterms-norad}a).
+These results highlight the importance of cloud-radiative interaction in the evolution of the tropopause-layer $N^2$.
 
@@
 In this paper, all of the variables were averaged over a full diurnal cycle to eliminate the effects of diurnal variability and isolate the overall storm evolution.
-Diurnal variations in static stability near the tropopause are potentially of interest with respect to the tropical cyclone diurnal cycle.
+These diurnal variations, however, are potentially of interest with respect to the tropical cyclone diurnal cycle.
 A preliminary investigation using an ensemble of CM1 simulations suggests that the static stability at the top of the cirrus canopy peaks in the early afternoon and decreases overnight (Sarah Ditchek, personal communication).
 The mechanisms that produce this diurnal cycle of static stability, and its potential consequences, are the subject of future work.
-
-% text...
-% \section{Section title}
-
-%vs
-
-% \section{Section title}
-% \subsection{subsection one}
-% text...
-% \subsection{subsection two}
-% \section{Section title}
-
-%%%
-% \section{First primary heading}
-
-% \subsection{First secondary heading}
-
-% \subsubsection{First tertiary heading}
-
-% \paragraph{First quaternary heading}
 
@@
 
-%FIGURE 10%
+%FIGURE 11%
+\begin{figure*}[ht]
+\centerline{\includegraphics[width=27pc]{run12+run13-vmax.png}}
+   \caption{Maximum 10-m wind speed (m s\textsuperscript{-1}) for (red) the simulation described in Section 2, and (blue) an identical simulation except condensate is not permitted to interact with radiation.}
+\label{fig:vmax-norad}
+\end{figure*}
+
+%FIGURE 12%
+\begin{figure*}[ht]
+\centerline{\includegraphics[width=39pc]{n2-norad.png}}
+   \caption{As in Fig. \ref{fig:n2-24hr-avgs}, but for the simulation in which radiation is not permitted to interact with condensate.}
+\label{fig:n2-norad}
+\end{figure*}
+
+%FIGURE 13%
+%\begin{figure*}[ht]
+%\centerline{\includegraphics[width=39pc]{adv-norad.png}}
+%   \caption{As in Fig. \ref{fig:adv-24-48}, but for the 48-72--hour period of the simulation in which radiation is not permitted to interact with condensate.}
+%\label{fig:adv-norad}
+%\end{figure*}
+
+%FIGURE 13%
+\begin{figure*}[ht]
+\centerline{\includegraphics[width=39pc]{budgetterms-norad.png}}
+   \caption{As in Fig. \ref{fig:stab-48-72}, but for the simulation in which radiation is not permitted to interact with condensate.}
+\label{fig:budgetterms-norad}
+\end{figure*}
+
+%FIGURE 14%
 \begin{figure*}[ht]
@@
 
-%FIGURE 11%
+%FIGURE 15%
 \begin{figure}[ht]
@@
 
-%FIGURE 12%
+%FIGURE 16%
 \begin{figure}[ht]

### 2018-08-23 paper.tex
REVISED AND SENT BACK TO REVIEWERS.

@@
 
-\authors{Patrick Duran\correspondingauthor{Patrick Duran, University of Alabama in Huntsville, 320 Sparkman Dr.
+\authors{Patrick Duran\correspondingauthor{Patrick Duran, University of Alabama in Huntsville, NSSTC \#4002, 320 Sparkman Dr.
 NW, Huntsville, AL 35805.}\thanks{Current affiliation: Earth System Science Center, University of Alabama in Huntsville} and John Molinari}
@@
 % and identify it as the capsule. Example: This is the end of the abstract. (Capsule Summary) This is the capsule summary.
+
 \abstract{Large changes in tropopause-layer static stability are examined during the rapid intensification (RI) of a simulated tropical cyclone (TC).
@@
 Outside of the eye, static stability increases considerably just above the cold-point tropopause, and the tropopause remains near its initial level.\\
-\indent A budget analysis reveals that the advection term, which includes differential advection of potential temperature ($\theta$) and direct advection of static stability, is important throughout the upper troposphere and lower stratosphere.
-Advection is particularly important within the eye, where it acts to destabilize the layer near and above the cold-point tropopause.
-Outside of the eye, a radial-vertical circulation develops during RI, with strong outflow below the tropopause and weak inflow above.
+\indent A budget analysis reveals that the advection terms, which include differential advection of potential temperature ($\theta$) and direct advection of static stability, are important throughout the upper troposphere and lower stratosphere.
+These terms are particularly pronounced within the eye, where they act to destabilize the layer near and above the cold-point tropopause.
+Outside of the eye, a radial--vertical circulation develops during RI, with strong outflow below the tropopause and weak inflow above.
 Differential advection of $\theta$ near the outflow jet provides forcing for stabilization below the outflow maximum and destabilization above.
@@
 Meanwhile, radiative cooling tendencies at the top of the cirrus canopy generally act to destabilize the upper troposphere and stabilize the lower stratosphere.
-%These turbulent and radiative processes combine to play an important role in the development of the strong stable layer immediately above the cold-point tropopause during RI.
-The results suggest that turbulence and radiation, alongside advection, play fundamental roles in the upper-level static stability evolution of TCs.}
+The results suggest that turbulence and radiation, alongside differential advection, play fundamental roles in the upper-level static stability evolution of TCs.
+These static stability tendencies could have implications for both the TC diurnal cycle and the tropopause-layer potential vorticity evolution in TCs.}
 
-%\abstract{Large changes in tropopause-layer static stability are examined during the rapid intensification (RI) of a tropical cyclone (TC) in an idealized, axisymmetric simulation.
-%Over the eye, static stability near the tropopause decreases and the cold-point tropopause height rises by up to 4 km at the storm center.
-%Outside of the eye, static stability increases considerably just above the cold-point tropopause, and the tropopause remains near its initial level.\\
-%\indent A budget analysis reveals that the advection term, which includes differential advection of potential temperature ($\theta$) and direct advection of static stability, is important throughout the upper troposphere and lower stratosphere.
-%Within the eye, differential advection plays a particularly important role in destabilizing the layer near and above the cold-point tropopause.
-%Outside of the eye, the upper-tropospheric outflow layer exports high-$\theta$ air from the eyewall to large radii in the upper troposphere.
-%This increase in $\theta$ forces stabilization below the outflow jet and destabilization above.
-%Vertical wind shear above and below the outflow maximum induces vertical gradients of turbulence, which also modify the vertical stability profile.
-%Meanwhile, radiative cooling tendencies at the top of the cirrus canopy generally act to destabilize the upper troposphere and stabilize the lower stratosphere.
-%These turbulent and radiative processes combine to play an important role in the development of the strong stable layer immediately above the cold-point tropopause during RI.}
-%The results suggest that turbulence and radiation, alongside advection, play fundamental roles in the upper-level static stability evolution of TCs.}
-%The conclusions are robust to changes in the initial thermodynamic profile and prescribed vertical mixing length within a reasonable range of values.}
 \begin{document}
@@
 
-%Perhaps introduce upper-tropospheric static stability and its relationship to the diurnal cycle before going into Patricia? Include references to Dunion, Navarro, and O'Neill here.
-%More recently, \cite{Dunionetal2014} documented a periodic oscillation of infrared brightness temperature in hurricanes, which they call the "TC diurnal pulse."
-%There will be a whole bunch of papers cited here...
-%At some point (probably in the Discussion) mention the possible importance of static stability asymmetries, in the context of the Dunion diurnal pulse
-
 Using a high-resolution dropsonde dataset collected during the Tropical Cyclone Intensity Experiment (TCI; \citeauthor{DoyleTCI} \citeyear{DoyleTCI}), \cite{DuranMolinari2018} observed dramatic changes in tropopause structure during the rapid intensification (RI) of Hurricane Patricia (2015).
@@
 After undergoing a remarkably rapid intensification, Hurricane Patricia (2015) attained the strongest wind speed ever recorded in a tropical cyclone (TC) (\citeauthor{Kimberlainetal2016} \citeyear{Kimberlainetal2016}; \citeauthor{Rogersetal2017} \citeyear{Rogersetal2017}).
-%High-altitude dropsonde observations taken during the Tropical Cyclone Intensity (TCI) experiment captured this RI in unprecedented detail \citep{DoyleTCI}.
 TCI dropsonde observations collected during this RI period revealed dramatic changes in the cold-point tropopause height and upper-level static stability \citep{DuranMolinari2018}.
@@
 Meanwhile outside of the eye, the static stability remained large and the tropopause stayed near its initial level.
-%The mechanisms that might have led to this tropopause-layer variability will be investigated in the current paper using idealized simulations.
 
@@
 In the midlevels, radial and vertical advection both played important roles in the development of the warm core, with the eddy component of radial advection dominating over the mean component.
-In the upper levels, however, only the mean component of vertical advection was important for warm-core development.
-Horizontal diffusion became particularly important near the outer edge of the eye during the later stage of RI; these diffusive tendencies produced regions of warming below regions of cooling (see \citeauthor{SternZhang2013} \citeyear{SternZhang2013}, their Fig.
+In the upper levels, however, only the mean component of vertical advection considerably affected warm-core development.
+Horizontal diffusion became particularly large near the outer edge of the eye during the later stage of RI; these diffusive tendencies produced regions of warming below regions of cooling (see \citeauthor{SternZhang2013} \citeyear{SternZhang2013}, their Fig.
 7t), which would act to decrease the vertical $\theta$ gradient.
@@
 
-Although hurricanes simulated in an axisymmetric framework tend to be more intense than those observed in nature, the intensity evolution of this simulation matches reasonably well with that observed in Hurricane Patricia\footnote{Although the intensities of the storms are comparable, the simplifications inherent to this modeling framework --- particularly axisymmetry and a lack of atmosphere--ocean coupling --- mean that the processes contributing to intensification probably are quite different.}.
+Since ocean coupling and asymmetric forcing are present in nature, the intent of this paper is not to formally simulate Hurricane Patricia.
+Rather, the intent is to simulate a storm with a similar intensification rate and examine the processes that produced the stability variations in the simulated storm.
 After an initial spin-up period of about 20 hours, the modeled storm (Fig.~\ref{fig:vmax+pmin}, blue lines) began an RI period that lasted approximately 18 hours.
@@
 
-The first term on the right-hand side of Eq. ~\ref{eq:dn2dt} is larger than the second term throughout most of the tropopause layer (not shown).
+The first term on the right-hand side of Eq.
+~\ref{eq:dn2dt} is an order of magnitude larger than the second term throughout most of the tropopause layer (not shown)\footnote{The magnitude of the second term is comparable to that of the first only in a radially-confined region near r=0 in the stratosphere.}.
 Consequently, the contribution of each of the terms in Eq.~\ref{eq:dthetadt} to the $N^2$ tendency can be interpreted in terms of a vertical gradient of each term.
@@
 Eqs. \ref{eq:budgetchange}-\ref{eq:residual} are evaluated for three consecutive 24-hour periods in Fig.~\ref{fig:mod+bud+res}.
-For this and all subsequent radial-vertical cross sections, a 1-2-1 smoother is applied once in the radial direction to eliminate $2\Delta r$ noise that appears in some of the raw model output and calculated fields.
+For this and all subsequent radial--vertical cross sections, a 1-2-1 smoother is applied once in the radial direction to eliminate $2\Delta r$ noise that appears in some of the raw model output and calculated fields.
       The left column of Fig.~\ref{fig:mod+bud+res} depicts the model changes computed using Eq.~\ref{eq:modelchange}, together with Eq.~\ref{eq:n2moist} in saturated environments.
@@
 To circumvent this problem, the absolute value of each of the terms is averaged.}. 
-Advection (Fig.~\ref{fig:avgbudterms}, red line) plays an important role in the mean tropopause-layer static stability tendency at all times, and vertical turbulence (Fig.~\ref{fig:avgbudterms}, blue line) and radiation (Fig.~\ref{fig:avgbudterms}, dark green line) also contribute significantly.
-The remaining three processes - horizontal turbulence, microphysics, and dissipative heating -  are negligible everywhere outside of the eyewall, and do not play important roles in the mesoscale tropopause variability.
-
-The preceding analysis indicates that, at all times, three budget terms dominate the tropopause-layer static stability tendency: advection, vertical turbulence, and radiation.
+Advection (Fig.~\ref{fig:avgbudterms}, red line) plays an essential role in the mean tropopause-layer static stability tendency at all times, and vertical turbulence (Fig.~\ref{fig:avgbudterms}, blue line) and radiation (Fig.~\ref{fig:avgbudterms}, dark green line) also contribute significantly.
 Variations in the magnitude and spatial structure of these terms drive the static stability changes depicted in Fig.~\ref{fig:mod+bud+res}; subsequent sections will focus on these variations and what causes them.
+The remaining three processes - horizontal turbulence, microphysics, and dissipative heating -  are negligible everywhere outside of the eyewall, and will not be included in the analysis.
 
@@
 
+%Outside of the eye, the turbulence and radiation terms largely offset because strong $\theta$ tendencies forced by advection produced instabilities that were then eliminated through mixing by the turbulence scheme.
+%These high-magnitude, but opposing forcings did not completely cancel, however.
 Outside of the eye, the $N^2$ evolution exhibited alternating layers of positive and negative tendencies.
@@
 Immediately below this layer, just above the cold-point tropopause, was a region of increasing $N^2$ that sloped outward from 17 km near the 30-km radius to just below 18 km outside of the 100-km radius.
-Advection and vertical turbulence both contributed to this positive $N^2$ tendency, with advection playing an important role below about 17.5 km and and turbulence playing an important role above.
+Advection and vertical turbulence both contributed to this positive $N^2$ tendency, with advection playing an important role below about 17.5 km and and turbulence acting to stabilize the layer above 17.5 km.
 The sum of advection and turbulence (Fig.~\ref{fig:stab-24-48}e) reveals two separate regions of increasing $N^2$ in the 17-18-km layer rather than one contiguous region.
@@
 
-  \subsection{The role of advection}
+  \subsection{The role of the advection terms}
 
-Advection played an important role in the tropopause-layer $N^2$ evolution at all stages of intensification, but for brevity, this section will focus only on the RI (24-48-hour) period.
+Advection played an essential role in the tropopause-layer $N^2$ evolution at all stages of intensification, but for brevity, this section will focus only on the RI (24-48-hour) period.
 To investigate the advective processes more closely, the individual contributions of horizontal and vertical advection during the RI period are shown in Fig.~\ref{fig:adv-24-48}, along with the corresponding time-mean radial and vertical velocities and $\theta$.
@@
 A layer of strong outflow formed at and below the tropopause during this period, with the outflow maximum (dashed cyan line) curving from the 14-km level at the 50-km radius to just below the 16-km level outside of the 80-km radius (Fig.~\ref{fig:adv-24-48}c).
-%The cyan line, by definition, represents the level at which the vertical gradient of radial velocity switched signs, with $\partial u/\partial z>0$ below the line and $\partial u/\partial z<0$ above.
 Notably, the $N^2$ tendency due to horizontal advection (Fig.~\ref{fig:adv-24-48}a) tended to switch signs at this line, with stabilization below the outflow maximum and destabilization above.
-%This suggests that vertical wind shear above and below the outflow maximum played an important role in the $N^2$ tendency during this time.
-%Examination of the third term on the right-hand side of Eq.
-\ref{eq:advtend} suggests that tilting of isentropes within these shear layers contributed to the strong $N^2$ tendencies that flanked the outflow maximum.
-%This is consistent with the outflow layer carrying air with increasingly large $\theta$ from the eyewall to large radii as the storm intensified.
-%This increase in $\theta$ maximized near the outflow maximum, which acted to decrease $\partial \theta/\partial z$ above the outflow maximum and increase it below.
 Outside of the eye and eyewall, isentropes generally sloped upward with radius (Fig. \ref{fig:adv-24-48}c, black lines).
@@
 Comparing the $N^2$ tendencies forced by horizontal (Fig.~\ref{fig:adv-24-48}a) and vertical (Fig.~\ref{fig:adv-24-48}b) advection to the total advective tendency seen in Fig.~\ref{fig:stab-24-48}b reveals that horizontal advective tendencies dominated the troposphere, while vertical advective tendencies dominated the layer near and above the tropopause.
-Thus, tilting of isentropes in the vicinity of the upper-tropospheric outflow maximum appears to be the most important advective process governing the $N^2$ tendency in the troposphere, whereas convergence of vertical velocity appears to be the most important advective process near the tropopause.
+Thus, tilting of isentropes in the vicinity of the upper-tropospheric outflow maximum appears to be the most important advective process governing the $N^2$ tendency in the troposphere, whereas convergence of vertical velocity dominates near the tropopause.
 
@@
 Other processes, such as the precipitaton of ice particles, must have caused this lowering of the cirrus canopy.
-
-  \subsubsection{Sensitivity to cloud-radiative forcing}
-
-To analyze more closely the effect of cloud-radiative forcing on the $N^2$ evolution, a simulation identical to that described in Section 2 was run, except the interaction between condensate and radiation was prohibited (as was described in \citeauthor{Buetal} \citeyear{Buetal} and \citeauthor{Fovelletal2016} \citeyear{Fovelletal2016}).
-The intensity evolution of this simulation (Fig.
-\ref{fig:vmax-norad}, blue line) compares well with that of the simulation described in Section 2 (Fig.
-\ref{fig:vmax-norad}, red line), except the storm without cloud-radiative forcing took longer to begin its RI period.
-Twenty-four-hour averages of $N^2$ reveal a similar overall evolution in the two simulations (compare Figs.
-\ref{fig:n2-24hr-avgs},\ref{fig:n2-norad}), except the lower-stratospheric $N^2$ maximum does not become as strong in the simulation without cloud-radiative forcing.
-The magnitude of the sum of the advection and turbulence terms immediately surrounding the tropopause in this simulation (Fig.
-\ref{fig:budgetterms-norad}e) is not as large as that in the full-radiation simulation (Fig.
-\ref{fig:stab-48-72}e).
-This suggests that radiative heating tendencies near the cloud top affect the radial-vertical circulation there, which then feeds back on to the advection and turbulence terms.
-The smaller turbulence and advective tendencies, combined with the near-zero radiative heating tendencies (Fig.
-\ref{fig:budgetterms-norad}d), leads to a smaller lower-stratospheric stabilization tendency (compare Figs.
-\ref{fig:stab-48-72}a,\ref{fig:budgetterms-norad}a).
-These results highlight the importance of cloud-radiative interaction in the evolution of the tropopause-layer $N^2$.
+The effect of the interaction of radiation with clouds near the tropopause is further investigated in Appendix A.
 
@@
 Just outside of these layers, however, vertical turbulence acted to increase $N^2$.
-The large vertical gradient of vertical eddy diffusivity near the tropopause played an important role in developing the lower-stratospheric stable layer during RI.
+The large vertical gradient of vertical eddy diffusivity near the tropopause contributed to the development of the lower-stratospheric stable layer during RI.
 These results support the hypothesized role of turbulence in setting the outflow-layer $\theta$ stratification in \cite{EmanuelRotunno2011}, although more experiments with different turbulence parameterizations are needed to investigate this problem more closely.
 
-  \section{Conclusions}
+  \section{Conclusions and future work}
 
@@
 Advection dominated within the eye, where it provided forcing for destabilization.
-Radiation and vertical turbulence played particularly important roles in developing the strong $N^2$ maximum just above the cold-point tropopause during RI.
+Meanwhile, radiation and vertical turbulence greatly contributed to developing the strong $N^2$ maximum just above the cold-point tropopause during RI.
 
@@
 
+An interesting consequence of increasing $N^2$ in the tropopause layer is its effect on potential vorticity (PV) near the tropopause.
+As the simulated TC intensified, PV increased considerably inside of the eye as relative vorticity strengthened within the radius of maximum winds (Fig. \ref{fig:pv}).
+Outside of the eye in the lower stratosphere, meanwhile, PV also increased as a consequence of strengthening static stability.
+The magnitude of PV in this layer is exceptionally large, but is consistent with analyses produced using observations from Hurricane Patricia (2015) that showed values exceeding 200 PVU near the tropopause \citep{BellConference}.
+Just above and below the tropopause at larger radii, meanwhile, negative PV developed as a consequence of strong anticyclonic relative vorticity associated with the TC outflow layer.
+An investigation of the details and consequences of this tropopause-layer PV evolution are left to future work, but these results suggest that the static stability tendency near the tropopause is an important consideration in such an analysis.
+
 In this paper, all of the variables were averaged over a full diurnal cycle to eliminate the effects of diurnal variability and isolate the overall storm evolution.
-These diurnal variations, however, are potentially of interest with respect to the tropical cyclone diurnal cycle.
-A preliminary investigation using an ensemble of CM1 simulations suggests that the static stability at the top of the cirrus canopy peaks in the early afternoon and decreases overnight (Sarah Ditchek, personal communication).
+%These diurnal variations, however, are potentially of interest with respect to the tropical cyclone diurnal cycle.
+A preliminary investigation of the diurnal cycle of $N^2$ using an ensemble of CM1 simulations suggests that the static stability at the top of the cirrus canopy peaks in the early afternoon and decreases overnight (Sarah Ditchek, 2018, personal communication).
 The mechanisms that produce this diurnal cycle of static stability, and its potential consequences, are the subject of future work.
@@
 \acknowledgments
-This work constituted a portion of the lead author's Ph.D. dissertation, which benefited greatly from the guidance of committee members Kristen Corbosiero, Robert Fovell, Brian Tang, and Ryan Torn.
+This work constituted a portion of the lead author's Ph.D. dissertation, which benefited from the guidance of committee members Kristen Corbosiero, Robert Fovell, Brian Tang, and Ryan Torn.
 We thank George Bryan for his continued development and support of Cloud Model 1, and Jeffrey Kepert and Erika Duran for helpful conversations related to this work.
-Comments and recommendations from Kerry Emanuel and two anonymous reviewers considerably improved a previous version of this manuscript.
+Comments and recommendations from Kerry Emanuel and two anonymous reviewers greatly improved a previous version of this manuscript.
 This research was supported by NSF grant AGS-1636799 and Office of Naval Research Grant N000141712110 as a part of the TCI Departmental Research Initiative.
@@
 %% Appendix title is necessary! For appendix title:
-%\appendixtitle{Sensitivity experiments}
-%The simulations exhibited some sensitivity to the initial thermodynamic profile and the prescribed vertical mixing length.
-%Although the details of the intensification and the tropopause-layer $N^2$ evolution varied when these quantities were changed, the conclusions of the paper remain unchanged.
-%
-%%%% Appendix section numbering (note, skip \section and begin with \subsection)
-% \subsection{Sensitivity to the initial thermodynamic profile}
-%A number of sensitivity experiments were conducted using a variety of initial soundings.
-%Changing the initial temperature and humidity profiles affected the timing of the onset of organized deep convection and the rapidity of intensification.
-%In all simulations, however, convection eventually penetrated to the tropopause, at which time vertical turbulence and radiation combined with advection to adjust the $N^2$ profile toward that which was observed in the control run.
-%By the end of the RI period in every simulation, all three processes were actively modifying the $N^2$ profile near the tropopause.
-%
-%As an example, 24-hour averages of $N^2$ are plotted in Fig.
-A1 for a simulation that was identical to that used in this paper, except the initial sounding was determined by averaging every CFSR grid point within 1000 km of TC Patricia's storm center at 18 UTC 21 October 2015 instead of averaging only within the 100-km radius.
-%Although the lower-stratospheric stable layer developed more slowly and was weaker than that shown in Fig.~\ref{fig:n2-24hr-avgs}, the overall evolution was quite similar and the same budget terms dominated the $N^2$ evolution.
-%
-% \subsection{Sensitivity to the vertical mixing length}
-%The rate of turbulent mixing in the Smagorinsky scheme used herein is highly dependent on a prescribed length scale.
-%The vertical mixing length used in this paper (100 m) was based on the sensitivity experiments of \cite{Bryan2012}.
-%Prescribing a smaller mixing length produces smaller $\theta$ tendencies due to turbulence, but even with a mixing length on the low end of those tested by \cite{Bryan2012}, turbulence still played an important role in the tropopause-layer $N^2$ evolution.
-%Fig. A2 shows the 24-hour-averaged contributions of turbulent mixing to the $N^2$ evolution from a simulation identical to that used in this paper, except with a vertical mixing length of 50 m.
-%At all times, vertical turbulence still played an important role in the tropopause-layer $N^2$ evolution, particularly during the latter stages of RI (48-72 hours).
+\appendixtitle{Sensitivity to cloud-radiative forcing}
+
+To analyze more closely the effect of cloud-radiative forcing on the $N^2$ evolution, a simulation identical to that described in Section 2 was run, except the interaction between condensate and radiation was prohibited (as was described in \citeauthor{Buetal} \citeyear{Buetal} and \citeauthor{Fovelletal2016} \citeyear{Fovelletal2016}).
+The intensity evolution of this simulation (Fig.
+A1, blue line) compares well with that of the simulation described in Section 2 (Fig.
+A1, red line), except the storm without cloud-radiative forcing took longer to begin its RI period.
+Twenty-four-hour averages of $N^2$ reveal a similar overall evolution in the two simulations (compare Figs.
+\ref{fig:n2-24hr-avgs}, A2), except the lower-stratospheric $N^2$ maximum does not become as strong in the simulation without cloud-radiative forcing.
+The magnitude of the sum of the advection and turbulence terms immediately surrounding the tropopause in this simulation (Fig.
+A3e) is not as large as that in the full-radiation simulation (Fig.
+\ref{fig:stab-48-72}e).
+This suggests that radiative heating tendencies near the cloud top affect the radial--vertical circulation there, which then feeds back on to the advection and turbulence terms.
+The smaller turbulence and advective tendencies, combined with the near-zero radiative heating tendencies (Fig.
+A3d), leads to a smaller lower-stratospheric stabilization tendency (compare Figs.
+\ref{fig:stab-48-72}a, A3a).
+These results highlight the importance of cloud-radiative interaction in the evolution of the tropopause-layer $N^2$.
 
@@
 \centerline{\includegraphics[width=39pc]{h024-h048-adv.png}}
-\caption{The contributions to the change in $N^2$ over the 24-48-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 h)\textsuperscript{-1}) by (a) horizontal advection and (b) vertical advection.
+\caption{The contributions to the change in $N^2$ over the 24-48-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 h)\textsuperscript{-1}) by (a) horizontal advection term and (b) vertical advectionterm.
 (c) The radial velocity (m s\textsuperscript{-1}; filled contours), potential temperature (K; thick black contours), cold-point tropopause height (orange line), and level of maximum outflow (dashed cyan line) averaged over the 24-48-hour period.
@@
 
-%FIGURE 11%
-\begin{figure*}[ht]
-\centerline{\includegraphics[width=27pc]{run12+run13-vmax.png}}
-   \caption{Maximum 10-m wind speed (m s\textsuperscript{-1}) for (red) the simulation described in Section 2, and (blue) an identical simulation except condensate is not permitted to interact with radiation.}
-\label{fig:vmax-norad}
-\end{figure*}
-
-%FIGURE 12%
-\begin{figure*}[ht]
-\centerline{\includegraphics[width=39pc]{n2-norad.png}}
-   \caption{As in Fig. \ref{fig:n2-24hr-avgs}, but for the simulation in which radiation is not permitted to interact with condensate.}
-\label{fig:n2-norad}
-\end{figure*}
-
-%FIGURE 13%
-%\begin{figure*}[ht]
-%\centerline{\includegraphics[width=39pc]{adv-norad.png}}
-%   \caption{As in Fig. \ref{fig:adv-24-48}, but for the 48-72--hour period of the simulation in which radiation is not permitted to interact with condensate.}
-%\label{fig:adv-norad}
-%\end{figure*}
-
-%FIGURE 13%
-\begin{figure*}[ht]
-\centerline{\includegraphics[width=39pc]{budgetterms-norad.png}}
-   \caption{As in Fig. \ref{fig:stab-48-72}, but for the simulation in which radiation is not permitted to interact with condensate.}
-\label{fig:budgetterms-norad}
-\end{figure*}
-
-%FIGURE 14%
+%FIGURE 10%
 \begin{figure*}[ht]
@@
 
-%FIGURE 15%
+%FIGURE 11%
 \begin{figure}[ht]
@@
 
-%FIGURE 16%
+%FIGURE 12%
 \begin{figure}[ht]
@@
 \end{figure}
+
+%FIGURE 13%
+\begin{figure}[ht]
+\centerline{\includegraphics[width=39pc]{pv-24hr-avgs.png}}
+\caption{Potential vorticity (PVU; 1 PVU = 10\textsuperscript{-6} K kg\textsuperscript{-1} m\textsuperscript{2} s\textsuperscript{-1}) and cold-point tropopause height (orange lines) averaged over (a) 0-24 hours, (b) 24-48 hours, and (c) 48-72 hours.}
+\label{fig:pv}
+\end{figure}
+
+%FIGURE A1%
+\begin{figure*}[ht]
+\centerline{\includegraphics[width=27pc]{run12+run13-vmax.png}}
+   \appendcaption{A1}{Maximum 10-m wind speed (m s\textsuperscript{-1}) for (red) the simulation described in Section 2, and (blue) an identical simulation except condensate is not permitted to interact with radiation.}
+\label{fig:vmax-norad}
+\end{figure*}
+
+%FIGURE A2%
+\begin{figure*}[ht]
+\centerline{\includegraphics[width=39pc]{n2-norad.png}}
+   \appendcaption{A2}{As in Fig. \ref{fig:n2-24hr-avgs}, but for the simulation in which radiation is not permitted to interact with condensate.}
+\label{fig:n2-norad}
+\end{figure*}
+
+%FIGURE A3%
+%\begin{figure*}[ht]
+%\centerline{\includegraphics[width=39pc]{adv-norad.png}}
+%   \caption{As in Fig. \ref{fig:adv-24-48}, but for the 48-72--hour period of the simulation in which radiation is not permitted to interact with condensate.}
+%\label{fig:adv-norad}
+%\end{figure*}
+
+%FIGURE A3%
+\begin{figure*}[ht]
+\centerline{\includegraphics[width=39pc]{budgetterms-norad.png}}
+   \appendcaption{A3}{As in Fig. \ref{fig:stab-48-72}, but for the simulation in which radiation is not permitted to interact with condensate.}
+\label{fig:budgetterms-norad}
+\end{figure*}
 
